### 2016-12-02 paper.tex
first commit

%                                                                 aa.dem
% AA vers. 9.1, LaTeX class for Astronomy & Astrophysics
% demonstration file
%                                                       (c) EDP Sciences
%-----------------------------------------------------------------------
%
%\documentclass[referee]{aa} % for a referee version
%\documentclass[onecolumn]{aa} % for a paper on 1 column  
%\documentclass[longauth]{aa} % for the long lists of affiliations 
%\documentclass[letter]{aa} % for the letters 
%\documentclass[bibyear]{aa} % if the references are not structured 
%                              according to the author-year natbib style

%
\documentclass{aa}

%
\usepackage{graphicx}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts}
\usepackage{hyperref}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage[options]{hyperref}
% To add links in your PDF file, use the package "hyperref"
% with options according to your LaTeX or PDFLaTeX drivers.
%
\begin{document}

   \title{Magnetized Polish doughnuts}

%   \subtitle{}

   \author{Gimeno
          \inst{1}
          \and
          Font\inst{1,2}
          }

   \institute{DAA\\
              \email{wuchterl@amok.ast.univie.ac.at}
         \and
             OAUV \\
             \email{c.ptolemy@hipparch.uheaven.space}
             }

   \date{}

% \abstract{}{}{}{}{} 
% 5 {} token are mandatory

  \abstract
  % context heading (optional)
  % {} leave it empty if necessary  
   {}
  % aims heading (mandatory)
   {bla}
  % methods heading (mandatory)
   {bla}
  % results heading (mandatory)
   {bla}
  % conclusions heading (optional), leave it empty if necessary 
   {}

   \keywords{keywords here
               }

   \maketitle
%
%-------------------------------------------------------------------

\section{Introduction}

\citet{Qian:2009} presented a method to build sequences of black hole accretion disks in dynamical equilibria based on
assuming distributions of angular momentum in the disks. Building on this work, we present here the extension of those
models to disks endowed with a purely toroidal magnetic field. For the particular case of constant angular momentum
distributions our method shows good agreement with the results of~\citet{Komissarov:2006}.

In this paper, we consider that the space-time is described by the Kerr metric (test-fluid approximation). We use the geometrized units where $G = c = 1$ and the $(-+++)$ signature for the metric.

%--------------------------------------------------------------------
\section{Framework}

\subsection{Distribution of angular momentum}
First, we introduce the specific angular momentum $l$ and the angular velocity $\Omega$ by the standard definitions,
\begin{equation}
l = - \frac{u_{\phi}}{u_t}, \;\;\; \Omega = \frac{u^{\phi}}{u^t},
\end{equation}
where $u^{\mu}$ is the fluid four-velocity and $g_{\mu\nu}$ is the metric tensor\footnote{In Kerr-Schild coordinates. Although the use of the Boyer-Lindquist coordinates yields exactly the same mathematical derivation and results.}.

The relationship between $l$ and $\Omega$ is given by the equations
\begin{equation}
l = - \frac{\Omega g_{\phi\phi} + g_{t\phi}}{\Omega g_{t\phi} + g_{tt}}, \;\;\; \Omega = - \frac{l g_{tt} + g_{t\phi}}{l g_{t\phi} + g_{\phi\phi}},
\end{equation}
where we are assuming circular motion, i.e. the four-velocity can be written as
\begin{equation}
u^{\mu} = (u^t, 0, 0, u^{\phi}),
\end{equation}
we also introduce the Keplerian angular momentum (for prograde motion) in the equatorial plane $l_{\mathrm{K}}$. 
\begin{equation}\label{eq:kepler}
l_{\mathrm{K}}(r) = \frac{M^{1/2}(r^{2}-2aM^{1/2}r^{1/2}+a^{2})}{r^{3/2}-2Mr^{1/2}+aM^{1/2}},
\end{equation}
In \citet{Jaroszynski:1980} is argued that the slope of the specific angular momentum should be between two cases: $l = \mathrm{const.}$ and $\Omega = \mathrm{const.}$.

%simulaciones?

We assume the angular momentum distribution proposed by \citet{Qian:2009} 
\begin{equation}
l (r,\theta) = \left\{ \label{eq:ansatz} 
  \begin{array}{lr}
    l_0 \left(\frac{l_{\mathrm{K}}(r)}{l_0}\right)^{\beta}\sin^{2\gamma}{\theta} &  \text{for } r \geq r_{\mathrm{ms}}\\
    l_{\mathrm{ms}}(r)\sin^{2\gamma}{\theta} & \text{for } r < r_{\mathrm{ms}}
  \end{array}
\right\}.
\end{equation}
where $r_{\mathrm{ms}}$ is the radius of the marginally stable circular orbit(INTRODUCIR RMS, RMB Y CUSP ANTES. Introduccion?), the constants $l_0$ and $l_{\mathrm{ms}}(r)$ are defined by $l_0 \equiv \eta l_{\mathrm{K}}(r_{\mathrm{ms}})$ and $l_{\mathrm{ms}}(r) \equiv l_0 [l_{\mathrm{K}}(r_{\mathrm{ms}})/l_0]^{\beta}$. It can be seen that the model for the distribution of angular momentum has three parameters $(\beta, \gamma, \eta)$
\begin{equation}
0 \leq \beta \leq 1, \quad -1 \leq \gamma \leq 1, \quad 1 \leq \eta \leq \eta_{\mathrm{max}},
\end{equation}
with $\eta_{\mathrm{max}} = l_{\mathrm{K}}(r_{\mathrm{mb}})/l_{\mathrm{K}}(r_{\mathrm{ms}})$. In this paper we chose $\eta = \eta_{\mathrm{max}}$, then we can write $l_0$ as $l_0 = l_{\mathrm{K}}(r_{\mathrm{mb}})$. We take this choice because (l comprendido entre lms y lmb para los valores de beta. Discos que comienzan en el cusp no tienen borde exterior para l = lmb.)

\subsection{Magnetized disks}

The equations of ideal GRMHD are
\begin{equation}\label{eq:e-m_cons}
\nabla_{\mu} T^{\mu\nu} = 0,
\end{equation}
\begin{equation}\label{eq:cons_faraday}
\nabla_{\mu} \ast F^{\mu\nu} = 0,
\end{equation}
\begin{equation}\label{eq:continuity}
\nabla_{\mu} (\rho u^{\mu}) = 0,
\end{equation}
where
\begin{equation}\label{eq:e-m_tensor}
T^{\mu\nu} = (w + b^2)u^{\mu}u^{\nu} + \left(p + \frac{1}{2}b^2\right)g^{\mu\nu} - b^{\mu}b^{\nu},
\end{equation}
is the energy-momentum tensor taking into account only the fluid and the Maxwell parts, $w$ and $p$ are the fluid enthalpy and pressure, respectively. And
\begin{equation}
\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu},
\end{equation}
is the Faraday tensor relative to an observer with four-velocity $u^{\mu}$ and $b^{\mu}$ is the magnetic field in that frame.
Assuming the magnetic field is purely azimuthal
\begin{equation}
b^r = b^{\theta} = 0,
\end{equation}
and taking into account that the flow is stationary and axisymmetric, we can see that \eqref{eq:continuity} is always satisfied. The same happens with \eqref{eq:cons_faraday}. Contracting the equation \eqref{eq:e-m_tensor} with the projection tensor $h^{\alpha}_{\beta} = \delta^{\alpha}_{\beta} + u^{\alpha}u_{\beta}$, we arrive at
\begin{equation}
(w + b^2)u_{\nu}\partial_i u^{\nu} + \partial_i\left(p + \frac{b^2}{2}\right) - b_{\nu}\partial_i b^{\nu},
\end{equation}
where the comma denotes partial derivatives and $i = r, \theta$. We can rewrite this equation in terms of the specific angular momentum $l$ and the angular velocity $\Omega$, to obtain

\begin{equation}\label{eq:diff_ver}
\partial_i(\ln u_t|) - \frac{\Omega \partial_i l}{1-l\Omega} + \frac{\partial_i p}{w} + \frac{\partial_i(\mathcal{L}b^2)}{2\mathcal{L}w} = 0,
\end{equation}
where 
\begin{equation}
\mathcal{L} = g_{t\phi}^2 - g_{tt}g_{\phi\phi}.
\end{equation}
To integrate the equation \eqref{eq:diff_ver} first we assume a barotropic equation of state $w = w(p)$ of the form
\begin{equation}\label{eq:eos_fluid}
p = K w^{\kappa},
\end{equation}
with $K$ and $\kappa$ constants.

Then, we define the magnetic pressure as $p_{\mathrm{m}} = b^2/2$. Also, we can define $\tilde{p}_{\mathrm{m}} = \mathcal{L} p_{\mathrm{m}}$ and $\tilde{w} = \mathcal{L} w$, so we can write an analogue of \eqref{eq:eos_fluid} for $\tilde{p}_{\mathrm{m}}$
\begin{equation}\label{eq:eos_mag_tilde}
\tilde{p}_{\mathrm{m}} = K_{\mathrm{m}} \tilde{w}_{\mathrm{m}}^{\eta},
\end{equation}
or, in terms of the magnetic pressure $p_{\mathrm{m}}$
\begin{equation}\label{eq:eos_mag}
p_{\mathrm{m}} = K_{\mathrm{m}} \mathcal{L}^{\eta-1} w^{\eta},
\end{equation}
where $K_{\mathrm{m}}$ and $\eta$ are constants.

This particular choice of relationships $w = w(p)$ and $\tilde{w} = \tilde{w}(\tilde{p}_{\mathrm{m}})$, fulfill the general relativistic version for a toroidal magnetic field of the von Zeipel theorem \citep{vonZeipel1924, Zanotti2015}, that means the surfaces of $\Omega$ and $l$ constant coincide.

We can rewrite equation \eqref{eq:diff_ver} and integrate it to give
\begin{equation}\label{eq:pre_full_int}
\ln |u_t| - \int^l_0 \frac{\Omega \mathrm{d}l}{1 - \Omega l} + \int^p_0 \frac{\mathrm{d}p}{w} + \int^{\tilde{p}_{\mathrm{m}}} \frac{\mathrm{d}\tilde{p}_{\mathrm{m}}}{\tilde{w}} = \mathrm{constant}.
\end{equation}
On the surface of the disk, and particularly on its inner edge,
\begin{equation}
p = \tilde{p}_{\mathrm{m}} = 0, \;\;\; u_t = u_{t, \mathrm{in}}, \;\;\; l = l_{\mathrm{in}}
\end{equation}
then, the constant of integration is given by
\begin{equation}
\mathrm{constant.} = \ln |u_t| - \int^l_{\mathrm{in}} \frac{\Omega \mathrm{d}l}{1 - \Omega l}.
\end{equation}
Defining the total potential $W$ \citet{Abramowicz:1978}, we can write
\begin{equation}\label{eq:potential}
W - W_{\mathrm{in}} = \ln|u_t| - \ln|u_{t,\mathrm{in}}| - \int^{l}_{l_{\mathrm{in}}} \frac{\Omega \mathrm{d}l}{1 - \Omega l},
\end{equation}
where $W_{\mathrm{in}}$ is the potential on the inner edge of the disk. With this definition, we can write \eqref{eq:pre_full_int} as
\begin{equation}\label{eq:full_int}
W - W_{\mathrm{in}} = \int^p_0 \frac{\mathrm{d}p}{w} + \int^{\tilde{p}_{\mathrm{m}}} \frac{\mathrm{d}\tilde{p}_{\mathrm{m}}}{\tilde{w}},
\end{equation}
and
\begin{equation}\label{eq:pre_enthalpy_eq}
W - W_{\rm{in}} + \frac{\kappa}{\kappa - 1}\frac{p}{w} + \frac{\eta}{\eta - 1}\frac{p_{\mathrm{m}}}{w} = 0,
\end{equation}
and then, replacing $p$ and $p_{\mathrm{m}}$ by equations \eqref{eq:eos_fluid} and \eqref{eq:eos_mag},
\begin{equation}\label{eq:enthalpy_eq}
W - W_{\rm{in}} + \frac{\kappa}{\kappa - 1} K w^{\kappa - 1} + \frac{\eta}{\eta - 1}K_{\mathrm{m}}(\mathcal{L} w)^{\eta - 1} = 0,
\end{equation}
which relates the distribution of potential with the distribution of enthalpy.

%--------------------------------------------------------------------
\section{Methodology}

\subsection{Building the disk}

To construct the disks we follow the procedure described below:

First, we find the location of $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$ as the solutions to the equation $l(r) - l_{\mathrm{K}} = 0$.
Next, we write the partial derivatives of the potential \eqref{eq:potential}
\begin{equation}\label{eq:radial_der_pot}
\partial_r W = \partial_r \ln|u_t| - \frac{\Omega \partial_rl}{1 - \Omega l},
\end{equation}
and
\begin{equation}\label{eq:polar_der_pot}
\partial_{\theta} W = \partial_{\theta} \ln|u_t| - \frac{\Omega \partial_{\theta}l}{1 - \Omega l}.
\end{equation}
Then, we integrate the radial partial derivative of the potential along the segment $[r_{\mathrm{cusp}}, r_{\mathrm{c}}]$ (assuming $W_{\mathrm{cusp}} = 0$) at the equatorial plane, thus obtaining the equatorial distribution of potential between $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$
\begin{equation}\label{eq:equatorial_pot}
W_{\mathrm{eq}}(r) = \int^{r}_{r_{\mathrm{cusp}}}\left(\partial_r \ln|u_t| - \frac{\Omega \partial_rl}{1 - \Omega l}\right).
\end{equation}
We can divide the equations \eqref{eq:radial_der_pot} and \eqref{eq:polar_der_pot} \citep{Qian:2009} to get
\begin{equation}\label{eq:F}
F(r, \theta) = -\frac{\partial_r W}{\partial_{\theta} W} = \frac{\mathrm{d}\theta}{\mathrm{d}r}.
\end{equation}
which is an ordinary differential equation that can be integrated to obtain the location of the equipotential surfaces.

Next, we choose all the initial values for the integration of the equation \eqref{eq:F} to be between $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$ ($\theta = \pi / 2$). Since we are only interested in the surfaces inside the Roche lobe, our choice of initial values provides us a mapping of the equipotential surfaces of the torus. Given that we have already obtained both the equipotential surfaces which cross the segment $[r_{\mathrm{cusp}}, r_{\mathrm{c}}]$ and the potential distribution there, we found the potential distribution for the torus.
Once we have the potential distribution, we can find the gas pressure at the center, from equation \eqref{eq:enthalpy_eq}
\begin{equation}
p_{\mathrm{c}} = w_{\mathrm{c}}(W_{\mathrm{in}} - W_{\mathrm{c}})\left(\frac{\kappa}{\kappa - 1} + \frac{\eta}{\eta - 1}\frac{1}{\beta_c}\right)^{-1},
\end{equation}

\subsection{Numerical code}

- Description of the numerical construction.

\subsection{Parameter space}

Parameters $\beta$, $\gamma$, $\eta$, $\beta_{\rm{mag}}$, $\kappa$, $\eta$, $r_{\rm{in}}$ and $a$. We do not vary $\kappa$ and $\eta$. And take $\eta = \eta_{max}$ for each value of $a$

%--------------------------------------------------------------------
\section{Results}

\begin{figure*}
\centering
\includegraphics[scale=0.4]{1.pdf}
\includegraphics[scale=0.4]{2.pdf}
\caption{Adiabatic exponent $\Gamma_1$.
            $\Gamma_1$ is plotted as a function of
            $\lg$ internal energy $\mathrm{[erg\,g^{-1}]}$ and $\lg$
            density $\mathrm{[g\,cm^{-3}]}$.}
           \label{FigGam}%
 \end{figure*}

%--------------------------------------------------------------------
\section{Conclusions}

%-------------------------------------- Two column figure (place early!)
%   \begin{figure*}
%   \centering
%   %%%\includegraphics{empty.eps}
%   %%%\includegraphics{empty.eps}
%   %%%\includegraphics{empty.eps}
%   \caption{Adiabatic exponent $\Gamma_1$.
%               $\Gamma_1$ is plotted as a function of
%               $\lg$ internal energy $\mathrm{[erg\,g^{-1}]}$ and $\lg$
%               density $\mathrm{[g\,cm^{-3}]}$.}
%              \label{FigGam}%
%    \end{figure*}
%

%--------------------------------------------------- One column table
%   \begin{table}
%      \caption[]{Opacity sources.}
%         \label{KapSou}
%     $$ 
%         \begin{array}{p{0.5\linewidth}l}
%            \hline
%            \noalign{\smallskip}
%            Source      &  T / {[\mathrm{K}]} \\
%            \noalign{\smallskip}
%            \hline
%            \noalign{\smallskip}
%            Yorke 1979, Yorke 1980a & \leq 1700^{\mathrm{a}}     \\
%%           Yorke 1979, Yorke 1980a & \leq 1700             \\
%            Kr\"ugel 1971           & 1700 \leq T \leq 5000 \\
%            Cox \& Stewart 1969     & 5000 \leq             \\
%            \noalign{\smallskip}
%            \hline
%         \end{array}
%     $$ 
%   \end{table}
%

\begin{acknowledgements}
      Bla, bla, bla.
\end{acknowledgements}

% WARNING
%-------------------------------------------------------------------
% Please note that we have included the references to the file aa.dem in
% order to compile it, but we ask you to:
%
% - use BibTeX with the regular commands:
%   \bibliographystyle{aa} % style aa.bst
%   \bibliography{references.bib} % your references Yourfile.bib
%
% - join the .bib files when you upload your source files
%-------------------------------------------------------------------

\bibliographystyle{bibtex/aa}
\bibliography{references}

\end{document}

### 2016-12-02 paper.tex
commit 1

@@
 \end{equation}
-where $r_{\mathrm{ms}}$ is the radius of the marginally stable circular orbit(INTRODUCIR RMS, RMB Y CUSP ANTES.
-Introduccion?), the constants $l_0$ and $l_{\mathrm{ms}}(r)$ are defined by $l_0 \equiv \eta l_{\mathrm{K}}(r_{\mathrm{ms}})$ and $l_{\mathrm{ms}}(r) \equiv l_0 [l_{\mathrm{K}}(r_{\mathrm{ms}})/l_0]^{\beta}$.
+where $r_{\mathrm{ms}}$ is the radius of the marginally stable circular orbit [Creo que seria mejor introducir el cusp, rmb y rms en la introduccion de alguna forma...], the constants $l_0$ and $l_{\mathrm{ms}}(r)$ are defined by $l_0 \equiv \eta l_{\mathrm{K}}(r_{\mathrm{ms}})$ and $l_{\mathrm{ms}}(r) \equiv l_0 [l_{\mathrm{K}}(r_{\mathrm{ms}})/l_0]^{\beta}$.
 It can be seen that the model for the distribution of angular momentum has three parameters $(\beta, \gamma, \eta)$
@@
 In this paper we chose $\eta = \eta_{\mathrm{max}}$, then we can write $l_0$ as $l_0 = l_{\mathrm{K}}(r_{\mathrm{mb}})$.
-We take this choice because (l comprendido entre lms y lmb para los valores de beta.
-Discos que comienzan en el cusp no tienen borde exterior para l = lmb.)
+We take this choice because [explicar que esta eleccion hace que el momento angular esté comprendido entre lmb y lms para variaciones de beta entre 0 y 1.
+Además los discos de momento angular constante que empiezan en el cusp, no tienen borde externo para l = lmb]
 
@@
 
-This particular choice of relationships $w = w(p)$ and $\tilde{w} = \tilde{w}(\tilde{p}_{\mathrm{m}})$, fulfill the general relativistic version for a toroidal magnetic field of the von Zeipel theorem \citep{vonZeipel1924, Zanotti2015}, that means the surfaces of $\Omega$ and $l$ constant coincide.
+This particular choice of relationships $w = w(p)$ and $\tilde{w} = \tilde{w}(\tilde{p}_{\mathrm{m}})$, fulfill the general relativistic version for a toroidal magnetic field of the von Zeipel theorem \citep{vonZeipel:1924, Zanotti:2015}, that means the surfaces of $\Omega$ and $l$ constant coincide.
 
@@
 which relates the distribution of potential with the distribution of enthalpy.
+
+Finally, we assume a polytropic equation of state given by
+\begin{equation}\label{eq:density_eq}
+p = K \rho^{\kappa}
+\end{equation}
+where $\rho$ is the fluid density.
 
@@
 \begin{equation}
-p_{\mathrm{c}} = w_{\mathrm{c}}(W_{\mathrm{in}} - W_{\mathrm{c}})\left(\frac{\kappa}{\kappa - 1} + \frac{\eta}{\eta - 1}\frac{1}{\beta_c}\right)^{-1},
+p_{\mathrm{c}} = w_{\mathrm{c}}(W_{\mathrm{in}} - W_{\mathrm{c}})\left(\frac{\kappa}{\kappa - 1} + \frac{\eta}{\eta - 1}\frac{1}{\beta_{\mathrm{c}}}\right)^{-1},
 \end{equation}
+where $w_{\mathrm{m}}$ is the enthalpy at the disk center and
+\begin{equation}\label{eq:beta_eq}
+\beta = p/p_{\mathrm{m}},
+\end{equation}
+is the magnetization parameter (being $\beta_{\mathrm{m}}$ the magnetization parameter at the disk center). By this definition, we can find the magnetic pressure at the disk center,
+\begin{equation}
+p_{\mathrm{m_{\mathrm{c}}}} = p_{\mathrm{c}}/\beta_{\mathrm{c}}
+\end{equation}
+With the pressures at the center, we can also find the constants $K$ and $K_{\mathrm{m}}$ using the equations \eqref{eq:eos_fluid} and \eqref{eq:eos_mag}.
+And, for a given inner radius of the disk $r_{\mathrm{in}}$ we can find the potential $W_{\mathrm{in}}$.
+We now have all the elements required to find the enthalpy distribution (equation \eqref{eq:enthalpy_eq}), the pressure and magnetic pressure distribution (equations \eqref{eq:eos_fluid} and \eqref{eq:eos_mag}), and the density (equation \eqref{eq:density_eq}).
 
@@
 
-- Description of the numerical construction.
+For the integration of equation \eqref{eq:equatorial_pot} we use the composite Simpson's rule, it is important to use a very small step of integration, because the slope is very steep.
+In this work, we use a step $h = 10^{-6}$ [tengo que revisar esto en el codigo].
+A bigger step gives an unacceptable lack of accuracy, we tested that fact by comparison with the analytic, constant angular momentum case.
+
+To integrate the ordinary differential equation \eqref{eq:F} we use the RK4 method.
+Here is also important to choose a suitable step of integration, specially at the outer end of the disk, this is because the equation \eqref{eq:F} diverges of the equatorial plane (the equipotential surfaces crosses the equatorial plane perpendicularly).
 
@@
 
-Parameters $\beta$, $\gamma$, $\eta$, $\beta_{\rm{mag}}$, $\kappa$, $\eta$, $r_{\rm{in}}$ and $a$. We do not vary $\kappa$ and $\eta$. And take $\eta = \eta_{max}$ for each value of $a$
+As in \citet{Komissarov:2006}, in this paper we have chosen the exponents $\kappa = \eta = 4/3$ and the enthalpy at the disk center $w_{\mathrm{c}} = 0$.
+That leaves us the magnetization parameter $\beta$, the parameters of the angular momentum distribution $\beta$ and $\gamma$, the BH spin parameter $a$ and the inner radius of the disk $r_{\mathrm{in}}$.
+This allows us to control the size, shape, thickness and magnetization of the disk.
 
@@
 \centering
-\includegraphics[scale=0.4]{1.pdf}
-\includegraphics[scale=0.4]{2.pdf}
-\caption{Adiabatic exponent $\Gamma_1$.
-            $\Gamma_1$ is plotted as a function of
-            $\lg$ internal energy $\mathrm{[erg\,g^{-1}]}$ and $\lg$
-            density $\mathrm{[g\,cm^{-3}]}$.}
+\includegraphics[scale=0.4]{images/1.pdf}
+\includegraphics[scale=0.4]{images/2.pdf}
+\caption{density plots}
            \label{FigGam}%

### 2017-01-16 paper.tex
--
Some work on the draft

@@
 %
+
 \begin{document}
 
-   \title{Magnetized Polish doughnuts}
+\title{Magnetized Polish doughnuts revisited}
 
@@
 
-   \author{Gimeno
-          \inst{1}
+   \author{Sergio Gimeno\inst{1}   \and Jos\'e A.~Font\inst{1,2} }
+
+   \institute{Departamento de Astronom\'{\i}a y Astrof\'{\i}sica, Universitat de Val\`encia, Dr. Moliner 50, 46100, Burjassot (Val\`encia), Spain.\\
+              \email{sergiso@alumni.uv.es}
          \and
-          Font\inst{1,2}
-          }
-
-   \institute{DAA\\
-              \email{wuchterl@amok.ast.univie.ac.at}
-         \and
-             OAUV \\
-             \email{c.ptolemy@hipparch.uheaven.space}
+             Observatori Astron\`omic, Universitat de Val\`encia, C/ Catedr\'atico Jos\'e Beltr\'an 2, 46980, Paterna (Val\`encia), Spain. \\
+             \email{j.antonio.font@uv.es}
              }
@@
 
-   \keywords{keywords here
-               }
+   \keywords{keywords here}
 
    \maketitle
-%
-%-------------------------------------------------------------------
 
+%%%%%%%%%%%
 \section{Introduction}
+%%%%%%%%%%%
 
-\citet{Qian:2009} presented a method to build sequences of black hole accretion disks in dynamical equilibria based on
-assuming distributions of angular momentum in the disks. Building on this work, we present here the extension of those
-models to disks endowed with a purely toroidal magnetic field. For the particular case of constant angular momentum
-distributions our method shows good agreement with the results of~\citet{Komissarov:2006}.
+% From Qian et al: 
+% We construct a new family of analytic models of black hole accretion disks in dynamical equilibria. 
+% Our construction is based on assuming distributions of angular momentum and entropy. For a 
+% particular choice of the distribution of angular momentum, we calculate the shapes of equipressure 
+% surfaces. The equipressure surfaces we find are similar to those in thick, slim and thin disks, and
+% to those in ADAFs.
+% Models of tori described here may be useful not only for accretion
+% disks but also for tori that formin the latest stages of neutron
+% star binary mergers. This is relevant for gamma ray bursts (Witt
+% et al. 1994) and gravitational waves (Baiotti et al. 2008).
 
-In this paper, we consider that the space-time is described by the Kerr metric (test-fluid approximation). We use the geometrized units where $G = c = 1$ and the $(-+++)$ signature for the metric.
+% From Komissarov:
+% The dynamics of accretion discs around galactic and extragalactic black holes may be influenced
+% by their magnetic field. In this paper, we generalize the fully relativistic theory of
+% stationary axisymmetric tori in Kerr metric of Abramowicz, Jaroszynski&Sikora by including
+% strong toroidal magnetic field and construct analytic solutions for barotropic tori with constant
+% angular momentum. This development is particularly important for the general relativistic
+% computational magnetohydrodynamics that suffers from the lack of exact analytic solutions
+% that are needed to test computer codes.
 
-%--------------------------------------------------------------------
+Matter accretion on to a black hole is the most efficient form of energy production known in nature. The conversion of the
+gravitational energy of the infalling matter into heat and radiation may reach efficiencies
+of about 43\% in the case of rotating (Kerr) black holes. For this reason, systems formed 
+by a black hole surrounded by an accretion disk are deemed responsible for many of the most energetic astronomical phenomena observed in the cosmos.
+In particular, (geometrically) thick accretion disks are believed to be present in quasars and other active galactic nuclei, some 
+X-ray binaries and microquasars, as well as in the central engine of gamma-ray bursts.
+
+The investigation of such systems, either by analytical or numerical means, may rely on the ability to construct suitable 
+representations based on physical assumptions.
+The construction of equilibrium models of stationary disks around black holes has a long tradition (see~\cite{Abramowicz:2013} and references therein).
+In particular, the so-called ``Polish doughnuts", developed by Paczy\'nski and collaborators~\citep{Abramowicz:1978}, provides a  very general method to build equilibrium configurations of perfect fluid matter
+ orbiting around a Kerr black hole.
+This fully relativistic model assumes that the disk is non-magnetized and that the matter obeys a  constant specific angular momentum distribution.
+\cite{Komissarov:2006} extended this method by adding a purely azimuthal magnetic
+ field to build magnetized tori around rotating black holes.
+Assuming different distributions of angular momentum in the disks, \citet{Qian:2009} presented a method to build sequences of black hole thick accretion disks in dynamical equilibria, restricted to the purely hydrodynamical case.
+Building on this work, we discuss here the extension of the
+models of~\citet{Qian:2009} to disks endowed with a purely toroidal magnetic field.
+For the particular case of constant angular momentum distributions our method shows good agreement with the results of~\citet{Komissarov:2006}.
+
+The organization of the paper is as follows:
+We assume that the test-fluid approximation holds, neglecting the self-gravity of the fluid, and assume that the space-time is described by the Kerr metric. We use geometrized units where $G = c = 1$.
+
+%%%%%%%%%%%
 \section{Framework}
+%%%%%%%%%%%
 
+Equilibrium tori around Kerr black holes are built assuming that the spacetime gravitational potentials and the fluid fields are stationary and axisymmetric.
+In all the derivations presented below, the Kerr metric is implicitely written using standard Boyer-Lindquist coordinates.
+It is convenient to introduce a number of relevant characteristic radii, such as the radius
+of the marginally stable circular orbit, $r_{\rm ms}$, and the radius of the marginally bound circular orbit, $r_{\rm mb}$, given by
+\begin{eqnarray}
+r_{\rm ms} &=& M\,\left(3+Z_2-\left[(3-Z_1)(3+Z_1+2Z_2)\right]^{1/2})\right)\,,
+\\
+r_{\rm mb} &=& 2M\,\left(  1-\frac{a_*}{2} + \sqrt{1-a_*} \right)\,,
+\end{eqnarray}
+where $Z_1=1+(1-a_*^2)^{1/3}[(1+a_*)^{1/3}+(1-a_*)^{1/3}]$, $Z_2=(3a_*^2+Z_1^2)^{1/2}$, and $a_*=a/M$, with $a$ and $M$ being the spin Kerr parameter and the black hole mass.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Distribution of angular momentum}
-First, we introduce the specific angular momentum $l$ and the angular velocity $\Omega$ by the standard definitions,
+%%%%%%%%%%%%%%%%%%%%%%%%
+
+We introduce the specific angular momentum $l$ and the angular velocity $\Omega$ employing the standard definitions,
 \begin{equation}
@@
 \end{equation}
-where $u^{\mu}$ is the fluid four-velocity and $g_{\mu\nu}$ is the metric tensor\footnote{In Kerr-Schild coordinates.
-Although the use of the Boyer-Lindquist coordinates yields exactly the same mathematical derivation and results.}.
-
+where $u^{\mu}$ is the fluid four-velocity.
+%
+%\footnote{In Kerr-Schild coordinates. Although the use of the Boyer-Lindquist coordinates yields exactly the same mathematical derivation and results.}.
+%
 The relationship between $l$ and $\Omega$ is given by the equations
@@
 \end{equation}
-where we are assuming circular motion, i.e. the four-velocity can be written as
+where $g_{\mu\nu}$ is the metric tensor and we are assuming circular motion, i.e. the four-velocity can be written as
 \begin{equation}
-u^{\mu} = (u^t, 0, 0, u^{\phi}),
+u^{\mu} = (u^t, 0, 0, u^{\phi})\,.
 \end{equation}
-we also introduce the Keplerian angular momentum (for prograde motion) in the equatorial plane $l_{\mathrm{K}}$. 
+We also introduce the Keplerian angular momentum (for prograde motion) in the equatorial plane $l_{\mathrm{K}}$. 
 \begin{equation}\label{eq:kepler}
-l_{\mathrm{K}}(r) = \frac{M^{1/2}(r^{2}-2aM^{1/2}r^{1/2}+a^{2})}{r^{3/2}-2Mr^{1/2}+aM^{1/2}},
+l_{\mathrm{K}}(r) = \frac{M^{1/2}(r^{2}-2aM^{1/2}r^{1/2}+a^{2})}{r^{3/2}-2Mr^{1/2}+aM^{1/2}}\,.
 \end{equation}
-In \citet{Jaroszynski:1980} is argued that the slope of the specific angular momentum should be between two cases: $l = \mathrm{const.}$ and $\Omega = \mathrm{const.}$.
 
-%simulaciones?
-
-We assume the angular momentum distribution proposed by \citet{Qian:2009} 
+\cite{Jaroszynski:1980} argued that the slope of the specific angular momentum should range between two cases, $l = \mathrm{const.}$ and $\Omega = \mathrm{const}$.
+Following \citet{Qian:2009} we assume an angular momentum distribution ansatz given by
 \begin{equation}
@@
   \end{array}
-\right\}.
+\right.
 \end{equation}
-where $r_{\mathrm{ms}}$ is the radius of the marginally stable circular orbit [Creo que seria mejor introducir el cusp, rmb y rms en la introduccion de alguna forma...], the constants $l_0$ and $l_{\mathrm{ms}}(r)$ are defined by $l_0 \equiv \eta l_{\mathrm{K}}(r_{\mathrm{ms}})$ and $l_{\mathrm{ms}}(r) \equiv l_0 [l_{\mathrm{K}}(r_{\mathrm{ms}})/l_0]^{\beta}$.
-It can be seen that the model for the distribution of angular momentum has three parameters $(\beta, \gamma, \eta)$
+where constants $l_0$ and $l_{\mathrm{ms}}(r)$ are defined by $l_0 \equiv \eta l_{\mathrm{K}}(r_{\mathrm{ms}})$ and $l_{\mathrm{ms}}(r) \equiv l_0 [l_{\mathrm{K}}(r_{\mathrm{ms}})/l_0]^{\beta}$.
+Therefore, the model for the distribution of angular momentum has three parameters $(\beta, \gamma, \eta)$, whose range of variation is given by~\citep{Qian:2009}
 \begin{equation}
@@
 with $\eta_{\mathrm{max}} = l_{\mathrm{K}}(r_{\mathrm{mb}})/l_{\mathrm{K}}(r_{\mathrm{ms}})$.
-In this paper we chose $\eta = \eta_{\mathrm{max}}$, then we can write $l_0$ as $l_0 = l_{\mathrm{K}}(r_{\mathrm{mb}})$.
+In this paper we choose $\eta = \eta_{\mathrm{max}}$, then we can write $l_0$ as $l_0 = l_{\mathrm{K}}(r_{\mathrm{mb}})$.
 We take this choice because [explicar que esta eleccion hace que el momento angular esté comprendido entre lmb y lms para variaciones de beta entre 0 y 1.
@@
 
+%%%%%%%%%%%%%%%%
 \subsection{Magnetized disks}
+%%%%%%%%%%%%%%%%
 
-The equations of ideal GRMHD are
-\begin{equation}\label{eq:e-m_cons}
-\nabla_{\mu} T^{\mu\nu} = 0,
-\end{equation}
-\begin{equation}\label{eq:cons_faraday}
-\nabla_{\mu} \ast F^{\mu\nu} = 0,
-\end{equation}
-\begin{equation}\label{eq:continuity}
-\nabla_{\mu} (\rho u^{\mu}) = 0,
-\end{equation}
-where
+The equations of ideal general relativistic MHD are $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and 
+$\nabla_{\mu} (\rho u^{\mu}) = 0$, 
+%\begin{equation}\label{eq:e-m_cons}
+%\nabla_{\mu} T^{\mu\nu} = 0,
+%\end{equation}
+%\begin{equation}\label{eq:cons_faraday}
+%\nabla_{\mu} \ast F^{\mu\nu} = 0,
+%\end{equation}
+%\begin{equation}\label{eq:continuity}
+%\nabla_{\mu} (\rho u^{\mu}) = 0,
+%\end{equation}
+where $\nabla_{\mu}$ is the covariant derivative and
 \begin{equation}\label{eq:e-m_tensor}
@@
 \end{equation}
-is the energy-momentum tensor taking into account only the fluid and the Maxwell parts, $w$ and $p$ are the fluid enthalpy and pressure, respectively. And
-\begin{equation}
-\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu},
-\end{equation}
-is the Faraday tensor relative to an observer with four-velocity $u^{\mu}$ and $b^{\mu}$ is the magnetic field in that frame.
-Assuming the magnetic field is purely azimuthal
-\begin{equation}
-b^r = b^{\theta} = 0,
-\end{equation}
-and taking into account that the flow is stationary and axisymmetric, we can see that \eqref{eq:continuity} is always satisfied.
-The same happens with \eqref{eq:cons_faraday}.
-Contracting the equation \eqref{eq:e-m_tensor} with the projection tensor $h^{\alpha}_{\beta} = \delta^{\alpha}_{\beta} + u^{\alpha}u_{\beta}$, we arrive at
+is the energy-momentum tensor of a magnetized perfect fluid, $w$ and $p$ being the fluid enthalpy and pressure, respectively. 
+Moreover,
+%\begin{equation}
+$^\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu}$
+%\end{equation}
+is the (dual of the) Faraday tensor relative to an observer with four-velocity $u^{\mu}$, and $b^{\mu}$ is the magnetic field in that frame.
+Assuming the magnetic field is purely azimuthal, i.e.~$b^r = b^{\theta} = 0$,
+and taking into account that the flow is stationary and axisymmetric, the conservation of the current density and of the Faraday tensor follow.
+Contracting Eq.~\eqref{eq:e-m_tensor} with the projection tensor $h^{\alpha}_{\beta} = \delta^{\alpha}_{\beta} + u^{\alpha}u_{\beta}$, we arrive at
 \begin{equation}
@@
 \end{equation}
-where the comma denotes partial derivatives and $i = r, \theta$. We can rewrite this equation in terms of the specific angular momentum $l$ and the angular velocity $\Omega$, to obtain
-
+where $i = r, \theta$. We can rewrite this equation in terms of the specific angular momentum $l$ and the angular velocity $\Omega$, to obtain
 \begin{equation}\label{eq:diff_ver}
@@
 \end{equation}
-To integrate the equation \eqref{eq:diff_ver} first we assume a barotropic equation of state $w = w(p)$ of the form
+To integrate Eq.~\eqref{eq:diff_ver} we first assume a barotropic equation of state $w = w(p)$ of the form
 \begin{equation}\label{eq:eos_fluid}
@@
 For the integration of equation \eqref{eq:equatorial_pot} we use the composite Simpson's rule, it is important to use a very small step of integration, because the slope is very steep.
-In this work, we use a step $h = 10^{-6}$ [tengo que revisar esto en el codigo].
+In this work, we use a step $h = 10^{-6}$ .
 A bigger step gives an unacceptable lack of accuracy, we tested that fact by comparison with the analytic, constant angular momentum case.
@@
 \includegraphics[scale=0.4]{images/2.pdf}
-\caption{density plots}
+\caption{test density plots}
            \label{FigGam}%
  \end{figure*}
+
+\begin{table*}
+\caption{test two column table}             
+\label{table:1}      
+\centering          
+\begin{tabular}{c c c c c c c c c c}
+\hline\hline
+
+Modelo & $\beta$ & $\gamma$ & $\beta_{\mathrm{c}}$ & $\Delta W$ & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ & $r_{p_{\rm{max}}}$ & $r_{p_{\mathrm{mag, max}}}$ & $p_{\mathrm{max}}$\\ 
+\hline                    
+  B-7 & $0.5$ & $0.5$ & $10^{3}$ & $-7.29 \times 10^{-2}$ & $1.27$ & $2.50$ & $1.971$ & $2.086$ & $1.83 \times 10^{-2}$\\ 
+  B-8 & $0.5$ & $0.5$ & $10^{2}$ & $-7.29 \times 10^{-2}$ & $1.27$ & $2.50$ & $1.971$ & $2.076$ & $1.82 \times 10^{-2}$\\ 
+  B-9 & $0.5$ & $0.5$ & $1$ & $-7.29 \times 10^{-2}$ & $1.27$ & $2.50$ & $1.931$ & $2.047$ & $1.68 \times 10^{-2}$\\ 
+  B-10 & $0.5$ & $0.5$ & $1$ & $-7.29 \times 10^{-2}$ & $1.27$ & $2.50$ & $1.761$ & $1.861$ & $1.10 \times 10^{-2}$\\ 
+  B-11 & $0.5$ & $0.5$ & $10^{-1}$ & $-7.29 \times 10^{-2}$ & $1.27$ & $2.50$ & $1.641$ & $1.701$ & $2.95 \times 10^{-3}$\\ 
+  B-12 & $0.5$ & $0.5$ & $10^{-2}$ & $-7.29 \times 10^{-2}$ & $1.27$ & $2.50$ & $1.621$ & $1.681$ & $3.59 \times 10^{-4}$\\ 
+  B-13 & $0.5$ & $0.5$ & $10^{-3}$ & $-7.29 \times 10^{-2}$ & $1.27$ & $2.50$ & $1.611$ & $1.671$ & $3.67 \times 10^{-5}$\\ 
+\hline                  
+\end{tabular}
+\end{table*}
 
@@
 \begin{acknowledgements}
-      Bla, bla, bla.
+      Work supported by the Spanish MINECO (grants AYA2013-40979-P and AYA2015-66899-C2-1-P) and the Generalitat Valenciana (PROMETEOII-2014-069).
 \end{acknowledgements}

### 2017-01-17 paper.tex
Some more work on the draft

@@
 The construction of equilibrium models of stationary disks around black holes has a long tradition (see~\cite{Abramowicz:2013} and references therein).
-In particular, the so-called ``Polish doughnuts", developed by Paczy\'nski and collaborators~\citep{Abramowicz:1978}, provides a  very general method to build equilibrium configurations of perfect fluid matter
+In particular, the so-called ``Polish doughnuts"~\citep{Abramowicz:1978,Kozlowski:1978} provide a  very general method to build equilibrium configurations of perfect fluid matter
  orbiting around a Kerr black hole.
 This fully relativistic model assumes that the disk is non-magnetized and that the matter obeys a  constant specific angular momentum distribution.
-\cite{Komissarov:2006} extended this method by adding a purely azimuthal magnetic
+This method was extended by~\cite{Komissarov:2006}  by adding a purely azimuthal magnetic
  field to build magnetized tori around rotating black holes.
@@
 %\end{equation}
-is the (dual of the) Faraday tensor relative to an observer with four-velocity $u^{\mu}$, and $b^{\mu}$ is the magnetic field in that frame.
-Assuming the magnetic field is purely azimuthal, i.e.~$b^r = b^{\theta} = 0$,
+is the (dual of the) Faraday tensor relative to an observer with four-velocity $u^{\mu}$, and $b^{\mu}$ is the magnetic field in that frame, with
+$b^2=b^{\mu}b_{\mu}$. Assuming the magnetic field is purely azimuthal, i.e.~$b^r = b^{\theta} = 0$,
 and taking into account that the flow is stationary and axisymmetric, the conservation of the current density and of the Faraday tensor follow.
@@
 \begin{equation}
-(w + b^2)u_{\nu}\partial_i u^{\nu} + \partial_i\left(p + \frac{b^2}{2}\right) - b_{\nu}\partial_i b^{\nu},
+(w + b^2)u_{\nu}\partial_i u^{\nu} + \partial_i\left(p + \frac{b^2}{2}\right) - b_{\nu}\partial_i b^{\nu}=0\,,
 \end{equation}
-where $i = r, \theta$. We can rewrite this equation in terms of the specific angular momentum $l$ and the angular velocity $\Omega$, to obtain
+where $i = r, \theta$. Following~\cite{Komissarov:2006} we rewrite this equation in terms of the specific angular momentum $l$ and the angular velocity $\Omega$, to obtain
 \begin{equation}\label{eq:diff_ver}
-\partial_i(\ln u_t|) - \frac{\Omega \partial_i l}{1-l\Omega} + \frac{\partial_i p}{w} + \frac{\partial_i(\mathcal{L}b^2)}{2\mathcal{L}w} = 0,
+\partial_i(\ln u_t|) - \frac{\Omega \partial_i l}{1-l\Omega} + \frac{\partial_i p}{w} + \frac{\partial_i(\mathcal{L}b^2)}{2\mathcal{L}w} = 0\,,
 \end{equation}
-where 
-\begin{equation}
-\mathcal{L} = g_{t\phi}^2 - g_{tt}g_{\phi\phi}.
-\end{equation}
+where $\mathcal{L} = g_{t\phi}^2 - g_{tt}g_{\phi\phi}$.
 To integrate Eq.~\eqref{eq:diff_ver} we first assume a barotropic equation of state $w = w(p)$ of the form
@@
 with $K$ and $\kappa$ constants.
-
-Then, we define the magnetic pressure as $p_{\mathrm{m}} = b^2/2$.
-Also, we can define $\tilde{p}_{\mathrm{m}} = \mathcal{L} p_{\mathrm{m}}$ and $\tilde{w} = \mathcal{L} w$, so we can write an analogue of \eqref{eq:eos_fluid} for $\tilde{p}_{\mathrm{m}}$
+Then, we define the magnetic pressure as $p_{\mathrm{m}} = b^2/2$, and introduce the definitions $\tilde{p}_{\mathrm{m}} = \mathcal{L} p_{\mathrm{m}}$ and $\tilde{w} = \mathcal{L} w$, in order to write an analog equation to Eq.~\eqref{eq:eos_fluid} for $\tilde{p}_{\mathrm{m}}$~\citep{Komissarov:2006}
 \begin{equation}\label{eq:eos_mag_tilde}
@@
 where $K_{\mathrm{m}}$ and $\eta$ are constants.
+This particular choice of relationships, $w = w(p)$ and $\tilde{w} = \tilde{w}(\tilde{p}_{\mathrm{m}})$, fulfill the general relativistic version of the von Zeipel theorem for a toroidal magnetic field~\citep{vonZeipel:1924, Zanotti:2015}, i.e.~the surfaces of constant $\Omega$ and constant $l$ coincide.
 
-This particular choice of relationships $w = w(p)$ and $\tilde{w} = \tilde{w}(\tilde{p}_{\mathrm{m}})$, fulfill the general relativistic version for a toroidal magnetic field of the von Zeipel theorem \citep{vonZeipel:1924, Zanotti:2015}, that means the surfaces of $\Omega$ and $l$ constant coincide.
-
-We can rewrite equation \eqref{eq:diff_ver} and integrate it to give
+Integrating Eq.~\eqref{eq:diff_ver} we obtain
 \begin{equation}\label{eq:pre_full_int}
-\ln |u_t| - \int^l_0 \frac{\Omega \mathrm{d}l}{1 - \Omega l} + \int^p_0 \frac{\mathrm{d}p}{w} + \int^{\tilde{p}_{\mathrm{m}}} \frac{\mathrm{d}\tilde{p}_{\mathrm{m}}}{\tilde{w}} = \mathrm{constant}.
+\ln |u_t| - \int^l_0 \frac{\Omega \mathrm{d}l}{1 - \Omega l} + \int^p_0 \frac{\mathrm{d}p}{w} + \int^{\tilde{p}_{\mathrm{m}}} \frac{\mathrm{d}\tilde{p}_{\mathrm{m}}}{\tilde{w}} = \mathrm{const}.
 \end{equation}
-On the surface of the disk, and particularly on its inner edge,
+On the surface of the disk, and particularly on its inner edge, the conditions
+$p = \tilde{p}_{\mathrm{m}} = 0, \; u_t = u_{t, \mathrm{in}}, \; l = l_{\mathrm{in}}$
+are satisfied and, therefore, the integration constant is given by
 \begin{equation}
-p = \tilde{p}_{\mathrm{m}} = 0, \;\;\; u_t = u_{t, \mathrm{in}}, \;\;\; l = l_{\mathrm{in}}
+\mathrm{const.} = \ln |u_t| - \int^l_{l_\mathrm{in}} \frac{\Omega \mathrm{d}l}{1 - \Omega l}\,.
 \end{equation}
-then, the constant of integration is given by
-\begin{equation}
-\mathrm{constant.} = \ln |u_t| - \int^l_{\mathrm{in}} \frac{\Omega \mathrm{d}l}{1 - \Omega l}.
-\end{equation}
-Defining the total potential $W$ \citet{Abramowicz:1978}, we can write
+We can also introduce the total (gravitational plus centrifugal) potential $W$~\citep{Abramowicz:1978} and write the integral form of the equation of motion as
 \begin{equation}\label{eq:potential}
@@
 \end{equation}
-where $W_{\mathrm{in}}$ is the potential on the inner edge of the disk. With this definition, we can write \eqref{eq:pre_full_int} as
+where $W_{\mathrm{in}}$ is the potential on the inner edge of the disk (in the equatorial plane). With this definition, we can write \eqref{eq:pre_full_int} as
 \begin{equation}\label{eq:full_int}

### 2017-01-17 paper.tex
Some more work on the draft

@@
 \begin{equation}\label{eq:pre_full_int}
-\ln |u_t| - \int^l_0 \frac{\Omega \mathrm{d}l}{1 - \Omega l} + \int^p_0 \frac{\mathrm{d}p}{w} + \int^{\tilde{p}_{\mathrm{m}}} \frac{\mathrm{d}\tilde{p}_{\mathrm{m}}}{\tilde{w}} = \mathrm{const}.
+\ln |u_t| - \int^l_0 \frac{\Omega \mathrm{d}l}{1 - \Omega l} + \int^p_0 \frac{\mathrm{d}p}{w} + \int_0^{\tilde{p}_{\mathrm{m}}} \frac{\mathrm{d}\tilde{p}_{\mathrm{m}}}{\tilde{w}} = \mathrm{const}.
 \end{equation}
@@
 $p = \tilde{p}_{\mathrm{m}} = 0, \; u_t = u_{t, \mathrm{in}}, \; l = l_{\mathrm{in}}$
-are satisfied and, therefore, the integration constant is given by
+are satisfied and, therefore, the integration constant is simply given by
 \begin{equation}
@@
 \end{equation}
-where $W_{\mathrm{in}}$ is the potential on the inner edge of the disk (in the equatorial plane). With this definition, we can write \eqref{eq:pre_full_int} as
+where $W_{\mathrm{in}}$ is the potential at the inner edge of the disk (in the equatorial plane). With this definition, we can write Eq.~\eqref{eq:pre_full_int} as
 \begin{equation}\label{eq:full_int}
-W - W_{\mathrm{in}} = \int^p_0 \frac{\mathrm{d}p}{w} + \int^{\tilde{p}_{\mathrm{m}}} \frac{\mathrm{d}\tilde{p}_{\mathrm{m}}}{\tilde{w}},
+W - W_{\mathrm{in}} = \int^p_0 \frac{\mathrm{d}p}{w} + \int_0^{\tilde{p}_{\mathrm{m}}} \frac{\mathrm{d}\tilde{p}_{\mathrm{m}}}{\tilde{w}},
 \end{equation}
-and
+which for a barotropic equation of state can be easily integrated to give
 \begin{equation}\label{eq:pre_enthalpy_eq}
-W - W_{\rm{in}} + \frac{\kappa}{\kappa - 1}\frac{p}{w} + \frac{\eta}{\eta - 1}\frac{p_{\mathrm{m}}}{w} = 0,
+W - W_{\rm{in}} + \frac{\kappa}{\kappa - 1}\frac{p}{w} + \frac{\eta}{\eta - 1}\frac{p_{\mathrm{m}}}{w} = 0\,.
 \end{equation}
-and then, replacing $p$ and $p_{\mathrm{m}}$ by equations \eqref{eq:eos_fluid} and \eqref{eq:eos_mag},
+Replacing $p$ and $p_{\mathrm{m}}$ by equations \eqref{eq:eos_fluid} and \eqref{eq:eos_mag}, the previous equation reduces to
 \begin{equation}\label{eq:enthalpy_eq}
@@
 
-Finally, we assume a polytropic equation of state given by
-\begin{equation}\label{eq:density_eq}
-p = K \rho^{\kappa}
-\end{equation}
-where $\rho$ is the fluid density.
+%Finally, we assume a polytropic equation of state given by
+%\begin{equation}\label{eq:density_eq}
+%p = K \rho^{\kappa}
+%\end{equation}
+%where $\rho$ is the fluid density.
 
-%--------------------------------------------------------------------
+%%%%%%%%%%%%
 \section{Methodology}
+%%%%%%%%%%%%
 
@@
 
-To construct the disks we follow the procedure described below:
-
-First, we find the location of $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$ as the solutions to the equation $l(r) - l_{\mathrm{K}} = 0$.
-Next, we write the partial derivatives of the potential \eqref{eq:potential}
+To construct the disks we follow the approach described in \citet{Qian:2009}.
+First, we find the radial location of the cusp and the center of the disk in the equatorial plane, $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$, defined as the solutions to the equation $l(r) - l_{\mathrm{K}} = 0$.
+Next, we compute the partial derivatives of the potential, Eq.~\eqref{eq:potential}
 \begin{equation}\label{eq:radial_der_pot}
-\partial_r W = \partial_r \ln|u_t| - \frac{\Omega \partial_rl}{1 - \Omega l},
+\partial_r W = \partial_r \ln|u_t| - \frac{\Omega \partial_rl}{1 - \Omega l}\,,
 \end{equation}
@@
 \begin{equation}\label{eq:polar_der_pot}
-\partial_{\theta} W = \partial_{\theta} \ln|u_t| - \frac{\Omega \partial_{\theta}l}{1 - \Omega l}.
+\partial_{\theta} W = \partial_{\theta} \ln|u_t| - \frac{\Omega \partial_{\theta}l}{1 - \Omega l}\,.
 \end{equation}
-Then, we integrate the radial partial derivative of the potential along the segment $[r_{\mathrm{cusp}}, r_{\mathrm{c}}]$ (assuming $W_{\mathrm{cusp}} = 0$) at the equatorial plane, thus obtaining the equatorial distribution of potential between $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$
+Then, we integrate the radial partial derivative of the potential along the segment $[r_{\mathrm{cusp}}, r_{\mathrm{c}}]$ (assuming $W_{\mathrm{cusp}} = 0$) at the equatorial plane, thus obtaining the equatorial distribution of the potential between $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$
 \begin{equation}\label{eq:equatorial_pot}
@@
 \end{equation}
-We can divide the equations \eqref{eq:radial_der_pot} and \eqref{eq:polar_der_pot} \citep{Qian:2009} to get
+Following \citet{Qian:2009} we can divide equations \eqref{eq:radial_der_pot} and \eqref{eq:polar_der_pot} to obtain
 \begin{equation}\label{eq:F}
-F(r, \theta) = -\frac{\partial_r W}{\partial_{\theta} W} = \frac{\mathrm{d}\theta}{\mathrm{d}r}.
+F(r, \theta) = -\frac{\partial_r W}{\partial_{\theta} W} = \frac{\mathrm{d}\theta}{\mathrm{d}r}\,,
 \end{equation}

### 2017-01-19 paper.tex
a bit of work

@@
 
-%--------------------------------------------------------------------
+%%%%%%%%%
 \section{Results}
+%%%%%%%%%
+
+Figure~\ref{komissarov} corresponds to the same constant specific angular momentum model presented by~\citet{Komissarov:2006}.
+The comparison shows that our approach can reproduce those previous results with good agreement.
+{\bf Complete description.}
 
@@
 \centering
-\includegraphics[scale=0.4]{images/1.pdf}
-\includegraphics[scale=0.4]{images/2.pdf}
-\caption{test density plots}
-           \label{FigGam}%
+\includegraphics[scale=0.32]{images/1_A.pdf}
+\hspace{-1.2cm}
+\includegraphics[scale=0.32]{images/1_B.pdf}
+\hspace{-0.8cm}
+\includegraphics[scale=0.32]{images/1_C.pdf}
+\caption{Comparison with Komissarov's solution for a constant angular momentum model.}
+           \label{komissarov}%
  \end{figure*}
+
+%\begin{figure*}
+%\centering
+%\includegraphics[scale=0.4]{images/1.pdf}
+%\includegraphics[scale=0.4]{images/2.pdf}
+%\caption{test density plots}
+%           \label{FigGam}%
+% \end{figure*}
 

### 2017-02-24 paper.tex
small change
Adding the new figures
Added figure 6
Major work on the draft

--- 2017-01-17 paper.tex
@@
 
-%
 \usepackage{graphicx}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \usepackage{txfonts}
 \usepackage{hyperref}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\usepackage[options]{hyperref}
-% To add links in your PDF file, use the package "hyperref"
-% with options according to your LaTeX or PDFLaTeX drivers.
-%
+\usepackage{color}
+\usepackage{float}
+
+\newcommand{\tf}[1]{\textcolor{red}{TF: #1}}
 
@@
 \title{Magnetized Polish doughnuts revisited}
-
-%   \subtitle{}
 
@@
 
-% \abstract{}{}{}{}{} 
-% 5 {} token are mandatory
+  \abstract
+{We discuss new sequences of magnetized, equilibrium tori around Kerr black holes by combining two approaches previously considered in the literature.
+Our approach assumes that the test-fluid approximation holds, hence we neglect the self-gravity of the fluid.
+The models are built assuming a particular form of the angular momentum distribution from which the location and morphology of surfaces of equal pressure can be computed.
+This ansatz includes the  constant angular momentum case originally employed in the construction of thick tori - or Polish doughnuts - and has already been used to build equilibrium sequences of purely hydrodynamical models.
+We discuss the properties of the new models and their dependence on the initial parameters.
+These new sequences can be used as initial data for magnetohydrodynamical evolutions in general relativity.}
 
-  \abstract
-  % context heading (optional)
-  % {} leave it empty if necessary  
-   {}
-  % aims heading (mandatory)
-   {bla}
-  % methods heading (mandatory)
-   {bla}
-  % results heading (mandatory)
-   {bla}
-  % conclusions heading (optional), leave it empty if necessary 
-   {}
-
-   \keywords{keywords here}
+   \keywords{\tf{Complete keywords}}
 
@@
 
-Matter accretion on to a black hole is the most efficient form of energy production known in nature. The conversion of the
-gravitational energy of the infalling matter into heat and radiation may reach efficiencies
-of about 43\% in the case of rotating (Kerr) black holes. For this reason, systems formed 
-by a black hole surrounded by an accretion disk are deemed responsible for many of the most energetic astronomical phenomena observed in the cosmos.
-In particular, (geometrically) thick accretion disks are believed to be present in quasars and other active galactic nuclei, some 
+Matter accretion on to black holes is the most efficient form of energy production known in nature. The conversion of the
+gravitational energy of the infalling matter into heat and radiation may reach efficiencies of about 43\% in the case of maximally rotating (Kerr) black holes.
+For this reason, systems formed by a black hole surrounded by an accretion disk are deemed responsible for many of the most energetic astronomical phenomena observed in the cosmos.
+In particular, (geometrically) thick accretion disks (or tori) are believed to be present in quasars and other active galactic nuclei, some 
 X-ray binaries and microquasars, as well as in the central engine of gamma-ray bursts.
+The latter are alluded to in connection with mergers of neutron star binaries and black hole neutron star binaries, as well as with the rotational collapse that ensues at the end of the life of some massive stars.
+As numerical simulations show, such events  often result in a black hole surrounded by a torus.
+\tf{We need to include a few references in this paragraph.}
 
-The investigation of such systems, either by analytical or numerical means, may rely on the ability to construct suitable 
+The investigation of this type of systems, either by analytical or numerical means, may rely on the ability to construct suitable 
 representations based on physical assumptions.
-The construction of equilibrium models of stationary disks around black holes has a long tradition (see~\cite{Abramowicz:2013} and references therein).
+The construction of equilibrium models of stationary disks around black holes has indeed a long tradition (see~\cite{Abramowicz:2013} and references therein).
 In particular, the so-called ``Polish doughnuts"~\citep{Abramowicz:1978,Kozlowski:1978} provide a  very general method to build equilibrium configurations of perfect fluid matter
@@
 This fully relativistic model assumes that the disk is non-magnetized and that the matter obeys a  constant specific angular momentum distribution.
-This method was extended by~\cite{Komissarov:2006}  by adding a purely azimuthal magnetic
+This method was later extended by~\cite{Komissarov:2006}  by adding a purely azimuthal magnetic
  field to build magnetized tori around rotating black holes.
-Assuming different distributions of angular momentum in the disks, \citet{Qian:2009} presented a method to build sequences of black hole thick accretion disks in dynamical equilibria, restricted to the purely hydrodynamical case.
-Building on this work, we discuss here the extension of the
-models of~\citet{Qian:2009} to disks endowed with a purely toroidal magnetic field.
-For the particular case of constant angular momentum distributions our method shows good agreement with the results of~\citet{Komissarov:2006}.
+On the other hand, assuming different distributions of angular momentum in the disks, \citet{Qian:2009} presented a method to build sequences of black hole thick accretion disks in dynamical equilibria, restricted however to the purely hydrodynamical case.
 
-The organization of the paper is as follows:
-We assume that the test-fluid approximation holds, neglecting the self-gravity of the fluid, and assume that the space-time is described by the Kerr metric. We use geometrized units where $G = c = 1$.
+ In this paper we combine the two approaches considered in~\cite{Komissarov:2006} and~\citet{Qian:2009} to build new sequences of equilibrium tori around Kerr black holes.
+ Building on those works, we present here the extension of the models of~\citet{Qian:2009} to account for disks endowed with a purely toroidal magnetic field.
+In our procedure we hence assume a form of the angular momentum distribution that departs from the constant case considered by~\cite{Komissarov:2006} and from which the location and morphology
+of surfaces of equal pressure can be numerically computed.
+As we shall show below, for the particular case of constant angular momentum distributions, our method is in good agreement with the results of~\citet{Komissarov:2006}.
+
+The organization of the paper is as follows: Section~\ref{framework} presents the analytic framework to build the disks while Section~\ref{methodology} explains the corresponding numerical procedure.
+The sequences of models are discussed in Section~\ref{results}.
+Finally, the conclusions are summarized in Section~\ref{conclusions}, where we also briefly indicate potential extensions of this work we plan to inspect.
+In our work we assume that the test-fluid approximation holds, thus neglecting the self-gravity of the fluid, and further assume that the spacetime is described by the Kerr metric.
+We use geometrized units where $G = c = 1$.
 
@@
 \section{Framework}
+\label{framework}
 %%%%%%%%%%%
@@
 \end{eqnarray}
-where $Z_1=1+(1-a_*^2)^{1/3}[(1+a_*)^{1/3}+(1-a_*)^{1/3}]$, $Z_2=(3a_*^2+Z_1^2)^{1/2}$, and $a_*=a/M$, with $a$ and $M$ being the spin Kerr parameter and the black hole mass.
+where we have defined the following quantities, $Z_1=1+(1-a_*^2)^{1/3}[(1+a_*)^{1/3}+(1-a_*)^{1/3}]$, $Z_2=(3a_*^2+Z_1^2)^{1/2}$, and $a_*=a/M$, with $a$ and $M$ being the spin Kerr parameter and the black hole mass.
+\tf{Check that the above expressions are correct.}
 
@@
 where $u^{\mu}$ is the fluid four-velocity.
-%
-%\footnote{In Kerr-Schild coordinates. Although the use of the Boyer-Lindquist coordinates yields exactly the same mathematical derivation and results.}.
-%
 The relationship between $l$ and $\Omega$ is given by the equations
@@
 with $\eta_{\mathrm{max}} = l_{\mathrm{K}}(r_{\mathrm{mb}})/l_{\mathrm{K}}(r_{\mathrm{ms}})$.
-In this paper we choose $\eta = \eta_{\mathrm{max}}$, then we can write $l_0$ as $l_0 = l_{\mathrm{K}}(r_{\mathrm{mb}})$.
+In this paper, and as it is done in~\citet{Qian:2009}, we choose $\eta = \eta_{\mathrm{max}}$, and then we can write $l_0$ as $l_0 = l_{\mathrm{K}}(r_{\mathrm{mb}})$.
 We take this choice because [explicar que esta eleccion hace que el momento angular esté comprendido entre lmb y lms para variaciones de beta entre 0 y 1.
-Además los discos de momento angular constante que empiezan en el cusp, no tienen borde externo para l = lmb]
+Además los discos de momento angular constante que empiezan en el cusp, no tienen borde externo para l = lmb] \tf{Write the explanation in the draft.}
 
@@
 
-The equations of ideal general relativistic MHD are $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and 
+The equations of ideal general relativistic MHD are the following conservation laws, $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and 
 $\nabla_{\mu} (\rho u^{\mu}) = 0$, 
@@
 \end{equation}
-where $K_{\mathrm{m}}$ and $\eta$ are constants.
+where $K_{\mathrm{m}}$ and $\eta$ are constants. \tf{I think we should use a different letter for the exponent instead of $\eta$ as it can be confused with the $\eta$ in the angular momentum ansatz.}
 This particular choice of relationships, $w = w(p)$ and $\tilde{w} = \tilde{w}(\tilde{p}_{\mathrm{m}})$, fulfill the general relativistic version of the von Zeipel theorem for a toroidal magnetic field~\citep{vonZeipel:1924, Zanotti:2015}, i.e.~the surfaces of constant $\Omega$ and constant $l$ coincide.
@@
 \end{equation}
-which relates the distribution of potential with the distribution of enthalpy.
-
-%Finally, we assume a polytropic equation of state given by
-%\begin{equation}\label{eq:density_eq}
-%p = K \rho^{\kappa}
-%\end{equation}
-%where $\rho$ is the fluid density.
+which relates the distribution of the potential with the distribution of enthalpy.
 
@@
 \section{Methodology}
+\label{methodology}
 %%%%%%%%%%%%
 
-\subsection{Building the disk}
+\begin{figure*}[t]
+\centering
+\includegraphics[scale=0.16]{figures/fig1a.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.16]{figures/fig1b.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.16]{figures/fig1c.pdf}
+\caption{Comparison with Komissarov's solution for a constant angular momentum model.
+The left panel shows the density distribution in logarithm scale for all radii and all angles while the middle and right panels show, respectively, the angular profile of the logarithm of the density at the centre of the disk and the radial profile of the density at the equatorial plane.}
+           \label{komissarov}%
+ \end{figure*}
 
-To construct the disks we follow the approach described in \citet{Qian:2009}.
-First, we find the radial location of the cusp and the center of the disk in the equatorial plane, $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$, defined as the solutions to the equation $l(r) - l_{\mathrm{K}} = 0$.
+%\subsection{Building the disk}
+
+To construct the magnetized disks we follow the approach described in \citet{Qian:2009}.
+First, we find the radial location of the cusp and of the centre of the disk in the equatorial plane, $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$, defined as the solutions to the equation $l(r) - l_{\mathrm{K}} = 0$.
 Next, we compute the partial derivatives of the potential, Eq.~\eqref{eq:potential}
@@
 where $w_{\mathrm{m}}$ is the enthalpy at the disk center and
-\begin{equation}\label{eq:beta_eq}
-\beta = p/p_{\mathrm{m}},
+\begin{equation}
+\label{eq:beta_eq}
+\beta_{\mathrm{c}} = p/p_{\mathrm{m}},
 \end{equation}
@@
 
-\subsection{Numerical code}
+%\subsection{Numerical code}
 
@@
 
-To integrate the ordinary differential equation \eqref{eq:F} we use the RK4 method.
+To integrate the ordinary differential equation \eqref{eq:F} we use a fourth-order Runge-Kutta method.
 Here is also important to choose a suitable step of integration, specially at the outer end of the disk, this is because the equation \eqref{eq:F} diverges of the equatorial plane (the equipotential surfaces crosses the equatorial plane perpendicularly).
 
-\subsection{Parameter space}
+%\subsection{Parameter space}
 
 As in \citet{Komissarov:2006}, in this paper we have chosen the exponents $\kappa = \eta = 4/3$ and the enthalpy at the disk center $w_{\mathrm{c}} = 0$.
-That leaves us the magnetization parameter $\beta$, the parameters of the angular momentum distribution $\beta$ and $\gamma$, the BH spin parameter $a$ and the inner radius of the disk $r_{\mathrm{in}}$.
+That leaves us the magnetization parameter $\beta_{\mathrm{c}}$, the parameters of the angular momentum distribution $\beta$ and $\gamma$, the black hole spin parameter $a$ and the inner radius of the disk $r_{\mathrm{in}}$.
 This allows us to control the size, shape, thickness and magnetization of the disk.
 
-%--------------------------------------------------------------------
-\section{Results}
-
-\begin{figure*}
-\centering
-\includegraphics[scale=0.4]{images/1.pdf}
-\includegraphics[scale=0.4]{images/2.pdf}
-\caption{test density plots}
-           \label{FigGam}%
- \end{figure*}
-
-\begin{table*}
-\caption{test two column table}             
+\begin{table}
+\caption{List of models.
+Form left to right the columns report: the black hole spin $a$, the parameters of the angular momentum distribution $\beta$ and $\gamma$, the magnetization parameter $\beta_{\mathrm{c}}$ for which a maximum pressure is achieved, the corresponding radii of the maximum thermal pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential diference between the center and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the disks, $r_{\mathrm{in}}$ and  $r_{\mathrm{out}}$.
+\tf{Complete table.}}
 \label{table:1}      
@@
 \hline\hline       
-
-Modelo & $\beta$ & $\gamma$ & $\beta_{\mathrm{c}}$ & $\Delta W$ & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ & $r_{p_{\rm{max}}}$ & $r_{p_{\mathrm{mag, max}}}$ & $p_{\mathrm{max}}$\\ 
+ & $a$ & $\beta$ & $\gamma$ & $\beta_{\mathrm{c}}$  & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W$ & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
 \hline           
-  B-7 & $0.5$ & $0.5$ & $10^{3}$ & $-7.29 \times 10^{-2}$ & $1.27$ & $2.50$ & $1.971$ & $2.086$ & $1.83 \times 10^{-2}$\\ 
-  B-8 & $0.5$ & $0.5$ & $10^{2}$ & $-7.29 \times 10^{-2}$ & $1.27$ & $2.50$ & $1.971$ & $2.076$ & $1.82 \times 10^{-2}$\\ 
-  B-9 & $0.5$ & $0.5$ & $1$ & $-7.29 \times 10^{-2}$ & $1.27$ & $2.50$ & $1.931$ & $2.047$ & $1.68 \times 10^{-2}$\\ 
-  B-10 & $0.5$ & $0.5$ & $1$ & $-7.29 \times 10^{-2}$ & $1.27$ & $2.50$ & $1.761$ & $1.861$ & $1.10 \times 10^{-2}$\\ 
-  B-11 & $0.5$ & $0.5$ & $10^{-1}$ & $-7.29 \times 10^{-2}$ & $1.27$ & $2.50$ & $1.641$ & $1.701$ & $2.95 \times 10^{-3}$\\ 
-  B-12 & $0.5$ & $0.5$ & $10^{-2}$ & $-7.29 \times 10^{-2}$ & $1.27$ & $2.50$ & $1.621$ & $1.681$ & $3.59 \times 10^{-4}$\\ 
-  B-13 & $0.5$ & $0.5$ & $10^{-3}$ & $-7.29 \times 10^{-2}$ & $1.27$ & $2.50$ & $1.611$ & $1.671$ & $3.67 \times 10^{-5}$\\ 
+A1 & $0.5$ & $0.0$ & $0.0$ &  &  &    &  &  & \\ 
+A2 &           & $0.5$ & $0.5$ &  &  &    &  &  & \\ 
+A3  &          & $0.9$ & $0.9$ &  &  &    &  &  &  \\ 
+A4  &          & $0.0$ & $0.9$ &  &  &    &  &  & \\ 
+A5   &         & $0.9$ & $0.0$ &  &  &    &  &  & \\ 
+A6   &         &           &           &  &  &    &  &  & \\ 
+A7   &         &           &           &  &  &    &  &  &\\ 
+ \hline 
+B1 & $0.9$ & $0.0$ & $0.0$ &  &  &    &  &  & \\ 
+B2 &           & $0.5$ & $0.5$ &  &  &    &  &  & \\ 
+B3  &          & $0.9$ & $0.9$ &  &  &    &  &  &  \\ 
+B4  &          & $0.0$ & $0.9$ &  &  &    &  &  & \\ 
+B5   &         & $0.9$ & $0.0$ &  &  &    &  &  & \\ 
+B6   &         &           &           &  &  &    &  &  & \\ 
+B7   &         &           &           &  &  &    &  &  &\\  
+ \hline 
+C1 & $0.99$ & $0.0$ & $0.0$ &  &  &    &  &  & \\ 
+C2 &             & $0.5$ & $0.5$ &  &  &    &  &  & \\ 
+C3  &            & $0.9$ & $0.9$ &  &  &    &  &  &  \\ 
+C4  &            & $0.0$ & $0.9$ &  &  &    &  &  & \\ 
+C5   &           & $0.9$ & $0.0$ &  &  &    &  &  & \\ 
+C6   &           &           &           &  &  &    &  &  & \\ 
+C7   &           &           &           &  &  &    &  &  &\\   
 \hline      
 \end{tabular}
-\end{table*}
+\end{table}
 
-%--------------------------------------------------------------------
+%%%%%%%%%
+\section{Results}
+\label{results}
+%%%%%%%%%
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.16]{figures/fig2_1_1.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.16]{figures/fig2_1_2.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.16]{figures/fig2_1_3.pdf}
+\\
+\includegraphics[scale=0.16]{figures/fig2_2_1.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.16]{figures/fig2_2_2.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.16]{figures/fig2_2_3.pdf}
+\\
+\includegraphics[scale=0.16]{figures/fig2_3_1.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.16]{figures/fig2_3_2.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.16]{figures/fig2_3_3.pdf}
+\\
+\includegraphics[scale=0.16]{figures/fig2_4_1.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.16]{figures/fig2_4_2.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.16]{figures/fig2_4_3.pdf}
+\\
+\includegraphics[scale=0.16]{figures/fig2_5_1.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.16]{figures/fig2_5_2.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.16]{figures/fig2_5_3.pdf}
+\caption{Isodensity distributions (in logarithm scale) for a representative sample of our models.
+From left to right the columns correspond to increasing values of the black hole spin: $a=0.5$, 0.9 and 0.99.
+From top to bottom the rows correspond to the following parameter combinations: a) $\gamma=\beta=0$; b) $\gamma=\beta=0.5$; c) $\gamma=\beta=0.9$; d) $\gamma=0.9$, $\beta=0$; e) $\gamma=0$, $\beta=0.9$.
+Note that the spatial scale of the plots differs as it has been chosen to facilitate the visualization of the disks.}
+\label{models}
+\end{figure*}
+
+\begin{figure*}[t]
+\centering
+\includegraphics[scale=0.16]{figures/fig3a.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.16]{figures/fig3b.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.16]{figures/fig3c.pdf}
+\caption{Effects of the magnetization in the structure of the disk. From left to right the values are $\beta_{\rm c}=10^3$, 1, and $10^{-3}$.}
+\label{magnetization}%
+\end{figure*}
+
+We start by assessing our procedure by first building a disk that can be directly compared with one of the two models in~\citet{Komissarov:2006}.
+This is shown in Figure~\ref{komissarov}, which corresponds to the same constant specific angular momentum model A presented by~\citet{Komissarov:2006}.
+The parameters of this model are $a=0.9$, $\beta_c=0.1$, and $l=2.8$.
+\tf{Is this the value of $l$ we use?}
+The visual comparison shows that our approach can reproduce those previous results with good agreement.
+The density distribution in the $(r\sin\theta,r\cos\theta)$ plane shown in the left panel of Fig.~\ref{komissarov} is remarkably similar to that shown in the left panel of Fig.~2 in~\citet{Komissarov:2006}.
+Not only the morphology of both models is nearly identical but also the range of variation of the density and the location of the disk center agree well in both cases.
+This can be most clearly seen in the middle and right panels of Fig.~\ref{komissarov} which show, repectively, the angular profile at $r_{\rm c}$ and the radial profile at $\theta=\pi/2$.
+These two figures can be directly compared with Fig.~3 of~\citet{Komissarov:2006}.
+\tf{There are some slight differences though.
+Is this because we do not use the exact same value of the angular momentum?}
+
+\begin{figure}[t]
+\centering
+\includegraphics[scale=0.2]{figures/fig4.pdf}
+\caption{Radial profiles of the density in the equatorial plane for $\beta=10^3$ (black curve), 1 (blue curve), and $10^{-3}$ (green curve). \tf{Check color code.}}
+\label{magnetization-profile}
+ \end{figure}
+
+\begin{figure}[t]
+\centering
+\includegraphics[scale=0.2]{figures/fig5.pdf}
+\caption{Radial profiles at the equatorial plane for models with $a=0.9$, $\beta_{\rm c}=10^{-3}$, and same combination of the $\gamma$ and $\beta$ parameters as in the rows of Fig.~\ref{models} (the specific values are indicated in the legend).
+\tf{Include a legend indicating the particular values of these two parameters.}}
+\label{more-profile}
+\end{figure}
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.16]{figures/fig6a.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.16]{figures/fig6b.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.16]{figures/fig6c.pdf}
+\caption{Caption. \tf{Complete the caption.}}
+           \label{max-vs-magnetization}%
+ \end{figure*}
+
+A representative sample of the isodensity surfaces (in logarithm scale) for some of our models appears in Figure~\ref{models}.
+From left to right the columns of this figure correspond to increasing values of the black hole spin, namely, $a=0.5$, 0.9 and 0.99, while from top to bottom the rows correspond to different combinations of the $\gamma$ and $\beta$ parameters that characterize the ansatz for the angular momentum distribution of~\citet{Qian:2009} (the particular values are indicated in the caption of the figure).
+The value of the magnetization parameter for all models in this figure is $\beta_{\rm c}=10^{-3}$.
+\tf{Is that correct?} A rapid inspection shows that the structure of the disks noticeable changes when the parameters change.
+Notice that the spatial scale in all of the plots of this figure has been chosen so as to facilitate the visualization of the disks (which can be fairly small in some cases) and, as such, is different in each plot.
+A typical Polish doughnut is represented by the model in the top-left panel.
+As the black hole spin increases, the maximum of the density (and of the pressure), which yields the center of the disk, moves inwards for all values of $\gamma$ and $\beta$.
+For $\gamma=0$ the disks are infinite, irrespective of the value of $a$.
+As $\gamma$ and $\beta$ increase from 0 to 0.9 (compare the three top rows) the disks become significantly thinner and radially smaller (see also Fig.~\ref{more-profile} below).
+\tf{Check if the description is correct.
+Add further relevant information.}
+
+Figure~\ref{magnetization} shows the effects of changing the parameter $\beta_{\rm c}$ (the magnetization) in the structure of the disks.
+From left to right the values plotted in each panel are $\beta_{\rm c}=10^3$, 1, and $10^{-3}$.
+The model chosen corresponds to $a=0.9$ and $\gamma=\beta=0.5$.
+The larger the value of $\beta_{\rm c}$ the less important the effects of the magnetization in the disk structure.
+Figure~\ref{magnetization} shows that for the kind of magnetic field distribution we are considering, the effects of magnetization are minor.
+The disk structure remains fairly similar for all values of $\beta_{\rm c}$ and the only quantitative differences are found in the location of the centre of the disk (which moves inward with decreasing $\beta_{\rm c}$) and of the range of variation of the isodensity contours (the maximum being slightly larger with decreasing $\beta_{\rm c}$).
+This can be more clearly visualized in Figure~\ref{magnetization-profile} which displays the radial profile at the equatorial plane of the logarithm of the density \tf{Is it $\log\rho$ or $\rho$?} for the same three cases plotted in Fig.~\ref{magnetization}.
+\tf{Check if the description is correct.
+Add further relevant information.}
+
+Next, we show in Fig.~\ref{more-profile} the corresponding radial profiles at the equatorial plane for the models with black hole spin $a=0.9$.
+We consider the case $\beta_{\rm c}=10^{-3}$ (highest magnetization) and the same combination of the $\gamma$ and $\beta$ parameters that we employed in Fig.~\ref{models}.
+Therefore, this plot depicts the radial profiles of the models occupying the central column of Fig.~\ref{models}.
+These profiles allow for a clearer quantification of the radial extent of the disks with $\gamma$ and $\beta$.
+As mentioned in the description of Fig.~\ref{models} as $\gamma$ and $\beta$ increase from 0 to 0.9 (compare black, blue, and green curves) the disks become gradually smaller.
+At the same time, the radial location of the centre increases and the maximum value of the central density (and pressure) decreases.
+It is worth noticing that the radial profiles of some of the models overlap below a certain radius.
+More precisely, the black and red curves overlap below $r\sim 4$ and also the green and orange curves.
+\tf{Check if the description is correct.
+Add further relevant information.}
+
+In order to provide a quantitative comparison of the structural differences that appear along the sequence of equilibrium models, we plot in Fig.~\ref{max-vs-magnetization} the variation of the maximum of the density (left panel), the radial location of the maximum of the thermal pressure (middle panel), and the radial location of the maximum of the magnetic pressure (right panel) as a function of the magnetization parameter $\beta_{\rm c}$.
+All quantities plotted are measured at the equatorial plane.
+Let us first consider the left panel.
+The line type used indicates the value of the black hole spin $a$, namely, a dotted line is for $a=0.5$, a dashed line for $a=0.9$, and a solid line for $a=0.99$.
+Correspondingly, the colour indicates the value of $\beta$ and $\gamma$ used, namely, red curves correspond to $\gamma=\beta=0$, the blue ones to $\gamma=\beta=0.5$, and the black ones to $\gamma=\beta=0.9$.
+\tf{Is my interpretation of the line type and colour code correct?} All curves show the same monotonically decreasing trend with $\beta_{\rm c}$: for small enough and large enough values of $\beta_{\rm c}$ the value of the density maximum does not change.
+However, in the interval $10^{-2}\le \beta_{\rm c} \le 10^{2}$, $\rho_{\rm max}$ changes abruptly.
+The larger the black hole spin the larger the drop in the maximum of the density.
+For sufficiently large values of $\beta_{\rm c}$ (small magnetization) the value of $\rho_{\rm max}$ stays constant to the same value irrespective of the black hole rotation.
+
+In the middle panel of Fig.~\ref{max-vs-magnetization} we show the radial location of the maximum of the thermal pressure as a function of $\beta_{\rm c}$.
+The black hole spin is $a=0.99$ \tf{is that correct?} and the values of $\beta$ and $\gamma$ are indicated in the legend.
+For all values of $\beta$ and $\gamma$, the maximum of the disk thermal pressure decreases with decreasing $\beta_{\rm c}$.
+Below $\beta_{\rm c}\sim 10^{-3}$ the location of the maximum does not change.
+The panel also shows that above $\beta_{\rm c}\sim 10^{3}$ the constant value of $r_{\rm max}$ is the same irrespective of $\beta$ and $\gamma$.
+
+The dependence of the location of the maximum of the magnetic pressure with $\beta_{\rm c}$ is shown in the right panel of Fig.~\ref{max-vs-magnetization}.
+While the maximum of the magnetic pressure also decreases with decreasing $\beta_{\rm c}$, the constant value achieved for values above $\beta_{\rm c}\sim 10^{3}$ does depend on the specific values of $\beta$ and $\gamma$.
+It must be noted that, for the magnetic pressure, all models seem to cross at roughly the same value of $r_{\rm max}$, as it is more clearly shown in the inset.
+
+%%%%%%%%%%%
 \section{Conclusions}
+\label{conclusions}
+%%%%%%%%%%%
 
-%-------------------------------------- Two column figure (place early!)
-%   \begin{figure*}
-%   \centering
-%   %%%\includegraphics{empty.eps}
-%   %%%\includegraphics{empty.eps}
-%   %%%\includegraphics{empty.eps}
-%   \caption{Adiabatic exponent $\Gamma_1$.
-%               $\Gamma_1$ is plotted as a function of
-%               $\lg$ internal energy $\mathrm{[erg\,g^{-1}]}$ and $\lg$
-%               density $\mathrm{[g\,cm^{-3}]}$.}
-%              \label{FigGam}%
-%    \end{figure*}
-%
+In this paper we have presented new sequences of magnetized, non-self-gravitating, equilibrium tori around Kerr black holes by combining two existing approaches~\citep{Komissarov:2006,Qian:2009}.
+Following~\citet{Qian:2009} the models have been built assuming a form of the angular momentum distribution from which the location and morphology
+of surfaces of equal pressure are computed.
+This ansatz includes as a limiting case the  constant angular momentum case originally employed in the construction of thick tori - or Polish doughnuts - and was already used by~\citet{Qian:2009} to build equilibrium sequences of purely hydrodynamical models.
+Our disks are endowed with a purely toroidal magnetic field, as in the work of~\citet{Komissarov:2006}, which provides the methodology to handle the magnetic terms.
 
-%--------------------------------------------------- One column table
-%   \begin{table}
-%      \caption[]{Opacity sources.}
-%         \label{KapSou}
-%     $$ 
-%         \begin{array}{p{0.5\linewidth}l}
-%            \hline
-%            \noalign{\smallskip}
-%            Source      &  T / {[\mathrm{K}]} \\
-%            \noalign{\smallskip}
-%            \hline
-%            \noalign{\smallskip}
-%            Yorke 1979, Yorke 1980a & \leq 1700^{\mathrm{a}}     \\
-%%           Yorke 1979, Yorke 1980a & \leq 1700             \\
-%            Kr\"ugel 1971           & 1700 \leq T \leq 5000 \\
-%            Cox \& Stewart 1969     & 5000 \leq             \\
-%            \noalign{\smallskip}
-%            \hline
-%         \end{array}
-%     $$ 
-%   \end{table}
-%
+We have discussed the properties of the new models and their dependence on the initial parameters. \tf{Expound on this presenting a short summary of our main findings.}
+
+\tf{To close the paper show a short outline of potential future work we plan to attempt with this research: inclusion of self-gravity as in the work of Stergioulas, and construction of disks around hairy black holes.}
 
 \begin{acknowledgements}
-      Work supported by the Spanish MINECO (grants AYA2013-40979-P and AYA2015-66899-C2-1-P) and the Generalitat Valenciana (PROMETEOII-2014-069).
+      Work supported by the Spanish MINECO (grant AYA2015-66899-C2-1-P) and the Generalitat Valenciana (PROMETEOII-2014-069).
 \end{acknowledgements}
-
-% WARNING
-%-------------------------------------------------------------------
-% Please note that we have included the references to the file aa.dem in
-% order to compile it, but we ask you to:
-%
-% - use BibTeX with the regular commands:
-%   \bibliographystyle{aa} % style aa.bst
-%   \bibliography{references.bib} % your references Yourfile.bib
-%
-% - join the .bib files when you upload your source files
-%-------------------------------------------------------------------
 

### 2017-03-14 paper.tex
Minor correction to adjust the order of the figures
Add files via upload

@@
 \newcommand{\tf}[1]{\textcolor{red}{TF: #1}}
+\newcommand{\sg}[1]{\textcolor{blue}{SG: #1}}
 
@@
 
-   \author{Sergio Gimeno\inst{1}   \and Jos\'e A.~Font\inst{1,2} }
+   \author{Sergio Gimeno-Soler\inst{1}   \and Jos\'e A.~Font\inst{1,2} }
 
@@
 
-   \keywords{\tf{Complete keywords}}
+   \keywords{accretion, accretion disks -- black hole physics -- magnetohydrodynamics (MHD)}
 
@@
 where we have defined the following quantities, $Z_1=1+(1-a_*^2)^{1/3}[(1+a_*)^{1/3}+(1-a_*)^{1/3}]$, $Z_2=(3a_*^2+Z_1^2)^{1/2}$, and $a_*=a/M$, with $a$ and $M$ being the spin Kerr parameter and the black hole mass.
-\tf{Check that the above expressions are correct.}
 
@@
 In this paper, and as it is done in~\citet{Qian:2009}, we choose $\eta = \eta_{\mathrm{max}}$, and then we can write $l_0$ as $l_0 = l_{\mathrm{K}}(r_{\mathrm{mb}})$.
-We take this choice because [explicar que esta eleccion hace que el momento angular esté comprendido entre lmb y lms para variaciones de beta entre 0 y 1.
-Además los discos de momento angular constante que empiezan en el cusp, no tienen borde externo para l = lmb] \tf{Write the explanation in the draft.}
+For this choice of $\eta$, we can find the location of the disk cusp at $r_{\mathrm{mb}} \leq r_{\mathrm{cusp}} \leq r_{\mathrm{ms}}$ (for $0 \leq \beta \leq 1$).
+Also, this guarantees that constant angular momentum disks ($\beta = \gamma = 0$) with its inner edge located at the cusp ($r_{\mathrm{in}} = r_{\mathrm{cusp}}$) have no outer bound.
 
@@
 \begin{equation}\label{eq:eos_mag_tilde}
-\tilde{p}_{\mathrm{m}} = K_{\mathrm{m}} \tilde{w}_{\mathrm{m}}^{\eta},
+\tilde{p}_{\mathrm{m}} = K_{\mathrm{m}} \tilde{w}_{\mathrm{m}}^{\lambda
+},
 \end{equation}
@@
 \begin{equation}\label{eq:eos_mag}
-p_{\mathrm{m}} = K_{\mathrm{m}} \mathcal{L}^{\eta-1} w^{\eta},
+p_{\mathrm{m}} = K_{\mathrm{m}} \mathcal{L}^{\lambda
+-1} w^{\lambda
+},
 \end{equation}
-where $K_{\mathrm{m}}$ and $\eta$ are constants. \tf{I think we should use a different letter for the exponent instead of $\eta$ as it can be confused with the $\eta$ in the angular momentum ansatz.}
+where $K_{\mathrm{m}}$ and $\lambda
+$ are constants.
 This particular choice of relationships, $w = w(p)$ and $\tilde{w} = \tilde{w}(\tilde{p}_{\mathrm{m}})$, fulfill the general relativistic version of the von Zeipel theorem for a toroidal magnetic field~\citep{vonZeipel:1924, Zanotti:2015}, i.e.~the surfaces of constant $\Omega$ and constant $l$ coincide.
+
+\begin{figure*}[t]
+\centering
+\includegraphics[scale=0.16]{figures/fig1a.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.16]{figures/fig1b.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.16]{figures/fig1c.pdf}
+\caption{\sg{update figures.}Comparison with Komissarov's solution for a constant angular momentum model.
+The left panel shows the density distribution in logarithm scale for all radii and all angles while the middle and right panels show, respectively, the angular profile of the logarithm of the density at the centre of the disk and the radial profile of the density at the equatorial plane.}
+           \label{komissarov}%
+ \end{figure*}
 
@@
 \begin{equation}\label{eq:pre_enthalpy_eq}
-W - W_{\rm{in}} + \frac{\kappa}{\kappa - 1}\frac{p}{w} + \frac{\eta}{\eta - 1}\frac{p_{\mathrm{m}}}{w} = 0\,.
+W - W_{\rm{in}} + \frac{\kappa}{\kappa - 1}\frac{p}{w} + \frac{\lambda
+}{\lambda
+ - 1}\frac{p_{\mathrm{m}}}{w} = 0\,.
 \end{equation}
@@
 \begin{equation}\label{eq:enthalpy_eq}
-W - W_{\rm{in}} + \frac{\kappa}{\kappa - 1} K w^{\kappa - 1} + \frac{\eta}{\eta - 1}K_{\mathrm{m}}(\mathcal{L} w)^{\eta - 1} = 0,
+W - W_{\rm{in}} + \frac{\kappa}{\kappa - 1} K w^{\kappa - 1} + \frac{\lambda
+}{\lambda
+ - 1}K_{\mathrm{m}}(\mathcal{L} w)^{\lambda
+ - 1} = 0,
 \end{equation}
@@
 %%%%%%%%%%%%
-
-\begin{figure*}[t]
-\centering
-\includegraphics[scale=0.16]{figures/fig1a.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.16]{figures/fig1b.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.16]{figures/fig1c.pdf}
-\caption{Comparison with Komissarov's solution for a constant angular momentum model.
-The left panel shows the density distribution in logarithm scale for all radii and all angles while the middle and right panels show, respectively, the angular profile of the logarithm of the density at the centre of the disk and the radial profile of the density at the equatorial plane.}
-           \label{komissarov}%
- \end{figure*}
 
@@
 \begin{equation}
-p_{\mathrm{c}} = w_{\mathrm{c}}(W_{\mathrm{in}} - W_{\mathrm{c}})\left(\frac{\kappa}{\kappa - 1} + \frac{\eta}{\eta - 1}\frac{1}{\beta_{\mathrm{c}}}\right)^{-1},
+p_{\mathrm{c}} = w_{\mathrm{c}}(W_{\mathrm{in}} - W_{\mathrm{c}})\left(\frac{\kappa}{\kappa - 1} + \frac{\lambda
+}{\lambda
+ - 1}\frac{1}{\beta_{\mathrm{m}_{\mathrm{c}}}}\right)^{-1},
 \end{equation}
-where $w_{\mathrm{m}}$ is the enthalpy at the disk center and
+where $w_{\mathrm{c}}$ is the enthalpy at the disk center and
 \begin{equation}
 \label{eq:beta_eq}
-\beta_{\mathrm{c}} = p/p_{\mathrm{m}},
+\beta_{\mathrm{m}} = p/p_{\mathrm{m}},
 \end{equation}
-is the magnetization parameter (being $\beta_{\mathrm{m}}$ the magnetization parameter at the disk center). By this definition, we can find the magnetic pressure at the disk center,
+is the magnetization parameter (being $\beta_{\mathrm{m}_{\mathrm{c}}}$ the magnetization parameter at the disk center). By this definition, we can find the magnetic pressure at the disk center,
 \begin{equation}
-p_{\mathrm{m_{\mathrm{c}}}} = p_{\mathrm{c}}/\beta_{\mathrm{c}}
+p_{\mathrm{m_{\mathrm{c}}}} = p_{\mathrm{c}}/\beta_{\mathrm{m}_{\mathrm{c}}}
 \end{equation}
@@
 
-As in \citet{Komissarov:2006}, in this paper we have chosen the exponents $\kappa = \eta = 4/3$ and the enthalpy at the disk center $w_{\mathrm{c}} = 0$.
-That leaves us the magnetization parameter $\beta_{\mathrm{c}}$, the parameters of the angular momentum distribution $\beta$ and $\gamma$, the black hole spin parameter $a$ and the inner radius of the disk $r_{\mathrm{in}}$.
+As in \citet{Komissarov:2006}, in this paper we have chosen the exponents $\kappa = \lambda
+ = 4/3$ and the enthalpy at the disk center $w_{\mathrm{c}} = 1$. That leaves us the magnetization parameter $\beta_{\mathrm{m}_{\mathrm{c}}}
+$, the parameters of the angular momentum distribution $\beta$ and $\gamma$, the black hole spin parameter $a$ and the inner radius of the disk $r_{\mathrm{in}}$.
 This allows us to control the size, shape, thickness and magnetization of the disk.
 
+% \begin{table}
+% \caption{List of models.
+Form left to right the columns report: the black hole spin $a$, the parameters of the angular momentum distribution $\beta$ and $\gamma$, the magnetization parameter $\beta_{\mathrm{m}_{\mathrm{c}}}
+% $ at the disk center, the corresponding radii of the maximum thermal pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential diference between the center and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the disks, $r_{\mathrm{in}}$ and  $r_{\mathrm{out}}$.}
+% \label{table:1}      
+% \centering          
+% \begin{tabular}{c c c c c c  c c c c}
+% \hline\hline       
+%  & $a$ & $\beta$ & $\gamma$ & $\beta_{\mathrm{m}_{\mathrm{c}}}
+% $  & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W$ & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
+% \hline           
+% A1 & $0.5$ & $0.0$ & $0.0$ & $10^{-3}$ &  $5.11$  & $5.51$ & $-6.35 \times 10^{-2}$ & $2.91$ & -- \\ 
+% A2 &           & $0.5$ & $0.5$ &  & $5.55$ &  $5.80$  & $-2.27 \times 10^{-2}$ & $3.20$ & $11.77$\\ 
+% A3  &          & $0.9$ & $0.9$ &  & $5.95$ &  $6.15$  & $-2.96 \times 10^{-3}$ & $3.70$ &  $9.583$\\ 
+% A4  &          & $0.0$ & $0.9$ &  & $5.21$ &  $5.51$  & $-6.35 \times 10^{-2}$ & $2.91$ & $9.680$\\ 
+% A5   &         & $0.9$ & $0.0$ &  & $5.90$ &  $6.10$  & $-2.95 \times 10^{-3}$ & $3.70$ & --\\ 
+%  \hline 
+% B1 & $0.9$ & $0.0$ & $0.0$ & $10^{-3}$ & $2.53$ &  $2.73$  & $-0.129$ & $1.73$ & -- \\ 
+% B2 &           & $0.5$ & $0.5$ &  & $2.81$ &  $2.91$  & $-4.32 \times 10^{-2}$ & $1.86$ & $5.35$\\ 
+% B3  &          & $0.9$ & $0.9$ &  & $3.03$ &  $3.13$  & $-5.39 \times 10^{-3}$ & $2.08$ & $4.52$\\ 
+% B4  &          & $0.0$ & $0.9$ &  & $2.65$ &  $2.80$  & $-0.129$ & $1.732$ & $4.54$\\ 
+% B5   &         & $0.9$ & $0.0$ &  & $3.03$ &  $3.13$  & $-5.39 \times 10^{-3}$ & $2.08$ & -- \\  
+%  \hline 
+% C1 & $0.99$ & $0.0$ & $0.0$ & $10^{-3}$ & $1.46$ & $1.51$ & $-0.246$ & $1.21$ & -- \\ 
+% C2 &             & $0.5$ & $0.5$ &  & $1.56$ &  $1.61$  & $-7.34 \times 10^{-2}$ & $1.26$ & $2.50$\\ 
+% C3  &            & $0.9$ & $0.9$ &  & $1.70$ &  $1.75$  & $-8.53 \times 10^{-3}$ & $1.35$ & $2.25$\\ 
+% C4  &            & $0.0$ & $0.9$ &  & $1.50$ &  $1.57$  & $-0.246$ & $1.21$ & $2.26$\\ 
+% C5   &           & $0.9$ & $0.0$ &  & $1.72$ &  $1.77$  & $-8.53 \times 10^{-3}$ & $1.35$ & --\\ 
+% \hline      
+% \end{tabular}
+% \end{table}
+
 \begin{table}
-\caption{List of models.
-Form left to right the columns report: the black hole spin $a$, the parameters of the angular momentum distribution $\beta$ and $\gamma$, the magnetization parameter $\beta_{\mathrm{c}}$ for which a maximum pressure is achieved, the corresponding radii of the maximum thermal pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential diference between the center and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the disks, $r_{\mathrm{in}}$ and  $r_{\mathrm{out}}$.
-\tf{Complete table.}}
+\caption{List of models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}
+$.
+Form left to right the columns report: the model name (with A, B and C standing for black hole spin $a = 0.5$, $0.9$ and $0.99$ respectively), the parameters of the angular momentum distribution $\beta$ and $\gamma$, , the corresponding radii of the maximum thermal pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential diference between the center and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the disks, $r_{\mathrm{in}}$ and $r_{\mathrm{out}}$.
+\sg{Update table.}}
 \label{table:1}      
 \centering          
-\begin{tabular}{c c c c c c  c c c c}
+\begin{tabular}{c c c c  c c c c}
 \hline\hline       
- & $a$ & $\beta$ & $\gamma$ & $\beta_{\mathrm{c}}$  & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W$ & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
+ & $\beta$ & $\gamma$ & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W$ & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
 \hline           
-A1 & $0.5$ & $0.0$ & $0.0$ &  &  &    &  &  & \\ 
-A2 &           & $0.5$ & $0.5$ &  &  &    &  &  & \\ 
-A3  &          & $0.9$ & $0.9$ &  &  &    &  &  &  \\ 
-A4  &          & $0.0$ & $0.9$ &  &  &    &  &  & \\ 
-A5   &         & $0.9$ & $0.0$ &  &  &    &  &  & \\ 
-A6   &         &           &           &  &  &    &  &  & \\ 
-A7   &         &           &           &  &  &    &  &  &\\ 
+A1 & $0.0$ & $0.0$ &  $7.15$  & $8.14$ & $-6.35 \times 10^{-2}$ & $2.91$ & -- \\ 
+A2 & $0.5$ & $0.5$ & $5.55$ &  $5.80$  & $-2.27 \times 10^{-2}$ & $3.20$ & $11.8$\\ 
+A3 & $0.9$ & $0.9$ & $5.95$ &  $6.15$  & $-2.96 \times 10^{-3}$ & $3.70$ &  $9.58$\\ 
+A4 & $0.0$ & $0.9$ & $5.21$ &  $5.51$  & $-6.35 \times 10^{-2}$ & $2.91$ & $9.68$\\ 
+A5 & $0.9$ & $0.0$ & $5.90$ &  $6.10$  & $-2.95 \times 10^{-3}$ & $3.70$ & --\\ 
  \hline 
-B1 & $0.9$ & $0.0$ & $0.0$ &  &  &    &  &  & \\ 
-B2 &           & $0.5$ & $0.5$ &  &  &    &  &  & \\ 
-B3  &          & $0.9$ & $0.9$ &  &  &    &  &  &  \\ 
-B4  &          & $0.0$ & $0.9$ &  &  &    &  &  & \\ 
-B5   &         & $0.9$ & $0.0$ &  &  &    &  &  & \\ 
-B6   &         &           &           &  &  &    &  &  & \\ 
-B7   &         &           &           &  &  &    &  &  &\\  
+B1 & $0.0$ & $0.0$ & $2.53$ &  $2.73$  & $-0.129$ & $1.73$ & -- \\ 
+B2 & $0.5$ & $0.5$ & $2.81$ &  $2.91$  & $-4.32 \times 10^{-2}$ & $1.86$ & $5.35$\\ 
+B3 & $0.9$ & $0.9$ & $3.03$ &  $3.13$  & $-5.39 \times 10^{-3}$ & $2.08$ & $4.52$\\ 
+B4 & $0.0$ & $0.9$ & $2.65$ &  $2.80$  & $-0.129$ & $1.73$ & $4.54$\\ 
+B5 & $0.9$ & $0.0$ & $3.03$ &  $3.13$  & $-5.39 \times 10^{-3}$ & $2.08$ & -- \\  
  \hline 
-C1 & $0.99$ & $0.0$ & $0.0$ &  &  &    &  &  & \\ 
-C2 &             & $0.5$ & $0.5$ &  &  &    &  &  & \\ 
-C3  &            & $0.9$ & $0.9$ &  &  &    &  &  &  \\ 
-C4  &            & $0.0$ & $0.9$ &  &  &    &  &  & \\ 
-C5   &           & $0.9$ & $0.0$ &  &  &    &  &  & \\ 
-C6   &           &           &           &  &  &    &  &  & \\ 
-C7   &           &           &           &  &  &    &  &  &\\   
+C1 & $0.0$ & $0.0$ & $1.46$ & $1.51$ & $-0.246$ & $1.21$ & -- \\ 
+C2 & $0.5$ & $0.5$ & $1.56$ &  $1.61$  & $-7.34 \times 10^{-2}$ & $1.26$ & $2.50$\\ 
+C3 & $0.9$ & $0.9$ & $1.70$ &  $1.75$  & $-8.53 \times 10^{-3}$ & $1.35$ & $2.25$\\ 
+C4 & $0.0$ & $0.9$ & $1.50$ &  $1.57$  & $-0.246$ & $1.21$ & $2.26$\\ 
+C5 & $0.9$ & $0.0$ & $1.72$ &  $1.77$  & $-8.53 \times 10^{-3}$ & $1.35$ & --\\ 
+\hline      
+\end{tabular}
+\end{table}
+
+\begin{table}
+\caption{List of models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 1
+$.
+Form left to right the columns report: the model name (with A, B and C standing for black hole spin $a = 0.5$, $0.9$ and $0.99$ respectively), the parameters of the angular momentum distribution $\beta$ and $\gamma$, , the corresponding radii of the maximum thermal pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential diference between the center and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the disks, $r_{\mathrm{in}}$ and $r_{\mathrm{out}}$.
+\sg{Update table.}}
+\label{table:3}      
+\centering          
+\begin{tabular}{c c c c  c c c c}
+\hline\hline       
+ & $\beta$ & $\gamma$ & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W$ & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
+\hline           
+A1 & $0.0$ & $0.0$ &  $5.11$  & $5.51$ & $-6.35 \times 10^{-2}$ & $2.91$ & -- \\ 
+A2 & $0.5$ & $0.5$ & $5.55$ &  $5.80$  & $-2.27 \times 10^{-2}$ & $3.20$ & $11.8$\\ 
+A3 & $0.9$ & $0.9$ & $5.95$ &  $6.15$  & $-2.96 \times 10^{-3}$ & $3.70$ &  $9.58$\\ 
+A4 & $0.0$ & $0.9$ & $5.21$ &  $5.51$  & $-6.35 \times 10^{-2}$ & $2.91$ & $9.68$\\ 
+A5 & $0.9$ & $0.0$ & $5.90$ &  $6.10$  & $-2.95 \times 10^{-3}$ & $3.70$ & --\\ 
+ \hline 
+B1 & $0.0$ & $0.0$ & $2.53$ &  $2.73$  & $-0.129$ & $1.73$ & -- \\ 
+B2 & $0.5$ & $0.5$ & $2.81$ &  $2.91$  & $-4.32 \times 10^{-2}$ & $1.86$ & $5.35$\\ 
+B3 & $0.9$ & $0.9$ & $3.03$ &  $3.13$  & $-5.39 \times 10^{-3}$ & $2.08$ & $4.52$\\ 
+B4 & $0.0$ & $0.9$ & $2.65$ &  $2.80$  & $-0.129$ & $1.73$ & $4.54$\\ 
+B5 & $0.9$ & $0.0$ & $3.03$ &  $3.13$  & $-5.39 \times 10^{-3}$ & $2.08$ & -- \\  
+ \hline 
+C1 & $0.0$ & $0.0$ & $1.46$ & $1.51$ & $-0.246$ & $1.21$ & -- \\ 
+C2 & $0.5$ & $0.5$ & $1.56$ &  $1.61$  & $-7.34 \times 10^{-2}$ & $1.26$ & $2.50$\\ 
+C3 & $0.9$ & $0.9$ & $1.70$ &  $1.75$  & $-8.53 \times 10^{-3}$ & $1.35$ & $2.25$\\ 
+C4 & $0.0$ & $0.9$ & $1.50$ &  $1.57$  & $-0.246$ & $1.21$ & $2.26$\\ 
+C5 & $0.9$ & $0.0$ & $1.72$ &  $1.77$  & $-8.53 \times 10^{-3}$ & $1.35$ & --\\ 
+\hline      
+\end{tabular}
+\end{table}
+
+\begin{table}
+\caption{List of models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}
+$.
+Form left to right the columns report: the model name (with A, B and C standing for black hole spin $a = 0.5$, $0.9$ and $0.99$ respectively), the parameters of the angular momentum distribution $\beta$ and $\gamma$, , the corresponding radii of the maximum thermal pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential diference between the center and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the disks, $r_{\mathrm{in}}$ and $r_{\mathrm{out}}$.}
+\label{table:3}      
+\centering          
+\begin{tabular}{c c c c  c c c c}
+\hline\hline       
+ & $\beta$ & $\gamma$ & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W$ & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
+\hline           
+A1 & $0.0$ & $0.0$ &  $5.11$  & $5.51$ & $-6.35 \times 10^{-2}$ & $2.91$ & -- \\ 
+A2 & $0.5$ & $0.5$ & $5.55$ &  $5.80$  & $-2.27 \times 10^{-2}$ & $3.20$ & $12$\\ 
+A3 & $0.9$ & $0.9$ & $5.95$ &  $6.15$  & $-2.96 \times 10^{-3}$ & $3.70$ &  $9.6$\\ 
+A4 & $0.0$ & $0.9$ & $5.21$ &  $5.51$  & $-6.35 \times 10^{-2}$ & $2.91$ & $9.7$\\ 
+A5 & $0.9$ & $0.0$ & $5.90$ &  $6.10$  & $-2.95 \times 10^{-3}$ & $3.70$ & --\\ 
+ \hline 
+B1 & $0.0$ & $0.0$ & $2.53$ &  $2.73$  & $-0.129$ & $1.73$ & -- \\ 
+B2 & $0.5$ & $0.5$ & $2.81$ &  $2.91$  & $-4.32 \times 10^{-2}$ & $1.86$ & $5.4$\\ 
+B3 & $0.9$ & $0.9$ & $3.03$ &  $3.13$  & $-5.39 \times 10^{-3}$ & $2.08$ & $4.5$\\ 
+B4 & $0.0$ & $0.9$ & $2.65$ &  $2.80$  & $-0.129$ & $1.73$ & $4.5$\\ 
+B5 & $0.9$ & $0.0$ & $3.03$ &  $3.13$  & $-5.39 \times 10^{-3}$ & $2.08$ & -- \\  
+ \hline 
+C1 & $0.0$ & $0.0$ & $1.46$ & $1.51$ & $-0.246$ & $1.21$ & -- \\ 
+C2 & $0.5$ & $0.5$ & $1.56$ &  $1.61$  & $-7.34 \times 10^{-2}$ & $1.26$ & $2.5$\\ 
+C3 & $0.9$ & $0.9$ & $1.70$ &  $1.75$  & $-8.53 \times 10^{-3}$ & $1.35$ & $2.3$\\ 
+C4 & $0.0$ & $0.9$ & $1.50$ &  $1.57$  & $-0.246$ & $1.21$ & $2.3$\\ 
+C5 & $0.9$ & $0.0$ & $1.72$ &  $1.77$  & $-8.53 \times 10^{-3}$ & $1.35$ & --\\ 
 \hline      
@@
 \includegraphics[scale=0.16]{figures/fig2_5_3.pdf}
-\caption{Isodensity distributions (in logarithm scale) for a representative sample of our models.
+\caption{Isodensity distributions for a representative sample of our models.
 From left to right the columns correspond to increasing values of the black hole spin: $a=0.5$, 0.9 and 0.99.
@@
 \includegraphics[scale=0.16]{figures/fig3c.pdf}
-\caption{Effects of the magnetization in the structure of the disk. From left to right the values are $\beta_{\rm c}=10^3$, 1, and $10^{-3}$.}
+\caption{Effects of the magnetization in the structure of the disk. From left to right the values are $\beta_{\mathrm{m}_{\mathrm{c}}}
+=10^3$, 1, and $10^{-3}$.}
 \label{magnetization}%
@@
 This is shown in Figure~\ref{komissarov}, which corresponds to the same constant specific angular momentum model A presented by~\citet{Komissarov:2006}.
-The parameters of this model are $a=0.9$, $\beta_c=0.1$, and $l=2.8$.
-\tf{Is this the value of $l$ we use?}
+The parameters of this model are $a=0.9$, $\beta_{\mathrm{m}_{\mathrm{c}}}=0.1$, and $l=2.8$.
 The visual comparison shows that our approach can reproduce those previous results with good agreement.
@@
 These two figures can be directly compared with Fig.~3 of~\citet{Komissarov:2006}.
-\tf{There are some slight differences though.
-Is this because we do not use the exact same value of the angular momentum?}
+It is relevant to mention that very small changes in the inner radius $r_{\mathrm{in}}$ have a significant effect on the maximum value of the density, that explains the small differences between our figures and the ones presented in~\citet{Komissarov:2006}.
 
@@
 \includegraphics[scale=0.2]{figures/fig4.pdf}
-\caption{Radial profiles of the density in the equatorial plane for $\beta=10^3$ (black curve), 1 (blue curve), and $10^{-3}$ (green curve). \tf{Check color code.}}
+\caption{Radial profiles of the density in the equatorial plane for $\beta=10^3$ (black curve), 1 (blue curve), and $10^{-3}$ (green curve). }
 \label{magnetization-profile}
@@
 \includegraphics[scale=0.2]{figures/fig5.pdf}
-\caption{Radial profiles at the equatorial plane for models with $a=0.9$, $\beta_{\rm c}=10^{-3}$, and same combination of the $\gamma$ and $\beta$ parameters as in the rows of Fig.~\ref{models} (the specific values are indicated in the legend).
-\tf{Include a legend indicating the particular values of these two parameters.}}
+\caption{Radial profiles at the equatorial plane for models with $a=0.9$, $\beta_{\mathrm{m}_{\mathrm{c}}}
+=10^{-3}$, and same combination of the $\gamma$ and $\beta$ parameters as in the rows of Fig.~\ref{models} (the specific values are indicated in the legend).}
 \label{more-profile}
@@
 \includegraphics[scale=0.16]{figures/fig6c.pdf}
-\caption{Caption. \tf{Complete the caption.}}
+\caption{The left panel shows the variation of the value for the maximum density with repect to the logarithm of the magnetization parameter.
+The solid, dashed and dashed lines refer to $a = 0.99$, $0.9$ and $0.5$ respectively and the colour code refers to the models shown in the legend.
+The middle panel shows the variation of the location of the density maximum (and thermal pressure) with respect to the logarithm of the magnetization parameter for the three models shown in the legend with $a = 0.99$.
+The right panel shows (also for $a = 0.99$) the variation of the location of the maximum of the magnetic pressure maximum with respect to the logarithm of the magnetization parameter.}
            \label{max-vs-magnetization}%
@@
 
-A representative sample of the isodensity surfaces (in logarithm scale) for some of our models appears in Figure~\ref{models}.
+A representative sample of the isodensity surfaces for some of our models appears in Figure~\ref{models}.
 From left to right the columns of this figure correspond to increasing values of the black hole spin, namely, $a=0.5$, 0.9 and 0.99, while from top to bottom the rows correspond to different combinations of the $\gamma$ and $\beta$ parameters that characterize the ansatz for the angular momentum distribution of~\citet{Qian:2009} (the particular values are indicated in the caption of the figure).
-The value of the magnetization parameter for all models in this figure is $\beta_{\rm c}=10^{-3}$.
-\tf{Is that correct?} A rapid inspection shows that the structure of the disks noticeable changes when the parameters change.
+The value of the magnetization parameter for all models in this figure is $\beta_{\mathrm{m}_{\mathrm{c}}}
+=10^{-3}$.
+A rapid inspection shows that the structure of the disks noticeable changes when the parameters change.
 Notice that the spatial scale in all of the plots of this figure has been chosen so as to facilitate the visualization of the disks (which can be fairly small in some cases) and, as such, is different in each plot.
 A typical Polish doughnut is represented by the model in the top-left panel.
-As the black hole spin increases, the maximum of the density (and of the pressure), which yields the center of the disk, moves inwards for all values of $\gamma$ and $\beta$.
-For $\gamma=0$ the disks are infinite, irrespective of the value of $a$.
+As the black hole spin increases, the disks are closer to the black hole and its relative size with respect to the black hole is smaller for all values of $\gamma$ and $\beta$.
+For $\gamma=0$ the disks are infinite, irrespective of the value of $a$ and $\beta$.
 As $\gamma$ and $\beta$ increase from 0 to 0.9 (compare the three top rows) the disks become significantly thinner and radially smaller (see also Fig.~\ref{more-profile} below).
-\tf{Check if the description is correct.
-Add further relevant information.}
+It is also interesting to note that the maximum value of the density is higher (with respect to the value at the disk center) as the spin increases.
 
-Figure~\ref{magnetization} shows the effects of changing the parameter $\beta_{\rm c}$ (the magnetization) in the structure of the disks.
-From left to right the values plotted in each panel are $\beta_{\rm c}=10^3$, 1, and $10^{-3}$.
-The model chosen corresponds to $a=0.9$ and $\gamma=\beta=0.5$.
-The larger the value of $\beta_{\rm c}$ the less important the effects of the magnetization in the disk structure.
+Figure~\ref{magnetization} shows the effects of changing the parameter $\beta_{\mathrm{m}_{\mathrm{c}}}
+$ (the magnetization) in the structure of the disks. From left to right the values plotted in each panel are $\beta_{\mathrm{m}_{\mathrm{c}}}
+=10^3$, 1, and $10^{-3}$. The model chosen corresponds to $a=0.9$ and $\gamma=\beta=0.5$. The larger the value of $\beta_{\mathrm{m}_{\mathrm{c}}}
+$ the less important the effects of the magnetization in the disk structure.
 Figure~\ref{magnetization} shows that for the kind of magnetic field distribution we are considering, the effects of magnetization are minor.
-The disk structure remains fairly similar for all values of $\beta_{\rm c}$ and the only quantitative differences are found in the location of the centre of the disk (which moves inward with decreasing $\beta_{\rm c}$) and of the range of variation of the isodensity contours (the maximum being slightly larger with decreasing $\beta_{\rm c}$).
-This can be more clearly visualized in Figure~\ref{magnetization-profile} which displays the radial profile at the equatorial plane of the logarithm of the density \tf{Is it $\log\rho$ or $\rho$?} for the same three cases plotted in Fig.~\ref{magnetization}.
-\tf{Check if the description is correct.
-Add further relevant information.}
+The disk structure remains fairly similar for all values of $\beta_{\mathrm{m}_{\mathrm{c}}}
+$ and the only quantitative differences are found in the location of the centre of the disk (which moves inward with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}
+$) and of the range of variation of the isodensity contours (the maximum being slightly larger with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}
+$).
+This can be more clearly visualized in Figure~\ref{magnetization-profile} which displays the radial profile at the equatorial plane of the density for the same three cases plotted in Fig.~\ref{magnetization}.
 
-Next, we show in Fig.~\ref{more-profile} the corresponding radial profiles at the equatorial plane for the models with black hole spin $a=0.9$.
-We consider the case $\beta_{\rm c}=10^{-3}$ (highest magnetization) and the same combination of the $\gamma$ and $\beta$ parameters that we employed in Fig.~\ref{models}.
+Next, we show in Fig.~\ref{more-profile} the corresponding radial profiles at the equatorial plane for the models with black hole spin $a=0.9$. We consider the case $\beta_{\mathrm{m}_{\mathrm{c}}}
+=10^{-3}$ (highest magnetization) and the same combination of the $\gamma$ and $\beta$ parameters that we employed in Fig.~\ref{models}.
 Therefore, this plot depicts the radial profiles of the models occupying the central column of Fig.~\ref{models}.
@@
 As mentioned in the description of Fig.~\ref{models} as $\gamma$ and $\beta$ increase from 0 to 0.9 (compare black, blue, and green curves) the disks become gradually smaller.
-At the same time, the radial location of the centre increases and the maximum value of the central density (and pressure) decreases.
+At the same time, the radial location of the density maximum increases and the maximum value of the central density (and pressure) decreases.
 It is worth noticing that the radial profiles of some of the models overlap below a certain radius.
-More precisely, the black and red curves overlap below $r\sim 4$ and also the green and orange curves.
-\tf{Check if the description is correct.
-Add further relevant information.}
+More precisely, the black and red curves overlap below $r\sim r_{\mathrm{c}}$ (which corresponds to $\rho \sim 1$) and also the green and orange curves.
+Also, this figure clearly shows that, besides modifying the thickness of the disk, $\beta$ is the parameter which determines the value of the density (and pressure) maximum.
+On the other hand, $\gamma$ is only relevant for its radial size.
 
-In order to provide a quantitative comparison of the structural differences that appear along the sequence of equilibrium models, we plot in Fig.~\ref{max-vs-magnetization} the variation of the maximum of the density (left panel), the radial location of the maximum of the thermal pressure (middle panel), and the radial location of the maximum of the magnetic pressure (right panel) as a function of the magnetization parameter $\beta_{\rm c}$.
+In order to provide a quantitative comparison of the structural differences that appear along the sequence of equilibrium models, we plot in Fig.~\ref{max-vs-magnetization} the variation of the maximum of the density (left panel), the radial location of the maximum of the thermal pressure (middle panel), and the radial location of the maximum of the magnetic pressure (right panel) as a function of the magnetization parameter $\beta_{\mathrm{m}_{\mathrm{c}}}
+$.
 All quantities plotted are measured at the equatorial plane.
@@
 Correspondingly, the colour indicates the value of $\beta$ and $\gamma$ used, namely, red curves correspond to $\gamma=\beta=0$, the blue ones to $\gamma=\beta=0.5$, and the black ones to $\gamma=\beta=0.9$.
-\tf{Is my interpretation of the line type and colour code correct?} All curves show the same monotonically decreasing trend with $\beta_{\rm c}$: for small enough and large enough values of $\beta_{\rm c}$ the value of the density maximum does not change.
-However, in the interval $10^{-2}\le \beta_{\rm c} \le 10^{2}$, $\rho_{\rm max}$ changes abruptly.
-The larger the black hole spin the larger the drop in the maximum of the density.
-For sufficiently large values of $\beta_{\rm c}$ (small magnetization) the value of $\rho_{\rm max}$ stays constant to the same value irrespective of the black hole rotation.
+All curves show the same monotonically decreasing trend with $\beta_{\mathrm{m}_{\mathrm{c}}}
+$: for small enough and large enough values of $\beta_{\mathrm{m}_{\mathrm{c}}}
+$ the value of the density maximum does not change. However, in the interval $10^{-2}\le \beta_{\mathrm{m}_{\mathrm{c}}}
+ \le 10^{2}$, $\rho_{\rm max}$ changes abruptly. The larger the black hole spin the larger the drop in the maximum of the density. For sufficiently large values of $\beta_{\mathrm{m}_{\mathrm{c}}}
+$ (small magnetization) the value of $\rho_{\rm max}$ stays constant to the same value irrespective of the black hole rotation.
 
-In the middle panel of Fig.~\ref{max-vs-magnetization} we show the radial location of the maximum of the thermal pressure as a function of $\beta_{\rm c}$.
-The black hole spin is $a=0.99$ \tf{is that correct?} and the values of $\beta$ and $\gamma$ are indicated in the legend.
-For all values of $\beta$ and $\gamma$, the maximum of the disk thermal pressure decreases with decreasing $\beta_{\rm c}$.
-Below $\beta_{\rm c}\sim 10^{-3}$ the location of the maximum does not change.
-The panel also shows that above $\beta_{\rm c}\sim 10^{3}$ the constant value of $r_{\rm max}$ is the same irrespective of $\beta$ and $\gamma$.
+In the middle panel of Fig.~\ref{max-vs-magnetization} we show the radial location of the maximum of the thermal pressure as a function of $\beta_{\mathrm{m}_{\mathrm{c}}}
+$.
+The black hole spin is $a=0.99$ and the values of $\beta$ and $\gamma$ are indicated in the legend.
+For all values of $\beta$ and $\gamma$, the maximum of the disk thermal pressure decreases with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}
+$. Below $\beta_{\mathrm{m}_{\mathrm{c}}}
+\sim 10^{-3}$ the location of the maximum does not change. The panel also shows that above $\beta_{\mathrm{m}_{\mathrm{c}}}
+\sim 10^{3}$ the constant value of $r_{\rm max}$ is the same irrespective of $\beta$ and $\gamma$ as we expected, because for purely hydrodynamic disks, $r_{\mathrm{max}} = r_{\mathrm{c}}$.
 
-The dependence of the location of the maximum of the magnetic pressure with $\beta_{\rm c}$ is shown in the right panel of Fig.~\ref{max-vs-magnetization}.
-While the maximum of the magnetic pressure also decreases with decreasing $\beta_{\rm c}$, the constant value achieved for values above $\beta_{\rm c}\sim 10^{3}$ does depend on the specific values of $\beta$ and $\gamma$.
+The dependence of the location of the maximum of the magnetic pressure with $\beta_{\mathrm{m}_{\mathrm{c}}}
+$ is shown in the right panel of Fig.~\ref{max-vs-magnetization}. While the maximum of the magnetic pressure also decreases with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}
+$, the constant value achieved for values above $\beta_{\mathrm{m}_{\mathrm{c}}}
+\sim 10^{3}$ does depend on the specific values of $\beta$ and $\gamma$.
 It must be noted that, for the magnetic pressure, all models seem to cross at roughly the same value of $r_{\rm max}$, as it is more clearly shown in the inset.
+
+It is relevant to add that in the left and middle panels, we do not show the data for the models with $\beta \neq \gamma$ as they coincide with the respective models with the same value of $\beta$.
+Also, the middle and right panels are only shown for $a=0.99$ because changing the spin parameter of the black hole only yield a change of scale, so if we choose the range of the graph accordingly they are identical irrespective of the value of $a$.
 
@@
 
-We have discussed the properties of the new models and their dependence on the initial parameters. \tf{Expound on this presenting a short summary of our main findings.}
+We have discussed the properties of the new models and their dependence on the initial parameters.
+We have found that the solutions we have built exhibit a saturation-like behaviour for magnetizations over $\beta_{\mathrm{m}_{\mathrm{c}}} \sim 10^{3}$ and below $\beta_{\mathrm{m}_{\mathrm{c}}} \sim 10^{-3}$, so these can be considered as the purely hydrodynamic and MHD limit cases.
+Also, we have shown the effect of changing of the $\beta$ and $\gamma$ parameters beyond the purely morphological ones in~\citet{Qian:2009}.
 
-\tf{To close the paper show a short outline of potential future work we plan to attempt with this research: inclusion of self-gravity as in the work of Stergioulas, and construction of disks around hairy black holes.}
+In the near future, we plan to extend this work following two paths: i) including the self-gravity of the disks as in the work of~\citet{Stergioulas:2011} and ii) constructing accretions disks around the hairy (both scalar and Proca) black holes described in~\citet{Herdeiro:2014} and~\citet{Herdeiro:2016}.
 

### 2017-03-14 paper.tex
Tables 1 & 2 updated. Figure 1 updated.

@@
 \includegraphics[scale=0.16]{figures/fig1c.pdf}
-\caption{\sg{update figures.}Comparison with Komissarov's solution for a constant angular momentum model.
+\caption{Comparison with Komissarov's solution for a constant angular momentum model.
 The left panel shows the density distribution in logarithm scale for all radii and all angles while the middle and right panels show, respectively, the angular profile of the logarithm of the density at the centre of the disk and the radial profile of the density at the equatorial plane.}
@@
 $.
-Form left to right the columns report: the model name (with A, B and C standing for black hole spin $a = 0.5$, $0.9$ and $0.99$ respectively), the parameters of the angular momentum distribution $\beta$ and $\gamma$, , the corresponding radii of the maximum thermal pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential diference between the center and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the disks, $r_{\mathrm{in}}$ and $r_{\mathrm{out}}$.
-\sg{Update table.}}
+Form left to right the columns report: the model name (with A, B and C standing for black hole spin $a = 0.5$, $0.9$ and $0.99$ respectively), the parameters of the angular momentum distribution $\beta$ and $\gamma$, , the corresponding radii of the maximum thermal pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential diference between the center and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the disks, $r_{\mathrm{in}}$ and $r_{\mathrm{out}}$.}
 \label{table:1}      
@@
 \hline\hline       
- & $\beta$ & $\gamma$ & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W$ & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
+ & $\beta$ & $\gamma$ & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W (\times 10^{-2})$ & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
 \hline           
-A1 & $0.0$ & $0.0$ &  $7.15$  & $8.14$ & $-6.35 \times 10^{-2}$ & $2.91$ & -- \\ 
-A2 & $0.5$ & $0.5$ & $5.55$ &  $5.80$  & $-2.27 \times 10^{-2}$ & $3.20$ & $11.8$\\ 
-A3 & $0.9$ & $0.9$ & $5.95$ &  $6.15$  & $-2.96 \times 10^{-3}$ & $3.70$ &  $9.58$\\ 
-A4 & $0.0$ & $0.9$ & $5.21$ &  $5.51$  & $-6.35 \times 10^{-2}$ & $2.91$ & $9.68$\\ 
-A5 & $0.9$ & $0.0$ & $5.90$ &  $6.10$  & $-2.95 \times 10^{-3}$ & $3.70$ & --\\ 
+A1 & $0.0$ & $0.0$ & $7.15$ &  $8.14$  & $-6.35$ & $2.91$ & -- \\ 
+A2 & $0.5$ & $0.5$ & $7.15$ &  $7.65$  & $-2.27$ & $3.20$ & $11.8$\\ 
+A3 & $0.9$ & $0.9$ & $7.15$ &  $7.45$  & $-0.30$ & $3.70$ &  $9.58$\\ 
+A4 & $0.0$ & $0.9$ & $7.15$ &  $8.32$  & $-6.35$ & $2.91$ & $9.68$\\ 
+A5 & $0.9$ & $0.0$ & $7.15$ &  $7.28$  & $-0.30$ & $3.70$ & --\\ 
  \hline 
-B1 & $0.0$ & $0.0$ & $2.53$ &  $2.73$  & $-0.129$ & $1.73$ & -- \\ 
-B2 & $0.5$ & $0.5$ & $2.81$ &  $2.91$  & $-4.32 \times 10^{-2}$ & $1.86$ & $5.35$\\ 
-B3 & $0.9$ & $0.9$ & $3.03$ &  $3.13$  & $-5.39 \times 10^{-3}$ & $2.08$ & $4.52$\\ 
-B4 & $0.0$ & $0.9$ & $2.65$ &  $2.80$  & $-0.129$ & $1.73$ & $4.54$\\ 
-B5 & $0.9$ & $0.0$ & $3.03$ &  $3.13$  & $-5.39 \times 10^{-3}$ & $2.08$ & -- \\  
+B1 & $0.0$ & $0.0$ & $3.59$ &  $3.98$  & $-12.9$ & $1.73$ & -- \\ 
+B2 & $0.5$ & $0.5$ & $3.59$ &  $3.83$  & $-4.32$ & $1.86$ & $5.35$\\ 
+B3 & $0.9$ & $0.9$ & $3.59$ &  $3.73$  & $-0.54$ & $2.08$ & $4.52$\\ 
+B4 & $0.0$ & $0.9$ & $3.59$ &  $3.85$  & $-12.9$ & $1.73$ & $4.54$\\ 
+B5 & $0.9$ & $0.0$ & $3.59$ &  $3.81$  & $-0.54$ & $2.08$ & -- \\  
  \hline 
-C1 & $0.0$ & $0.0$ & $1.46$ & $1.51$ & $-0.246$ & $1.21$ & -- \\ 
-C2 & $0.5$ & $0.5$ & $1.56$ &  $1.61$  & $-7.34 \times 10^{-2}$ & $1.26$ & $2.50$\\ 
-C3 & $0.9$ & $0.9$ & $1.70$ &  $1.75$  & $-8.53 \times 10^{-3}$ & $1.35$ & $2.25$\\ 
-C4 & $0.0$ & $0.9$ & $1.50$ &  $1.57$  & $-0.246$ & $1.21$ & $2.26$\\ 
-C5 & $0.9$ & $0.0$ & $1.72$ &  $1.77$  & $-8.53 \times 10^{-3}$ & $1.35$ & --\\ 
+C1 & $0.0$ & $0.0$ & $1.98$ &  $2.28$  & $-24.6$ & $1.21$ & -- \\ 
+C2 & $0.5$ & $0.5$ & $1.98$ &  $2.09$  & $-7.34$ & $1.26$ & $2.50$\\ 
+C3 & $0.9$ & $0.9$ & $1.98$ &  $2.04$  & $-0.85$ & $1.35$ & $2.25$\\ 
+C4 & $0.0$ & $0.9$ & $1.98$ &  $2.10$  & $-24.6$ & $1.21$ & $2.26$\\ 
+C5 & $0.9$ & $0.0$ & $1.98$ &  $2.08$  & $-0.85$ & $1.35$ & --\\ 
 \hline      
@@
 $.
-Form left to right the columns report: the model name (with A, B and C standing for black hole spin $a = 0.5$, $0.9$ and $0.99$ respectively), the parameters of the angular momentum distribution $\beta$ and $\gamma$, , the corresponding radii of the maximum thermal pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential diference between the center and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the disks, $r_{\mathrm{in}}$ and $r_{\mathrm{out}}$.
-\sg{Update table.}}
+Form left to right the columns report: the model name (with A, B and C standing for black hole spin $a = 0.5$, $0.9$ and $0.99$ respectively), the parameters of the angular momentum distribution $\beta$ and $\gamma$, , the corresponding radii of the maximum thermal pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential diference between the center and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the disks, $r_{\mathrm{in}}$ and $r_{\mathrm{out}}$.}
 \label{table:3}      
@@
 \hline\hline       
- & $\beta$ & $\gamma$ & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W$ & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
+ & $\beta$ & $\gamma$ & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W (\times 10^{-2})$ & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
 \hline           
-A1 & $0.0$ & $0.0$ &  $5.11$  & $5.51$ & $-6.35 \times 10^{-2}$ & $2.91$ & -- \\ 
-A2 & $0.5$ & $0.5$ & $5.55$ &  $5.80$  & $-2.27 \times 10^{-2}$ & $3.20$ & $11.8$\\ 
-A3 & $0.9$ & $0.9$ & $5.95$ &  $6.15$  & $-2.96 \times 10^{-3}$ & $3.70$ &  $9.58$\\ 
-A4 & $0.0$ & $0.9$ & $5.21$ &  $5.51$  & $-6.35 \times 10^{-2}$ & $2.91$ & $9.68$\\ 
-A5 & $0.9$ & $0.0$ & $5.90$ &  $6.10$  & $-2.95 \times 10^{-3}$ & $3.70$ & --\\ 
+A1 & $0.0$ & $0.0$ & $6.00$ &  $6.49$  & $-6.35$ & $2.91$ & -- \\ 
+A2 & $0.5$ & $0.5$ & $6.25$ &  $6.66$  & $-2.27$ & $3.20$ & $11.8$\\ 
+A3 & $0.9$ & $0.9$ & $6.50$ &  $6.80$  & $-0.30$ & $3.70$ &  $9.58$\\ 
+A4 & $0.0$ & $0.9$ & $6.00$ &  $6.49$  & $-6.35$ & $2.91$ & $9.68$\\ 
+A5 & $0.9$ & $0.0$ & $6.50$ &  $6.80$  & $-0.30$ & $3.70$ & --\\ 
  \hline 
-B1 & $0.0$ & $0.0$ & $2.53$ &  $2.73$  & $-0.129$ & $1.73$ & -- \\ 
-B2 & $0.5$ & $0.5$ & $2.81$ &  $2.91$  & $-4.32 \times 10^{-2}$ & $1.86$ & $5.35$\\ 
-B3 & $0.9$ & $0.9$ & $3.03$ &  $3.13$  & $-5.39 \times 10^{-3}$ & $2.08$ & $4.52$\\ 
-B4 & $0.0$ & $0.9$ & $2.65$ &  $2.80$  & $-0.129$ & $1.73$ & $4.54$\\ 
-B5 & $0.9$ & $0.0$ & $3.03$ &  $3.13$  & $-5.39 \times 10^{-3}$ & $2.08$ & -- \\  
+B1 & $0.0$ & $0.0$ & $3.02$ &  $3.26$  & $-12.9$ & $1.73$ & -- \\ 
+B2 & $0.5$ & $0.5$ & $3.16$ &  $3.35$  & $-4.32$ & $1.86$ & $5.35$\\
+B3 & $0.9$ & $0.9$ & $3.29$ &  $3.43$  & $-0.54$ & $2.08$ & $4.52$\\ 
+B4 & $0.0$ & $0.9$ & $3.02$ &  $3.26$  & $-12.9$ & $1.73$ & $4.54$\\  
+B5 & $0.9$ & $0.0$ & $3.29$ &  $3.43$  & $-0.54$ & $2.08$ & -- \\ 
  \hline 
-C1 & $0.0$ & $0.0$ & $1.46$ & $1.51$ & $-0.246$ & $1.21$ & -- \\ 
-C2 & $0.5$ & $0.5$ & $1.56$ &  $1.61$  & $-7.34 \times 10^{-2}$ & $1.26$ & $2.50$\\ 
-C3 & $0.9$ & $0.9$ & $1.70$ &  $1.75$  & $-8.53 \times 10^{-3}$ & $1.35$ & $2.25$\\ 
-C4 & $0.0$ & $0.9$ & $1.50$ &  $1.57$  & $-0.246$ & $1.21$ & $2.26$\\ 
-C5 & $0.9$ & $0.0$ & $1.72$ &  $1.77$  & $-8.53 \times 10^{-3}$ & $1.35$ & --\\ 
+C1 & $0.0$ & $0.0$ & $1.68$ &  $1.80$  & $-0.246$ & $1.21$ & -- \\ 
+C2 & $0.5$ & $0.5$ & $1.77$ &  $1.86$  & $-7.34$ & $1.26$ & $2.50$\\  
+C3 & $0.9$ & $0.9$ & $1.84$ &  $1.91$  & $-0.85$ & $1.35$ & $2.25$\\ 
+C4 & $0.0$ & $0.9$ & $1.68$ &  $1.80$  & $-24.6$ & $1.21$ & $2.26$\\ 
+C5 & $0.9$ & $0.0$ & $1.84$ &  $1.91$  & $-0.85$ & $1.35$ & --\\ 
 \hline      
@@
 \hline\hline       
- & $\beta$ & $\gamma$ & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W$ & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
+ & $\beta$ & $\gamma$ & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W (\times 10^{-2})$ & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
 \hline           
-A1 & $0.0$ & $0.0$ &  $5.11$  & $5.51$ & $-6.35 \times 10^{-2}$ & $2.91$ & -- \\ 
-A2 & $0.5$ & $0.5$ & $5.55$ &  $5.80$  & $-2.27 \times 10^{-2}$ & $3.20$ & $12$\\ 
-A3 & $0.9$ & $0.9$ & $5.95$ &  $6.15$  & $-2.96 \times 10^{-3}$ & $3.70$ &  $9.6$\\ 
-A4 & $0.0$ & $0.9$ & $5.21$ &  $5.51$  & $-6.35 \times 10^{-2}$ & $2.91$ & $9.7$\\ 
-A5 & $0.9$ & $0.0$ & $5.90$ &  $6.10$  & $-2.95 \times 10^{-3}$ & $3.70$ & --\\ 
+A1 & $0.0$ & $0.0$ & $5.11$ &  $5.51$  & $-6.35$ & $2.91$ & -- \\ 
+A2 & $0.5$ & $0.5$ & $5.55$ &  $5.80$  & $-2.27$ & $3.20$ & $11.8$\\ 
+A3 & $0.9$ & $0.9$ & $5.95$ &  $6.15$  & $-0.30$ & $3.70$ &  $9.58$\\ 
+A4 & $0.0$ & $0.9$ & $5.21$ &  $5.51$  & $-6.35$ & $2.91$ & $9.68$\\  
+A5 & $0.9$ & $0.0$ & $5.90$ &  $6.10$  & $-0.30$ & $3.70$ & --\\
  \hline 
-B1 & $0.0$ & $0.0$ & $2.53$ &  $2.73$  & $-0.129$ & $1.73$ & -- \\ 
-B2 & $0.5$ & $0.5$ & $2.81$ &  $2.91$  & $-4.32 \times 10^{-2}$ & $1.86$ & $5.4$\\ 
-B3 & $0.9$ & $0.9$ & $3.03$ &  $3.13$  & $-5.39 \times 10^{-3}$ & $2.08$ & $4.5$\\ 
-B4 & $0.0$ & $0.9$ & $2.65$ &  $2.80$  & $-0.129$ & $1.73$ & $4.5$\\ 
-B5 & $0.9$ & $0.0$ & $3.03$ &  $3.13$  & $-5.39 \times 10^{-3}$ & $2.08$ & -- \\  
+B1 & $0.0$ & $0.0$ & $2.53$ &  $2.73$  & $-12.9$ & $1.73$ & -- \\ 
+B2 & $0.5$ & $0.5$ & $2.81$ &  $2.91$  & $-4.32$ & $1.86$ & $5.35$\\
+B3 & $0.9$ & $0.9$ & $3.03$ &  $3.13$  & $-0.54$ & $2.08$ & $4.52$\\  
+B4 & $0.0$ & $0.9$ & $2.65$ &  $2.80$  & $-12.9$ & $1.73$ & $4.54$\\ 
+B5 & $0.9$ & $0.0$ & $3.03$ &  $3.13$  & $-0.54$ & $2.08$ & -- \\  
  \hline 
-C1 & $0.0$ & $0.0$ & $1.46$ & $1.51$ & $-0.246$ & $1.21$ & -- \\ 
-C2 & $0.5$ & $0.5$ & $1.56$ &  $1.61$  & $-7.34 \times 10^{-2}$ & $1.26$ & $2.5$\\ 
-C3 & $0.9$ & $0.9$ & $1.70$ &  $1.75$  & $-8.53 \times 10^{-3}$ & $1.35$ & $2.3$\\ 
-C4 & $0.0$ & $0.9$ & $1.50$ &  $1.57$  & $-0.246$ & $1.21$ & $2.3$\\ 
-C5 & $0.9$ & $0.0$ & $1.72$ &  $1.77$  & $-8.53 \times 10^{-3}$ & $1.35$ & --\\ 
+C1 & $0.0$ & $0.0$ & $1.46$ &  $1.51$  & $-24.6$ & $1.21$ & -- \\ 
+C2 & $0.5$ & $0.5$ & $1.56$ &  $1.61$  & $-7.34$ & $1.26$ & $2.50$\\ 
+C3 & $0.9$ & $0.9$ & $1.70$ &  $1.75$  & $-0.85$ & $1.35$ & $2.25$\\ 
+C4 & $0.0$ & $0.9$ & $1.50$ &  $1.57$  & $-24.6$ & $1.21$ & $2.26$\\ 
+C5 & $0.9$ & $0.0$ & $1.72$ &  $1.77$  & $-0.85$ & $1.35$ & --\\ 
 \hline      

### 2017-03-19 paper.tex
Final version

@@
-%                                                                 aa.dem
-% AA vers. 9.1, LaTeX class for Astronomy & Astrophysics
-% demonstration file
-%                                                       (c) EDP Sciences
-%-----------------------------------------------------------------------
-%
-%\documentclass[referee]{aa} % for a referee version
-%\documentclass[onecolumn]{aa} % for a paper on 1 column  
-%\documentclass[longauth]{aa} % for the long lists of affiliations 
-%\documentclass[letter]{aa} % for the letters 
-%\documentclass[bibyear]{aa} % if the references are not structured 
-%                              according to the author-year natbib style
-
-%
 \documentclass{aa}
@@
 
-\title{Magnetized Polish doughnuts revisited}
+\title{Magnetised Polish doughnuts revisited}
 
 \author{Sergio Gimeno-Soler\inst{1}   \and Jos\'e A.~Font\inst{1,2} }
-
-   \institute{Departamento de Astronom\'{\i}a y Astrof\'{\i}sica, Universitat de Val\`encia, Dr. Moliner 50, 46100, Burjassot (Val\`encia), Spain.\\
-              \email{sergiso@alumni.uv.es}
+\institute{Departamento de Astronom\'{\i}a y Astrof\'{\i}sica, Universitat de Val\`encia, Dr. Moliner 50, 46100, Burjassot (Val\`encia), Spain.\\\email{sergiso@alumni.uv.es}
 \and
@@
   \abstract
-{We discuss new sequences of magnetized, equilibrium tori around Kerr black holes by combining two approaches previously considered in the literature.
-Our approach assumes that the test-fluid approximation holds, hence we neglect the self-gravity of the fluid.
+{We discuss a procedure to build new sequences of magnetised, equilibrium tori around Kerr black holes which combines two approaches previously considered in the literature.
+For simplicity we assume that the test-fluid approximation holds, and hence we neglect the self-gravity of the fluid.
 The models are built assuming a particular form of the angular momentum distribution from which the location and morphology of surfaces of equal pressure can be computed.
-This ansatz includes the  constant angular momentum case originally employed in the construction of thick tori - or Polish doughnuts - and has already been used to build equilibrium sequences of purely hydrodynamical models.
+This ansatz includes, in particular, the  constant angular momentum case originally employed in the construction of thick tori -- or Polish doughnuts -- and it has already been used to build equilibrium sequences of purely hydrodynamical models.
 We discuss the properties of the new models and their dependence on the initial parameters.
@@
 
-   \keywords{accretion, accretion disks -- black hole physics -- magnetohydrodynamics (MHD)}
+   \keywords{accretion, accretion discs -- black hole physics -- magnetohydrodynamics (MHD)}
 
@@
 
-% From Qian et al: 
-% We construct a new family of analytic models of black hole accretion disks in dynamical equilibria. 
-% Our construction is based on assuming distributions of angular momentum and entropy. For a 
-% particular choice of the distribution of angular momentum, we calculate the shapes of equipressure 
-% surfaces. The equipressure surfaces we find are similar to those in thick, slim and thin disks, and
-% to those in ADAFs.
-% Models of tori described here may be useful not only for accretion
-% disks but also for tori that formin the latest stages of neutron
-% star binary mergers. This is relevant for gamma ray bursts (Witt
-% et al. 1994) and gravitational waves (Baiotti et al. 2008).
-
-% From Komissarov:
-% The dynamics of accretion discs around galactic and extragalactic black holes may be influenced
-% by their magnetic field. In this paper, we generalize the fully relativistic theory of
-% stationary axisymmetric tori in Kerr metric of Abramowicz, Jaroszynski&Sikora by including
-% strong toroidal magnetic field and construct analytic solutions for barotropic tori with constant
-% angular momentum. This development is particularly important for the general relativistic
-% computational magnetohydrodynamics that suffers from the lack of exact analytic solutions
-% that are needed to test computer codes.
-
 Matter accretion on to black holes is the most efficient form of energy production known in nature. The conversion of the
 gravitational energy of the infalling matter into heat and radiation may reach efficiencies of about 43\% in the case of maximally rotating (Kerr) black holes.
-For this reason, systems formed by a black hole surrounded by an accretion disk are deemed responsible for many of the most energetic astronomical phenomena observed in the cosmos.
-In particular, (geometrically) thick accretion disks (or tori) are believed to be present in quasars and other active galactic nuclei, some 
-X-ray binaries and microquasars, as well as in the central engine of gamma-ray bursts.
+For this reason, systems formed by a black hole surrounded by an accretion disc are deemed responsible for many of the most energetic astronomical phenomena observed in the cosmos.
+In particular, (geometrically) thick accretion discs (or tori) are believed to be present in quasars and other active galactic nuclei, some X-ray binaries and microquasars, as well as in the central engine of gamma-ray bursts.
 The latter are alluded to in connection with mergers of neutron star binaries and black hole neutron star binaries, as well as with the rotational collapse that ensues at the end of the life of some massive stars.
-As numerical simulations show, such events  often result in a black hole surrounded by a torus.
-\tf{We need to include a few references in this paragraph.}
+As numerical simulations show, such events  often result in a black hole surrounded by a torus (see e.g.~\cite{Rezzolla:2010,Sekiguchi:2011,Faber:2012,Shibata:2011}).
 
@@
 representations based on physical assumptions.
-The construction of equilibrium models of stationary disks around black holes has indeed a long tradition (see~\cite{Abramowicz:2013} and references therein).
-In particular, the so-called ``Polish doughnuts"~\citep{Abramowicz:1978,Kozlowski:1978} provide a  very general method to build equilibrium configurations of perfect fluid matter
- orbiting around a Kerr black hole.
-This fully relativistic model assumes that the disk is non-magnetized and that the matter obeys a  constant specific angular momentum distribution.
-This method was later extended by~\cite{Komissarov:2006}  by adding a purely azimuthal magnetic
- field to build magnetized tori around rotating black holes.
-On the other hand, assuming different distributions of angular momentum in the disks, \citet{Qian:2009} presented a method to build sequences of black hole thick accretion disks in dynamical equilibria, restricted however to the purely hydrodynamical case.
+The construction of equilibrium models of stationary discs around black holes has indeed a long tradition (see~\cite{Abramowicz:2013} and references therein).
+In particular, the so-called ``Polish doughnuts"~\citep{Abramowicz:1978,Kozlowski:1978} provide a  very general method to build equilibrium configurations of perfect fluid matter orbiting around a Kerr black hole.
+This fully relativistic model assumes that the disc is non-magnetised and that the matter obeys a  constant specific angular momentum distribution.
+This method was later extended by~\cite{Komissarov:2006}  by adding a purely azimuthal magnetic field to build magnetised tori around rotating black holes.
+On the other hand, assuming different distributions of angular momentum in the discs, \citet{Qian:2009} presented a method to build sequences of black hole thick accretion discs in dynamical equilibria, restricted however to the purely hydrodynamical case.
 
  In this paper we combine the two approaches considered in~\cite{Komissarov:2006} and~\citet{Qian:2009} to build new sequences of equilibrium tori around Kerr black holes.
- Building on those works, we present here the extension of the models of~\citet{Qian:2009} to account for disks endowed with a purely toroidal magnetic field.
+Building on these works, we present here the extension of the models of~\citet{Qian:2009} to account for discs endowed with a purely toroidal magnetic field.
 In our procedure we hence assume a form of the angular momentum distribution that departs from the constant case considered by~\cite{Komissarov:2006} and from which the location and morphology
@@
 
-The organization of the paper is as follows: Section~\ref{framework} presents the analytic framework to build the disks while Section~\ref{methodology} explains the corresponding numerical procedure.
+The organization of the paper is as follows: Section~\ref{framework} presents the analytic framework to build the discs while Section~\ref{methodology} explains the corresponding numerical procedure.
 The sequences of models are discussed in Section~\ref{results}.
@@
 In our work we assume that the test-fluid approximation holds, thus neglecting the self-gravity of the fluid, and further assume that the spacetime is described by the Kerr metric.
+In mathematical expressions below Greek indices are spacetime indices running from 0 to 3 and Latin indices are only spatial.
 We use geometrized units where $G = c = 1$.
@@
 \end{eqnarray}
-where we have defined the following quantities, $Z_1=1+(1-a_*^2)^{1/3}[(1+a_*)^{1/3}+(1-a_*)^{1/3}]$, $Z_2=(3a_*^2+Z_1^2)^{1/2}$, and $a_*=a/M$, with $a$ and $M$ being the spin Kerr parameter and the black hole mass.
+where we have defined the following quantities, $Z_1=1+(1-a_*^2)^{1/3}[(1+a_*)^{1/3}+(1-a_*)^{1/3}]$, $Z_2=(3a_*^2+Z_1^2)^{1/2}$, and $a_*=a/M$, with $a$ and $M$ being the spin Kerr parameter and the black hole mass, respectively.
 
@@
 \end{equation}
-We also introduce the Keplerian angular momentum (for prograde motion) in the equatorial plane $l_{\mathrm{K}}$. 
+We also introduce the Keplerian angular momentum (for prograde motion) in the equatorial plane $l_{\mathrm{K}}$, defined as 
 \begin{equation}\label{eq:kepler}
@@
 
-\cite{Jaroszynski:1980} argued that the slope of the specific angular momentum should range between two cases, $l = \mathrm{const.}$ and $\Omega = \mathrm{const}$.
+\cite{Jaroszynski:1980} argued that the slope of the specific angular momentum should range between two limiting cases, namely $l = \mathrm{const.}$ and $\Omega = \mathrm{const}$.
 Following \citet{Qian:2009} we assume an angular momentum distribution ansatz given by
@@
 where constants $l_0$ and $l_{\mathrm{ms}}(r)$ are defined by $l_0 \equiv \eta l_{\mathrm{K}}(r_{\mathrm{ms}})$ and $l_{\mathrm{ms}}(r) \equiv l_0 [l_{\mathrm{K}}(r_{\mathrm{ms}})/l_0]^{\beta}$.
-Therefore, the model for the distribution of angular momentum has three parameters $(\beta, \gamma, \eta)$, whose range of variation is given by~\citep{Qian:2009}
+Therefore, the model for the distribution of angular momentum has three free parameters, $\beta$ , $\gamma$ and $\eta$, whose range of variation is given by~\citep{Qian:2009}
 \begin{equation}
@@
 with $\eta_{\mathrm{max}} = l_{\mathrm{K}}(r_{\mathrm{mb}})/l_{\mathrm{K}}(r_{\mathrm{ms}})$.
-In this paper, and as it is done in~\citet{Qian:2009}, we choose $\eta = \eta_{\mathrm{max}}$, and then we can write $l_0$ as $l_0 = l_{\mathrm{K}}(r_{\mathrm{mb}})$.
-For this choice of $\eta$, we can find the location of the disk cusp at $r_{\mathrm{mb}} \leq r_{\mathrm{cusp}} \leq r_{\mathrm{ms}}$ (for $0 \leq \beta \leq 1$).
-Also, this guarantees that constant angular momentum disks ($\beta = \gamma = 0$) with its inner edge located at the cusp ($r_{\mathrm{in}} = r_{\mathrm{cusp}}$) have no outer bound.
+In this paper, and as it is done for hydrodynamical discs in~\citet{Qian:2009}, we choose $\eta = \eta_{\mathrm{max}}$, and then we can write $l_0$ as $l_0 = l_{\mathrm{K}}(r_{\mathrm{mb}})$.
+For this choice of $\eta$, we can find the location of the cusp of the disc  within the range $r_{\mathrm{mb}} \leq r_{\mathrm{cusp}} \leq r_{\mathrm{ms}}$ (for $0 \leq \beta \leq 1$).
+Moreover, this value of $\eta$ guarantees that constant angular momentum discs ($\beta = \gamma = 0$) with their inner edge located at the cusp ($r_{\mathrm{in}} = r_{\mathrm{cusp}}$) have no outer boundary, i.e~they are infinite discs (see also~\cite{Font:2002}).
+\tf{Check that the last sentence is correct.}
 
 %%%%%%%%%%%%%%%%
-\subsection{Magnetized disks}
+\subsection{Magnetised discs}
 %%%%%%%%%%%%%%%%
@@
 $\nabla_{\mu} (\rho u^{\mu}) = 0$, 
-%\begin{equation}\label{eq:e-m_cons}
-%\nabla_{\mu} T^{\mu\nu} = 0,
-%\end{equation}
-%\begin{equation}\label{eq:cons_faraday}
-%\nabla_{\mu} \ast F^{\mu\nu} = 0,
-%\end{equation}
-%\begin{equation}\label{eq:continuity}
-%\nabla_{\mu} (\rho u^{\mu}) = 0,
-%\end{equation}
 where $\nabla_{\mu}$ is the covariant derivative and
@@
 \end{equation}
-is the energy-momentum tensor of a magnetized perfect fluid, $w$ and $p$ being the fluid enthalpy and pressure, respectively. 
-Moreover,
-%\begin{equation}
-$^\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu}$
-%\end{equation}
-is the (dual of the) Faraday tensor relative to an observer with four-velocity $u^{\mu}$, and $b^{\mu}$ is the magnetic field in that frame, with
+is the energy-momentum tensor of a magnetised perfect fluid, $w$ and $p$ being the fluid enthalpy and pressure, respectively. 
+Moreover, $^\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu}$ is the (dual of the) Faraday tensor relative to an observer with 
+four-velocity $u^{\mu}$, and $b^{\mu}$ is the magnetic field in that frame, with
 $b^2=b^{\mu}b_{\mu}$. Assuming the magnetic field is purely azimuthal, i.e.~$b^r = b^{\theta} = 0$,
 and taking into account that the flow is stationary and axisymmetric, the conservation of the current density and of the Faraday tensor follow.
-Contracting Eq.~\eqref{eq:e-m_tensor} with the projection tensor $h^{\alpha}_{\beta} = \delta^{\alpha}_{\beta} + u^{\alpha}u_{\beta}$, we arrive at
+Contracting Eq.~\eqref{eq:e-m_tensor} with the projection tensor $h^{\alpha}_{\,\,\beta} = \delta^{\alpha}_{\,\,\beta} + u^{\alpha}u_{\beta}$, we arrive at
 \begin{equation}
@@
 \end{equation}
-where $i = r, \theta$. Following~\cite{Komissarov:2006} we rewrite this equation in terms of the specific angular momentum $l$ and the angular velocity $\Omega$, to obtain
+where $i = r, \theta$. Following~\cite{Komissarov:2006} we rewrite this equation in terms of the specific angular momentum $l$ and of the angular velocity $\Omega$, to obtain
 \begin{equation}\label{eq:diff_ver}
@@
 $ are constants.
-This particular choice of relationships, $w = w(p)$ and $\tilde{w} = \tilde{w}(\tilde{p}_{\mathrm{m}})$, fulfill the general relativistic version of the von Zeipel theorem for a toroidal magnetic field~\citep{vonZeipel:1924, Zanotti:2015}, i.e.~the surfaces of constant $\Omega$ and constant $l$ coincide.
+This particular choice of barotropic relationships, $w = w(p)$ and $\tilde{w} = \tilde{w}(\tilde{p}_{\mathrm{m}})$, fulfill the general relativistic version of the von Zeipel theorem for a toroidal magnetic field~\citep{vonZeipel:1924, Zanotti:2015}, i.e.~the surfaces of constant $\Omega$ and constant $l$ coincide.
 
-\begin{figure*}[t]
-\centering
-\includegraphics[scale=0.16]{figures/fig1a.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.16]{figures/fig1b.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.16]{figures/fig1c.pdf}
-\caption{Comparison with Komissarov's solution for a constant angular momentum model.
-The left panel shows the density distribution in logarithm scale for all radii and all angles while the middle and right panels show, respectively, the angular profile of the logarithm of the density at the centre of the disk and the radial profile of the density at the equatorial plane.}
-           \label{komissarov}%
- \end{figure*}
-
-Integrating Eq.~\eqref{eq:diff_ver} we obtain
+We can now integrate Eq.~\eqref{eq:diff_ver} to obtain
 \begin{equation}\label{eq:pre_full_int}
@@
 \end{equation}
-On the surface of the disk, and particularly on its inner edge, the conditions
+On the surface of the disc, and particularly on its inner edge, the conditions
 $p = \tilde{p}_{\mathrm{m}} = 0, \; u_t = u_{t, \mathrm{in}}, \; l = l_{\mathrm{in}}$
@@
 \end{equation}
-We can also introduce the total (gravitational plus centrifugal) potential $W$~\citep{Abramowicz:1978} and write the integral form of the equation of motion as
+We can also introduce the total (gravitational plus centrifugal) potential $W$~\citep{Abramowicz:1978} and write the integral form of the equation of motion (the relativistic Euler equation) as
 \begin{equation}\label{eq:potential}
@@
 \end{equation}
-where $W_{\mathrm{in}}$ is the potential at the inner edge of the disk (in the equatorial plane). With this definition, we can write Eq.~\eqref{eq:pre_full_int} as
+where $W_{\mathrm{in}}$ is the potential at the inner edge of the disc (in the equatorial plane). With this definition, we can write Eq.~\eqref{eq:pre_full_int} as
 \begin{equation}\label{eq:full_int}
@@
 
-%\subsection{Building the disk}
-
-To construct the magnetized disks we follow the approach described in \citet{Qian:2009}.
-First, we find the radial location of the cusp and of the centre of the disk in the equatorial plane, $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$, defined as the solutions to the equation $l(r) - l_{\mathrm{K}} = 0$.
+To construct our models of magnetised discs we follow the approach described in \citet{Qian:2009}.
+First, we find the radial location of the cusp and of the centre of the disc in the equatorial plane, $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$, defined as the solutions to the equation $l(r) - l_{\mathrm{K}} = 0$.
 Next, we compute the partial derivatives of the potential, Eq.~\eqref{eq:potential}
@@
 \begin{equation}\label{eq:equatorial_pot}
-W_{\mathrm{eq}}(r) = \int^{r}_{r_{\mathrm{cusp}}}\left(\partial_r \ln|u_t| - \frac{\Omega \partial_rl}{1 - \Omega l}\right).
+W_{\mathrm{eq}}(r) = \int^{r_{\mathrm{c}}}_{r_{\mathrm{cusp}}}\left(\partial_r \ln|u_t| - \frac{\Omega \partial_rl}{1 - \Omega l}\right).
 \end{equation}
-Following \citet{Qian:2009} we can divide equations \eqref{eq:radial_der_pot} and \eqref{eq:polar_der_pot} to obtain
+Following~\citet{Qian:2009} (see also~\citet{Jaroszynski:1980}) we can divide equations \eqref{eq:radial_der_pot} and \eqref{eq:polar_der_pot} to obtain
 \begin{equation}\label{eq:F}
@@
 \end{equation}
-which is an ordinary differential equation that can be integrated to obtain the location of the equipotential surfaces.
+where function $F(r, \theta)$ is known in closed form for the Kerr metric once an assumption for the angular momentum distribution has been made (cf.~Eq.~(\ref{eq:ansatz})).
+For this reason, Eq.~(\ref{eq:F}) also takes the form of an ordinary differential equation for the surfaces of constant pressure, $\theta=\theta(r)$, which, upon integration, yields the location of those surfaces.
 
-Next, we choose all the initial values for the integration of the equation \eqref{eq:F} to be between $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$ ($\theta = \pi / 2$).
-Since we are only interested in the surfaces inside the Roche lobe, our choice of initial values provides us a mapping of the equipotential surfaces of the torus.
-Given that we have already obtained both the equipotential surfaces which cross the segment $[r_{\mathrm{cusp}}, r_{\mathrm{c}}]$ and the potential distribution there, we found the potential distribution for the torus.
-Once we have the potential distribution, we can find the gas pressure at the center, from equation \eqref{eq:enthalpy_eq}
+\begin{figure*}[t]
+\centering
+\includegraphics[scale=0.16]{figures/fig1a.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.16]{figures/fig1b.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.16]{figures/fig1c.pdf}
+\caption{Comparison with Komissarov's solution for a constant angular momentum model.
+The left panel shows the density distribution in logarithm scale for all radii and all angles while the middle and right panels show, respectively, the angular profile of the logarithm of the density at the centre of the disc and the radial profile of the density at the equatorial plane.}
+\label{komissarov}
+\end{figure*}
+
+Next, we choose all the initial radial values for the integration of Eq.~\eqref{eq:F} to lie between $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$ ($\theta = \pi / 2$).
+Since we are only interested in the equipressure surfaces inside the Roche lobe of the disc, our choice of initial values provides us a mapping of the equipotential surfaces of the torus.
+Given that we have already obtained both the equipotential surfaces which cross the segment $[r_{\mathrm{cusp}}, r_{\mathrm{c}}]$ and the potential \tf{pressure?} distribution there, we can obtain the potential distribution for the torus.
+Once we have the potential distribution, we can find the gas pressure at the centre of the disc from Eq.~\eqref{eq:enthalpy_eq} \tf{we need to discuss this paragraph to see if we can improve the writing}
 \begin{equation}
@@
 \end{equation}
-where $w_{\mathrm{c}}$ is the enthalpy at the disk center and
+where $w_{\mathrm{c}}$ is the enthalpy at the centre and
 \begin{equation}
@@
 \end{equation}
-is the magnetization parameter (being $\beta_{\mathrm{m}_{\mathrm{c}}}$ the magnetization parameter at the disk center). By this definition, we can find the magnetic pressure at the disk center,
+is the magnetisation parameter ($\beta_{\mathrm{m}_{\mathrm{c}}}$ being the magnetisation parameter at the centre of the disc). Using this definition, we can find the magnetic pressure at the centre,
 \begin{equation}
-p_{\mathrm{m_{\mathrm{c}}}} = p_{\mathrm{c}}/\beta_{\mathrm{m}_{\mathrm{c}}}
+p_{\mathrm{m_{\mathrm{c}}}} = p_{\mathrm{c}}/\beta_{\mathrm{m}_{\mathrm{c}}}\,.
 \end{equation}
-With the pressures at the center, we can also find the constants $K$ and $K_{\mathrm{m}}$ using the equations \eqref{eq:eos_fluid} and \eqref{eq:eos_mag}.
-And, for a given inner radius of the disk $r_{\mathrm{in}}$ we can find the potential $W_{\mathrm{in}}$.
-We now have all the elements required to find the enthalpy distribution (equation \eqref{eq:enthalpy_eq}), the pressure and magnetic pressure distribution (equations \eqref{eq:eos_fluid} and \eqref{eq:eos_mag}), and the density (equation \eqref{eq:density_eq}).
+With both pressures known at the centre, fluid and magnetic, we can now find the constants $K$ and $K_{\mathrm{m}}$ using equations \eqref{eq:eos_fluid} and \eqref{eq:eos_mag}.
+Therefore, for a given inner radius of the disc $r_{\mathrm{in}}$ we can obtain the potential $W_{\mathrm{in}}$.
+We now finally have all the ingredients required to find the enthalpy distribution (Eq.~\eqref{eq:enthalpy_eq}), the fluid pressure and magnetic pressure distributions (Eqs.~\eqref{eq:eos_fluid} and \eqref{eq:eos_mag}), and the density distribution (Eq.~\eqref{eq:density_eq}).
+\tf{which equation?}
 
-%\subsection{Numerical code}
-
-For the integration of equation \eqref{eq:equatorial_pot} we use the composite Simpson's rule, it is important to use a very small step of integration, because the slope is very steep.
-In this work, we use a step $h = 10^{-6}$ .
-A bigger step gives an unacceptable lack of accuracy, we tested that fact by comparison with the analytic, constant angular momentum case.
-
-To integrate the ordinary differential equation \eqref{eq:F} we use a fourth-order Runge-Kutta method.
-Here is also important to choose a suitable step of integration, specially at the outer end of the disk, this is because the equation \eqref{eq:F} diverges of the equatorial plane (the equipotential surfaces crosses the equatorial plane perpendicularly).
-
-%\subsection{Parameter space}
-
-As in \citet{Komissarov:2006}, in this paper we have chosen the exponents $\kappa = \lambda
- = 4/3$ and the enthalpy at the disk center $w_{\mathrm{c}} = 1$. That leaves us the magnetization parameter $\beta_{\mathrm{m}_{\mathrm{c}}}
-$, the parameters of the angular momentum distribution $\beta$ and $\gamma$, the black hole spin parameter $a$ and the inner radius of the disk $r_{\mathrm{in}}$.
-This allows us to control the size, shape, thickness and magnetization of the disk.
-
-% \begin{table}
-% \caption{List of models.
-Form left to right the columns report: the black hole spin $a$, the parameters of the angular momentum distribution $\beta$ and $\gamma$, the magnetization parameter $\beta_{\mathrm{m}_{\mathrm{c}}}
-% $ at the disk center, the corresponding radii of the maximum thermal pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential diference between the center and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the disks, $r_{\mathrm{in}}$ and  $r_{\mathrm{out}}$.}
-% \label{table:1}      
-% \centering          
-% \begin{tabular}{c c c c c c  c c c c}
-% \hline\hline       
-%  & $a$ & $\beta$ & $\gamma$ & $\beta_{\mathrm{m}_{\mathrm{c}}}
-% $  & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W$ & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
-% \hline           
-% A1 & $0.5$ & $0.0$ & $0.0$ & $10^{-3}$ &  $5.11$  & $5.51$ & $-6.35 \times 10^{-2}$ & $2.91$ & -- \\ 
-% A2 &           & $0.5$ & $0.5$ &  & $5.55$ &  $5.80$  & $-2.27 \times 10^{-2}$ & $3.20$ & $11.77$\\ 
-% A3  &          & $0.9$ & $0.9$ &  & $5.95$ &  $6.15$  & $-2.96 \times 10^{-3}$ & $3.70$ &  $9.583$\\ 
-% A4  &          & $0.0$ & $0.9$ &  & $5.21$ &  $5.51$  & $-6.35 \times 10^{-2}$ & $2.91$ & $9.680$\\ 
-% A5   &         & $0.9$ & $0.0$ &  & $5.90$ &  $6.10$  & $-2.95 \times 10^{-3}$ & $3.70$ & --\\ 
-%  \hline 
-% B1 & $0.9$ & $0.0$ & $0.0$ & $10^{-3}$ & $2.53$ &  $2.73$  & $-0.129$ & $1.73$ & -- \\ 
-% B2 &           & $0.5$ & $0.5$ &  & $2.81$ &  $2.91$  & $-4.32 \times 10^{-2}$ & $1.86$ & $5.35$\\ 
-% B3  &          & $0.9$ & $0.9$ &  & $3.03$ &  $3.13$  & $-5.39 \times 10^{-3}$ & $2.08$ & $4.52$\\ 
-% B4  &          & $0.0$ & $0.9$ &  & $2.65$ &  $2.80$  & $-0.129$ & $1.732$ & $4.54$\\ 
-% B5   &         & $0.9$ & $0.0$ &  & $3.03$ &  $3.13$  & $-5.39 \times 10^{-3}$ & $2.08$ & -- \\  
-%  \hline 
-% C1 & $0.99$ & $0.0$ & $0.0$ & $10^{-3}$ & $1.46$ & $1.51$ & $-0.246$ & $1.21$ & -- \\ 
-% C2 &             & $0.5$ & $0.5$ &  & $1.56$ &  $1.61$  & $-7.34 \times 10^{-2}$ & $1.26$ & $2.50$\\ 
-% C3  &            & $0.9$ & $0.9$ &  & $1.70$ &  $1.75$  & $-8.53 \times 10^{-3}$ & $1.35$ & $2.25$\\ 
-% C4  &            & $0.0$ & $0.9$ &  & $1.50$ &  $1.57$  & $-0.246$ & $1.21$ & $2.26$\\ 
-% C5   &           & $0.9$ & $0.0$ &  & $1.72$ &  $1.77$  & $-8.53 \times 10^{-3}$ & $1.35$ & --\\ 
-% \hline      
-% \end{tabular}
-% \end{table}
+For the integration of Eq.~\eqref{eq:equatorial_pot} we use the composite Simpson's rule.
+It is important to use a very small integration step because the slope is very steep.
+In this work, we use a step $h = 10^{-6}$.
+Using the analytic, constant angular momentum case for comparison, we tested that
+a larger value of $h$ gives unacceptable accuracy losses.
+On the other hand, to integrate the ordinary differential equation \eqref{eq:F} we use a fourth-order Runge-Kutta method.
+Again, it is also important here to choose a suitable step of integration, especially at the outer end of the disc, because Eq.~\eqref{eq:F} diverges at the equatorial plane (the equipotential surfaces cross the equatorial plane perpendicularly).
 
 \begin{table}
-\caption{List of models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}
-$.
-Form left to right the columns report: the model name (with A, B and C standing for black hole spin $a = 0.5$, $0.9$ and $0.99$ respectively), the parameters of the angular momentum distribution $\beta$ and $\gamma$, , the corresponding radii of the maximum thermal pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential diference between the center and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the disks, $r_{\mathrm{in}}$ and $r_{\mathrm{out}}$.}
+\caption{List of models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$.
+From left to right the columns report: the model name (with A, B and C standing for black hole spin $a = 0.5$, $0.9$ and $0.99$, respectively), the parameters of the angular momentum distribution $\beta$ and $\gamma$, the corresponding radii of the maximum thermal pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential difference between the centre and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the discs, $r_{\mathrm{in}}$ and $r_{\mathrm{out}}$.}
 \label{table:1}      
@@
 \hline\hline       
- & $\beta$ & $\gamma$ & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W (\times 10^{-2})$ & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
+ & $\beta$ & $\gamma$ & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W$               & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
+ &              &                   &                          &                                        & $(\times 10^{-2})$     &                              &  \\
 \hline           
@@
 \begin{table}
-\caption{List of models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 1
-$.
-Form left to right the columns report: the model name (with A, B and C standing for black hole spin $a = 0.5$, $0.9$ and $0.99$ respectively), the parameters of the angular momentum distribution $\beta$ and $\gamma$, , the corresponding radii of the maximum thermal pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential diference between the center and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the disks, $r_{\mathrm{in}}$ and $r_{\mathrm{out}}$.}
-\label{table:3}      
+\caption{List of models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 1$. The naming of the models and the parameters reported in the columns are as in Table~\ref{table:1}.}             
+\label{table:2}      
 \centering          
@@
 
+%%%%%%%%%
+\section{Results}
+\label{results}
+%%%%%%%%%
+
+To reduce the number of free parameters to build the initial models we do as in~\citet{Komissarov:2006} and fix the values of the equation of state exponents, $\kappa$ and $\lambda$, and of the enthalpy at the disc centre, $w_{\mathrm{c}}$.
+More precisely, we choose $\kappa = \lambda = 4/3$ and $w_{\mathrm{c}} = 1$.
+This still leaves us with five parameters to control the size, shape, thickness, and magnetisation of the disc, namely the magnetisation parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$, the parameters of the angular momentum distribution $\beta$ and $\gamma$, the black hole spin parameter $a$, and the inner radius of the disc $r_{\mathrm{in}}$.
+We build a series of 45 models, whose main features are summarised in Table~\ref{table:1} (for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$, i.e.~models where the effects of the magnetisation are unimportant), Table~\ref{table:2} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$, i.e.~equipartition models), and Table~\ref{table:3} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$, i.e.~highly-magnetised models).
+
+We start by assessing our procedure by first building an extra disc model that can be directly compared with one of the two models in~\citet{Komissarov:2006}.
+This is shown in Figure~\ref{komissarov}, which corresponds to the same constant specific angular momentum model A presented by~\citet{Komissarov:2006}.
+The parameters of this model are $a=0.9$, $\beta_{\mathrm{m}_{\mathrm{c}}}=0.1$, and $l=2.8$.
+The visual comparison shows that our approach can reproduce those previous results with good agreement.
+The density distribution in the $(r\sin\theta,r\cos\theta)$ plane shown in the left panel of Fig.~\ref{komissarov} is remarkably similar to that shown in the left panel of Fig.~2 in~\citet{Komissarov:2006}.
+Not only the morphology of both models is nearly identical but also the range of variation of the density and the location of the disc centre agree well in both cases.
+This can be most clearly seen in the middle and right panels of Fig.~\ref{komissarov} which show, repectively, the angular profile at $r_{\rm c}$ and the radial profile at $\theta=\pi/2$.
+These two figures can be directly compared with Fig.~3 of~\citet{Komissarov:2006}.
+It is relevant to mention that very small changes in the location of the inner radius $r_{\mathrm{in}}$ have a significant effect on the maximum value of the density, which explains the small differences between our figures and the ones presented in~\citet{Komissarov:2006}.
+
 \begin{table}
-\caption{List of models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}
-$.
-Form left to right the columns report: the model name (with A, B and C standing for black hole spin $a = 0.5$, $0.9$ and $0.99$ respectively), the parameters of the angular momentum distribution $\beta$ and $\gamma$, , the corresponding radii of the maximum thermal pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential diference between the center and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the disks, $r_{\mathrm{in}}$ and $r_{\mathrm{out}}$.}
+\caption{List of models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$. The naming of the models and the parameters reported in the columns are as in Table~\ref{table:1}.}             
 \label{table:3}      
@@
 \end{table}
-
-%%%%%%%%%
-\section{Results}
-\label{results}
-%%%%%%%%%
 
@@
 \includegraphics[scale=0.16]{figures/fig2_5_3.pdf}
-\caption{Isodensity distributions for a representative sample of our models.
+\caption{Isodensity distributions for all models of Table~\ref{table:3}.
 From left to right the columns correspond to increasing values of the black hole spin: $a=0.5$, 0.9 and 0.99.
 From top to bottom the rows correspond to the following parameter combinations: a) $\gamma=\beta=0$; b) $\gamma=\beta=0.5$; c) $\gamma=\beta=0.9$; d) $\gamma=0.9$, $\beta=0$; e) $\gamma=0$, $\beta=0.9$.
-Note that the spatial scale of the plots differs as it has been chosen to facilitate the visualization of the disks.}
+Note that the spatial scale of the plots differs as it has been chosen to facilitate the visualization of the discs.}
 \label{models}
@@
 \includegraphics[scale=0.16]{figures/fig3c.pdf}
-\caption{Effects of the magnetization in the structure of the disk. From left to right the values are $\beta_{\mathrm{m}_{\mathrm{c}}}
+\caption{Effects of the magnetisation in the structure of the disc. From left to right the values are $\beta_{\mathrm{m}_{\mathrm{c}}}
 =10^3$, 1, and $10^{-3}$.}
-\label{magnetization}%
+\label{magnetisation}%
 \end{figure*}
 
-We start by assessing our procedure by first building a disk that can be directly compared with one of the two models in~\citet{Komissarov:2006}.
-This is shown in Figure~\ref{komissarov}, which corresponds to the same constant specific angular momentum model A presented by~\citet{Komissarov:2006}.
-The parameters of this model are $a=0.9$, $\beta_{\mathrm{m}_{\mathrm{c}}}=0.1$, and $l=2.8$.
-The visual comparison shows that our approach can reproduce those previous results with good agreement.
-The density distribution in the $(r\sin\theta,r\cos\theta)$ plane shown in the left panel of Fig.~\ref{komissarov} is remarkably similar to that shown in the left panel of Fig.~2 in~\citet{Komissarov:2006}.
-Not only the morphology of both models is nearly identical but also the range of variation of the density and the location of the disk center agree well in both cases.
-This can be most clearly seen in the middle and right panels of Fig.~\ref{komissarov} which show, repectively, the angular profile at $r_{\rm c}$ and the radial profile at $\theta=\pi/2$.
-These two figures can be directly compared with Fig.~3 of~\citet{Komissarov:2006}.
-It is relevant to mention that very small changes in the inner radius $r_{\mathrm{in}}$ have a significant effect on the maximum value of the density, that explains the small differences between our figures and the ones presented in~\citet{Komissarov:2006}.
+A representative sample of the isodensity surfaces for some of our models appears in Figure~\ref{models}.
+We plot, in particular, the models of Table~\ref{table:3}, for which the value of the magnetisation parameter is the highest, $\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$.
+From left to right the columns of this figure correspond to increasing values of the black hole spin, namely, $a=0.5$, 0.9 and 0.99, while from top to bottom the rows correspond to different combinations of the $\gamma$ and $\beta$ parameters that characterize the ansatz for the angular momentum distribution of~\citet{Qian:2009} (the particular values are indicated in the caption of the figure).
+A rapid inspection shows that the structure of the discs noticeable changes when the parameters change.
+Notice that the spatial scale in all of the plots of this figure has been chosen so as to facilitate the visualization of the discs (which can be fairly small in some cases) and, as such, is different in each plot.
+A typical Polish doughnut is represented by the model in the top-left panel.
+As the black hole spin increases, the discs are closer to the black hole and its relative size with respect to the black hole is smaller for all values of $\gamma$ and $\beta$.
+For $\gamma=0$ the discs are infinite, irrespective of the value of $a$ and $\beta$.
+As $\gamma$ and $\beta$ increase from 0 to 0.9 (compare the three top rows) the discs become significantly thinner and radially smaller (see also Fig.~\ref{more-profile} below).
+It is also interesting to note that the maximum value of the density is higher (with respect to the value at the disc centre) as the spin increases.
 
@@
 \caption{Radial profiles of the density in the equatorial plane for $\beta=10^3$ (black curve), 1 (blue curve), and $10^{-3}$ (green curve). }
-\label{magnetization-profile}
+\label{magnetisation-profile}
  \end{figure}
@@
 \includegraphics[scale=0.16]{figures/fig6c.pdf}
-\caption{The left panel shows the variation of the value for the maximum density with repect to the logarithm of the magnetization parameter.
-The solid, dashed and dashed lines refer to $a = 0.99$, $0.9$ and $0.5$ respectively and the colour code refers to the models shown in the legend.
-The middle panel shows the variation of the location of the density maximum (and thermal pressure) with respect to the logarithm of the magnetization parameter for the three models shown in the legend with $a = 0.99$.
-The right panel shows (also for $a = 0.99$) the variation of the location of the maximum of the magnetic pressure maximum with respect to the logarithm of the magnetization parameter.}
-           \label{max-vs-magnetization}%
+\caption{Effects of $\beta_{\mathrm{m}_{\mathrm{c}}}$.
+Left panel: variation of the value of the maximum density with respect to the logarithm of the magnetisation parameter.
+The solid, dashed, and dotted lines refer to $a = 0.99$, $0.9$ and $0.5$, respectively, and the colour code refers to the models shown in the legend.
+Middle panel: variation of the location of the density maximum (and thermal pressure) with respect to the logarithm of the magnetisation parameter for the three models shown in the legend with $a = 0.99$.
+Right panel: variation (also for $a = 0.99$) of the location of the maximum of the magnetic pressure with respect to the logarithm of $\beta_{\mathrm{m}_{\mathrm{c}}}$.}
+           \label{max-vs-magnetisation}%
  \end{figure*}
 
-A representative sample of the isodensity surfaces for some of our models appears in Figure~\ref{models}.
-From left to right the columns of this figure correspond to increasing values of the black hole spin, namely, $a=0.5$, 0.9 and 0.99, while from top to bottom the rows correspond to different combinations of the $\gamma$ and $\beta$ parameters that characterize the ansatz for the angular momentum distribution of~\citet{Qian:2009} (the particular values are indicated in the caption of the figure).
-The value of the magnetization parameter for all models in this figure is $\beta_{\mathrm{m}_{\mathrm{c}}}
-=10^{-3}$.
-A rapid inspection shows that the structure of the disks noticeable changes when the parameters change.
-Notice that the spatial scale in all of the plots of this figure has been chosen so as to facilitate the visualization of the disks (which can be fairly small in some cases) and, as such, is different in each plot.
-A typical Polish doughnut is represented by the model in the top-left panel.
-As the black hole spin increases, the disks are closer to the black hole and its relative size with respect to the black hole is smaller for all values of $\gamma$ and $\beta$.
-For $\gamma=0$ the disks are infinite, irrespective of the value of $a$ and $\beta$.
-As $\gamma$ and $\beta$ increase from 0 to 0.9 (compare the three top rows) the disks become significantly thinner and radially smaller (see also Fig.~\ref{more-profile} below).
-It is also interesting to note that the maximum value of the density is higher (with respect to the value at the disk center) as the spin increases.
+Figure~\ref{magnetisation} shows the effects of changing the parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$ (the magnetisation) in the structure of the discs.
+From left to right the values plotted in each panel are $\beta_{\mathrm{m}_{\mathrm{c}}}=10^3$, 1, and $10^{-3}$.
+The model chosen corresponds to $a=0.9$ and $\gamma=\beta=0.5$.
+The larger the value of $\beta_{\mathrm{m}_{\mathrm{c}}}$ the less important the effects of the magnetisation in the disc structure.
+Figure~\ref{magnetisation} shows that, at least for the kind of magnetic field distribution we are considering, the effects of the magnetisation are minor.
+The disc structure remains fairly similar for all values of $\beta_{\mathrm{m}_{\mathrm{c}}}
+$ and the only quantitative differences are found in the location of the centre of the disc (which moves inward with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$) and of the range of variation of the isodensity contours (the maximum being slightly larger with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$).
+This can be more clearly visualized in Figure~\ref{magnetisation-profile} which displays the radial profile at the equatorial plane of the density for the same three cases plotted in Fig.~\ref{magnetisation}.
 
-Figure~\ref{magnetization} shows the effects of changing the parameter $\beta_{\mathrm{m}_{\mathrm{c}}}
-$ (the magnetization) in the structure of the disks. From left to right the values plotted in each panel are $\beta_{\mathrm{m}_{\mathrm{c}}}
-=10^3$, 1, and $10^{-3}$. The model chosen corresponds to $a=0.9$ and $\gamma=\beta=0.5$. The larger the value of $\beta_{\mathrm{m}_{\mathrm{c}}}
-$ the less important the effects of the magnetization in the disk structure.
-Figure~\ref{magnetization} shows that for the kind of magnetic field distribution we are considering, the effects of magnetization are minor.
-The disk structure remains fairly similar for all values of $\beta_{\mathrm{m}_{\mathrm{c}}}
-$ and the only quantitative differences are found in the location of the centre of the disk (which moves inward with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}
-$) and of the range of variation of the isodensity contours (the maximum being slightly larger with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}
-$).
-This can be more clearly visualized in Figure~\ref{magnetization-profile} which displays the radial profile at the equatorial plane of the density for the same three cases plotted in Fig.~\ref{magnetization}.
-
-Next, we show in Fig.~\ref{more-profile} the corresponding radial profiles at the equatorial plane for the models with black hole spin $a=0.9$. We consider the case $\beta_{\mathrm{m}_{\mathrm{c}}}
-=10^{-3}$ (highest magnetization) and the same combination of the $\gamma$ and $\beta$ parameters that we employed in Fig.~\ref{models}.
+Next, we show in Fig.~\ref{more-profile} the corresponding radial profiles at the equatorial plane for the models with black hole spin $a=0.9$.
+We consider the case $\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$ (highest magnetisation) and the same combination of the $\gamma$ and $\beta$ parameters that we employed in Fig.~\ref{models}.
 Therefore, this plot depicts the radial profiles of the models occupying the central column of Fig.~\ref{models}.
-These profiles allow for a clearer quantification of the radial extent of the disks with $\gamma$ and $\beta$.
-As mentioned in the description of Fig.~\ref{models} as $\gamma$ and $\beta$ increase from 0 to 0.9 (compare black, blue, and green curves) the disks become gradually smaller.
-At the same time, the radial location of the density maximum increases and the maximum value of the central density (and pressure) decreases.
+These profiles allow for a clearer quantification of the radial extent of the discs with $\gamma$ and $\beta$.
+As mentioned in the description of Fig.~\ref{models} as $\gamma$ and $\beta$ increase from 0 to 0.9 (compare black, blue, and green curves) the discs become gradually smaller.
+At the same time, the radial location of the density maximum increases \tf{decreases?} and the maximum value of the central density (and pressure) decreases \tf{increases?}.
 It is worth noticing that the radial profiles of some of the models overlap below a certain radius.
 More precisely, the black and red curves overlap below $r\sim r_{\mathrm{c}}$ (which corresponds to $\rho \sim 1$) and also the green and orange curves.
-Also, this figure clearly shows that, besides modifying the thickness of the disk, $\beta$ is the parameter which determines the value of the density (and pressure) maximum.
-On the other hand, $\gamma$ is only relevant for its radial size.
+In addition, this figure clearly shows that, besides modifying the thickness of the disc, $\beta$ is the parameter which determines the value of the density (and pressure) maximum.
+On the other hand, the parameter $\gamma$ is only relevant for controlling the radial size of the discs.
 
-In order to provide a quantitative comparison of the structural differences that appear along the sequence of equilibrium models, we plot in Fig.~\ref{max-vs-magnetization} the variation of the maximum of the density (left panel), the radial location of the maximum of the thermal pressure (middle panel), and the radial location of the maximum of the magnetic pressure (right panel) as a function of the magnetization parameter $\beta_{\mathrm{m}_{\mathrm{c}}}
-$.
+In order to provide a quantitative comparison of the structural differences that appear along the sequence of equilibrium models, we plot in Fig.~\ref{max-vs-magnetisation} the variation of the maximum of the density (left panel), the radial location of the maximum of the thermal pressure (middle panel), and the radial location of the maximum of the magnetic pressure (right panel) as a function of the magnetisation parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$.
 All quantities plotted are measured at the equatorial plane.
@@
 The line type used indicates the value of the black hole spin $a$, namely, a dotted line is for $a=0.5$, a dashed line for $a=0.9$, and a solid line for $a=0.99$.
-Correspondingly, the colour indicates the value of $\beta$ and $\gamma$ used, namely, red curves correspond to $\gamma=\beta=0$, the blue ones to $\gamma=\beta=0.5$, and the black ones to $\gamma=\beta=0.9$.
+Correspondingly, the colour of the lines indicates the value of $\beta$ and $\gamma$ used, namely, red curves correspond to $\gamma=\beta=0$, the blue ones to $\gamma=\beta=0.5$, and the black ones to $\gamma=\beta=0.9$.
 All curves show the same monotonically decreasing trend with $\beta_{\mathrm{m}_{\mathrm{c}}}
-$: for small enough and large enough values of $\beta_{\mathrm{m}_{\mathrm{c}}}
-$ the value of the density maximum does not change. However, in the interval $10^{-2}\le \beta_{\mathrm{m}_{\mathrm{c}}}
- \le 10^{2}$, $\rho_{\rm max}$ changes abruptly. The larger the black hole spin the larger the drop in the maximum of the density. For sufficiently large values of $\beta_{\mathrm{m}_{\mathrm{c}}}
-$ (small magnetization) the value of $\rho_{\rm max}$ stays constant to the same value irrespective of the black hole rotation.
+$, yet for small enough and large enough values of $\beta_{\mathrm{m}_{\mathrm{c}}} $ the value of the density maximum does not change.
+However, in the interval $10^{-2}\le \beta_{\mathrm{m}_{\mathrm{c}}} \le 10^{2}$, $\rho_{\rm max}$ changes abruptly.
+The larger the black hole spin the larger the drop in the maximum of the density.
+For sufficiently large values of $\beta_{\mathrm{m}_{\mathrm{c}}}$ (small magnetisation) the value of $\rho_{\rm max}$ stays constant to the same value irrespective of the black hole rotation.
 
-In the middle panel of Fig.~\ref{max-vs-magnetization} we show the radial location of the maximum of the thermal pressure as a function of $\beta_{\mathrm{m}_{\mathrm{c}}}
-$.
+In the middle panel of Fig.~\ref{max-vs-magnetisation} we show the radial location of the maximum of the thermal pressure as a function of $\beta_{\mathrm{m}_{\mathrm{c}}}$.
 The black hole spin is $a=0.99$ and the values of $\beta$ and $\gamma$ are indicated in the legend.
-For all values of $\beta$ and $\gamma$, the maximum of the disk thermal pressure decreases with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}
-$. Below $\beta_{\mathrm{m}_{\mathrm{c}}}
-\sim 10^{-3}$ the location of the maximum does not change. The panel also shows that above $\beta_{\mathrm{m}_{\mathrm{c}}}
-\sim 10^{3}$ the constant value of $r_{\rm max}$ is the same irrespective of $\beta$ and $\gamma$ as we expected, because for purely hydrodynamic disks, $r_{\mathrm{max}} = r_{\mathrm{c}}$.
+For all values of $\beta$ and $\gamma$, the maximum of the location of the disc thermal pressure decreases with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$.
+Below $\beta_{\mathrm{m}_{\mathrm{c}}}\sim 10^{-3}$ the location of the maximum does no longer change.
+The panel also shows that above $\beta_{\mathrm{m}_{\mathrm{c}}}\sim 10^{3}$ the constant value of $r_{\rm max}$ is the same irrespective of $\beta$ and $\gamma$, as expected, because for purely hydrodynamic discs, $r_{\mathrm{max}} = r_{\mathrm{c}}$.
 
-The dependence of the location of the maximum of the magnetic pressure with $\beta_{\mathrm{m}_{\mathrm{c}}}
-$ is shown in the right panel of Fig.~\ref{max-vs-magnetization}. While the maximum of the magnetic pressure also decreases with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}
-$, the constant value achieved for values above $\beta_{\mathrm{m}_{\mathrm{c}}}
-\sim 10^{3}$ does depend on the specific values of $\beta$ and $\gamma$.
-It must be noted that, for the magnetic pressure, all models seem to cross at roughly the same value of $r_{\rm max}$, as it is more clearly shown in the inset.
+The dependence of the location of the maximum of the magnetic pressure with $\beta_{\mathrm{m}_{\mathrm{c}}}$ is shown in the right panel of Fig.~\ref{max-vs-magnetisation}.
+While this location also decreases with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$, the constant value achieved for values above $\beta_{\mathrm{m}_{\mathrm{c}}}\sim 10^{3}$ does depend on the specific values of $\beta$ and $\gamma$, contrary to what happens with the fluid pressure.
+It must be noted that the location of the maximum of the magnetic pressure is nearly identical for all models considered when $\beta_{\mathrm{m}_{\mathrm{c}}} \sim $ \tf{indicate approximate value}.
+At this value of $\beta_{\mathrm{m}_{\mathrm{c}}}$ all models seem to cross, as it is more clearly shown in the inset of the right panel of Fig.~\ref{max-vs-magnetisation}.
 
-It is relevant to add that in the left and middle panels, we do not show the data for the models with $\beta \neq \gamma$ as they coincide with the respective models with the same value of $\beta$.
-Also, the middle and right panels are only shown for $a=0.99$ because changing the spin parameter of the black hole only yield a change of scale, so if we choose the range of the graph accordingly they are identical irrespective of the value of $a$.
+As a final remark we note that in the left and middle panels of Fig.~\ref{max-vs-magnetisation} we do not show the data for models with $\beta \neq \gamma$ as they coincide with the respective models with the same value of $\beta$.
+Moreover, the middle and right panels only show the data for $a=0.99$ because changing the value of the spin parameter of the black hole only yields a change of scale.
+Therefore, if we choose the range of the graph accordingly, the plots are identical irrespective of the value of $a$.
+\tf{rephrase last sentence better?}
 
@@
 
-In this paper we have presented new sequences of magnetized, non-self-gravitating, equilibrium tori around Kerr black holes by combining two existing approaches~\citep{Komissarov:2006,Qian:2009}.
-Following~\citet{Qian:2009} the models have been built assuming a form of the angular momentum distribution from which the location and morphology
-of surfaces of equal pressure are computed.
-This ansatz includes as a limiting case the constant angular momentum case originally employed in the construction of thick tori - or Polish doughnuts - and was already used by~\citet{Qian:2009} to build equilibrium sequences of purely hydrodynamical models.
-Our disks are endowed with a purely toroidal magnetic field, as in the work of~\citet{Komissarov:2006}, which provides the methodology to handle the magnetic terms.
+In this paper we have presented a procedure to build equilibrium sequences of magnetised, non-self-gravitating discs around Kerr black holes which combines the two existing approaches of~\citet{Komissarov:2006} and~\citet{Qian:2009}.
+On the one hand we have followed~\citet{Qian:2009} and have assumed a form of the angular momentum distribution in the disc from which the location and morphology of surfaces of equal pressure can be computed.
+As a limiting case, this ansatz includes the constant angular momentum case originally employed in the construction of thick tori -- or Polish doughnuts~\citep{Abramowicz:1978,Kozlowski:1978}  -- and was already used by~\citet{Qian:2009} to build equilibrium sequences of purely hydrodynamical models.
+On the other hand, our discs are endowed with a purely toroidal magnetic field, as in the work of~\citet{Komissarov:2006}, which provides the methodology we have followed to handle the magnetic terms.
 
-We have discussed the properties of the new models and their dependence on the initial parameters.
-We have found that the solutions we have built exhibit a saturation-like behaviour for magnetizations over $\beta_{\mathrm{m}_{\mathrm{c}}} \sim 10^{3}$ and below $\beta_{\mathrm{m}_{\mathrm{c}}} \sim 10^{-3}$, so these can be considered as the purely hydrodynamic and MHD limit cases.
-Also, we have shown the effect of changing of the $\beta$ and $\gamma$ parameters beyond the purely morphological ones in~\citet{Qian:2009}.
-
-In the near future, we plan to extend this work following two paths: i) including the self-gravity of the disks as in the work of~\citet{Stergioulas:2011} and ii) constructing accretions disks around the hairy (both scalar and Proca) black holes described in~\citet{Herdeiro:2014} and~\citet{Herdeiro:2016}.
+We have discussed the properties of the new models and their dependence on the initial parameters, namely the magnetisation parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$, the parameters $\beta$ and $\gamma$ describing the angular momentum distribution, the black hole spin parameter $a$, and the inner radius of the disc $r_{\mathrm{in}}$.
+We have shown the effects of changing $\beta$ and $\gamma$ beyond the purely hydrodynamical case considered in~\citet{Qian:2009}.
+The mophology of the solutions we have built no longer changes for magnetisation values above $\beta_{\mathrm{m}_{\mathrm{c}}} \sim 10^{3}$ and below $\beta_{\mathrm{m}_{\mathrm{c}}} \sim 10^{-3}$.
+These cases can thus be considered as the hydrodynamical and MHD limiting cases, respectively.
+The new sequences of magnetised discs around black holes presented in this work can be used as initial data for magnetohydrodynamical evolutions in general relativity.
+In the near future, we plan to extend this work along two main directions, namely (i) including the self-gravity of the discs, following the approach laid out in~\citet{Stergioulas:2011}, and (ii) constructing accretion discs around hairy black holes, both, with scalar and Proca hair~\citep{Herdeiro:2014,Herdeiro:2016}.
 

### 2017-03-21 paper.tex
last version

@@
 \author{Sergio Gimeno-Soler\inst{1}   \and Jos\'e A.~Font\inst{1,2} }
-\institute{Departamento de Astronom\'{\i}a y Astrof\'{\i}sica, Universitat de Val\`encia, Dr. Moliner 50, 46100, Burjassot (Val\`encia), Spain.\\\email{sergiso@alumni.uv.es}
+\institute{Departamento de Astronom\'{\i}a y Astrof\'{\i}sica, Universitat de Val\`encia, Dr. Moliner 50, 46100, Burjassot (Val\`encia), Spain.\\\email{sergio.gimeno@uv.es}
 \and
@@
 Moreover, this value of $\eta$ guarantees that constant angular momentum discs ($\beta = \gamma = 0$) with their inner edge located at the cusp ($r_{\mathrm{in}} = r_{\mathrm{cusp}}$) have no outer boundary, i.e~they are infinite discs (see also~\cite{Font:2002}).
-\tf{Check that the last sentence is correct.}
 
@@
 where function $F(r, \theta)$ is known in closed form for the Kerr metric once an assumption for the angular momentum distribution has been made (cf.~Eq.~(\ref{eq:ansatz})).
-For this reason, Eq.~(\ref{eq:F}) also takes the form of an ordinary differential equation for the surfaces of constant pressure, $\theta=\theta(r)$, which, upon integration, yields the location of those surfaces.
+For this reason, Eq.~(\ref{eq:F}) also takes the form of an ordinary differential equation for the surfaces of constant potential, $\theta=\theta(r)$, which, upon integration, yields the location of those surfaces.
+Note that in~\citet{Qian:2009} these are surfaces of constant {\it pressure} instead, since their discs are purely hydrodynamical.
 
@@
 Next, we choose all the initial radial values for the integration of Eq.~\eqref{eq:F} to lie between $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$ ($\theta = \pi / 2$).
-Since we are only interested in the equipressure surfaces inside the Roche lobe of the disc, our choice of initial values provides us a mapping of the equipotential surfaces of the torus.
-Given that we have already obtained both the equipotential surfaces which cross the segment $[r_{\mathrm{cusp}}, r_{\mathrm{c}}]$ and the potential \tf{pressure?} distribution there, we can obtain the potential distribution for the torus.
-Once we have the potential distribution, we can find the gas pressure at the centre of the disc from Eq.~\eqref{eq:enthalpy_eq} \tf{we need to discuss this paragraph to see if we can improve the writing}
+Since we are only interested in the equipotential surfaces inside the Roche lobe of the disc, our choice of initial values provides us a mapping of the equipotential surfaces of the torus.
+Given that we have already obtained both the equipotential surfaces $\theta(r)$ which cross the segment $[r_{\mathrm{cusp}}, r_{\mathrm{c}}]$ at the equatorial plane and the values of the potential in that segment, we can obtain the complete potential distribution for the torus (outside of that segment).
+Once we have the potential distribution, we can find the gas pressure at the centre of the disc from Eq.~\eqref{eq:enthalpy_eq},
 \begin{equation}
@@
 Therefore, for a given inner radius of the disc $r_{\mathrm{in}}$ we can obtain the potential $W_{\mathrm{in}}$.
-We now finally have all the ingredients required to find the enthalpy distribution (Eq.~\eqref{eq:enthalpy_eq}), the fluid pressure and magnetic pressure distributions (Eqs.~\eqref{eq:eos_fluid} and \eqref{eq:eos_mag}), and the density distribution (Eq.~\eqref{eq:density_eq}).
-\tf{which equation?}
+We now finally have all the ingredients required to find the enthalpy distribution (Eq.~\eqref{eq:enthalpy_eq}), the fluid pressure and magnetic pressure distributions (Eqs.~\eqref{eq:eos_fluid} and \eqref{eq:eos_mag}), and the density distribution, which can be trivially obtained inverting the barotropic relation, $p = K \rho^{\kappa}$.
 
@@
 As mentioned in the description of Fig.~\ref{models} as $\gamma$ and $\beta$ increase from 0 to 0.9 (compare black, blue, and green curves) the discs become gradually smaller.
-At the same time, the radial location of the density maximum increases \tf{decreases?} and the maximum value of the central density (and pressure) decreases \tf{increases?}.
+At the same time, the radial location of the density maximum increases and the maximum value of the central density (and pressure) decreases.
 It is worth noticing that the radial profiles of some of the models overlap below a certain radius.
@@
 While this location also decreases with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$, the constant value achieved for values above $\beta_{\mathrm{m}_{\mathrm{c}}}\sim 10^{3}$ does depend on the specific values of $\beta$ and $\gamma$, contrary to what happens with the fluid pressure.
-It must be noted that the location of the maximum of the magnetic pressure is nearly identical for all models considered when $\beta_{\mathrm{m}_{\mathrm{c}}} \sim $ \tf{indicate approximate value}.
+It must be noted that the location of the maximum of the magnetic pressure is nearly identical for all models considered when $\log_{10}\beta_{\mathrm{m}_{\mathrm{c}}} \sim 0.5$.
 At this value of $\beta_{\mathrm{m}_{\mathrm{c}}}$ all models seem to cross, as it is more clearly shown in the inset of the right panel of Fig.~\ref{max-vs-magnetisation}.
@@
 Moreover, the middle and right panels only show the data for $a=0.99$ because changing the value of the spin parameter of the black hole only yields a change of scale.
-Therefore, if we choose the range of the graph accordingly, the plots are identical irrespective of the value of $a$.
-\tf{rephrase last sentence better?}
+Therefore, if we chose the range of the graph accordingly, the plots would be identical (same relative differences between the curves) irrespective of the value of $a$.
 

### 2017-04-04 paper.tex
final version including Fragile and Stergioulas comments

@@
 For simplicity we assume that the test-fluid approximation holds, and hence we neglect the self-gravity of the fluid.
-The models are built assuming a particular form of the angular momentum distribution from which the location and morphology of surfaces of equal pressure can be computed.
+The models are built assuming a particular form of the angular momentum distribution from which the location and morphology of equipotential surfaces can be computed.
 This ansatz includes, in particular, the  constant angular momentum case originally employed in the construction of thick tori -- or Polish doughnuts -- and it has already been used to build equilibrium sequences of purely hydrodynamical models.
@@
 Building on these works, we present here the extension of the models of~\citet{Qian:2009} to account for discs endowed with a purely toroidal magnetic field.
-In our procedure we hence assume a form of the angular momentum distribution that departs from the constant case considered by~\cite{Komissarov:2006} and from which the location and morphology
-of surfaces of equal pressure can be numerically computed.
+In our procedure we hence assume a form of the angular momentum distribution that departs from the constant case considered by~\cite{Komissarov:2006} and from which the location and morphology of the equipotential surfaces can be numerically computed.
 As we shall show below, for the particular case of constant angular momentum distributions, our method is in good agreement with the results of~\citet{Komissarov:2006}.
+We also note the recent work of~\citet{Wielgus:2015} where Komissarov's solution was extended for the particular case of power-law distributions of angular momentum.
+Moreover, the magnetised tori of~\citet{Wielgus:2015} were used to explore the growth of the magneto-rotational instabilty (MRI) through time-dependent numerical simulations.
+In particular, the long-term evolution of those tori has been recently investigated by~\citet{Fragile:2017}, who paid special attention to the decay of their magnetisation.
 
@@
 This still leaves us with five parameters to control the size, shape, thickness, and magnetisation of the disc, namely the magnetisation parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$, the parameters of the angular momentum distribution $\beta$ and $\gamma$, the black hole spin parameter $a$, and the inner radius of the disc $r_{\mathrm{in}}$.
-We build a series of 45 models, whose main features are summarised in Table~\ref{table:1} (for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$, i.e.~models where the effects of the magnetisation are unimportant), Table~\ref{table:2} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$, i.e.~equipartition models), and Table~\ref{table:3} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$, i.e.~highly-magnetised models).
+We build a series of 45 models, whose main features are summarised in Table~\ref{table:1} (for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$, i.e.~models where the effects of the magnetisation are unimportant), Table~\ref{table:2} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$, i.e.~equipartition models), and Table~\ref{table:3} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$, i.e.~highly-magnetised models).
 
@@
 A representative sample of the isodensity surfaces for some of our models appears in Figure~\ref{models}.
-We plot, in particular, the models of Table~\ref{table:3}, for which the value of the magnetisation parameter is the highest, $\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$.
+We plot, in particular, the models of Table~\ref{table:3}, for which the magnetisation is highest ($\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$).
 From left to right the columns of this figure correspond to increasing values of the black hole spin, namely, $a=0.5$, 0.9 and 0.99, while from top to bottom the rows correspond to different combinations of the $\gamma$ and $\beta$ parameters that characterize the ansatz for the angular momentum distribution of~\citet{Qian:2009} (the particular values are indicated in the caption of the figure).
@@
 In this paper we have presented a procedure to build equilibrium sequences of magnetised, non-self-gravitating discs around Kerr black holes which combines the two existing approaches of~\citet{Komissarov:2006} and~\citet{Qian:2009}.
-On the one hand we have followed~\citet{Qian:2009} and have assumed a form of the angular momentum distribution in the disc from which the location and morphology of surfaces of equal pressure can be computed.
+On the one hand we have followed~\citet{Qian:2009} and have assumed a form of the angular momentum distribution in the disc from which the location and morphology of surfaces of equal potential can be computed.
 As a limiting case, this ansatz includes the constant angular momentum case originally employed in the construction of thick tori -- or Polish doughnuts~\citep{Abramowicz:1978,Kozlowski:1978}  -- and was already used by~\citet{Qian:2009} to build equilibrium sequences of purely hydrodynamical models.
 On the other hand, our discs are endowed with a purely toroidal magnetic field, as in the work of~\citet{Komissarov:2006}, which provides the methodology we have followed to handle the magnetic terms.
+On a similar note, we cite the work of~\citet{Wielgus:2015} who have recently extended the solution of~\citet{Komissarov:2006} to include non-constant specific angular momentum tori.
+These authors  limited their consideration to power-law distributions and were particularly focused on the stability of such tori to the MRI.
+The approach discussed in our work differs from that of~\citet{Wielgus:2015} and, moreover, we have explored a much wider parameter space.
 
@@
 \begin{acknowledgements}
+It is a pleasure to thank P.~C.~Fragile and N.~Stergioulas for useful discussions and comments.
 Work supported by the Spanish MINECO (grant AYA2015-66899-C2-1-P) and the Generalitat Valenciana (PROMETEOII-2014-069).

### 2017-06-16 paper_revised/referee_reply.txt
-Work on the reply.

Dear A&A Editor,

Thank you for sending us the report of the referee, whom we thank for
carefully reading our manuscript and providing very useful feedback. We 
have made several changes addressing the issues raised in the report, 
which are listed below together with our response. The changes made in 
the manuscript are highlighted in boldface, to facilitate identification. 
We hope that with these amendments the paper will be considered 
acceptable for publication on Astronomy and Astrophysics.

       Best wishes,

       The authors

----------------------------------------------------------------------
Report of the Referee -- AA/2017/30935
----------------------------------------------------------------------

> The paper presents a new procedure to construct sequences of equilibrium
> tori around Kerr black holes that are endowed with a toroidal magnetic
> field. These configurations are not expected to be produced under generic
> conditions but the construction of such equilibria is interesting per se
> and has a rather long history. Furthermore, as discussed by the authors,
> the availability of such equilibria can be employed in test simulations
> of general-relativistic codes in ideal MHD.

> The paper is nicely written with a clear discussion of the procedure
> followed and of the properties of the tori that have been found. The
> paper is essentially ready for publication but there are a few aspects
> that could be improved and that I ask the authors to consider.
>

> - Title: I frankly find it unnecessarily colloquial. I do not insist but
> I think a more pragmatic title such as "A new method for the
> construction of magnetized tori around black holes" is scientifically
> more informative.

We agree with the referee about the title being colloquial. Our choice was
motivated by the title of the paper of Qian et al (2009), “The Polish 
doughnuts revisited …”, of which our paper might be considered an extension 
(by incorporating magnetic fields). We would prefer to keep the original 
title, if the referee concurred. If that were not the case, we would not
object to having it changed to his/her suggestion. (“A new method for the
construction of magnetized tori around black holes”.)

> - Sec. 2.1: the authors introduce the concept of cusp but do not really
> define it

> - Sec. 2.1: they introduce the equation of state (13) but do not discuss
> how they treat the specific internal energy that is part of the
> enthalpy used in (13). A comment should be added.
>

> - Sec. 2.1: I am not clear how the magnetic field is actually
> prescribed. The author mention that the only nonzero component of
> the magnetic field in the comoving frame is the azimuthal one but I am
> still unclear how the strength of this component is specified. A
> comment should be added.

> - Sec. 2.1: More on this topic: do the fluid isobaric surfaces (i.e. the
> surfaces of constant fluid pressure) coincide with the magnetic
> isobaric surfaces (i.e. the surfaces of constant magnetic pressure)?
> How are these surfaces related to the iso-density surfaces? A comment
> should be added.
>

> - Sec. 3: the authors are a bit too sloppy when referring to the fluid
> pressure, which they call respectively: "fluid pressure", "gas
> pressure" "thermal pressure", and sometimes simply as "pressure". Since
> distinguishing the fluid, magnetic and total pressure is important, I
> ask the authors to always just talk of "fluid pressure".

We have followed the recomendation of the referee and in the revised version
of the paper only mentions to “fluid pressure”, “magnetic pressure”, and 
“total pressure” appear. Those appearances are highlighted in boldface
throughout.

> - Sec. 3: similar considerations apply to the density, which should
> be referred to as "rest-mass density"
>

Done.

> - Sec. 3: the authors discuss that the rest-mass density distribution can
> "be trivially obtained inverting the barotropic relation, p = K
> rho^kappa". I am not sure this is so trivial unless an assumption is
> made on the specific internal energy; the authors should discuss more
> clearly how they actually obtain the density from Eqs. (12) and (14).
>

> - Sec. 3: the authors discuss that Eq. (24) diverges for theta --> pi/2,
> i.e. at the equator. I am a bit puzzled by this statement and I wonder if
> this is an exact statement, ie whether it is true that

> partial_theta W = 0 for theta --> pi/2.

> If this is an exact result, I urge the authors to prove it. If it is
> not, I urge the authors to simply mention that the gradients become
> very small.
>

> - Fig. 1: as with the middle panel, I suggest that the right
> panel should also show the logarithm of the rest-mass density.
>

> - Fig. 2: all of the panels would benefit from a legend showing the
> corresponding values of gamma and beta. This would avoid having to read the caption repeatdly. The same is true also for Fig. 3.
>

> - Fig. 4: the caption should be corrected in "beta = 10^3 --> beta_{m_c}
> = 10^3".

> - Fig. 4: the authors do not discuss what is the largest magnetization
> that they can handle. I agree that beta_{m_c} = 10^{-3} is probably
> already quite high, but what happens for say beta_{m_c} = 10^{-6}? Can
> a solution still be found?

> - Sec. 4: I find the discussion in this section the less clear; a lot
> of the considerations appear phenomenological but I can't find the
> simple back-of-the-envelope demonstration that what the authors observe
> numerically is what should be expected on physical grounds. For
> example, the authors find that the rho_max increases with magnetization
> (left panel of Fig. 6) or that the position of the rest-mass density
> maximum moves in with increasing magnetization (middle panel of
> Fig. 6). What are the physical reasons for this behavior? I have some
> suggestions on this but I urge the authors to provide some simple and
> intuitive explanations first.
>

> - References: the list is already quite complete but maybe it can be
> complemented with the following ones, many of which are actually
> written by one of the authors.

> A comprehensive discussion of the properties of tori from merging binaries:

> http://adsabs.harvard.edu/abs/2016arXiv160703540B
>

> First detailed discussion of non-constant specific angular momentum tori:

> http://adsabs.harvard.edu/abs/2004MNRAS.354.1040M

> First discussion of the dynamics of magnetized tori built with the
> Komissarov solution

> http://adsabs.harvard.edu/abs/2007MNRAS.378.1101M

We have incorporated in the article the first and the third references 
suggested by the referee. However, we have not incorporated the second 
reference. While this is a very relevant work in the context of oscillations 
of non-constant-angular momentum disks, including this reference in our 
work seems to us a bit forced since it discusses aspects which are a bit 
away from the main discourse of our paper.

### 2017-06-16 paper_revised/paper_revised.tex
Revised version of the paper.
Work on the reply.

--- 2017-04-04 paper.tex
@@
-\documentclass{aa}
+\documentclass[referee]{aa}
 
@@
 The latter are alluded to in connection with mergers of neutron star binaries and black hole neutron star binaries, as well as with the rotational collapse that ensues at the end of the life of some massive stars.
-As numerical simulations show, such events  often result in a black hole surrounded by a torus (see e.g.~\cite{Rezzolla:2010,Sekiguchi:2011,Faber:2012,Shibata:2011}).
+As numerical simulations show, such events  often result in a black hole surrounded by a torus (see e.g.~\cite{Rezzolla:2010,Sekiguchi:2011,Faber:2012,Shibata:2011,Baiotti:2017}).
 
@@
 This method was later extended by~\cite{Komissarov:2006}  by adding a purely azimuthal magnetic field to build magnetised tori around rotating black holes.
+{\bf Dynamical evolutions of magnetized tori built with the Komissarov solution were first reported by~\cite{Montero:2007}.}
 On the other hand, assuming different distributions of angular momentum in the discs, \citet{Qian:2009} presented a method to build sequences of black hole thick accretion discs in dynamical equilibria, restricted however to the purely hydrodynamical case.
@@
 \end{equation}
-is the energy-momentum tensor of a magnetised perfect fluid, $w$ and $p$ being the fluid enthalpy and pressure, respectively. 
+is the energy-momentum tensor of a magnetised perfect fluid, $w$ and $p$ being the fluid enthalpy and {\bf fluid} pressure, respectively. 
 Moreover, $^\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu}$ is the (dual of the) Faraday tensor relative to an observer with 
@@
 For this reason, Eq.~(\ref{eq:F}) also takes the form of an ordinary differential equation for the surfaces of constant potential, $\theta=\theta(r)$, which, upon integration, yields the location of those surfaces.
-Note that in~\citet{Qian:2009} these are surfaces of constant {\it pressure} instead, since their discs are purely hydrodynamical.
+Note that in~\citet{Qian:2009} these are surfaces of constant {\it {\bf fluid} pressure} instead, since their discs are purely hydrodynamical.
 
@@
 \centering
-\includegraphics[scale=0.16]{figures/fig1a.pdf}
+\includegraphics[scale=0.14]{figures/fig1a.pdf}
 \hspace{-0.3cm}
-\includegraphics[scale=0.16]{figures/fig1b.pdf}
+\includegraphics[scale=0.14]{figures/fig1b.pdf}
 \hspace{-0.2cm}
-\includegraphics[scale=0.16]{figures/fig1c.pdf}
+\includegraphics[scale=0.14]{figures/fig1c.pdf}
 \caption{Comparison with Komissarov's solution for a constant angular momentum model.
-The left panel shows the density distribution in logarithm scale for all radii and all angles while the middle and right panels show, respectively, the angular profile of the logarithm of the density at the centre of the disc and the radial profile of the density at the equatorial plane.}
+The left panel shows the {\bf rest-mass} density distribution in logarithm scale for all radii and all angles while the middle and right panels show, respectively, the angular profile of the logarithm of the {\bf rest-mass} density at the centre of the disc and the radial profile of the {\bf rest-mass} density at the equatorial plane.}
 \label{komissarov}
@@
 Given that we have already obtained both the equipotential surfaces $\theta(r)$ which cross the segment $[r_{\mathrm{cusp}}, r_{\mathrm{c}}]$ at the equatorial plane and the values of the potential in that segment, we can obtain the complete potential distribution for the torus (outside of that segment).
-Once we have the potential distribution, we can find the gas pressure at the centre of the disc from Eq.~\eqref{eq:enthalpy_eq},
+Once we have the potential distribution, we can find the {\bf fluid} pressure at the centre of the disc from Eq.~\eqref{eq:enthalpy_eq},
 \begin{equation}
@@
 Therefore, for a given inner radius of the disc $r_{\mathrm{in}}$ we can obtain the potential $W_{\mathrm{in}}$.
-We now finally have all the ingredients required to find the enthalpy distribution (Eq.~\eqref{eq:enthalpy_eq}), the fluid pressure and magnetic pressure distributions (Eqs.~\eqref{eq:eos_fluid} and \eqref{eq:eos_mag}), and the density distribution, which can be trivially obtained inverting the barotropic relation, $p = K \rho^{\kappa}$.
+We now finally have all the ingredients required to find the enthalpy distribution (Eq.~\eqref{eq:enthalpy_eq}), the fluid pressure and magnetic pressure distributions (Eqs.~\eqref{eq:eos_fluid} and \eqref{eq:eos_mag}), and the {\bf rest-mass} density distribution, which can be trivially obtained inverting the barotropic relation, $p = K \rho^{\kappa}$.
 
@@
 \caption{List of models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$.
-From left to right the columns report: the model name (with A, B and C standing for black hole spin $a = 0.5$, $0.9$ and $0.99$, respectively), the parameters of the angular momentum distribution $\beta$ and $\gamma$, the corresponding radii of the maximum thermal pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential difference between the centre and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the discs, $r_{\mathrm{in}}$ and $r_{\mathrm{out}}$.}
+From left to right the columns report: the model name (with A, B and C standing for black hole spin $a = 0.5$, $0.9$ and $0.99$, respectively), the parameters of the angular momentum distribution $\beta$ and $\gamma$, the corresponding radii of the maximum {\bf fluid} pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential difference between the centre and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the discs, $r_{\mathrm{in}}$ and $r_{\mathrm{out}}$.}
 \label{table:1}      
@@
 The visual comparison shows that our approach can reproduce those previous results with good agreement.
-The density distribution in the $(r\sin\theta,r\cos\theta)$ plane shown in the left panel of Fig.~\ref{komissarov} is remarkably similar to that shown in the left panel of Fig.~2 in~\citet{Komissarov:2006}.
-Not only the morphology of both models is nearly identical but also the range of variation of the density and the location of the disc centre agree well in both cases.
+The {\bf rest-mass} density distribution in the $(r\sin\theta,r\cos\theta)$ plane shown in the left panel of Fig.~\ref{komissarov} is remarkably similar to that shown in the left panel of Fig.~2 in~\citet{Komissarov:2006}.
+Not only the morphology of both models is nearly identical but also the range of variation of the {\bf rest-mass} density and the location of the disc centre agree well in both cases.
 This can be most clearly seen in the middle and right panels of Fig.~\ref{komissarov} which show, repectively, the angular profile at $r_{\rm c}$ and the radial profile at $\theta=\pi/2$.
 These two figures can be directly compared with Fig.~3 of~\citet{Komissarov:2006}.
-It is relevant to mention that very small changes in the location of the inner radius $r_{\mathrm{in}}$ have a significant effect on the maximum value of the density, which explains the small differences between our figures and the ones presented in~\citet{Komissarov:2006}.
+It is relevant to mention that very small changes in the location of the inner radius $r_{\mathrm{in}}$ have a significant effect on the maximum value of the {\bf rest-mass} density, which explains the small differences between our figures and the ones presented in~\citet{Komissarov:2006}.
 
@@
 \centering
-\includegraphics[scale=0.16]{figures/fig2_1_1.pdf}
+\includegraphics[scale=0.14]{figures/fig2_1_1.pdf}
 \hspace{-0.3cm}
-\includegraphics[scale=0.16]{figures/fig2_1_2.pdf}
+\includegraphics[scale=0.14]{figures/fig2_1_2.pdf}
 \hspace{-0.2cm}
-\includegraphics[scale=0.16]{figures/fig2_1_3.pdf}
+\includegraphics[scale=0.14]{figures/fig2_1_3.pdf}
 \\
-\includegraphics[scale=0.16]{figures/fig2_2_1.pdf}
+\includegraphics[scale=0.14]{figures/fig2_2_1.pdf}
 \hspace{-0.3cm}
-\includegraphics[scale=0.16]{figures/fig2_2_2.pdf}
+\includegraphics[scale=0.14]{figures/fig2_2_2.pdf}
 \hspace{-0.2cm}
-\includegraphics[scale=0.16]{figures/fig2_2_3.pdf}
+\includegraphics[scale=0.14]{figures/fig2_2_3.pdf}
 \\
-\includegraphics[scale=0.16]{figures/fig2_3_1.pdf}
+\includegraphics[scale=0.14]{figures/fig2_3_1.pdf}
 \hspace{-0.3cm}
-\includegraphics[scale=0.16]{figures/fig2_3_2.pdf}
+\includegraphics[scale=0.14]{figures/fig2_3_2.pdf}
 \hspace{-0.2cm}
-\includegraphics[scale=0.16]{figures/fig2_3_3.pdf}
+\includegraphics[scale=0.14]{figures/fig2_3_3.pdf}
 \\
-\includegraphics[scale=0.16]{figures/fig2_4_1.pdf}
+\includegraphics[scale=0.14]{figures/fig2_4_1.pdf}
 \hspace{-0.3cm}
-\includegraphics[scale=0.16]{figures/fig2_4_2.pdf}
+\includegraphics[scale=0.14]{figures/fig2_4_2.pdf}
 \hspace{-0.2cm}
-\includegraphics[scale=0.16]{figures/fig2_4_3.pdf}
+\includegraphics[scale=0.14]{figures/fig2_4_3.pdf}
 \\
-\includegraphics[scale=0.16]{figures/fig2_5_1.pdf}
+\includegraphics[scale=0.14]{figures/fig2_5_1.pdf}
 \hspace{-0.3cm}
-\includegraphics[scale=0.16]{figures/fig2_5_2.pdf}
+\includegraphics[scale=0.14]{figures/fig2_5_2.pdf}
 \hspace{-0.2cm}
-\includegraphics[scale=0.16]{figures/fig2_5_3.pdf}
+\includegraphics[scale=0.14]{figures/fig2_5_3.pdf}
 \caption{Isodensity distributions for all models of Table~\ref{table:3}.
@@
 \centering
-\includegraphics[scale=0.16]{figures/fig3a.pdf}
+\includegraphics[scale=0.14]{figures/fig3a.pdf}
 \hspace{-0.3cm}
-\includegraphics[scale=0.16]{figures/fig3b.pdf}
+\includegraphics[scale=0.14]{figures/fig3b.pdf}
 \hspace{-0.2cm}
-\includegraphics[scale=0.16]{figures/fig3c.pdf}
+\includegraphics[scale=0.14]{figures/fig3c.pdf}
 \caption{Effects of the magnetisation in the structure of the disc. From left to right the values are $\beta_{\mathrm{m}_{\mathrm{c}}}
@@
 As $\gamma$ and $\beta$ increase from 0 to 0.9 (compare the three top rows) the discs become significantly thinner and radially smaller (see also Fig.~\ref{more-profile} below).
-It is also interesting to note that the maximum value of the density is higher (with respect to the value at the disc centre) as the spin increases.
+It is also interesting to note that the maximum value of the {\bf rest-mass} density is higher (with respect to the value at the disc centre) as the spin increases.
 
@@
 \includegraphics[scale=0.2]{figures/fig4.pdf}
-\caption{Radial profiles of the density in the equatorial plane for $\beta=10^3$ (black curve), 1 (blue curve), and $10^{-3}$ (green curve). }
+\caption{Radial profiles of the {\bf rest-mass} density in the equatorial plane for $\beta=10^3$ (black curve), 1 (blue curve), and $10^{-3}$ (green curve). }
 \label{magnetisation-profile}
@@
 \centering
-\includegraphics[scale=0.16]{figures/fig6a.pdf}
+\includegraphics[scale=0.14]{figures/fig6a.pdf}
 \hspace{-0.3cm}
-\includegraphics[scale=0.16]{figures/fig6b.pdf}
+\includegraphics[scale=0.14]{figures/fig6b.pdf}
 \hspace{-0.2cm}
-\includegraphics[scale=0.16]{figures/fig6c.pdf}
+\includegraphics[scale=0.14]{figures/fig6c.pdf}
 \caption{Effects of $\beta_{\mathrm{m}_{\mathrm{c}}}$.
-Left panel: variation of the value of the maximum density with respect to the logarithm of the magnetisation parameter.
+Left panel: variation of the value of the maximum {\bf rest-mass} density with respect to the logarithm of the magnetisation parameter.
 The solid, dashed, and dotted lines refer to $a = 0.99$, $0.9$ and $0.5$, respectively, and the colour code refers to the models shown in the legend.
-Middle panel: variation of the location of the density maximum (and thermal pressure) with respect to the logarithm of the magnetisation parameter for the three models shown in the legend with $a = 0.99$.
+Middle panel: variation of the location of the {\bf rest-mass} density maximum (and {\bf fluid} pressure) with respect to the logarithm of the magnetisation parameter for the three models shown in the legend with $a = 0.99$.
 Right panel: variation (also for $a = 0.99$) of the location of the maximum of the magnetic pressure with respect to the logarithm of $\beta_{\mathrm{m}_{\mathrm{c}}}$.}
@@
 $ and the only quantitative differences are found in the location of the centre of the disc (which moves inward with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$) and of the range of variation of the isodensity contours (the maximum being slightly larger with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$).
-This can be more clearly visualized in Figure~\ref{magnetisation-profile} which displays the radial profile at the equatorial plane of the density for the same three cases plotted in Fig.~\ref{magnetisation}.
+This can be more clearly visualized in Figure~\ref{magnetisation-profile} which displays the radial profile at the equatorial plane of the {\bf rest-mass} density for the same three cases plotted in Fig.~\ref{magnetisation}.
 
@@
 As mentioned in the description of Fig.~\ref{models} as $\gamma$ and $\beta$ increase from 0 to 0.9 (compare black, blue, and green curves) the discs become gradually smaller.
-At the same time, the radial location of the density maximum increases and the maximum value of the central density (and pressure) decreases.
+At the same time, the radial location of the {\bf rest-mass} density maximum increases and the maximum value of the central {\bf rest-mass} density (and pressure) decreases.
 It is worth noticing that the radial profiles of some of the models overlap below a certain radius.
 More precisely, the black and red curves overlap below $r\sim r_{\mathrm{c}}$ (which corresponds to $\rho \sim 1$) and also the green and orange curves.
-In addition, this figure clearly shows that, besides modifying the thickness of the disc, $\beta$ is the parameter which determines the value of the density (and pressure) maximum.
+In addition, this figure clearly shows that, besides modifying the thickness of the disc, $\beta$ is the parameter which determines the value of the {\bf rest-mass} density (and pressure) maximum.
 On the other hand, the parameter $\gamma$ is only relevant for controlling the radial size of the discs.
 
-In order to provide a quantitative comparison of the structural differences that appear along the sequence of equilibrium models, we plot in Fig.~\ref{max-vs-magnetisation} the variation of the maximum of the density (left panel), the radial location of the maximum of the thermal pressure (middle panel), and the radial location of the maximum of the magnetic pressure (right panel) as a function of the magnetisation parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$.
+In order to provide a quantitative comparison of the structural differences that appear along the sequence of equilibrium models, we plot in Fig.~\ref{max-vs-magnetisation} the variation of the maximum of the {\bf rest-mass} density (left panel), the radial location of the maximum of the {\bf fluid} pressure (middle panel), and the radial location of the maximum of the magnetic pressure (right panel) as a function of the magnetisation parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$.
 All quantities plotted are measured at the equatorial plane.
@@
 Correspondingly, the colour of the lines indicates the value of $\beta$ and $\gamma$ used, namely, red curves correspond to $\gamma=\beta=0$, the blue ones to $\gamma=\beta=0.5$, and the black ones to $\gamma=\beta=0.9$.
-All curves show the same monotonically decreasing trend with $\beta_{\mathrm{m}_{\mathrm{c}}}
-$, yet for small enough and large enough values of $\beta_{\mathrm{m}_{\mathrm{c}}} $ the value of the density maximum does not change.
+All curves show the same monotonically decreasing trend with $\beta_{\mathrm{m}_{\mathrm{c}}}$, yet for small enough and large enough values of $\beta_{\mathrm{m}_{\mathrm{c}}} $ the value of the {\bf rest-mass} density maximum does not change.
 However, in the interval $10^{-2}\le \beta_{\mathrm{m}_{\mathrm{c}}} \le 10^{2}$, $\rho_{\rm max}$ changes abruptly.
-The larger the black hole spin the larger the drop in the maximum of the density.
+The larger the black hole spin the larger the drop in the maximum of the {\bf rest-mass} density.
 For sufficiently large values of $\beta_{\mathrm{m}_{\mathrm{c}}}$ (small magnetisation) the value of $\rho_{\rm max}$ stays constant to the same value irrespective of the black hole rotation.
 
-In the middle panel of Fig.~\ref{max-vs-magnetisation} we show the radial location of the maximum of the thermal pressure as a function of $\beta_{\mathrm{m}_{\mathrm{c}}}$.
+In the middle panel of Fig.~\ref{max-vs-magnetisation} we show the radial location of the maximum of the {\bf fluid} pressure as a function of $\beta_{\mathrm{m}_{\mathrm{c}}}$.
 The black hole spin is $a=0.99$ and the values of $\beta$ and $\gamma$ are indicated in the legend.
-For all values of $\beta$ and $\gamma$, the maximum of the location of the disc thermal pressure decreases with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$.
+For all values of $\beta$ and $\gamma$, the maximum of the location of the disc {\bf fluid} pressure decreases with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$.
 Below $\beta_{\mathrm{m}_{\mathrm{c}}}\sim 10^{-3}$ the location of the maximum does no longer change.

### 2017-06-16 paper_revised/paper_revised.tex
A little more work on the paper.

@@
 For this choice of $\eta$, we can find the location of the cusp of the disc  within the range $r_{\mathrm{mb}} \leq r_{\mathrm{cusp}} \leq r_{\mathrm{ms}}$ (for $0 \leq \beta \leq 1$).
-Moreover, this value of $\eta$ guarantees that constant angular momentum discs ($\beta = \gamma = 0$) with their inner edge located at the cusp ($r_{\mathrm{in}} = r_{\mathrm{cusp}}$) have no outer boundary, i.e~they are infinite discs (see also~\cite{Font:2002}).
+{\bf The cusp is defined as the circle in the equatorial plane on which the pressure gradient vanishes and the angular momentum of the disc equals the Keplerian angular momentum.} Moreover, this value of $\eta$ guarantees that constant angular momentum discs ($\beta = \gamma = 0$) with their inner edge located at the cusp ($r_{\mathrm{in}} = r_{\mathrm{cusp}}$) have no outer boundary, i.e~they are infinite discs (see also~\cite{Font:2002}).
 

### 2017-06-19 paper_revised/paper_revised.tex
corrected minor typo

@@
 with $K$ and $\kappa$ constants.
-Then, we define the magnetic pressure as $p_{\mathrm{m}} = b^2/2$, and introduce the definitions $\tilde{p}_{\mathrm{m}} = \mathcal{L} p_{\mathrm{m}}$ and $\tilde{w} = \mathcal{L} w$, in order to write an analog equation to Eq.~\eqref{eq:eos_fluid} for $\tilde{p}_{\mathrm{m}}$~\citep{Komissarov:2006}
+Then, we define the magnetic pressure as $p_{\mathrm{m}} = b^2/2$, and introduce the definitions $\tilde{p}_{\mathrm{m}} = \mathcal{L} p_{\mathrm{m}}$ and $\tilde{w} = \mathcal{L} w$, in order to write an analogue equation to Eq.~\eqref{eq:eos_fluid} for $\tilde{p}_{\mathrm{m}}$~\citep{Komissarov:2006}
 \begin{equation}\label{eq:eos_mag_tilde}

### 2017-06-20 paper_revised/reply_referee.tex
added reply_referee.tex

%
% version 27.10.16
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%        reply
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{article}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{amsfonts}
\textheight 22.cm
\textwidth 16.5 cm
\oddsidemargin 0.5cm
\evensidemargin 0.5cm
\topmargin=-1.cm
\hoffset -0.5cm
 \usepackage{amssymb}

\tolerance=10000
\pagenumbering{arabic}
\textheight 22.cm
\textwidth 16.5 cm
\oddsidemargin 0.5cm\evensidemargin 0.5cm
\topmargin=-1.cm
\hoffset -0.5cm
\date{\today}

\newcommand{\bnabla}{\mbox{\boldmath $\nabla$}}
%\newcommand{\bomega}{\mbox{\boldmath $\omega$}}
\newcommand{\bOmega}{\mbox{\boldmath $\Omega$}}

\newcommand{\insertplot}[5]{\begin{figure}
 \hfill\hbox to 0.05in{\vbox to #5in{\vfill
 \inputplot{#1}{#4}{#5}}\hfill}
 \hfill\vspace{-.1in}
 \caption{#2}\label{#3}
 \end{figure}}
 \newcommand{\inputplot}[3]{\special{ps:: gsave #2 -36 mul 0 rmoveto
   currentpoint translate #2 7.0 div #3 5.0 div scale}
 \special{ps: plotfile #1}\special{ps:: grestore}}
\newcounter{fig}   \newcommand{\lbfig}[1]{\refstepcounter{fig}
\label{#1} }

\newcommand{\vphi}{\varphi}
\newcommand{\DS}{\displaystyle}
\newcommand{\pih}{\frac{\pi}{2}}
\newcommand{\sqdetg}{\sqrt{-g}}
\newcommand{\sqdetgi}{\frac{1}{\sqrt{-g}}}
\newcommand{\edil}{e^{2\kappa \phi}}
\newcommand{\bA}{\bar{A}}
\newcommand{\bF}{\bar{F}}
\newcommand{\bD}{\bar{D}}

\renewcommand{\a}{\alpha}
\renewcommand{\b}{\beta}
\renewcommand{\c}{\gamma}
\renewcommand{\d}{\delta}  
\newcommand{\g}{\nu}
\renewcommand{\l}{\lambda}
\renewcommand{\t}{\theta}
\newcommand{\rot}{\mbox{rot}}
\renewcommand{\div}{\mbox{div}}
\newcommand{\cosec}{\mbox{cosec}}

\newcommand{\ta}{\theta}
\newcommand{\Si}{\Sigma}
\newcommand{\vf}{\varphi}
\newcommand{\dd}{\mbox{d}}
\newcommand{\tr}{\mbox{tr}}
\newcommand{\la}{\lambda}
\newcommand{\ka}{\kappa}
\newcommand{\f}{\phi}
\newcommand{\al}{\alpha}
\newcommand{\ga}{\gamma}
\newcommand{\de}{\delta}
\newcommand{\si}{\sigma}
\newcommand{\bomega}{\mbox{\boldmath $\omega$}}
\newcommand{\bsi}{\mbox{\boldmath $\sigma$}}
\newcommand{\bchi}{\mbox{\boldmath $\chi$}}
\newcommand{\bal}{\mbox{\boldmath $\alpha$}}
\newcommand{\bpsi}{\mbox{\boldmath $\psi$}}
\newcommand{\brho}{\mbox{\boldmath $\varrho$}}
\newcommand{\beps}{\mbox{\boldmath $\varepsilon$}}
\newcommand{\bxi}{\mbox{\boldmath $\xi$}}
\newcommand{\bbeta}{\mbox{\boldmath $\beta$}}
\newcommand{\ee}{\end{equation}}
\newcommand{\eea}{\end{eqnarray}}
\newcommand{\be}{\begin{equation}}
\newcommand{\bea}{\begin{eqnarray}}

\newcommand{\pont}{{\,^\ast\!}R\,R}

\newcommand{\ii}{\mbox{i}}
\newcommand{\e}{\mbox{e}}
\newcommand{\pa}{\partial}
\newcommand{\Om}{\Omega}
\newcommand{\vep}{\varepsilon}
%\newcommand{\bfR}{{\bf R}}
\newcommand{\bfph}{{\bf \phi}}
\newcommand{\lm}{\lambda}
\def\theequation{\arabic{equation}}
%\topmargin= -02cm\textheight= 23.cm\textwidth= 16.cm
%\oddsidemargin=-01cm\evensidemargin=-01cm \font\sqi=cmssq8
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\newcommand{\re}[1]{(\ref{#1})}
\newcommand{\R}{{\rm I \hspace{-0.52ex} R}}
\newcommand{\N}{{\sf N\hspace*{-1.0ex}\rule{0.15ex}%
{1.3ex}\hspace*{1.0ex}}}
\newcommand{\Q}{{\sf Q\hspace*{-1.1ex}\rule{0.15ex}%
{1.5ex}\hspace*{1.1ex}}}
\newcommand{\C}{{\sf C\hspace*{-0.9ex}\rule{0.15ex}%
{1.3ex}\hspace*{0.9ex}}}
\newcommand{\eins}{1\hspace{-0.56ex}{\rm I}}
\renewcommand{\thefootnote}{\arabic{footnote}}

\def\theequation{\thesection.\arabic{equation}}

\begin{document}

\title{ 
{\bf Reply to the  Referee report:} \\ {\large AA/2017/30935} \\  {\large  \textit{Magnetised Polish doughnuts revisited}\\ by Sergio Gimeno-Soler and Jos\'e A. Font.}
}

\maketitle

Dear A\&A Editor,

\bigskip

Thank you for sending us the report of the referee, whom we thank for
carefully reading our manuscript and providing very useful feedback. We 
have made several changes addressing the issues raised in the report, 
which are listed below together with our response. The changes made in 
the manuscript are highlighted in boldface, to facilitate identification. 
We hope that with these amendments the paper will be considered 
acceptable for publication on \textit{Astronomy and Astrophysics}.

\bigskip

Best wishes,

\bigskip

The authors

\bigskip

\section*{Referee report -- AA/2017/30935}

We are grateful to the referee for the interesting comments provided in his/her report.
We have followed the referee's suggestions and have incorporated most of his/her comments 
in our manuscript. Below, we ({\bf A}) address the various issues raised by the referee ({\bf R}).

\bigskip

{\bf R:} The paper presents a new procedure to construct sequences of equilibrium
tori around Kerr black holes that are endowed with a toroidal magnetic
field. These configurations are not expected to be produced under generic
conditions but the construction of such equilibria is interesting per se
and has a rather long history. Furthermore, as discussed by the authors,
the availability of such equilibria can be employed in test simulations
of general-relativistic codes in ideal MHD.The paper is nicely written with a clear discussion of the procedure
followed and of the properties of the tori that have been found. The
paper is essentially ready for publication but there are a few aspects
that could be improved and that I ask the authors to consider.

\bigskip

{\bf R:} - Title: I frankly find it unnecessarily colloquial. I do not insist but
I think a more pragmatic title such as ``A new method for the
construction of magnetized tori around black holes" is scientifically
more informative.

\bigskip

{\bf A:} We agree with the referee about the title being colloquial. Our choice was
motivated by the title of the paper of Qian et al (2009), ``The Polish 
doughnuts revisited …", of which our paper might be considered an extension 
(by incorporating magnetic fields). We would prefer to keep the original 
title, if the referee concurred. If that were not the case, we would not
object to having it changed to his/her suggestion. (``A new method for the
construction of magnetized tori around black holes".)

\bigskip

{\bf R:} - Sec. 2.1: the authors introduce the concept of cusp but do not really
define it

\bigskip

{\bf A:} We have included the following definition: ``The cusp is defined as the circle 
in the equatorial plane on which the pressure gradient vanishes and the angular 
momentum of the disk equals the Keplerian angular momentum."

\bigskip

{\bf R:} - Sec. 2.1: they introduce the equation of state (13) but do not discuss
how they treat the specific internal energy that is part of the
enthalpy used in (13). A comment should be added.

\bigskip

{\bf A:}

\bigskip

{\bf R:} - Sec. 2.1: I am not clear how the magnetic field is actually
prescribed. The author mention that the only nonzero component of
the magnetic field in the comoving frame is the azimuthal one but I am
still unclear how the strength of this component is specified. A
comment should be added.

\bigskip

{\bf A:}

\bigskip

{\bf R:} - Sec. 2.1: More on this topic: do the fluid isobaric surfaces (i.e. the
surfaces of constant fluid pressure) coincide with the magnetic
isobaric surfaces (i.e. the surfaces of constant magnetic pressure)?
How are these surfaces related to the iso-density surfaces? A comment
should be added.

\bigskip

{\bf A:}

\bigskip

{\bf R:} - Sec. 3: the authors are a bit too sloppy when referring to the fluid
pressure, which they call respectively: ``fluid pressure", ``gas
pressure" ``thermal pressure", and sometimes simply as ``pressure". Since
distinguishing the fluid, magnetic and total pressure is important, I
ask the authors to always just talk of ``fluid pressure".

\bigskip

{\bf A:} We have followed the recomendation of the referee and in the revised version
of the paper only mentions to ``fluid pressure", ``magnetic pressure", and 
``total pressure" appear. Those appearances are highlighted in boldface
throughout.

\bigskip

{\bf R:} - Sec. 3: similar considerations apply to the density, which should
be referred to as ``rest-mass density"

\bigskip

{\bf A:} Done.

\bigskip

{\bf R:} - Sec. 3: the authors discuss that the rest-mass density distribution can
``be trivially obtained inverting the barotropic relation, $p = K
rho^kappa$". I am not sure this is so trivial unless an assumption is
made on the specific internal energy; the authors should discuss more
clearly how they actually obtain the density from Eqs. (12) and (14).

\bigskip

{\bf A:}

\bigskip

{\bf R:} - Sec. 3: the authors discuss that Eq. (24) diverges for $\theta \rightarrow \pi/2$,
i.e. at the equator. I am a bit puzzled by this statement and I wonder if
this is an exact statement, ie whether it is true that

\begin{equation}
\partial_{\theta} W = 0 \ \mathrm{for} \ \theta \rightarrow \frac{\pi}{2}.
\end{equation}

If this is an exact result, I urge the authors to prove it. If it is
not, I urge the authors to simply mention that the gradients become
very small.

\bigskip

{\bf A:}

\bigskip

{\bf R:} - Fig. 1: as with the middle panel, I suggest that the right
panel should also show the logarithm of the rest-mass density.

\bigskip

{\bf A:}

\bigskip

{\bf R:} - Fig. 2: all of the panels would benefit from a legend showing the
corresponding values of gamma and beta. This would avoid having to read the caption repeatdly. The same is true also for Fig. 3.

\bigskip

{\bf A:}

\bigskip

{\bf R:} - Fig. 4: the caption should be corrected in ``$\beta = 10^3$ --> $\beta_{m_c}
= 10^3$".

\bigskip

{\bf A:}

\bigskip

{\bf R:} - Fig. 4: the authors do not discuss what is the largest magnetization
that they can handle. I agree that $\beta_{m_c} = 10^{-3}$ is probably
already quite high, but what happens for say $\beta_{m_c} = 10^{-6}$? Can
a solution still be found?

\bigskip

{\bf A:}

\bigskip

{\bf R:} - Sec. 4: I find the discussion in this section the less clear; a lot
of the considerations appear phenomenological but I can't find the
simple back-of-the-envelope demonstration that what the authors observe
numerically is what should be expected on physical grounds. For
example, the authors find that the $\rho_{\mathrm{max}}$ increases with magnetization
(left panel of Fig. 6) or that the position of the rest-mass density
maximum moves in with increasing magnetization (middle panel of
Fig. 6). What are the physical reasons for this behavior? I have some
suggestions on this but I urge the authors to provide some simple and
intuitive explanations first.

\bigskip

{\bf A:}

\bigskip

{\bf R:} - References: the list is already quite complete but maybe it can be
complemented with the following ones, many of which are actually
written by one of the authors.

A comprehensive discussion of the properties of tori from merging binaries:

http://adsabs.harvard.edu/abs/2016arXiv160703540B

First detailed discussion of non-constant specific angular momentum tori:

http://adsabs.harvard.edu/abs/2004MNRAS.354.1040M

First discussion of the dynamics of magnetized tori built with the Komissarov solution

http://adsabs.harvard.edu/abs/2007MNRAS.378.1101M

\bigskip

{\bf A:} We have incorporated in the article the first and the third references 
suggested by the referee. However, we have not incorporated the second 
reference. While this is a very relevant work in the context of oscillations 
of non-constant-angular momentum disks, including this reference in our 
work seems to us a bit forced since it discusses aspects which are a bit 
away from the main discourse of our paper.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
\begin{small}
\begin{thebibliography}{99}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
%

%  
\end{thebibliography}

 \end{small}

 \end{document}

### 2017-06-21 paper_revised/reply_referee.tex
two questions answered

@@
 ``be trivially obtained inverting the barotropic relation, $p = K
-rho^kappa$". I am not sure this is so trivial unless an assumption is
+\rho^{\kappa}$". I am not sure this is so trivial unless an assumption is
 made on the specific internal energy; the authors should discuss more
@@
 
-{\bf A:}
+{\bf A:} We present the proof for this statement:
+
+Equation (22) of the paper gives us
+
+\begin{equation}
+\partial_{\theta} W = \partial_{\theta} \ln|u_t| - \frac{\Omega \partial_{\theta}l}{1 - \Omega l}\, = 0.
+\end{equation}
+
+Then, we can prove the two terms of this equation are equal to zero for $\theta = \pi/2$.
+
+First, we take the derivative of the angular momentum distribution $\partial_{\theta} l$.
+Looking at equation (7), we can write the angular momentum distribution as $l(r, \theta) = l(r) \sin^{2\gamma} \theta$, so we can write the derivative as
+
+\begin{equation}
+\partial_{\theta} l = 2\gamma l(r) \sin^{2\gamma - 1} \theta \cos \theta
+\end{equation}
+
+Taking $\theta = \pi/2$ means $\partial_{\theta} l = 0$, so the second term equals to zero.
+
+To show that the first term is also zero, we write it as
+
+\begin{equation}
+\partial_{\theta} \ln|u_t| = \partial_{\theta} \ln \left(\frac{\mathcal{L}}{\mathcal{A}}\right)^{\frac{1}{2}}
+\end{equation}
+
+where $\mathcal{L} = g_{t \phi}^2 - g_{tt} g_{\phi\phi}$ and $\mathcal{A} = g_{\phi\phi} + 2 l g_{t\phi} + l^2g_{tt}$ and we have dropped the absolute value, as it is irrelevant to this discussion.
+Then, the derivative is
+
+\begin{equation}
+\partial_{\theta} \ln|u_t| = \frac{1}{2} \frac{\mathcal{A}}{\mathcal{L}}\frac{\partial_{\theta}{\mathcal{L}}\mathcal{A} - \mathcal{L}\partial_{\theta}\mathcal{A}}{\mathcal{A}^2} = \frac{1}{2} \frac{\partial_{\theta}{\mathcal{L}}\mathcal{A} - \mathcal{L}\partial_{\theta}\mathcal{A}}{\mathcal{A} \mathcal{L}}
+\end{equation}
+
+We use Boyer-Lindquist coordinates, so we can write the metric components as
+
+\begin{equation}
+g_{tt} = - \left(1 - \frac{2Mr}{\rho^2}\right), \ g_{t\phi} = -\frac{2Mar\sin^2\theta}{\rho^2}, \ g_{\phi\phi} = \left(r^2 + a^2 + \frac{2Ma^2r\sin^2\theta}{\rho^2}\right) \sin^2 \theta,
+\end{equation}
+
+where $\rho^2 = r^2 + a^2\cos^2 \theta$.
+Given this particular coordinates, we can write $\mathcal{L}$ as $\mathcal{L} = \Delta \sin^2 \theta$, where $\Delta = r^2 - 2Mr + a^2$, then $\partial_{\theta}\mathcal{L} = 2\gamma \Delta \sin^{2\gamma - 1} \theta \cos \theta$, which is zero for $\theta = \pi/2$.
+Now, we take the derivative of $\mathcal{A}$
+
+\begin{equation}
+\partial_{\theta} \mathcal{A} = \partial_{\theta} g_{\phi\phi} + 2 (\partial_{\theta} l) g_{t\phi} + 2l\partial_{\theta} g_{t\phi} + 2l(\partial_{\theta} l) g_{tt} + l^2 \partial_{\theta} g_{tt} = \partial_{\theta} g_{\phi\phi} + 2l\partial_{\theta} g_{t\phi} + l^2 \partial_{\theta} g_{tt},
+\end{equation}
+
+where we have used the previous result on $\partial_{\theta} l$.
+If we inspect the metric components, is easy to see that all the terms depending on $\theta$ are functions of $\sin^2 \theta$ or $\cos^2 \theta$.
+This means their $\theta$ derivatives will have at least a $\cos \theta$ multiplying.
+Then $\partial_{\theta} \mathcal{A} = 0$.
+Then $\partial_{\theta} \ln|u_t|$ is also zero.
 
@@
 
-{\bf R:} - Fig. 4: the caption should be corrected in ``$\beta = 10^3$ --> $\beta_{m_c}
+{\bf R:} - Fig. 4: the caption should be corrected in ``$\beta = 10^3$ $\rightarrow $ $\beta_{m_c}
 = 10^3$".
@@
 
-{\bf A:}
+{\bf A:} Done.
 

### 2017-06-21 paper_revised/paper_revised.tex
two questions answered

@@
 \includegraphics[scale=0.2]{figures/fig4.pdf}
-\caption{Radial profiles of the {\bf rest-mass} density in the equatorial plane for $\beta=10^3$ (black curve), 1 (blue curve), and $10^{-3}$ (green curve). }
+\caption{Radial profiles of the {\bf rest-mass} density in the equatorial plane for \bf{$\beta_{\mathrm{m}_{\mathrm{c}}}=10^3$} (black curve), 1 (blue curve), and $10^{-3}$ (green curve). }
 \label{magnetisation-profile}

### 2017-06-28 paper_revised/reply_referee.tex
modificaciones en la respuesta

@@
 
-{\bf A:}
+{\bf A:} The specific internal energy $\varepsilon$ is obtained by combining the ideal fluid (gamma-law)
+equation of state which, in the notation used in the paper we write $P=(\kappa-1)\rho\varepsilon$,
+and the barotropic equation of state. Solving for $\varepsilon$ we obtain
+\begin{eqnarray*}
+\varepsilon=\frac{K}{\kappa-1}\rho^{\kappa-1}\,.
+\end{eqnarray*}
+We have incorporated the following statements at the end of the paragraph after Eq.~(14):
+``We note that the specific internal energy $\varepsilon$ is needed to compute the enthalpy. We obtain
+this quantity by combining the ideal fluid and the barotropic equations of state, which yields 
+$\varepsilon=\frac{K}{\kappa-1}\rho^{\kappa-1}$."
+
+\bigskip
+
+{\bf Toni: creo que la expresi\'on anterior es incorrecta porque estoy usando $\rho$ cuando deber\'{\i}a usar $\omega$. Tenemos que
+hablarlo.\}
 

### 2017-06-28 paper_revised/reply_referee.tex
minor typo
more work on the reply

@@
 
-{\bf A:} The specific internal energy $\varepsilon$ is obtained by combining the ideal fluid (gamma-law)
-equation of state which, in the notation used in the paper we write $P=(\kappa-1)\rho\varepsilon$,
-and the barotropic equation of state. Solving for $\varepsilon$ we obtain
-\begin{eqnarray*}
-\varepsilon=\frac{K}{\kappa-1}\rho^{\kappa-1}\,.
-\end{eqnarray*}
-We have incorporated the following statements at the end of the paragraph after Eq.~(14):
-``We note that the specific internal energy $\varepsilon$ is needed to compute the enthalpy. We obtain
-this quantity by combining the ideal fluid and the barotropic equations of state, which yields 
-$\varepsilon=\frac{K}{\kappa-1}\rho^{\kappa-1}$."
-
-\bigskip
-
-{\bf Toni: creo que la expresi\'on anterior es incorrecta porque estoy usando $\rho$ cuando deber\'{\i}a usar $\omega$. Tenemos que
-hablarlo.\}
+{\bf A:} We address this issue below where the referee comments on the ``assumption of the specific
+internal energy", since we believe both queries are related.
 
@@
 {\bf A:} 
+The specific internal energy $\varepsilon$ is obtained by combining the ideal fluid (gamma-law)
+equation of state which, in the notation used in the paper we write $P=(\kappa-1)\rho\varepsilon$,
+and the barotropic equation of state. Solving for $\varepsilon$ we obtain
+\begin{eqnarray*}
+\varepsilon=\frac{K}{\kappa-1}\rho^{\kappa-1}\,.
+\end{eqnarray*}
+We have incorporated the following statements at the end of the paragraph after Eq.~(27):
+``We note that the specific internal energy $\varepsilon$ is needed to compute the enthalpy. We obtain
+this quantity by combining the ideal fluid and the barotropic equations of state, which yields 
+$\varepsilon=\frac{K}{\kappa-1}\rho^{\kappa-1}$."
 

### 2017-06-28 paper_revised/reply_referee.tex
more work on the reply

@@
 
-{\bf R:} - Sec. 3: the authors discuss that Eq. (24) diverges for $\theta \rightarrow \pi/2$,
+{\bf R:} - Sec. 3: the authors discuss that Eq.~(24) diverges for $\theta \rightarrow \pi/2$,
 i.e. at the equator. I am a bit puzzled by this statement and I wonder if
@@
 
-{\bf A:} We present the proof for this statement:
+{\bf A:} We believe this is an exact result and present the proof below:
 
-Equation (22) of the paper gives us
+\bigskip
 
-\begin{equation}
+Eq.~(22) of the paper gives us
+
+\begin{eqnarray*}
 \partial_{\theta} W = \partial_{\theta} \ln|u_t| - \frac{\Omega \partial_{\theta}l}{1 - \Omega l}\, = 0.
-\end{equation}
+\end{eqnarray*}
 
-Then, we can prove the two terms of this equation are equal to zero for $\theta = \pi/2$.
+Then, we have to prove that either the two terms of this equation are equal or they  are identically zero at $\theta = \pi/2$. We shall see that the latter is true.
+First, we take the derivative of the angular momentum distribution $\partial_{\theta} l$.
+From Eq.~(7) we can write the angular momentum distribution as $l(r, \theta) = l(r) \sin^{2\gamma} \theta$, so that the derivative reads
+\begin{eqnarray*}
+\partial_{\theta} l = 2\gamma l(r) \sin^{2\gamma - 1} \theta \cos \theta \,.
+\end{eqnarray*}
+Taking $\theta = \pi/2$ leads to $\partial_{\theta} l = 0$, so the second term equals to zero.
+To show that the first term is also zero, we write it as
+\begin{eqnarray*}
+\partial_{\theta} \ln|u_t| = \partial_{\theta} \ln \left(\frac{\mathcal{L}}{\mathcal{A}}\right)^{\frac{1}{2}}\,,
+\end{eqnarray*}
+where $\mathcal{L} = g_{t \phi}^2 - g_{tt} g_{\phi\phi}$ and $\mathcal{A} = g_{\phi\phi} + 2 l g_{t\phi} + l^2g_{tt}$, and we have dropped the absolute value, as it is irrelevant to this discussion.
+Then, the derivative is
+\begin{eqnarray*}
+\partial_{\theta} \ln|u_t| = \frac{1}{2} \frac{\mathcal{A}}{\mathcal{L}}\frac{\partial_{\theta}{\mathcal{L}}\mathcal{A} - \mathcal{L}\partial_{\theta}\mathcal{A}}{\mathcal{A}^2} = \frac{1}{2} \frac{\partial_{\theta}{\mathcal{L}}\mathcal{A} - \mathcal{L}\partial_{\theta}\mathcal{A}}{\mathcal{A} \mathcal{L}}\,.
+\end{eqnarray*}
+We use Boyer-Lindquist coordinates, for which the metric components read
+\begin{eqnarray*}
+g_{tt} = - \left(1 - \frac{2Mr}{\rho^2}\right), \ g_{t\phi} = -\frac{2Mar\sin^2\theta}{\rho^2}, \ g_{\phi\phi} = \left(r^2 + a^2 + \frac{2Ma^2r\sin^2\theta}{\rho^2}\right) \sin^2 \theta\,,
+\end{eqnarray*}
+where $\rho^2 = r^2 + a^2\cos^2 \theta$.
+Therefore, we obtain $\mathcal{L} = \Delta \sin^2 \theta$, where $\Delta = r^2 - 2Mr + a^2$, and its derivative $\partial_{\theta}\mathcal{L} = 2 \Delta \sin \theta \cos \theta$, which is zero for $\theta = \pi/2$.
+Next, we take the derivative of $\mathcal{A}$
+\begin{eqnarray*}
+\partial_{\theta} \mathcal{A} = \partial_{\theta} g_{\phi\phi} + 2 (\partial_{\theta} l) g_{t\phi} + 2l\partial_{\theta} g_{t\phi} + 2l(\partial_{\theta} l) g_{tt} + l^2 \partial_{\theta} g_{tt} = \partial_{\theta} g_{\phi\phi} + 2l\partial_{\theta} g_{t\phi} + l^2 \partial_{\theta} g_{tt}\,,
+\end{eqnarray*}
+where we have used the previous result that $\partial_{\theta} l=0$ at $\theta = \pi/2$.
+By inspecting the metric components, it is easy to see that all terms depending on $\theta$ are functions of $\sin^2 \theta$ or $\cos^2 \theta$.
+This means their $\theta$ derivatives will have at least a $\cos \theta$ multiplying.
+Then $\partial_{\theta} \mathcal{A} = 0$ at $\theta = \pi/2$.
+Therefore, $\partial_{\theta} \ln|u_t|$ is also zero at $\theta = \pi/2$.
 
-First, we take the derivative of the angular momentum distribution $\partial_{\theta} l$.
-Looking at equation (7), we can write the angular momentum distribution as $l(r, \theta) = l(r) \sin^{2\gamma} \theta$, so we can write the derivative as
+\bigskip
 
-\begin{equation}
-\partial_{\theta} l = 2\gamma l(r) \sin^{2\gamma - 1} \theta \cos \theta
-\end{equation}
-
-Taking $\theta = \pi/2$ means $\partial_{\theta} l = 0$, so the second term equals to zero.
-
-To show that the first term is also zero, we write it as
-
-\begin{equation}
-\partial_{\theta} \ln|u_t| = \partial_{\theta} \ln \left(\frac{\mathcal{L}}{\mathcal{A}}\right)^{\frac{1}{2}}
-\end{equation}
-
-where $\mathcal{L} = g_{t \phi}^2 - g_{tt} g_{\phi\phi}$ and $\mathcal{A} = g_{\phi\phi} + 2 l g_{t\phi} + l^2g_{tt}$ and we have dropped the absolute value, as it is irrelevant to this discussion.
-Then, the derivative is
-
-\begin{equation}
-\partial_{\theta} \ln|u_t| = \frac{1}{2} \frac{\mathcal{A}}{\mathcal{L}}\frac{\partial_{\theta}{\mathcal{L}}\mathcal{A} - \mathcal{L}\partial_{\theta}\mathcal{A}}{\mathcal{A}^2} = \frac{1}{2} \frac{\partial_{\theta}{\mathcal{L}}\mathcal{A} - \mathcal{L}\partial_{\theta}\mathcal{A}}{\mathcal{A} \mathcal{L}}
-\end{equation}
-
-We use Boyer-Lindquist coordinates, so we can write the metric components as
-
-\begin{equation}
-g_{tt} = - \left(1 - \frac{2Mr}{\rho^2}\right), \ g_{t\phi} = -\frac{2Mar\sin^2\theta}{\rho^2}, \ g_{\phi\phi} = \left(r^2 + a^2 + \frac{2Ma^2r\sin^2\theta}{\rho^2}\right) \sin^2 \theta,
-\end{equation}
-
-where $\rho^2 = r^2 + a^2\cos^2 \theta$.
-Given this particular coordinates, we can write $\mathcal{L}$ as $\mathcal{L} = \Delta \sin^2 \theta$, where $\Delta = r^2 - 2Mr + a^2$, then $\partial_{\theta}\mathcal{L} = 2\gamma \Delta \sin^{2\gamma - 1} \theta \cos \theta$, which is zero for $\theta = \pi/2$.
-Now, we take the derivative of $\mathcal{A}$
-
-\begin{equation}
-\partial_{\theta} \mathcal{A} = \partial_{\theta} g_{\phi\phi} + 2 (\partial_{\theta} l) g_{t\phi} + 2l\partial_{\theta} g_{t\phi} + 2l(\partial_{\theta} l) g_{tt} + l^2 \partial_{\theta} g_{tt} = \partial_{\theta} g_{\phi\phi} + 2l\partial_{\theta} g_{t\phi} + l^2 \partial_{\theta} g_{tt},
-\end{equation}
-
-where we have used the previous result on $\partial_{\theta} l$.
-If we inspect the metric components, is easy to see that all the terms depending on $\theta$ are functions of $\sin^2 \theta$ or $\cos^2 \theta$.
-This means their $\theta$ derivatives will have at least a $\cos \theta$ multiplying.
-Then $\partial_{\theta} \mathcal{A} = 0$.
-Then $\partial_{\theta} \ln|u_t|$ is also zero.
+We have incorporated this simple demonstration as a short appendix in the manuscript.
 

### 2017-06-28 paper_revised/reply_referee.tex
more work on the reply

@@
 
-{\bf A:}
+{\bf A:} The reason we show the middle panel in logarithm scale and the right panel in linear scale is because this is the choice 
+ in Komissarov (2006). We have followed the same choice in order to facilitate the qualitative and quantitative comparison
+for this constant angular momentum test. If the referee concurred, we would prefer to keep the right panel in linear scale. If not, we would
+not mind changing the right panel to logarithmic scale.
 
@@
 {\bf R:} - Fig. 2: all of the panels would benefit from a legend showing the
-corresponding values of gamma and beta. This would avoid having to read the caption repeatdly. The same is true also for Fig. 3.
+corresponding values of gamma and beta. This would avoid having to read the caption repeatedly. The same is true also for Fig. 3.
 
@@
 
+\bigskip
+
 A comprehensive discussion of the properties of tori from merging binaries:
 
-http://adsabs.harvard.edu/abs/2016arXiv160703540B
+{\tt http://adsabs.harvard.edu/abs/2016arXiv160703540B}
+
+\bigskip
 
@@
 
-http://adsabs.harvard.edu/abs/2004MNRAS.354.1040M
+{\tt http://adsabs.harvard.edu/abs/2004MNRAS.354.1040M}
+
+\bigskip
 
@@
 
-http://adsabs.harvard.edu/abs/2007MNRAS.378.1101M
+{\tt http://adsabs.harvard.edu/abs/2007MNRAS.378.1101M}
 
@@
 
-{\bf A:} We have incorporated in the article the first and the third references 
+{\bf A:} We have incorporated in the revised version of the article the first and the third references 
 suggested by the referee. However, we have not incorporated the second 
-reference. While this is a very relevant work in the context of oscillations 
+reference. While this work is relevant in the context of oscillations 
 of non-constant-angular momentum disks, including this reference in our 
 work seems to us a bit forced since it discusses aspects which are a bit 
-away from the main discourse of our paper.
+away from the main topic under discussion in our paper.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
-\begin{small}
-\begin{thebibliography}{99}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
+%\begin{small}
+%\begin{thebibliography}{99}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
+%%
 %
+%%  
+%\end{thebibliography}
 
-%  
-\end{thebibliography}
-
- \end{small}
+% \end{small}
 

### 2017-06-28 paper_revised/paper_revised.tex
work on the paper
more work
first version of the appendices

@@
 We now finally have all the ingredients required to find the enthalpy distribution (Eq.~\eqref{eq:enthalpy_eq}), the fluid pressure and magnetic pressure distributions (Eqs.~\eqref{eq:eos_fluid} and \eqref{eq:eos_mag}), and the {\bf rest-mass} density distribution, which can be trivially obtained inverting the barotropic relation, $p = K \rho^{\kappa}$.
+{\bf We note that the specific internal energy $\varepsilon$ is needed to compute the enthalpy.
+We obtain
+this quantity by combining the ideal fluid and the barotropic equations of state, which yields 
+$\varepsilon=\frac{K}{\kappa-1}\rho^{\kappa-1}$.}
 
@@
 Again, it is also important here to choose a suitable step of integration, especially at the outer end of the disc, because Eq.~\eqref{eq:F} diverges at the equatorial plane (the equipotential surfaces cross the equatorial plane perpendicularly).
+{\bf We show the proof for this statment at appendix \ref{div_partial_W}.}
 
@@
 While this location also decreases with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$, the constant value achieved for values above $\beta_{\mathrm{m}_{\mathrm{c}}}\sim 10^{3}$ does depend on the specific values of $\beta$ and $\gamma$, contrary to what happens with the fluid pressure.
-It must be noted that the location of the maximum of the magnetic pressure is nearly identical for all models considered when $\log_{10}\beta_{\mathrm{m}_{\mathrm{c}}} \sim 0.5$.
+{\bf It must be noted that the location of the maximum of the magnetic pressure is nearly identical for all models considered when $\beta_{\mathrm{m}_{\mathrm{c}}} = 1/(\lambda - 1) = 3$ ({\bf we show the proof for this affirmation at the appendix \ref{app_magmax})}.
+At this value of $\beta_{\mathrm{m}_{\mathrm{c}}}$ all models cross at $r_{\mathrm{m}_{\mathrm{max}}} = r_{\mathrm{c}}$, as it is more clearly shown in the inset of the right panel of Fig.~\ref{max-vs-magnetisation}}
+
+% It must be noted that the location of the maximum of the magnetic pressure is nearly identical for all models considered when $\log_{10}\beta_{\mathrm{m}_{\mathrm{c}}} \sim 0.5$.
 At this value of $\beta_{\mathrm{m}_{\mathrm{c}}}$ all models seem to cross, as it is more clearly shown in the inset of the right panel of Fig.~\ref{max-vs-magnetisation}.
@@
 
+\begin{appendix}
+\section{Divergence of equation \eqref{eq:F} at $\theta = \pi/2$}\label{div_partial_W}
+
+Eq.~\eqref{eq:polar_der_pot} of the paper gives us
+
+\begin{eqnarray*}
+\partial_{\theta} W = \partial_{\theta} \ln|u_t| - \frac{\Omega \partial_{\theta}l}{1 - \Omega l}\, = 0.
+\end{eqnarray*}
+
+Then, we have to prove that either the two terms of this equation are equal or they are identically zero at $\theta = \pi/2$. We shall see that the latter is true.
+First, we take the derivative of the angular momentum distribution $\partial_{\theta} l$.
+From Eq.~(7) we can write the angular momentum distribution as $l(r, \theta) = l(r) \sin^{2\gamma} \theta$, so that the derivative reads
+\begin{eqnarray*}
+\partial_{\theta} l = 2\gamma l(r) \sin^{2\gamma - 1} \theta \cos \theta \,.
+\end{eqnarray*}
+Taking $\theta = \pi/2$ leads to $\partial_{\theta} l = 0$, so the second term equals to zero.
+To show that the first term is also zero, we write it as
+\begin{eqnarray*}
+\partial_{\theta} \ln|u_t| = \partial_{\theta} \ln \left(\frac{\mathcal{L}}{\mathcal{A}}\right)^{\frac{1}{2}}\,,
+\end{eqnarray*}
+where $\mathcal{L} = g_{t \phi}^2 - g_{tt} g_{\phi\phi}$ and $\mathcal{A} = g_{\phi\phi} + 2 l g_{t\phi} + l^2g_{tt}$, and we have dropped the absolute value, as it is irrelevant to this discussion.
+Then, the derivative is
+\begin{eqnarray*}
+\partial_{\theta} \ln|u_t| = \frac{1}{2} \frac{\mathcal{A}}{\mathcal{L}}\frac{\mathcal{A}\partial_{\theta}{\mathcal{L}} - \mathcal{L}\partial_{\theta}\mathcal{A}}{\mathcal{A}^2} = \frac{1}{2} \frac{\mathcal{A}\partial_{\theta}{\mathcal{L}} - \mathcal{L}\partial_{\theta}\mathcal{A}}{\mathcal{A} \mathcal{L}}\,.
+\end{eqnarray*}
+We use Boyer-Lindquist coordinates, for which the metric components read
+\begin{eqnarray*}
+g_{tt} = - \left(1 - \frac{2Mr}{\rho^2}\right), \ g_{t\phi} = -\frac{2Mar\sin^2\theta}{\rho^2}, \ g_{\phi\phi} = \left(r^2 + a^2 + \frac{2Ma^2r\sin^2\theta}{\rho^2}\right) \sin^2 \theta\,,
+\end{eqnarray*}
+where $\rho^2 = r^2 + a^2\cos^2 \theta$.
+Therefore, we obtain $\mathcal{L} = \Delta \sin^2 \theta$, where $\Delta = r^2 - 2Mr + a^2$, and its derivative $\partial_{\theta}\mathcal{L} = 2 \Delta \sin \theta \cos \theta$, which is zero for $\theta = \pi/2$.
+Next, we take the derivative of $\mathcal{A}$
+\begin{eqnarray*}
+\partial_{\theta} \mathcal{A} = \partial_{\theta} g_{\phi\phi} + 2 (\partial_{\theta} l) g_{t\phi} + 2l\partial_{\theta} g_{t\phi} + 2l(\partial_{\theta} l) g_{tt} + l^2 \partial_{\theta} g_{tt} = \partial_{\theta} g_{\phi\phi} + 2l\partial_{\theta} g_{t\phi} + l^2 \partial_{\theta} g_{tt}\,,
+\end{eqnarray*}
+where we have used the previous result that $\partial_{\theta} l=0$ at $\theta = \pi/2$.
+By inspecting the metric components, it is easy to see that all terms depending on $\theta$ are functions of $\sin^2 \theta$ or $\cos^2 \theta$.
+This means their $\theta$ derivatives will have at least a $\cos \theta$ multiplying.
+Then $\partial_{\theta} \mathcal{A} = 0$ at $\theta = \pi/2$.
+Therefore, $\partial_{\theta} \ln|u_t|$ is also zero at $\theta = \pi/2$.
+
+\section{Magnetization for $r_{\mathrm{m}_{\mathrm{max}}} = r_{\mathrm{c}}$}\label{app_magmax}
+
+Here, we derive the condition $\beta_{\mathrm{m}_{\mathrm{c}}} = 1/(\lambda - 1)$ for $r_{\mathrm{m}_{\mathrm{max}}} = r_{\mathrm{c}}$.
+First, we can use equation~\eqref{eq:eos_mag} to write
+
+\begin{equation}\label{eq_max}
+\frac{\partial{p_{\mathrm{m}}(r)}}{\partial r} = \partial_{r} \left(K_{\mathrm{m}} \mathcal{L}^{\lambda -1} w^{\lambda}\right) = 0,
+\end{equation}
+
+Computing, we arrive at
+
+\begin{equation}
+\partial_{r} p_{\mathrm{m}} = K_{\mathrm{m}} \mathcal{L}^{\lambda - 2}w^{\lambda} [(\lambda - 1)(\partial_r \mathcal{L}) w + \lambda \mathcal{L} (\partial_r w)].
+\end{equation}
+
+We can see that inside the disc $K_{\mathrm{m}} \mathcal{L}^{\lambda - 2}w^{\lambda} \neq 0$, So to fulfill the extremum condition \eqref{eq_max} we need
+
+\begin{equation}\label{eq:simple_expr}
+(\lambda - 1)(\partial_r \mathcal{L}) w + \lambda \mathcal{L} (\partial_r w) = 0
+\end{equation}
+
+To evaluate this expressión, we need to compute the partial derivatives $\partial_r \mathcal{L}$ and $\partial_r w$.
+The derivative of $\mathcal{L}$ is esay to compute, as $\mathcal{L} = \Delta \sin^2 \theta$.
+So its partial derivative is
+
+\begin{equation}
+\partial_r \mathcal{L} = 2(r-M)\sin^2 \theta
+\end{equation}
+
+Now, we take our attention to $\partial_r w$. From eq.~\eqref{eq:enthalpy_eq} we have
+
+\begin{equation}
+w = \left[-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right]^{\frac{1}{\lambda-1}}
+\end{equation}
+
+Then, we can take its derivative
+
+\begin{equation}
+\partial_r w = \frac{w}{\lambda - 1} \left[-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right]^{-1} \left[\left(-\partial_r W \left(\frac{\lambda -1 }{\lambda}\right) \frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right) + \left(-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{-(\lambda - 1) K_{\mathrm{m}} \mathcal{L}^{\lambda - 2} \partial_r \mathcal{L}}{(K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1})^2}\right)\right]
+\end{equation}
+
+Since we are at $r = r_{\mathrm{c}}$ the derivative of the potential is zero ($\partial_r W(r, \pi/2)|_{r = r_{\mathrm{c}}} = 0$), so we can simplify the expression to get
+
+\begin{equation}
+\partial_r w = \frac{w}{\lambda - 1} \left[-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right]^{-1} \left(-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right)\left[\frac{-(\lambda - 1) K_{\mathrm{m}} \mathcal{L}^{\lambda - 2} \partial_r \mathcal{L}}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right]
+\end{equation}
+
+And we can further simplify this, to arrive at
+
+\begin{equation}
+\partial_r w = - w \left[\frac{K_{\mathrm{m}} \mathcal{L}^{\lambda - 2} \partial_r \mathcal{L}}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right]
+\end{equation}
+
+Then, we can insert this expression at eq.~\eqref{eq:simple_expr} to obtain
+
+\begin{equation}
+(\partial_r \mathcal{L}) w [(\lambda -1)(K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}) - \lambda K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}] = 0
+\end{equation}
+
+As $(\partial_r \mathcal{L}) w \neq 0$ inside the disc, we can simplify this, to arrive at
+
+\begin{equation}
+K (\lambda - 1) = K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}
+\end{equation}
+
+The, we can use equations \eqref{eq:eos_fluid}, \eqref{eq:eos_mag} and \eqref{eq:beta_eq} at the center (remember that $w_{\mathrm{c}} = 1$) to write $K$ as $K = \beta_{\mathrm{m}_{\mathrm{c}}} K_\mathrm{m}\mathcal{L}^{\lambda -1}$.
+This allows us to write the simple expression
+
+\begin{equation}
+\beta_{\mathrm{m}_{\mathrm{c}}} = \frac{1}{\lambda - 1}
+\end{equation}
+
+\sg{We should add a short discussion of the generality of this result.}
+
+\end{appendix}
+
 \end{document}

### 2017-06-29 paper_revised/reply_referee.tex
more work on the reply

@@
 
-We have incorporated this simple demonstration as a short appendix in the manuscript.
+We have incorporated this simple demonstration as Appendix A in the manuscript.
+
+\bigskip
+
+We have also incorporated a second appendix in the manuscript, Appendix B, to explain why indeed, as shown in the inset of the right panel of Fig.~6, all models cross at $r_{\mathrm{m}_{\mathrm{max}}} = r_{\mathrm{c}}$ for a very specific value of $\beta_{\mathrm{m}_{\mathrm{c}}}$.
+Correspondingly, we have added the following text towards the end of Section 4: ``{\bf It must be noted that the location of the maximum of the magnetic pressure is identical for all models considered when $\beta_{\mathrm{m}_{\mathrm{c}}} \equiv 1/(\lambda - 1) = 3$, as we show in Appendix~B.
+At this value of $\beta_{\mathrm{m}_{\mathrm{c}}}$ all models cross at $r_{\mathrm{m}_{\mathrm{max}}} = r_{\mathrm{c}}$, as it is more clearly shown in the inset of the right panel of Fig.~6.}"
 

### 2017-06-29 paper_revised/paper_revised.tex
work on the paper

@@
 Again, it is also important here to choose a suitable step of integration, especially at the outer end of the disc, because Eq.~\eqref{eq:F} diverges at the equatorial plane (the equipotential surfaces cross the equatorial plane perpendicularly).
-{\bf We show the proof for this statment at appendix \ref{div_partial_W}.}
+{\bf We show the proof of this statment in Appendix~\ref{div_partial_W}.}
 
@@
 While this location also decreases with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$, the constant value achieved for values above $\beta_{\mathrm{m}_{\mathrm{c}}}\sim 10^{3}$ does depend on the specific values of $\beta$ and $\gamma$, contrary to what happens with the fluid pressure.
-{\bf It must be noted that the location of the maximum of the magnetic pressure is nearly identical for all models considered when $\beta_{\mathrm{m}_{\mathrm{c}}} = 1/(\lambda - 1) = 3$ ({\bf we show the proof for this affirmation at the appendix \ref{app_magmax})}.
-At this value of $\beta_{\mathrm{m}_{\mathrm{c}}}$ all models cross at $r_{\mathrm{m}_{\mathrm{max}}} = r_{\mathrm{c}}$, as it is more clearly shown in the inset of the right panel of Fig.~\ref{max-vs-magnetisation}}
+{\bf It must be noted that the location of the maximum of the magnetic pressure is identical for all models considered when $\beta_{\mathrm{m}_{\mathrm{c}}} \equiv 1/(\lambda - 1) = 3$, as we show in Appendix~\ref{app_magmax}.
+At this value of $\beta_{\mathrm{m}_{\mathrm{c}}}$ all models cross at $r_{\mathrm{m}_{\mathrm{max}}} = r_{\mathrm{c}}$, as it is more clearly shown in the inset of the right panel of Fig.~\ref{max-vs-magnetisation}.}
 

### 2017-06-29 paper_revised/paper_revised.tex
work on the paper

--- 2017-06-21 paper_revised/paper_revised.tex
@@
 Again, it is also important here to choose a suitable step of integration, especially at the outer end of the disc, because Eq.~\eqref{eq:F} diverges at the equatorial plane (the equipotential surfaces cross the equatorial plane perpendicularly).
+{\bf We show the proof of this statment in Appendix~\ref{div_partial_W}.}
 
@@
 While this location also decreases with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$, the constant value achieved for values above $\beta_{\mathrm{m}_{\mathrm{c}}}\sim 10^{3}$ does depend on the specific values of $\beta$ and $\gamma$, contrary to what happens with the fluid pressure.
-It must be noted that the location of the maximum of the magnetic pressure is nearly identical for all models considered when $\log_{10}\beta_{\mathrm{m}_{\mathrm{c}}} \sim 0.5$.
+{\bf It must be noted that the location of the maximum of the magnetic pressure is identical for all models considered when $\beta_{\mathrm{m}_{\mathrm{c}}} \equiv 1/(\lambda - 1) = 3$, as we show in Appendix~\ref{app_magmax}.
+At this value of $\beta_{\mathrm{m}_{\mathrm{c}}}$ all models cross at $r_{\mathrm{m}_{\mathrm{max}}} = r_{\mathrm{c}}$, as it is more clearly shown in the inset of the right panel of Fig.~\ref{max-vs-magnetisation}.}
+
+% It must be noted that the location of the maximum of the magnetic pressure is nearly identical for all models considered when $\log_{10}\beta_{\mathrm{m}_{\mathrm{c}}} \sim 0.5$.
 At this value of $\beta_{\mathrm{m}_{\mathrm{c}}}$ all models seem to cross, as it is more clearly shown in the inset of the right panel of Fig.~\ref{max-vs-magnetisation}.
@@
 
+\begin{appendix}
+\section{Divergence of equation~\eqref{eq:F} at $\theta = \pi/2$}\label{div_partial_W}
+To prove that Eq.~\eqref{eq:F} diverges at $\theta = \pi/2$ we need to show that
+Eq.~\eqref{eq:polar_der_pot} vanishes at the equator, i.e.
+\begin{eqnarray}
+\partial_{\theta} W = \partial_{\theta} \ln|u_t| - \frac{\Omega \partial_{\theta}l}{1 - \Omega l}\, = 0.
+\end{eqnarray}
+Then, we have to prove that either the two terms of this equation are equal or they are identically zero at $\theta = \pi/2$. We shall see that the latter is true.
+First, we take the derivative of the angular momentum distribution $\partial_{\theta} l$.
+From Eq.~(7) we can write the angular momentum distribution as $l(r, \theta) = l(r) \sin^{2\gamma} \theta$, so that the derivative reads
+\begin{eqnarray}
+\partial_{\theta} l = 2\gamma l(r) \sin^{2\gamma - 1} \theta \cos \theta \,.
+\end{eqnarray}
+Taking $\theta = \pi/2$ leads to $\partial_{\theta} l = 0$, so the second term equals to zero.
+To show that the first term is also zero, we write it as
+\begin{eqnarray}
+\partial_{\theta} \ln|u_t| = \partial_{\theta} \ln \left(\frac{\mathcal{L}}{\mathcal{A}}\right)^{\frac{1}{2}}\,,
+\end{eqnarray}
+where $\mathcal{L} = g_{t \phi}^2 - g_{tt} g_{\phi\phi}$ and $\mathcal{A} = g_{\phi\phi} + 2 l g_{t\phi} + l^2g_{tt}$, and we have dropped the absolute value, as it is irrelevant to this discussion.
+Then, the derivative is
+\begin{eqnarray}
+\partial_{\theta} \ln|u_t| = \frac{1}{2} \frac{\mathcal{A}}{\mathcal{L}}\frac{\mathcal{A}\partial_{\theta}{\mathcal{L}} - \mathcal{L}\partial_{\theta}\mathcal{A}}{\mathcal{A}^2} = \frac{1}{2} \frac{\mathcal{A}\partial_{\theta}{\mathcal{L}} - \mathcal{L}\partial_{\theta}\mathcal{A}}{\mathcal{A} \mathcal{L}}\,.
+\end{eqnarray}
+We use Boyer-Lindquist coordinates, for which the metric components read
+\begin{eqnarray}
+g_{tt} = - \left(1 - \frac{2Mr}{\rho^2}\right), \ g_{t\phi} = -\frac{2Mar\sin^2\theta}{\rho^2}, \ g_{\phi\phi} = \left(r^2 + a^2 + \frac{2Ma^2r\sin^2\theta}{\rho^2}\right) \sin^2 \theta\,,
+\end{eqnarray}
+where $\rho^2 = r^2 + a^2\cos^2 \theta$.
+Therefore, we obtain $\mathcal{L} = \Delta \sin^2 \theta$, where $\Delta = r^2 - 2Mr + a^2$, and its derivative $\partial_{\theta}\mathcal{L} = 2 \Delta \sin \theta \cos \theta$, which is zero for $\theta = \pi/2$.
+Next, we take the derivative of $\mathcal{A}$
+\begin{eqnarray}
+\partial_{\theta} \mathcal{A} = \partial_{\theta} g_{\phi\phi} + 2 (\partial_{\theta} l) g_{t\phi} + 2l\partial_{\theta} g_{t\phi} + 2l(\partial_{\theta} l) g_{tt} + l^2 \partial_{\theta} g_{tt} = \partial_{\theta} g_{\phi\phi} + 2l\partial_{\theta} g_{t\phi} + l^2 \partial_{\theta} g_{tt}\,,
+\end{eqnarray}
+where we have used the previous result that $\partial_{\theta} l=0$ at $\theta = \pi/2$.
+By inspecting the metric components, it is easy to see that all terms depending on $\theta$ are functions of $\sin^2 \theta$ or $\cos^2 \theta$.
+This means their $\theta$ derivatives will have at least a $\cos \theta$ multiplying.
+Then $\partial_{\theta} \mathcal{A} = 0$ at $\theta = \pi/2$.
+Therefore, $\partial_{\theta} \ln|u_t|$ is also zero at $\theta = \pi/2$.
+
+\section{Value of the magnetisation parameter for $r_{\mathrm{m}_{\mathrm{max}}} = r_{\mathrm{c}}$}\label{app_magmax}
+In this appendix we derive the condition $\beta_{\mathrm{m}_{\mathrm{c}}} = 1/(\lambda - 1)$ for $r_{\mathrm{m}_{\mathrm{max}}} = r_{\mathrm{c}}$.
+First, we can use Eq.~\eqref{eq:eos_mag} to write 
+\begin{eqnarray}\label{eq_max}
+\frac{\partial{p_{\mathrm{m}}(r)}}{\partial r} = \partial_{r} \left(K_{\mathrm{m}} \mathcal{L}^{\lambda -1} w^{\lambda}\right) = 0\,,
+\end{eqnarray}
+which yields
+\begin{eqnarray}
+\partial_{r} p_{\mathrm{m}} = K_{\mathrm{m}} \mathcal{L}^{\lambda - 2}w^{\lambda} [(\lambda - 1)(\partial_r \mathcal{L}) w + \lambda \mathcal{L} (\partial_r w)]=0\,.
+\end{eqnarray}
+Inside the disc $K_{\mathrm{m}} \mathcal{L}^{\lambda - 2}w^{\lambda} \neq 0$. Therefore, to fulfill the extremum condition~\eqref{eq_max} we need 
+\begin{equation}\label{eq:simple_expr}
+(\lambda - 1)(\partial_r \mathcal{L}) w + \lambda \mathcal{L} (\partial_r w) = 0\,.
+\end{equation}
+To evaluate this expression, we need to compute the partial derivatives $\partial_r \mathcal{L}$ and $\partial_r w$.
+The derivative of $\mathcal{L}$ is straightforward, since $\mathcal{L} = \Delta \sin^2 \theta$,
+\begin{equation}
+\partial_r \mathcal{L} = 2(r-M)\sin^2 \theta\,.
+\end{equation}
+Let us now discuss $\partial_r w$. From Eq.~\eqref{eq:enthalpy_eq} we have
+\begin{equation}
+w = \left[-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right]^{\frac{1}{\lambda-1}}\,.
+\end{equation}
+Taking its derivative we obtain
+\begin{eqnarray}
+\partial_r w &=& \frac{w}{\lambda - 1} \left[-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right]^{-1} 
+\nonumber \\
+&\times&
+\left[\left(-\partial_r W \left(\frac{\lambda -1 }{\lambda}\right) \frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right) + \left(-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{-(\lambda - 1) K_{\mathrm{m}} \mathcal{L}^{\lambda - 2} \partial_r \mathcal{L}}{(K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1})^2}\right)\right]\,.
+\end{eqnarray}
+Since at $r = r_{\mathrm{c}}$ the derivative of the potential is zero, $\partial_r W(r, \pi/2)|_{r = r_{\mathrm{c}}} = 0$, we can simplify the above expression to obtain
+\begin{eqnarray}
+\partial_r w &=& \frac{w}{\lambda - 1} \left[-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right]^{-1} 
+\nonumber \\
+&\times&
+\left(-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right)\left[\frac{-(\lambda - 1) K_{\mathrm{m}} \mathcal{L}^{\lambda - 2} \partial_r \mathcal{L}}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right]\,,
+\end{eqnarray}
+which can be further simplified to the following form
+\begin{equation}
+\partial_r w = - w \left[\frac{K_{\mathrm{m}} \mathcal{L}^{\lambda - 2} \partial_r \mathcal{L}}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right]\,.
+\end{equation}
+Next, by inserting this expression in Eq.~\eqref{eq:simple_expr} we obtain
+\begin{equation}
+(\partial_r \mathcal{L}) w [(\lambda -1)(K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}) - \lambda K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}] = 0\,.
+\end{equation}
+Since $(\partial_r \mathcal{L}) w \neq 0$ inside the disc, the above equation leads to 
+\begin{equation}
+K (\lambda - 1) = K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}\,.
+\end{equation}
+Moreover, we can use Eqs.~\eqref{eq:eos_fluid}, \eqref{eq:eos_mag} and \eqref{eq:beta_eq} at the center (remember that $w_{\mathrm{c}} = 1$) to write $K$ as $K = \beta_{\mathrm{m}_{\mathrm{c}}} K_\mathrm{m}\mathcal{L}^{\lambda -1}$.
+Therefore, this allows us to obtain the following simple expression for the value of the magnetisation parameter at the center of the disc
+\begin{equation}
+\beta_{\mathrm{m}_{\mathrm{c}}} = \frac{1}{\lambda - 1}\,.
+\end{equation}
+
+\sg{We should add a short discussion of the generality of this result.}
+
+\end{appendix}
+
 \end{document}

### 2017-07-03 paper_revised/paper_revised.tex
work on the paper

@@
 We now finally have all the ingredients required to find the enthalpy distribution (Eq.~\eqref{eq:enthalpy_eq}), the fluid pressure and magnetic pressure distributions (Eqs.~\eqref{eq:eos_fluid} and \eqref{eq:eos_mag}), and the {\bf rest-mass} density distribution, which can be trivially obtained inverting the barotropic relation, $p = K \rho^{\kappa}$.
-{\bf We note that the specific internal energy $\varepsilon$ is needed to compute the enthalpy.
-We obtain
-this quantity by combining the ideal fluid and the barotropic equations of state, which yields 
-$\varepsilon=\frac{K}{\kappa-1}\rho^{\kappa-1}$.}
+{\bf We note that the fluid enthalpy $w$ includes the rest-mass density $\rho$, and can thus be defined as $w=\rho h$ where $h$ is the specific enthalpy.
+The relativistic definition of this quantity is $h=1+\varepsilon+p/\rho$, where $\varepsilon$ is
+the specific internal energy. From a thermodynamical point of view a non-relativistic fluid satisfies $h=1$. Therefore,
+since we use poytropic equations of state (relating $p$ with either $w$ or $\rho$ in the same functional form) we are
+implictly assuming that $h=1$, i.e.~the discs we build in our procedure are non-relativistic from a thermodynamical point of view.}
+%{\bf We note that the specific internal energy $\varepsilon$ is needed to compute the enthalpy. We obtain
+%this quantity by combining the ideal fluid and the barotropic equations of state, which yields 
+%$\varepsilon=\frac{K}{\kappa-1}\rho^{\kappa-1}$.}
 
@@
 It is important to use a very small integration step because the slope is very steep.
-In this work, we use a step $h = 10^{-6}$.
+In this work, we use a step $\Delta r = 10^{-6}$.
 Using the analytic, constant angular momentum case for comparison, we tested that
-a larger value of $h$ gives unacceptable accuracy losses.
+a larger value of $\Delta r$ gives unacceptable accuracy losses.
 On the other hand, to integrate the ordinary differential equation \eqref{eq:F} we use a fourth-order Runge-Kutta method.
@@
 We build a series of 45 models, whose main features are summarised in Table~\ref{table:1} (for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$, i.e.~models where the effects of the magnetisation are unimportant), Table~\ref{table:2} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$, i.e.~equipartition models), and Table~\ref{table:3} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$, i.e.~highly-magnetised models).
+{\bf
+We note in particular that the radii of the maximum fluid pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, respectively, for the same value of $\beta_{\mathrm{m}_{\mathrm{c}}}$, never coincide.
+This also reflects the fact that constant fluid pressure surfaces do not coincide with constant magnetic pressure surfaces.}
 

### 2017-07-03 paper_revised/reply_referee.tex
work on the paper

@@
 
-{\bf A:} We address this issue below where the referee comments on the ``assumption of the specific
-internal energy", since we believe both queries are related.
+{\bf A:} In our work we are following the same procedure as in Komissarov (2006), where no comment on the treatment
+of the specific internal energy is explicitly provided. We have simply followed the same approach and have used the
+same polytropic relationship between the enthalpy and the fluid pressure, Eq.~(12), and between the rest-mass density and the
+fluid pressure (as can be read in the paragraph following Eq.~(27)). Thanks to the remark of the referee we now realise 
+that by doing this we (and Komissarov) are making an implicit assumption about the internal energy. By looking at the 
+expression of the stress-energy tensor in Eq.~(9) of the manuscript, we see that the fluid enthalpy $w$ includes the 
+rest-mass density $\rho$, and can thus be defined as $w=\rho h$ where $h$ is the specific enthalpy. The relativistic definition 
+of this quantity (in units with $c=1$) is $h=1+\varepsilon+p/\rho$, where $\varepsilon$ is the specific internal energy and 
+$p$ is the fluid pressure. From a thermodynamical point of view a fluid is non-relativistic in the limit $h=1$. Therefore,
+since both equations of state we use are polytropes (relating $p$ with $w$ or with $\rho$ in the same functional form) we 
+conclude that we are implictly assuming that $h=1$ in our models, i.e.~the disks we build in our procedure are non-relativistic 
+from a thermodynamical point of view.
+
+\bigskip
+
+We have included the following comment at the end of the paragraph following Eq.~(27): 
+``We notae that the fluid enthalpy $w$ includes the rest-mass density $\rho$, and can thus be defined as $w=\rho h$ where
+$h$ is the specific enthalpy. The relativistic definition of this quantity is $h=1+\varepsilon+p/\rho$, where $\varepsilon$ is
+the specific internal energy. From a thermodynamical point of view a non-relativistic fluid satisfies $h=1$. Therefore,
+since we use poytropic equations of state (relating $p$ with either $w$ or $\rho$ in the same functional form) we are
+implictly assuming that $h=1$, i.e.~the discs we build in our procedure are non-relativistic from a thermodynamical point of view."
+
+\bigskip
+
+To avoid confusion, we have changed the name of variable used for the step of the Simpson's rule from $h$ to $\Delta r$.
 
@@
 
-{\bf A:}
+{\bf A:} We have not included further details about the prescription of the magnetic field because, in practice, in our procedure we 
+only need to use $p_m\equiv b^2/2$,
+and not the individual components of the magnetic-field themselves. We believe that including those extra details in the manuscript does not
+provide relevant information. If interested, the referee is addressed to appendix A of Komissarov 
+(2006) for the derivation of the explicit relations (which we do not employ anyway).
 
@@
 
-{\bf A:}
+{\bf A:} They do not coincide, as can be inferred from Eqs.~(12) and (14).
+Also notice that the values of $r_{\rm max}$ and $r_{\rm m,max}$ reported in the tables, do not coincide, which shows that fluid isobaric surfaces and magnetic isobaric surfaces cannot coincide.
+On the other hand, the iso-density surfaces and the fluid isobaric surfaces do coincide, since both variables are related by the barotropic equation of state.
+
+\bigskip
+
+We have included the following text at the end of the first paragraph of the results section: ``We note in particular that the radii of the maximum fluid pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, respectively, for the same value of $\beta_{\mathrm{m}_{\mathrm{c}}}$, never coincide.
+This also reflects the fact that constant fluid pressure surfaces do not coincide with constant magnetic pressure surfaces."
 
@@
 {\bf A:} 
-The specific internal energy $\varepsilon$ is obtained by combining the ideal fluid (gamma-law)
-equation of state which, in the notation used in the paper we write $P=(\kappa-1)\rho\varepsilon$,
-and the barotropic equation of state. Solving for $\varepsilon$ we obtain
-\begin{eqnarray*}
-\varepsilon=\frac{K}{\kappa-1}\rho^{\kappa-1}\,.
-\end{eqnarray*}
-We have incorporated the following statements at the end of the paragraph after Eq.~(27):
-``We note that the specific internal energy $\varepsilon$ is needed to compute the enthalpy. We obtain
-this quantity by combining the ideal fluid and the barotropic equations of state, which yields 
-$\varepsilon=\frac{K}{\kappa-1}\rho^{\kappa-1}$."
+We have addressed this issue previously, while responding to a related query raised by the referee.
+
+%The specific internal energy $\varepsilon$ is obtained by combining the ideal fluid (gamma-law)
+%equation of state which, in the notation used in the paper we write $P=(\kappa-1)\rho\varepsilon$,
+%and the barotropic equation of state. Solving for $\varepsilon$ we obtain
+%\begin{eqnarray*}
+%\varepsilon=\frac{K}{\kappa-1}\rho^{\kappa-1}\,.
+%\end{eqnarray*}
+%We have incorporated the following statements at the end of the paragraph after Eq.~(27):
+%``We note that the specific internal energy $\varepsilon$ is needed to compute the enthalpy. We obtain
+%this quantity by combining the ideal fluid and the barotropic equations of state, which yields 
+%$\varepsilon=\frac{K}{\kappa-1}\rho^{\kappa-1}$."
 
@@
 
-{\bf A:}
+{\bf A:} We have built models with very small values of $\beta_{m_c}$, such as  $\beta_{m_c} = 10^{-20}$ (extremely high magnetisation) without encountering numerical difficulties.
+In practice we have found that there are no qualitative differences in the structure of the discs once $\beta_{m_c}$ becomes smaller than a sufficiently small value, about $\beta_{m_c}=10^{-3}$.
+This is
+the reason why we choose that particular value as our lower limit in the figures and tables of the manuscript.
 

### 2017-07-04 paper_revised/paper_revised.tex
brief discussion at the end of appendix B

@@
 
+\sg{It is relevant to note that the only reference to the explicit form of the metric it is done to show that $\mathcal{L} \neq 0$ and $\partial r \mathcal{L} \neq 0$ inside the disk.
+This means that our result holds for any stationary and axisymmetric metric if the aforementioned inequalities hold.
+
+Also, if the angular momentum distribution allows the existence of a cusp and a center (and $r_{\mathrm{c}} \neq r_{\mathrm{cusp}}$) the result also holds for any angular momentum distribution.}
+
 \end{appendix}

### 2017-07-04 paper_revised/reply_referee.tex
work on the paper

@@
 in the equatorial plane on which the pressure gradient vanishes and the angular 
-momentum of the disk equals the Keplerian angular momentum."
+momentum of the disc equals the Keplerian angular momentum."
 
@@
 {\bf A:} In our work we are following the same procedure as in Komissarov (2006), where no comment on the treatment
-of the specific internal energy is explicitly provided. We have simply followed the same approach and have used the
+of the specific internal energy is explicitly provided. Since we have been guided by this previous result, we have used the
 same polytropic relationship between the enthalpy and the fluid pressure, Eq.~(12), and between the rest-mass density and the
@@
 We have included the following comment at the end of the paragraph following Eq.~(27): 
-``We notae that the fluid enthalpy $w$ includes the rest-mass density $\rho$, and can thus be defined as $w=\rho h$ where
+``We note that the fluid enthalpy $w$ includes the rest-mass density $\rho$, and can thus be defined as $w=\rho h$ where
 $h$ is the specific enthalpy. The relativistic definition of this quantity is $h=1+\varepsilon+p/\rho$, where $\varepsilon$ is
@@
 We have also incorporated a second appendix in the manuscript, Appendix B, to explain why indeed, as shown in the inset of the right panel of Fig.~6, all models cross at $r_{\mathrm{m}_{\mathrm{max}}} = r_{\mathrm{c}}$ for a very specific value of $\beta_{\mathrm{m}_{\mathrm{c}}}$.
-Correspondingly, we have added the following text towards the end of Section 4: ``{\bf It must be noted that the location of the maximum of the magnetic pressure is identical for all models considered when $\beta_{\mathrm{m}_{\mathrm{c}}} \equiv 1/(\lambda - 1) = 3$, as we show in Appendix~B.
+Correspondingly, we have added the following text towards the end of Section 4: ``{It must be noted that the location of the maximum of the magnetic pressure is identical for all models considered when $\beta_{\mathrm{m}_{\mathrm{c}}} \equiv 1/(\lambda - 1) = 3$, as we show in Appendix~B.
 At this value of $\beta_{\mathrm{m}_{\mathrm{c}}}$ all models cross at $r_{\mathrm{m}_{\mathrm{max}}} = r_{\mathrm{c}}$, as it is more clearly shown in the inset of the right panel of Fig.~6.}"
@@
 
-{\bf R:} - Sec. 4: I find the discussion in this section the less clear; a lot
+{\bf R:} - Sec.~4: I find the discussion in this section the less clear; a lot
 of the considerations appear phenomenological but I can't find the
@@
 
-{\bf A:}
+{\bf A:} We appreciate the comment of the referee and apologize if the discussion is Section 4 is not sufficiently clear. We have been
+analyzing in more detail our findings and have come up with the following simple explanations for our numerical observations.
+
+\bigskip
+
+To explain the movement of the maximum of the rest-mass density towards smaller $r$ we can start by computing the radial derivative of the enthaply, which should vanish at $r=r_{\rm max}$.
+From Eq.~(20) we have
+\begin{eqnarray*}
+\partial_r w=\partial_r\left[
+-\Delta W \left( \frac{\lambda-1}{\lambda}\right)\frac{1}{K+K_m \mathcal{L}^{\lambda-1}}
+\right]^{\frac{1}{\lambda-1}}\,,
+\end{eqnarray*}
+where we have used $\kappa=\lambda$ and have defined $\Delta W\equiv W-W_{\rm in}$. After some algebra, we arrive at the following expression for the radial derivative of the potential:
+\begin{eqnarray*}
+\partial_r W(r)|_{r=r_{\rm max}}=\frac{(\lambda-1) \Delta W(r_{\rm max})}{\mathcal{L}(r_{\rm max})}
+\left[
+\frac{(\partial_r \mathcal{L})|_{r=r_{\rm max}}}{1+\beta_{{\rm m}_{\rm c}}\left(\frac{\mathcal{L}(r_c)}{\mathcal{L}(r_{\rm max})} \right)^{\lambda-1}}
+\right]\,.
+\end{eqnarray*}
+All the factors on the r.h.s.~of this expression are positive, except for $\Delta W(r_{\rm max})$ which is negative.
+For $\beta_{{\rm m}_{\rm c}}\rightarrow \infty$,  $\partial_r W(r)|_{r=r_{\rm max}}=0$, which is attained at $r_{\rm max}=r_c$, which is a minimum of the potential.
+As $\beta_{{\rm m}_{\rm c}}$ decreases (and hence the magnetisation increases) the r.h.s.~increases in absolute value being always negative.
+Therefore, the position of $r_{\rm max}$ has to move towards smaller radii.
+
+\bigskip
+
+On the other hand, to explain the increase of $\rho_{\mathrm{max}}$ with magnetisation we can start with the same equation for the enthalpy $w$ as before (in our classical thermodynamical limit $w=\rho$).
+Next, we take $K=p_c$ and $K_m=\frac{p_c}{\beta_{{\rm m}_{\rm c}} \mathcal{L}_{c}^{\lambda-1}}$, where subindex $c$ means that the corresponding expressions are evaluated at the centre of the disc.
+We also use Eq.~(25) to write
+\begin{eqnarray*}
+p_c=-\Delta W_c \left( \frac{\lambda-1}{\lambda} \right) \left(  \frac{\beta_{{\rm m}_{\rm c}}}{1+\beta_{{\rm m}_{\rm c}}} \right)\,.
+\end{eqnarray*}
+Substituting these expressions in the equation for the enthalpy we obtain:
+\begin{eqnarray*}
+w|_{r=r_{\rm max}}= \left[
+\frac{\Delta W(r_{\rm max})}{\Delta W(r_{\rm c})}\left(
+\frac{1+\beta_{{\rm m}_{\rm c}}}{\left( \frac{\mathcal{L}(r_{\rm max})}{\mathcal{L}(r_c)}   \right)^{\lambda-1}+\beta_{{\rm m}_{\rm c}}}
+\right)
+\right]^{\frac{1}{\lambda-1}}\,.
+\end{eqnarray*}
+We note that $\frac{\mathcal{L}(r_{\rm max})}{\mathcal{L}(r_c)}\le 1$ and therefore the factor in parenthesis on the r.h.s.~is always $\ge 1$.
+Despite $\frac{\Delta W(r_{\rm max})}{\Delta W(r_{\rm c})}\le 1$ our numerical models are such that the product of the two factors on the r.h.s.~is always $\ge 1$.
+Therefore, the value of the rest-mass density at the maximum, $\rho_{\rm max}$, increases with magnetisation.
+
+\bigskip
+If the referee considered these explanations satisfactory and would like to have them included in the manuscript, we would be happy to do so.
 

### 2017-07-04 paper_revised/paper_revised.tex
work on the paper

--- 2017-07-03 paper_revised/paper_revised.tex
@@
 \end{equation}
-
-\sg{We should add a short discussion of the generality of this result.}
+It is relevant to note that the only reference to the explicit form of the metric is done to show that $\mathcal{L} \neq 0$ and $\partial r \mathcal{L} \neq 0$ inside the disc.
+This means that our result holds for any stationary and axisymmetric metric if the aforementioned inequalities hold.
+Moreover, the result is also true for any angular momentum distribution that allows for the existence of a cusp and a centre (and $r_{\mathrm{c}} \neq r_{\mathrm{cusp}}$).
 

### 2017-07-04 paper_revised/paper_revised.tex
some typos corrected

@@
 \end{equation}
-Moreover, we can use Eqs.~\eqref{eq:eos_fluid}, \eqref{eq:eos_mag} and \eqref{eq:beta_eq} at the center (remember that $w_{\mathrm{c}} = 1$) to write $K$ as $K = \beta_{\mathrm{m}_{\mathrm{c}}} K_\mathrm{m}\mathcal{L}^{\lambda -1}$.
-Therefore, this allows us to obtain the following simple expression for the value of the magnetisation parameter at the center of the disc
+Moreover, we can use Eqs.~\eqref{eq:eos_fluid}, \eqref{eq:eos_mag} and \eqref{eq:beta_eq} at the centre (remember that $w_{\mathrm{c}} = 1$) to write $K$ as $K = \beta_{\mathrm{m}_{\mathrm{c}}} K_\mathrm{m}\mathcal{L}^{\lambda -1}$.
+Therefore, this allows us to obtain the following simple expression for the value of the magnetisation parameter at the centre of the disc
 \begin{equation}

### 2017-07-10 paper_revised_v2/paper_revised_v2.tex
paper_revised_v2
'enthalpy density'

--- 2017-07-04 paper_revised/paper_revised.tex
@@
-\documentclass[referee]{aa}
+\documentclass{aa}
 
@@
 \end{equation}
-is the energy-momentum tensor of a magnetised perfect fluid, $w$ and $p$ being the fluid enthalpy and {\bf fluid} pressure, respectively. 
+is the energy-momentum tensor of a magnetised perfect fluid, $w$ and $p$ being the {\bf fluid enthalpy density}and {\bf fluid} pressure, respectively. 
 Moreover, $^\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu}$ is the (dual of the) Faraday tensor relative to an observer with 
@@
 \end{equation}
-which relates the distribution of the potential with the distribution of enthalpy.
+which relates the distribution of the potential with the distribution of the {\bf enthalpy density}.
 
@@
 \end{equation}
-where $w_{\mathrm{c}}$ is the enthalpy at the centre and
+where $w_{\mathrm{c}}$ is the {\bf enthalpy density} at the centre and
 \begin{equation}
@@
 Therefore, for a given inner radius of the disc $r_{\mathrm{in}}$ we can obtain the potential $W_{\mathrm{in}}$.
-We now finally have all the ingredients required to find the enthalpy distribution (Eq.~\eqref{eq:enthalpy_eq}), the fluid pressure and magnetic pressure distributions (Eqs.~\eqref{eq:eos_fluid} and \eqref{eq:eos_mag}), and the {\bf rest-mass} density distribution, which can be trivially obtained inverting the barotropic relation, $p = K \rho^{\kappa}$.
-{\bf We note that the fluid enthalpy $w$ includes the rest-mass density $\rho$, and can thus be defined as $w=\rho h$ where $h$ is the specific enthalpy.
+We now finally have all the ingredients required to find the {\bf enthalpy density} distribution (Eq.~\eqref{eq:enthalpy_eq}), the fluid pressure and magnetic pressure distributions (Eqs.~\eqref{eq:eos_fluid} and \eqref{eq:eos_mag}), and the rest-mass density distribution, which can be trivially obtained inverting the barotropic relation, $p = K \rho^{\kappa}$.
+We note that the fluid {\bf enthalpy density} $w$ includes the rest-mass density $\rho$, and can thus be defined as $w=\rho h$ where $h$ is the specific enthalpy.
 The relativistic definition of this quantity is $h=1+\varepsilon+p/\rho$, where $\varepsilon$ is
@@
 since we use poytropic equations of state (relating $p$ with either $w$ or $\rho$ in the same functional form) we are
-implictly assuming that $h=1$, i.e.~the discs we build in our procedure are non-relativistic from a thermodynamical point of view.}
+implictly assuming that $h=1$, i.e.~the discs we build in our procedure are non-relativistic from a thermodynamical point of view.
 %{\bf We note that the specific internal energy $\varepsilon$ is needed to compute the enthalpy. We obtain
@@
 
-To reduce the number of free parameters to build the initial models we do as in~\citet{Komissarov:2006} and fix the values of the equation of state exponents, $\kappa$ and $\lambda$, and of the enthalpy at the disc centre, $w_{\mathrm{c}}$.
+To reduce the number of free parameters to build the initial models we do as in~\citet{Komissarov:2006} and fix the values of the equation of state exponents, $\kappa$ and $\lambda$, and of the {\bf enthalpy density} at the disc centre, $w_{\mathrm{c}}$.
 More precisely, we choose $\kappa = \lambda = 4/3$ and $w_{\mathrm{c}} = 1$.
@@
 We have shown the effects of changing $\beta$ and $\gamma$ beyond the purely hydrodynamical case considered in~\citet{Qian:2009}.
-The mophology of the solutions we have built no longer changes for magnetisation values above $\beta_{\mathrm{m}_{\mathrm{c}}} \sim 10^{3}$ and below $\beta_{\mathrm{m}_{\mathrm{c}}} \sim 10^{-3}$.
+The morphology of the solutions we have built no longer changes for magnetisation values above $\beta_{\mathrm{m}_{\mathrm{c}}} \sim 10^{3}$ and below $\beta_{\mathrm{m}_{\mathrm{c}}} \sim 10^{-3}$.
 These cases can thus be considered as the hydrodynamical and MHD limiting cases, respectively.
@@
 \begin{eqnarray}
-g_{tt} = - \left(1 - \frac{2Mr}{\rho^2}\right), \ g_{t\phi} = -\frac{2Mar\sin^2\theta}{\rho^2}, \ g_{\phi\phi} = \left(r^2 + a^2 + \frac{2Ma^2r\sin^2\theta}{\rho^2}\right) \sin^2 \theta\,,
+g_{tt} = - \left(1 - \frac{2Mr}{\rho^2}\right), \ g_{t\phi} = -\frac{2Mar\sin^2\theta}{\rho^2},
+\nonumber \\
+g_{\phi\phi} = \left(r^2 + a^2 + \frac{2Ma^2r\sin^2\theta}{\rho^2}\right) \sin^2 \theta\,,
 \end{eqnarray}
@@
 \begin{eqnarray}
-\partial_{\theta} \mathcal{A} = \partial_{\theta} g_{\phi\phi} + 2 (\partial_{\theta} l) g_{t\phi} + 2l\partial_{\theta} g_{t\phi} + 2l(\partial_{\theta} l) g_{tt} + l^2 \partial_{\theta} g_{tt} = \partial_{\theta} g_{\phi\phi} + 2l\partial_{\theta} g_{t\phi} + l^2 \partial_{\theta} g_{tt}\,,
+\partial_{\theta} \mathcal{A} = \partial_{\theta} g_{\phi\phi} + 2 (\partial_{\theta} l) g_{t\phi} + 2l\partial_{\theta} g_{t\phi} + 2l(\partial_{\theta} l) g_{tt} + l^2 \partial_{\theta} g_{tt} = 
+\nonumber \\
+= \partial_{\theta} g_{\phi\phi} + 2l\partial_{\theta} g_{t\phi} + l^2 \partial_{\theta} g_{tt}\,,
 \end{eqnarray}
@@
 &\times&
-\left(-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right)\left[\frac{-(\lambda - 1) K_{\mathrm{m}} \mathcal{L}^{\lambda - 2} \partial_r \mathcal{L}}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right]\,,
+\left(-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right)
+\nonumber \\
+&\times&\left[\frac{-(\lambda - 1) K_{\mathrm{m}} \mathcal{L}^{\lambda - 2} \partial_r \mathcal{L}}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right]\,,
 \end{eqnarray}

### 2017-07-10 paper_revised_v2/paper_revised_v2.tex
removed boldface

@@
 This method was later extended by~\cite{Komissarov:2006}  by adding a purely azimuthal magnetic field to build magnetised tori around rotating black holes.
-{\bf Dynamical evolutions of magnetized tori built with the Komissarov solution were first reported by~\cite{Montero:2007}.}
+Dynamical evolutions of magnetized tori built with the Komissarov solution were first reported by~\cite{Montero:2007}.
 On the other hand, assuming different distributions of angular momentum in the discs, \citet{Qian:2009} presented a method to build sequences of black hole thick accretion discs in dynamical equilibria, restricted however to the purely hydrodynamical case.
@@
 For this choice of $\eta$, we can find the location of the cusp of the disc  within the range $r_{\mathrm{mb}} \leq r_{\mathrm{cusp}} \leq r_{\mathrm{ms}}$ (for $0 \leq \beta \leq 1$).
-{\bf The cusp is defined as the circle in the equatorial plane on which the pressure gradient vanishes and the angular momentum of the disc equals the Keplerian angular momentum.} Moreover, this value of $\eta$ guarantees that constant angular momentum discs ($\beta = \gamma = 0$) with their inner edge located at the cusp ($r_{\mathrm{in}} = r_{\mathrm{cusp}}$) have no outer boundary, i.e~they are infinite discs (see also~\cite{Font:2002}).
+The cusp is defined as the circle in the equatorial plane on which the pressure gradient vanishes and the angular momentum of the disc equals the Keplerian angular momentum.
+Moreover, this value of $\eta$ guarantees that constant angular momentum discs ($\beta = \gamma = 0$) with their inner edge located at the cusp ($r_{\mathrm{in}} = r_{\mathrm{cusp}}$) have no outer boundary, i.e~they are infinite discs (see also~\cite{Font:2002}).
 
@@
 \end{equation}
-is the energy-momentum tensor of a magnetised perfect fluid, $w$ and $p$ being the {\bf fluid enthalpy density}and {\bf fluid} pressure, respectively. 
+is the energy-momentum tensor of a magnetised perfect fluid, $w$ and $p$ being the {\bf fluid enthalpy density} and fluid pressure, respectively. 
 Moreover, $^\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu}$ is the (dual of the) Faraday tensor relative to an observer with 
@@
 For this reason, Eq.~(\ref{eq:F}) also takes the form of an ordinary differential equation for the surfaces of constant potential, $\theta=\theta(r)$, which, upon integration, yields the location of those surfaces.
-Note that in~\citet{Qian:2009} these are surfaces of constant {\it {\bf fluid} pressure} instead, since their discs are purely hydrodynamical.
+Note that in~\citet{Qian:2009} these are surfaces of constant {\it fluid pressure} instead, since their discs are purely hydrodynamical.
 
@@
 \caption{Comparison with Komissarov's solution for a constant angular momentum model.
-The left panel shows the {\bf rest-mass} density distribution in logarithm scale for all radii and all angles while the middle and right panels show, respectively, the angular profile of the logarithm of the {\bf rest-mass} density at the centre of the disc and the radial profile of the {\bf rest-mass} density at the equatorial plane.}
+The left panel shows the rest-mass density distribution in logarithm scale for all radii and all angles while the middle and right panels show, respectively, the angular profile of the logarithm of the rest-mass density at the centre of the disc and the radial profile of the rest-mass density at the equatorial plane.}
 \label{komissarov}
@@
 Given that we have already obtained both the equipotential surfaces $\theta(r)$ which cross the segment $[r_{\mathrm{cusp}}, r_{\mathrm{c}}]$ at the equatorial plane and the values of the potential in that segment, we can obtain the complete potential distribution for the torus (outside of that segment).
-Once we have the potential distribution, we can find the {\bf fluid} pressure at the centre of the disc from Eq.~\eqref{eq:enthalpy_eq},
+Once we have the potential distribution, we can find the fluid pressure at the centre of the disc from Eq.~\eqref{eq:enthalpy_eq},
 \begin{equation}
@@
 Again, it is also important here to choose a suitable step of integration, especially at the outer end of the disc, because Eq.~\eqref{eq:F} diverges at the equatorial plane (the equipotential surfaces cross the equatorial plane perpendicularly).
-{\bf We show the proof of this statment in Appendix~\ref{div_partial_W}.}
+We show the proof of this statment in Appendix~\ref{div_partial_W}.
 
@@
 \caption{List of models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$.
-From left to right the columns report: the model name (with A, B and C standing for black hole spin $a = 0.5$, $0.9$ and $0.99$, respectively), the parameters of the angular momentum distribution $\beta$ and $\gamma$, the corresponding radii of the maximum {\bf fluid} pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential difference between the centre and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the discs, $r_{\mathrm{in}}$ and $r_{\mathrm{out}}$.}
+From left to right the columns report: the model name (with A, B and C standing for black hole spin $a = 0.5$, $0.9$ and $0.99$, respectively), the parameters of the angular momentum distribution $\beta$ and $\gamma$, the corresponding radii of the maximum fluid pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential difference between the centre and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the discs, $r_{\mathrm{in}}$ and $r_{\mathrm{out}}$.}
 \label{table:1}      
@@
 We build a series of 45 models, whose main features are summarised in Table~\ref{table:1} (for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$, i.e.~models where the effects of the magnetisation are unimportant), Table~\ref{table:2} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$, i.e.~equipartition models), and Table~\ref{table:3} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$, i.e.~highly-magnetised models).
-{\bf
+
 We note in particular that the radii of the maximum fluid pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, respectively, for the same value of $\beta_{\mathrm{m}_{\mathrm{c}}}$, never coincide.
-This also reflects the fact that constant fluid pressure surfaces do not coincide with constant magnetic pressure surfaces.}
+This also reflects the fact that constant fluid pressure surfaces do not coincide with constant magnetic pressure surfaces.
 
@@
 The visual comparison shows that our approach can reproduce those previous results with good agreement.
-The {\bf rest-mass} density distribution in the $(r\sin\theta,r\cos\theta)$ plane shown in the left panel of Fig.~\ref{komissarov} is remarkably similar to that shown in the left panel of Fig.~2 in~\citet{Komissarov:2006}.
-Not only the morphology of both models is nearly identical but also the range of variation of the {\bf rest-mass} density and the location of the disc centre agree well in both cases.
+The rest-mass density distribution in the $(r\sin\theta,r\cos\theta)$ plane shown in the left panel of Fig.~\ref{komissarov} is remarkably similar to that shown in the left panel of Fig.~2 in~\citet{Komissarov:2006}.
+Not only the morphology of both models is nearly identical but also the range of variation of the rest-mass density and the location of the disc centre agree well in both cases.
 This can be most clearly seen in the middle and right panels of Fig.~\ref{komissarov} which show, repectively, the angular profile at $r_{\rm c}$ and the radial profile at $\theta=\pi/2$.
 These two figures can be directly compared with Fig.~3 of~\citet{Komissarov:2006}.
-It is relevant to mention that very small changes in the location of the inner radius $r_{\mathrm{in}}$ have a significant effect on the maximum value of the {\bf rest-mass} density, which explains the small differences between our figures and the ones presented in~\citet{Komissarov:2006}.
+It is relevant to mention that very small changes in the location of the inner radius $r_{\mathrm{in}}$ have a significant effect on the maximum value of the rest-mass density, which explains the small differences between our figures and the ones presented in~\citet{Komissarov:2006}.
 
@@
 As $\gamma$ and $\beta$ increase from 0 to 0.9 (compare the three top rows) the discs become significantly thinner and radially smaller (see also Fig.~\ref{more-profile} below).
-It is also interesting to note that the maximum value of the {\bf rest-mass} density is higher (with respect to the value at the disc centre) as the spin increases.
+It is also interesting to note that the maximum value of the rest-mass density is higher (with respect to the value at the disc centre) as the spin increases.
 
@@
 \includegraphics[scale=0.2]{figures/fig4.pdf}
-\caption{Radial profiles of the {\bf rest-mass} density in the equatorial plane for \bf{$\beta_{\mathrm{m}_{\mathrm{c}}}=10^3$} (black curve), 1 (blue curve), and $10^{-3}$ (green curve). }
+\caption{Radial profiles of the rest-mass density in the equatorial plane for {$\beta_{\mathrm{m}_{\mathrm{c}}}=10^3$} (black curve), 1 (blue curve), and $10^{-3}$ (green curve). }
 \label{magnetisation-profile}
@@
 \caption{Effects of $\beta_{\mathrm{m}_{\mathrm{c}}}$.
-Left panel: variation of the value of the maximum {\bf rest-mass} density with respect to the logarithm of the magnetisation parameter.
+Left panel: variation of the value of the maximum rest-mass density with respect to the logarithm of the magnetisation parameter.
 The solid, dashed, and dotted lines refer to $a = 0.99$, $0.9$ and $0.5$, respectively, and the colour code refers to the models shown in the legend.
-Middle panel: variation of the location of the {\bf rest-mass} density maximum (and {\bf fluid} pressure) with respect to the logarithm of the magnetisation parameter for the three models shown in the legend with $a = 0.99$.
+Middle panel: variation of the location of the rest-mass density maximum (and fluid pressure) with respect to the logarithm of the magnetisation parameter for the three models shown in the legend with $a = 0.99$.
 Right panel: variation (also for $a = 0.99$) of the location of the maximum of the magnetic pressure with respect to the logarithm of $\beta_{\mathrm{m}_{\mathrm{c}}}$.}
@@
 $ and the only quantitative differences are found in the location of the centre of the disc (which moves inward with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$) and of the range of variation of the isodensity contours (the maximum being slightly larger with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$).
-This can be more clearly visualized in Figure~\ref{magnetisation-profile} which displays the radial profile at the equatorial plane of the {\bf rest-mass} density for the same three cases plotted in Fig.~\ref{magnetisation}.
+This can be more clearly visualized in Figure~\ref{magnetisation-profile} which displays the radial profile at the equatorial plane of the rest-mass density for the same three cases plotted in Fig.~\ref{magnetisation}.
 
@@
 As mentioned in the description of Fig.~\ref{models} as $\gamma$ and $\beta$ increase from 0 to 0.9 (compare black, blue, and green curves) the discs become gradually smaller.
-At the same time, the radial location of the {\bf rest-mass} density maximum increases and the maximum value of the central {\bf rest-mass} density (and pressure) decreases.
+At the same time, the radial location of the rest-mass density maximum increases and the maximum value of the central rest-mass density (and pressure) decreases.
 It is worth noticing that the radial profiles of some of the models overlap below a certain radius.
 More precisely, the black and red curves overlap below $r\sim r_{\mathrm{c}}$ (which corresponds to $\rho \sim 1$) and also the green and orange curves.
-In addition, this figure clearly shows that, besides modifying the thickness of the disc, $\beta$ is the parameter which determines the value of the {\bf rest-mass} density (and pressure) maximum.
+In addition, this figure clearly shows that, besides modifying the thickness of the disc, $\beta$ is the parameter which determines the value of the rest-mass density (and pressure) maximum.
 On the other hand, the parameter $\gamma$ is only relevant for controlling the radial size of the discs.
 
-In order to provide a quantitative comparison of the structural differences that appear along the sequence of equilibrium models, we plot in Fig.~\ref{max-vs-magnetisation} the variation of the maximum of the {\bf rest-mass} density (left panel), the radial location of the maximum of the {\bf fluid} pressure (middle panel), and the radial location of the maximum of the magnetic pressure (right panel) as a function of the magnetisation parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$.
+In order to provide a quantitative comparison of the structural differences that appear along the sequence of equilibrium models, we plot in Fig.~\ref{max-vs-magnetisation} the variation of the maximum of the rest-mass density (left panel), the radial location of the maximum of the fluid pressure (middle panel), and the radial location of the maximum of the magnetic pressure (right panel) as a function of the magnetisation parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$.
 All quantities plotted are measured at the equatorial plane.
@@
 Correspondingly, the colour of the lines indicates the value of $\beta$ and $\gamma$ used, namely, red curves correspond to $\gamma=\beta=0$, the blue ones to $\gamma=\beta=0.5$, and the black ones to $\gamma=\beta=0.9$.
-All curves show the same monotonically decreasing trend with $\beta_{\mathrm{m}_{\mathrm{c}}}$, yet for small enough and large enough values of $\beta_{\mathrm{m}_{\mathrm{c}}} $ the value of the {\bf rest-mass} density maximum does not change.
+All curves show the same monotonically decreasing trend with $\beta_{\mathrm{m}_{\mathrm{c}}}$, yet for small enough and large enough values of $\beta_{\mathrm{m}_{\mathrm{c}}} $ the value of the rest-mass density maximum does not change.
 However, in the interval $10^{-2}\le \beta_{\mathrm{m}_{\mathrm{c}}} \le 10^{2}$, $\rho_{\rm max}$ changes abruptly.
-The larger the black hole spin the larger the drop in the maximum of the {\bf rest-mass} density.
+The larger the black hole spin the larger the drop in the maximum of the rest-mass density.
 For sufficiently large values of $\beta_{\mathrm{m}_{\mathrm{c}}}$ (small magnetisation) the value of $\rho_{\rm max}$ stays constant to the same value irrespective of the black hole rotation.
 
-In the middle panel of Fig.~\ref{max-vs-magnetisation} we show the radial location of the maximum of the {\bf fluid} pressure as a function of $\beta_{\mathrm{m}_{\mathrm{c}}}$.
+In the middle panel of Fig.~\ref{max-vs-magnetisation} we show the radial location of the maximum of the fluid pressure as a function of $\beta_{\mathrm{m}_{\mathrm{c}}}$.
 The black hole spin is $a=0.99$ and the values of $\beta$ and $\gamma$ are indicated in the legend.
-For all values of $\beta$ and $\gamma$, the maximum of the location of the disc {\bf fluid} pressure decreases with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$.
+For all values of $\beta$ and $\gamma$, the maximum of the location of the disc fluid pressure decreases with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$.
 Below $\beta_{\mathrm{m}_{\mathrm{c}}}\sim 10^{-3}$ the location of the maximum does no longer change.
@@
 While this location also decreases with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$, the constant value achieved for values above $\beta_{\mathrm{m}_{\mathrm{c}}}\sim 10^{3}$ does depend on the specific values of $\beta$ and $\gamma$, contrary to what happens with the fluid pressure.
-{\bf It must be noted that the location of the maximum of the magnetic pressure is identical for all models considered when $\beta_{\mathrm{m}_{\mathrm{c}}} \equiv 1/(\lambda - 1) = 3$, as we show in Appendix~\ref{app_magmax}.
-At this value of $\beta_{\mathrm{m}_{\mathrm{c}}}$ all models cross at $r_{\mathrm{m}_{\mathrm{max}}} = r_{\mathrm{c}}$, as it is more clearly shown in the inset of the right panel of Fig.~\ref{max-vs-magnetisation}.}
+It must be noted that the location of the maximum of the magnetic pressure is identical for all models considered when $\beta_{\mathrm{m}_{\mathrm{c}}} \equiv 1/(\lambda - 1) = 3$, as we show in Appendix~\ref{app_magmax}.
+At this value of $\beta_{\mathrm{m}_{\mathrm{c}}}$ all models cross at $r_{\mathrm{m}_{\mathrm{max}}} = r_{\mathrm{c}}$, as it is more clearly shown in the inset of the right panel of Fig.~\ref{max-vs-magnetisation}.
 

### 2017-07-10 paper_revised_v2/paper_revised_v2.tex
added comment about maximum magnetisation

@@
 We build a series of 45 models, whose main features are summarised in Table~\ref{table:1} (for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$, i.e.~models where the effects of the magnetisation are unimportant), Table~\ref{table:2} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$, i.e.~equipartition models), and Table~\ref{table:3} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$, i.e.~highly-magnetised models).
+{\bf We have built models with very small values of $\beta_{m_c}$, such as  $\beta_{m_c} = 10^{-20}$ (extremely high magnetisation) without encountering numerical difficulties.
+In practice we have found that there are no qualitative differences in the structure of the discs once $\beta_{m_c}$ becomes smaller than a sufficiently small value, about $\beta_{m_c}=10^{-3}$.
+This is
+the reason why we choose that particular value as our lower limit in the figures and tables of the manuscript.}
 

### 2017-07-10 paper_revised_v2/paper_revised_v2.tex
minor typos corrected

--- 2017-07-10 paper_revised_v2/paper_revised_v2.tex
@@
 We build a series of 45 models, whose main features are summarised in Table~\ref{table:1} (for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$, i.e.~models where the effects of the magnetisation are unimportant), Table~\ref{table:2} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$, i.e.~equipartition models), and Table~\ref{table:3} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$, i.e.~highly-magnetised models).
+{\bf We have built models with very small values of $\beta_{\mathrm{m}_{\mathrm{c}}}$, such as  $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-20}$ (extremely high magnetisation) without encountering numerical difficulties.
+In practice we have found that there are no qualitative differences in the structure of the discs once $\beta_{\mathrm{m}_{\mathrm{c}}}$ becomes smaller than a sufficiently small value, about $\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$.
+This is the reason why we choose that particular value as our lower limit in the figures and tables of the manuscript.}
 

### 2017-07-10 paper_revised_v2/paper_revised_v2.tex
small typo

@@
 \end{equation}
-It is relevant to note that the only reference to the explicit form of the metric is done to show that $\mathcal{L} \neq 0$ and $\partial r \mathcal{L} \neq 0$ inside the disc.
+It is relevant to note that the only reference to the explicit form of the metric is done to show that $\mathcal{L} \neq 0$ and $\partial_r \mathcal{L} \neq 0$ inside the disc.
 This means that our result holds for any stationary and axisymmetric metric if the aforementioned inequalities hold.

### 2017-07-10 paper_revised_v2/paper_revised_v2.tex
some small rewording

@@
 We build a series of 45 models, whose main features are summarised in Table~\ref{table:1} (for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$, i.e.~models where the effects of the magnetisation are unimportant), Table~\ref{table:2} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$, i.e.~equipartition models), and Table~\ref{table:3} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$, i.e.~highly-magnetised models).
-{\bf We have built models with very small values of $\beta_{\mathrm{m}_{\mathrm{c}}}$, such as  $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-20}$ (extremely high magnetisation) without encountering numerical difficulties.
-In practice we have found that there are no qualitative differences in the structure of the discs once $\beta_{\mathrm{m}_{\mathrm{c}}}$ becomes smaller than a sufficiently small value, about $\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$.
+{\bf We note that we can build models with very small values of $\beta_{\mathrm{m}_{\mathrm{c}}}$, such as  e.g.~$\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-20}$ (extremely high magnetisation) without encountering numerical difficulties.
+No qualitative differences in the structure of the discs are found once $\beta_{\mathrm{m}_{\mathrm{c}}}$ becomes smaller than a sufficiently small value, about $\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$.
 This is the reason why we choose that particular value as our lower limit in the figures and tables of the manuscript.}

### 2017-07-11 paper_revised_v2/paper_revised_v2.tex
breaking properly eq. B6 when using two-column format
final version

@@
 \caption{Comparison with Komissarov's solution for a constant angular momentum model.
-The left panel shows the rest-mass density distribution in logarithm scale for all radii and all angles while the middle and right panels show, respectively, the angular profile of the logarithm of the rest-mass density at the centre of the disc and the radial profile of the rest-mass density at the equatorial plane.}
+The left panel shows the rest-mass density distribution in logarithm scale for all radii and all angles while the middle and right panels show, respectively, the angular profile of the logarithm of the rest-mass density at the centre of the disc and the radial profile of {\bf the logarithm of} the rest-mass density at the equatorial plane.}
 \label{komissarov}
@@
 This can be most clearly seen in the middle and right panels of Fig.~\ref{komissarov} which show, repectively, the angular profile at $r_{\rm c}$ and the radial profile at $\theta=\pi/2$.
-These two figures can be directly compared with Fig.~3 of~\citet{Komissarov:2006}.
+{\bf The middle figure} can be directly compared with Fig.~3 of~\citet{Komissarov:2006}.
 It is relevant to mention that very small changes in the location of the inner radius $r_{\mathrm{in}}$ have a significant effect on the maximum value of the rest-mass density, which explains the small differences between our figures and the ones presented in~\citet{Komissarov:2006}.
@@
 &\times&
-\left[\left(-\partial_r W \left(\frac{\lambda -1 }{\lambda}\right) \frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right) + \left(-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{-(\lambda - 1) K_{\mathrm{m}} \mathcal{L}^{\lambda - 2} \partial_r \mathcal{L}}{(K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1})^2}\right)\right]\,.
+\left[\left(-\partial_r W \left(\frac{\lambda -1 }{\lambda}\right) \frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right) 
+\right.
+\nonumber \\
+&+& \left.
+\left(-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{-(\lambda - 1) K_{\mathrm{m}} \mathcal{L}^{\lambda - 2} \partial_r \mathcal{L}}{(K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1})^2}\right)\right]\,.
 \end{eqnarray}

### 2017-07-12 paper_accepted/paper_accepted.tex
boldface removed. Added referee acknowledgement

--- 2017-07-11 paper_revised_v2/paper_revised_v2.tex
@@
 \usepackage{float}
-
-\newcommand{\tf}[1]{\textcolor{red}{TF: #1}}
-\newcommand{\sg}[1]{\textcolor{blue}{SG: #1}}
 
@@
 \end{equation}
-is the energy-momentum tensor of a magnetised perfect fluid, $w$ and $p$ being the {\bf fluid enthalpy density} and fluid pressure, respectively. 
+is the energy-momentum tensor of a magnetised perfect fluid, $w$ and $p$ being the fluid enthalpy density and fluid pressure, respectively. 
 Moreover, $^\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu}$ is the (dual of the) Faraday tensor relative to an observer with 
@@
 \end{equation}
-which relates the distribution of the potential with the distribution of the {\bf enthalpy density}.
+which relates the distribution of the potential with the distribution of the enthalpy density.
 
@@
 \caption{Comparison with Komissarov's solution for a constant angular momentum model.
-The left panel shows the rest-mass density distribution in logarithm scale for all radii and all angles while the middle and right panels show, respectively, the angular profile of the logarithm of the rest-mass density at the centre of the disc and the radial profile of {\bf the logarithm of} the rest-mass density at the equatorial plane.}
+The left panel shows the rest-mass density distribution in logarithm scale for all radii and all angles while the middle and right panels show, respectively, the angular profile of the logarithm of the rest-mass density at the centre of the disc and the radial profile of the logarithm of the rest-mass density at the equatorial plane.}
 \label{komissarov}
@@
 \end{equation}
-where $w_{\mathrm{c}}$ is the {\bf enthalpy density} at the centre and
+where $w_{\mathrm{c}}$ is the enthalpy density at the centre and
 \begin{equation}
@@
 Therefore, for a given inner radius of the disc $r_{\mathrm{in}}$ we can obtain the potential $W_{\mathrm{in}}$.
-We now finally have all the ingredients required to find the {\bf enthalpy density} distribution (Eq.~\eqref{eq:enthalpy_eq}), the fluid pressure and magnetic pressure distributions (Eqs.~\eqref{eq:eos_fluid} and \eqref{eq:eos_mag}), and the rest-mass density distribution, which can be trivially obtained inverting the barotropic relation, $p = K \rho^{\kappa}$.
-We note that the fluid {\bf enthalpy density} $w$ includes the rest-mass density $\rho$, and can thus be defined as $w=\rho h$ where $h$ is the specific enthalpy.
+We now finally have all the ingredients required to find the enthalpy density distribution (Eq.~\eqref{eq:enthalpy_eq}), the fluid pressure and magnetic pressure distributions (Eqs.~\eqref{eq:eos_fluid} and \eqref{eq:eos_mag}), and the rest-mass density distribution, which can be trivially obtained inverting the barotropic relation, $p = K \rho^{\kappa}$.
+We note that the fluid enthalpy density $w$ includes the rest-mass density $\rho$, and can thus be defined as $w=\rho h$ where $h$ is the specific enthalpy.
 The relativistic definition of this quantity is $h=1+\varepsilon+p/\rho$, where $\varepsilon$ is
@@
 implictly assuming that $h=1$, i.e.~the discs we build in our procedure are non-relativistic from a thermodynamical point of view.
-%{\bf We note that the specific internal energy $\varepsilon$ is needed to compute the enthalpy. We obtain
-%this quantity by combining the ideal fluid and the barotropic equations of state, which yields 
-%$\varepsilon=\frac{K}{\kappa-1}\rho^{\kappa-1}$.}
 
@@
 
-To reduce the number of free parameters to build the initial models we do as in~\citet{Komissarov:2006} and fix the values of the equation of state exponents, $\kappa$ and $\lambda$, and of the {\bf enthalpy density} at the disc centre, $w_{\mathrm{c}}$.
+To reduce the number of free parameters to build the initial models we do as in~\citet{Komissarov:2006} and fix the values of the equation of state exponents, $\kappa$ and $\lambda$, and of the enthalpy density at the disc centre, $w_{\mathrm{c}}$.
 More precisely, we choose $\kappa = \lambda = 4/3$ and $w_{\mathrm{c}} = 1$.
@@
 We build a series of 45 models, whose main features are summarised in Table~\ref{table:1} (for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$, i.e.~models where the effects of the magnetisation are unimportant), Table~\ref{table:2} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$, i.e.~equipartition models), and Table~\ref{table:3} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$, i.e.~highly-magnetised models).
-{\bf We note that we can build models with very small values of $\beta_{\mathrm{m}_{\mathrm{c}}}$, such as  e.g.~$\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-20}$ (extremely high magnetisation) without encountering numerical difficulties.
+We note that we can build models with very small values of $\beta_{\mathrm{m}_{\mathrm{c}}}$, such as  e.g.~$\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-20}$ (extremely high magnetisation) without encountering numerical difficulties.
 No qualitative differences in the structure of the discs are found once $\beta_{\mathrm{m}_{\mathrm{c}}}$ becomes smaller than a sufficiently small value, about $\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$.
-This is the reason why we choose that particular value as our lower limit in the figures and tables of the manuscript.}
+This is the reason why we choose that particular value as our lower limit in the figures and tables of the manuscript.
 
@@
 This can be most clearly seen in the middle and right panels of Fig.~\ref{komissarov} which show, repectively, the angular profile at $r_{\rm c}$ and the radial profile at $\theta=\pi/2$.
-{\bf The middle figure} can be directly compared with Fig.~3 of~\citet{Komissarov:2006}.
+The middle figure can be directly compared with Fig.~3 of~\citet{Komissarov:2006}.
 It is relevant to mention that very small changes in the location of the inner radius $r_{\mathrm{in}}$ have a significant effect on the maximum value of the rest-mass density, which explains the small differences between our figures and the ones presented in~\citet{Komissarov:2006}.
@@
 
-% It must be noted that the location of the maximum of the magnetic pressure is nearly identical for all models considered when $\log_{10}\beta_{\mathrm{m}_{\mathrm{c}}} \sim 0.5$.
-At this value of $\beta_{\mathrm{m}_{\mathrm{c}}}$ all models seem to cross, as it is more clearly shown in the inset of the right panel of Fig.~\ref{max-vs-magnetisation}.
-
 As a final remark we note that in the left and middle panels of Fig.~\ref{max-vs-magnetisation} we do not show the data for models with $\beta \neq \gamma$ as they coincide with the respective models with the same value of $\beta$.
@@
 It is a pleasure to thank P.~C.~Fragile and N.~Stergioulas for useful discussions and comments.
+We thank the referee, L.~Rezzolla, for his constructive report which improved the manuscript.
 Work supported by the Spanish MINECO (grant AYA2015-66899-C2-1-P) and the Generalitat Valenciana (PROMETEOII-2014-069).

### 2017-07-12 paper_accepted/paper_accepted.tex
removed referee version
minor typos

@@
 Equilibrium tori around Kerr black holes are built assuming that the spacetime gravitational potentials and the fluid fields are stationary and axisymmetric.
-In all the derivations presented below, the Kerr metric is implicitely written using standard Boyer-Lindquist coordinates.
+In all the derivations presented below, the Kerr metric is implicitly written using standard Boyer-Lindquist coordinates.
 It is convenient to introduce a number of relevant characteristic radii, such as the radius
@@
 since we use poytropic equations of state (relating $p$ with either $w$ or $\rho$ in the same functional form) we are
-implictly assuming that $h=1$, i.e.~the discs we build in our procedure are non-relativistic from a thermodynamical point of view.
+implicitly assuming that $h=1$, i.e.~the discs we build in our procedure are non-relativistic from a thermodynamical point of view.
 

### 2017-07-14 paper_lang_rev/paper_lang_rev.tex
paper_lang_rev

--- 2017-07-12 paper_accepted/paper_accepted.tex
@@
 {We discuss a procedure to build new sequences of magnetised, equilibrium tori around Kerr black holes which combines two approaches previously considered in the literature.
-For simplicity we assume that the test-fluid approximation holds, and hence we neglect the self-gravity of the fluid.
-The models are built assuming a particular form of the angular momentum distribution from which the location and morphology of equipotential surfaces can be computed.
+For simplicity we have assumed that the test-fluid approximation holds, and hence we neglected the self-gravity of the fluid.
+The models were built assuming a particular form of the angular momentum distribution from which the location and morphology of equipotential surfaces can be computed.
 This ansatz includes, in particular, the  constant angular momentum case originally employed in the construction of thick tori -- or Polish doughnuts -- and it has already been used to build equilibrium sequences of purely hydrodynamical models.
@@
 
-The investigation of this type of systems, either by analytical or numerical means, may rely on the ability to construct suitable 
+Investigation of such systems, either by analytical or numerical means, may rely on the ability to construct suitable 
 representations based on physical assumptions.
@@
 This method was later extended by~\cite{Komissarov:2006}  by adding a purely azimuthal magnetic field to build magnetised tori around rotating black holes.
-Dynamical evolutions of magnetized tori built with the Komissarov solution were first reported by~\cite{Montero:2007}.
+Dynamical evolutions of magnetised tori built with the Komissarov solution were first reported by~\cite{Montero:2007}.
 On the other hand, assuming different distributions of angular momentum in the discs, \citet{Qian:2009} presented a method to build sequences of black hole thick accretion discs in dynamical equilibria, restricted however to the purely hydrodynamical case.
 
- In this paper we combine the two approaches considered in~\cite{Komissarov:2006} and~\citet{Qian:2009} to build new sequences of equilibrium tori around Kerr black holes.
+ In this paper we have combined the two approaches considered in~\cite{Komissarov:2006} and~\citet{Qian:2009} to build new sequences of equilibrium tori around Kerr black holes.
 Building on these works, we present here the extension of the models of~\citet{Qian:2009} to account for discs endowed with a purely toroidal magnetic field.
-In our procedure we hence assume a form of the angular momentum distribution that departs from the constant case considered by~\cite{Komissarov:2006} and from which the location and morphology of the equipotential surfaces can be numerically computed.
+In our procedure we hence assumed a form of the angular momentum distribution that departs from the constant case considered by~\cite{Komissarov:2006} and from which the location and morphology of the equipotential surfaces can be numerically computed.
 As we shall show below, for the particular case of constant angular momentum distributions, our method is in good agreement with the results of~\citet{Komissarov:2006}.
@@
 
-The organization of the paper is as follows: Section~\ref{framework} presents the analytic framework to build the discs while Section~\ref{methodology} explains the corresponding numerical procedure.
-The sequences of models are discussed in Section~\ref{results}.
-Finally, the conclusions are summarized in Section~\ref{conclusions}, where we also briefly indicate potential extensions of this work we plan to inspect.
+The organization of the paper is as follows: Sect.~\ref{framework} presents the analytic framework to build the discs while Sect.~\ref{methodology} explains the corresponding numerical procedure.
+The sequences of models are discussed in Sect.~\ref{results}.
+Finally, the conclusions are summarised in Sect.~\ref{conclusions}, where we also briefly indicate potential extensions of this work we plan to inspect.
 In our work we assume that the test-fluid approximation holds, thus neglecting the self-gravity of the fluid, and further assume that the spacetime is described by the Kerr metric.
 In mathematical expressions below Greek indices are spacetime indices running from 0 to 3 and Latin indices are only spatial.
-We use geometrized units where $G = c = 1$.
+We use geometrised units where $G = c = 1$.
 
@@
 
-Equilibrium tori around Kerr black holes are built assuming that the spacetime gravitational potentials and the fluid fields are stationary and axisymmetric.
+Equilibrium tori around Kerr black holes were built assuming that the spacetime gravitational potentials and the fluid fields are stationary and axisymmetric.
 In all the derivations presented below, the Kerr metric is implicitly written using standard Boyer-Lindquist coordinates.
@@
 \end{equation}
-where $g_{\mu\nu}$ is the metric tensor and we are assuming circular motion, i.e. the four-velocity can be written as
+where $g_{\mu\nu}$ is the metric tensor and we are assuming circular motion, that is, the four-velocity can be written as
 \begin{equation}
@@
 four-velocity $u^{\mu}$, and $b^{\mu}$ is the magnetic field in that frame, with
-$b^2=b^{\mu}b_{\mu}$. Assuming the magnetic field is purely azimuthal, i.e.~$b^r = b^{\theta} = 0$,
+$b^2=b^{\mu}b_{\mu}$. Assuming the magnetic field is purely azimuthal, that is, $b^r = b^{\theta} = 0$,
 and taking into account that the flow is stationary and axisymmetric, the conservation of the current density and of the Faraday tensor follow.
@@
 $ are constants.
-This particular choice of barotropic relationships, $w = w(p)$ and $\tilde{w} = \tilde{w}(\tilde{p}_{\mathrm{m}})$, fulfill the general relativistic version of the von Zeipel theorem for a toroidal magnetic field~\citep{vonZeipel:1924, Zanotti:2015}, i.e.~the surfaces of constant $\Omega$ and constant $l$ coincide.
+This particular choice of barotropic relationships, $w = w(p)$ and $\tilde{w} = \tilde{w}(\tilde{p}_{\mathrm{m}})$, fulfill the general relativistic version of the von Zeipel theorem for a toroidal magnetic field~\citep{vonZeipel:1924, Zanotti:2015}, that is, the surfaces of constant $\Omega$ and constant $l$ coincide.
 
@@
 %%%%%%%%%%%%
-\section{Methodology}
+\section{Method}
 \label{methodology}
@@
 For this reason, Eq.~(\ref{eq:F}) also takes the form of an ordinary differential equation for the surfaces of constant potential, $\theta=\theta(r)$, which, upon integration, yields the location of those surfaces.
-Note that in~\citet{Qian:2009} these are surfaces of constant {\it fluid pressure} instead, since their discs are purely hydrodynamical.
+We note that in~\citet{Qian:2009} these are surfaces of constant {\it fluid pressure} instead, since their discs are purely hydrodynamical.
 
@@
 since we use poytropic equations of state (relating $p$ with either $w$ or $\rho$ in the same functional form) we are
-implicitly assuming that $h=1$, i.e.~the discs we build in our procedure are non-relativistic from a thermodynamical point of view.
+implicitly assuming that $h=1$, that is, the discs we build in our procedure are non-relativistic from a thermodynamical point of view.
 
@@
 \begin{table}
-\caption{List of models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$.
+\caption{Models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$.
 From left to right the columns report: the model name (with A, B and C standing for black hole spin $a = 0.5$, $0.9$ and $0.99$, respectively), the parameters of the angular momentum distribution $\beta$ and $\gamma$, the corresponding radii of the maximum fluid pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential difference between the centre and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the discs, $r_{\mathrm{in}}$ and $r_{\mathrm{out}}$.}
@@
 \begin{table}
-\caption{List of models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 1$. The naming of the models and the parameters reported in the columns are as in Table~\ref{table:1}.}             
+\caption{Models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 1$. The naming of the models and the parameters reported in the columns are as in Table~\ref{table:1}.}             
 \label{table:2}      
@@
 This still leaves us with five parameters to control the size, shape, thickness, and magnetisation of the disc, namely the magnetisation parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$, the parameters of the angular momentum distribution $\beta$ and $\gamma$, the black hole spin parameter $a$, and the inner radius of the disc $r_{\mathrm{in}}$.
-We build a series of 45 models, whose main features are summarised in Table~\ref{table:1} (for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$, i.e.~models where the effects of the magnetisation are unimportant), Table~\ref{table:2} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$, i.e.~equipartition models), and Table~\ref{table:3} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$, i.e.~highly-magnetised models).
-We note that we can build models with very small values of $\beta_{\mathrm{m}_{\mathrm{c}}}$, such as  e.g.~$\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-20}$ (extremely high magnetisation) without encountering numerical difficulties.
+We build a series of 45 models, whose main features are summarised in Table~\ref{table:1} (for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$, that is, models where the effects of the magnetisation are unimportant), Table~\ref{table:2} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$, i.e.~equipartition models), and Table~\ref{table:3} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$, i.e.~highly-magnetised models).
+We note that we can build models with very small values of $\beta_{\mathrm{m}_{\mathrm{c}}}$, such as for example $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-20}$ (extremely high magnetisation) without encountering numerical difficulties.
 No qualitative differences in the structure of the discs are found once $\beta_{\mathrm{m}_{\mathrm{c}}}$ becomes smaller than a sufficiently small value, about $\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$.
@@
 We start by assessing our procedure by first building an extra disc model that can be directly compared with one of the two models in~\citet{Komissarov:2006}.
-This is shown in Figure~\ref{komissarov}, which corresponds to the same constant specific angular momentum model A presented by~\citet{Komissarov:2006}.
+This is shown in Fig.~\ref{komissarov}, which corresponds to the same constant specific angular momentum model A presented by~\citet{Komissarov:2006}.
 The parameters of this model are $a=0.9$, $\beta_{\mathrm{m}_{\mathrm{c}}}=0.1$, and $l=2.8$.
@@
 \begin{table}
-\caption{List of models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$. The naming of the models and the parameters reported in the columns are as in Table~\ref{table:1}.}             
+\caption{Models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$. The naming of the models and the parameters reported in the columns are as in Table~\ref{table:1}.}             
 \label{table:3}      
@@
 
-A representative sample of the isodensity surfaces for some of our models appears in Figure~\ref{models}.
+A representative sample of the isodensity surfaces for some of our models appears in Fig.~\ref{models}.
 We plot, in particular, the models of Table~\ref{table:3}, for which the magnetisation is highest ($\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$).
-From left to right the columns of this figure correspond to increasing values of the black hole spin, namely, $a=0.5$, 0.9 and 0.99, while from top to bottom the rows correspond to different combinations of the $\gamma$ and $\beta$ parameters that characterize the ansatz for the angular momentum distribution of~\citet{Qian:2009} (the particular values are indicated in the caption of the figure).
+From left to right the columns of this figure correspond to increasing values of the black hole spin, namely, $a=0.5$, 0.9 and 0.99, while from top to bottom the rows correspond to different combinations of the $\gamma$ and $\beta$ parameters that characterise the ansatz for the angular momentum distribution of~\citet{Qian:2009} (the particular values are indicated in the caption of the figure).
 A rapid inspection shows that the structure of the discs noticeable changes when the parameters change.
@@
 
-Figure~\ref{magnetisation} shows the effects of changing the parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$ (the magnetisation) in the structure of the discs.
+Fig~\ref{magnetisation} shows the effects of changing the parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$ (the magnetisation) in the structure of the discs.
 From left to right the values plotted in each panel are $\beta_{\mathrm{m}_{\mathrm{c}}}=10^3$, 1, and $10^{-3}$.
@@
 The larger the value of $\beta_{\mathrm{m}_{\mathrm{c}}}$ the less important the effects of the magnetisation in the disc structure.
-Figure~\ref{magnetisation} shows that, at least for the kind of magnetic field distribution we are considering, the effects of the magnetisation are minor.
+Fig~\ref{magnetisation} shows that, at least for the kind of magnetic field distribution we are considering, the effects of the magnetisation are minor.
 The disc structure remains fairly similar for all values of $\beta_{\mathrm{m}_{\mathrm{c}}}
 $ and the only quantitative differences are found in the location of the centre of the disc (which moves inward with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$) and of the range of variation of the isodensity contours (the maximum being slightly larger with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$).
-This can be more clearly visualized in Figure~\ref{magnetisation-profile} which displays the radial profile at the equatorial plane of the rest-mass density for the same three cases plotted in Fig.~\ref{magnetisation}.
+This can be more clearly visualised in Fig.~\ref{magnetisation-profile} which displays the radial profile at the equatorial plane of the rest-mass density for the same three cases plotted in Fig.~\ref{magnetisation}.
 
@@
 It is a pleasure to thank P.~C.~Fragile and N.~Stergioulas for useful discussions and comments.
-We thank the referee, L.~Rezzolla, for his constructive report which improved the manuscript.
+We thank the referee for his constructive report which improved the manuscript.
 Work supported by the Spanish MINECO (grant AYA2015-66899-C2-1-P) and the Generalitat Valenciana (PROMETEOII-2014-069).
@@
 To prove that Eq.~\eqref{eq:F} diverges at $\theta = \pi/2$ we need to show that
-Eq.~\eqref{eq:polar_der_pot} vanishes at the equator, i.e.
+Eq.~\eqref{eq:polar_der_pot} vanishes at the equator, that is
 \begin{eqnarray}

### 2017-07-14 paper_lang_rev/paper_lang_rev.tex
work on language corrections

--- 2017-07-12 paper_accepted/paper_accepted.tex
@@
 \usepackage{float}
+
+\newcommand{\tf}[1]{\textcolor{red}{TF: #1}}
+\newcommand{\sg}[1]{\textcolor{blue}{#1}}
 
@@
 {We discuss a procedure to build new sequences of magnetised, equilibrium tori around Kerr black holes which combines two approaches previously considered in the literature.
-For simplicity we assume that the test-fluid approximation holds, and hence we neglect the self-gravity of the fluid.
-The models are built assuming a particular form of the angular momentum distribution from which the location and morphology of equipotential surfaces can be computed.
+For simplicity we \sg{have assumed} that the test-fluid approximation holds, and hence we \sg{neglected} the self-gravity of the fluid.
+The models \sg{were} built assuming a particular form of the angular momentum distribution from which the location and morphology of equipotential surfaces can be computed.
 This ansatz includes, in particular, the  constant angular momentum case originally employed in the construction of thick tori -- or Polish doughnuts -- and it has already been used to build equilibrium sequences of purely hydrodynamical models.
@@
 
-The investigation of this type of systems, either by analytical or numerical means, may rely on the ability to construct suitable 
+\sg{Investigation} of \sg{such} systems, either by analytical or numerical means, may rely on the ability to construct suitable 
 representations based on physical assumptions.
 The construction of equilibrium models of stationary discs around black holes has indeed a long tradition (see~\cite{Abramowicz:2013} and references therein).
-In particular, the so-called ``Polish doughnuts"~\citep{Abramowicz:1978,Kozlowski:1978} provide a  very general method to build equilibrium configurations of perfect fluid matter orbiting around a Kerr black hole.
+In particular, the \sg{`Polish doughnuts'}~\citep{Abramowicz:1978,Kozlowski:1978} provide a  very general method to build equilibrium configurations of perfect fluid matter orbiting around a Kerr black hole.
 This fully relativistic model assumes that the disc is non-magnetised and that the matter obeys a  constant specific angular momentum distribution.
@@
 
- In this paper we combine the two approaches considered in~\cite{Komissarov:2006} and~\citet{Qian:2009} to build new sequences of equilibrium tori around Kerr black holes.
+ In this paper we \sg{have combined} the two approaches considered in~\cite{Komissarov:2006} and~\citet{Qian:2009} to build new sequences of equilibrium tori around Kerr black holes.
 Building on these works, we present here the extension of the models of~\citet{Qian:2009} to account for discs endowed with a purely toroidal magnetic field.
-In our procedure we hence assume a form of the angular momentum distribution that departs from the constant case considered by~\cite{Komissarov:2006} and from which the location and morphology of the equipotential surfaces can be numerically computed.
+In our procedure we hence \sg{assumed} a form of the angular momentum distribution that departs from the constant case considered by~\cite{Komissarov:2006} and from which the location and morphology of the equipotential surfaces can be numerically computed.
 As we shall show below, for the particular case of constant angular momentum distributions, our method is in good agreement with the results of~\citet{Komissarov:2006}.
@@
 
-The organization of the paper is as follows: Section~\ref{framework} presents the analytic framework to build the discs while Section~\ref{methodology} explains the corresponding numerical procedure.
-The sequences of models are discussed in Section~\ref{results}.
-Finally, the conclusions are summarized in Section~\ref{conclusions}, where we also briefly indicate potential extensions of this work we plan to inspect.
+The organization of the paper is as follows: \sg{Sect.}~\ref{framework} presents the analytic framework to build the discs while \sg{Sect.}~\ref{methodology} explains the corresponding numerical procedure.
+The sequences of models are discussed in \sg{Sect.}~\ref{results}.
+Finally, the conclusions are summarized in \sg{Sect.}~\ref{conclusions}, where we also briefly indicate potential extensions of this work we plan to inspect.
 In our work we assume that the test-fluid approximation holds, thus neglecting the self-gravity of the fluid, and further assume that the spacetime is described by the Kerr metric.
@@
 
-Equilibrium tori around Kerr black holes are built assuming that the spacetime gravitational potentials and the fluid fields are stationary and axisymmetric.
+Equilibrium tori around Kerr black holes \sg{were} built assuming that the spacetime gravitational potentials and the fluid fields are stationary and axisymmetric.
 In all the derivations presented below, the Kerr metric is implicitly written using standard Boyer-Lindquist coordinates.
@@
 \end{equation}
-where $g_{\mu\nu}$ is the metric tensor and we are assuming circular motion, i.e. the four-velocity can be written as
+where $g_{\mu\nu}$ is the metric tensor and we are assuming circular motion, \sg{that is,} the four-velocity can be written as
 \begin{equation}
@@
 four-velocity $u^{\mu}$, and $b^{\mu}$ is the magnetic field in that frame, with
-$b^2=b^{\mu}b_{\mu}$. Assuming the magnetic field is purely azimuthal, i.e.~$b^r = b^{\theta} = 0$,
+$b^2=b^{\mu}b_{\mu}$. Assuming the magnetic field is purely azimuthal, \sg{that is} $b^r = b^{\theta} = 0$,
 and taking into account that the flow is stationary and axisymmetric, the conservation of the current density and of the Faraday tensor follow.
@@
 $ are constants.
-This particular choice of barotropic relationships, $w = w(p)$ and $\tilde{w} = \tilde{w}(\tilde{p}_{\mathrm{m}})$, fulfill the general relativistic version of the von Zeipel theorem for a toroidal magnetic field~\citep{vonZeipel:1924, Zanotti:2015}, i.e.~the surfaces of constant $\Omega$ and constant $l$ coincide.
+This particular choice of barotropic relationships, $w = w(p)$ and $\tilde{w} = \tilde{w}(\tilde{p}_{\mathrm{m}})$, fulfill the general relativistic version of the von Zeipel theorem for a toroidal magnetic field~\citep{vonZeipel:1924, Zanotti:2015}, \sg{that is,} the surfaces of constant $\Omega$ and constant $l$ coincide.
 
@@
 %%%%%%%%%%%%
-\section{Methodology}
+\section{\sg{Method}}
 \label{methodology}
@@
 For this reason, Eq.~(\ref{eq:F}) also takes the form of an ordinary differential equation for the surfaces of constant potential, $\theta=\theta(r)$, which, upon integration, yields the location of those surfaces.
-Note that in~\citet{Qian:2009} these are surfaces of constant {\it fluid pressure} instead, since their discs are purely hydrodynamical.
+\sg{We note} that in~\citet{Qian:2009} these are surfaces of constant {\it fluid pressure} instead, since their discs are purely hydrodynamical.
 
@@
 since we use poytropic equations of state (relating $p$ with either $w$ or $\rho$ in the same functional form) we are
-implicitly assuming that $h=1$, i.e.~the discs we build in our procedure are non-relativistic from a thermodynamical point of view.
+implicitly assuming that $h=1$, \sg{that is,} the discs we build in our procedure are non-relativistic from a thermodynamical point of view.
 
@@
 \begin{table}
-\caption{List of models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$.
+\caption{\sg{Models} for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$.
 From left to right the columns report: the model name (with A, B and C standing for black hole spin $a = 0.5$, $0.9$ and $0.99$, respectively), the parameters of the angular momentum distribution $\beta$ and $\gamma$, the corresponding radii of the maximum fluid pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential difference between the centre and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the discs, $r_{\mathrm{in}}$ and $r_{\mathrm{out}}$.}
@@
 \begin{table}
-\caption{List of models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 1$. The naming of the models and the parameters reported in the columns are as in Table~\ref{table:1}.}             
+\caption{\sg{Models} for $\beta_{\mathrm{m}_{\mathrm{c}}} = 1$. The naming of the models and the parameters reported in the columns are as in Table~\ref{table:1}.}             
 \label{table:2}      
@@
 We build a series of 45 models, whose main features are summarised in Table~\ref{table:1} (for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$, i.e.~models where the effects of the magnetisation are unimportant), Table~\ref{table:2} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$, i.e.~equipartition models), and Table~\ref{table:3} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$, i.e.~highly-magnetised models).
-We note that we can build models with very small values of $\beta_{\mathrm{m}_{\mathrm{c}}}$, such as  e.g.~$\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-20}$ (extremely high magnetisation) without encountering numerical difficulties.
+We note that we can build models with very small values of $\beta_{\mathrm{m}_{\mathrm{c}}}$, such as \sg{for example} $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-20}$ (extremely high magnetisation) without encountering numerical difficulties.
 No qualitative differences in the structure of the discs are found once $\beta_{\mathrm{m}_{\mathrm{c}}}$ becomes smaller than a sufficiently small value, about $\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$.
@@
 We start by assessing our procedure by first building an extra disc model that can be directly compared with one of the two models in~\citet{Komissarov:2006}.
-This is shown in Figure~\ref{komissarov}, which corresponds to the same constant specific angular momentum model A presented by~\citet{Komissarov:2006}.
+This is shown in \sg{Fig.}~\ref{komissarov}, which corresponds to the same constant specific angular momentum model A presented by~\citet{Komissarov:2006}.
 The parameters of this model are $a=0.9$, $\beta_{\mathrm{m}_{\mathrm{c}}}=0.1$, and $l=2.8$.
@@
 \begin{table}
-\caption{List of models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$. The naming of the models and the parameters reported in the columns are as in Table~\ref{table:1}.}             
+\caption{\sg{Models} for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$. The naming of the models and the parameters reported in the columns are as in Table~\ref{table:1}.}             
 \label{table:3}      
@@
 
-A representative sample of the isodensity surfaces for some of our models appears in Figure~\ref{models}.
+A representative sample of the isodensity surfaces for some of our models appears in \sg{Fig.}~\ref{models}.
 We plot, in particular, the models of Table~\ref{table:3}, for which the magnetisation is highest ($\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$).
@@
 The larger the value of $\beta_{\mathrm{m}_{\mathrm{c}}}$ the less important the effects of the magnetisation in the disc structure.
-Figure~\ref{magnetisation} shows that, at least for the kind of magnetic field distribution we are considering, the effects of the magnetisation are minor.
+\sg{Fig.}~\ref{magnetisation} shows that, at least for the kind of magnetic field distribution we are considering, the effects of the magnetisation are minor.
 The disc structure remains fairly similar for all values of $\beta_{\mathrm{m}_{\mathrm{c}}}
 $ and the only quantitative differences are found in the location of the centre of the disc (which moves inward with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$) and of the range of variation of the isodensity contours (the maximum being slightly larger with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$).
-This can be more clearly visualized in Figure~\ref{magnetisation-profile} which displays the radial profile at the equatorial plane of the rest-mass density for the same three cases plotted in Fig.~\ref{magnetisation}.
+This can be more clearly visualized in \sg{Fig.}~\ref{magnetisation-profile} which displays the radial profile at the equatorial plane of the rest-mass density for the same three cases plotted in Fig.~\ref{magnetisation}.
 
@@
 It is worth noticing that the radial profiles of some of the models overlap below a certain radius.
-More precisely, the black and red curves overlap below $r\sim r_{\mathrm{c}}$ (which corresponds to $\rho \sim 1$) and also the green and orange curves.
+More precisely, \sg{the models with equal $\beta$} overlap below $r\sim r_{\mathrm{c}}$ (which corresponds to $\rho \sim 1$).
 In addition, this figure clearly shows that, besides modifying the thickness of the disc, $\beta$ is the parameter which determines the value of the rest-mass density (and pressure) maximum.
@@
 All quantities plotted are measured at the equatorial plane.
-Let us first consider the left panel.
+\sg{Let us first consider the left panel.
 The line type used indicates the value of the black hole spin $a$, namely, a dotted line is for $a=0.5$, a dashed line for $a=0.9$, and a solid line for $a=0.99$.
-Correspondingly, the colour of the lines indicates the value of $\beta$ and $\gamma$ used, namely, red curves correspond to $\gamma=\beta=0$, the blue ones to $\gamma=\beta=0.5$, and the black ones to $\gamma=\beta=0.9$.
+Correspondingly, the colour of the lines indicates the value of $\beta$ and $\gamma$ used, namely, red curves correspond to $\gamma=\beta=0$, the blue ones to $\gamma=\beta=0.5$, and the black ones to $\gamma=\beta=0.9$ \bf{Seg\'un lo que han dicho arriba, todo esto deber\'ia ser borrado.}}.
 All curves show the same monotonically decreasing trend with $\beta_{\mathrm{m}_{\mathrm{c}}}$, yet for small enough and large enough values of $\beta_{\mathrm{m}_{\mathrm{c}}} $ the value of the rest-mass density maximum does not change.
@@
 To prove that Eq.~\eqref{eq:F} diverges at $\theta = \pi/2$ we need to show that
-Eq.~\eqref{eq:polar_der_pot} vanishes at the equator, i.e.
+Eq.~\eqref{eq:polar_der_pot} vanishes at the equator, \sg{that is}
 \begin{eqnarray}

### 2017-07-15 paper_lang_rev/paper_lang_rev.tex
work on language corrections & typo

@@
 This method was later extended by~\cite{Komissarov:2006}  by adding a purely azimuthal magnetic field to build magnetised tori around rotating black holes.
-Dynamical evolutions of magnetized tori built with the Komissarov solution were first reported by~\cite{Montero:2007}.
+Dynamical evolutions of \sg{magnetised} tori built with the Komissarov solution were first reported by~\cite{Montero:2007}.
 On the other hand, assuming different distributions of angular momentum in the discs, \citet{Qian:2009} presented a method to build sequences of black hole thick accretion discs in dynamical equilibria, restricted however to the purely hydrodynamical case.
@@
 The sequences of models are discussed in \sg{Sect.}~\ref{results}.
-Finally, the conclusions are summarized in \sg{Sect.}~\ref{conclusions}, where we also briefly indicate potential extensions of this work we plan to inspect.
+Finally, the conclusions are \sg{summarised} in \sg{Sect.}~\ref{conclusions}, where we also briefly indicate potential extensions of this work we plan to inspect.
 In our work we assume that the test-fluid approximation holds, thus neglecting the self-gravity of the fluid, and further assume that the spacetime is described by the Kerr metric.
 In mathematical expressions below Greek indices are spacetime indices running from 0 to 3 and Latin indices are only spatial.
-We use geometrized units where $G = c = 1$.
+We use \sg{geometrised} units where $G = c = 1$.
 
@@
  \hline 
-C1 & $0.0$ & $0.0$ & $1.68$ &  $1.80$  & $-0.246$ & $1.21$ & -- \\ 
+C1 & $0.0$ & $0.0$ & $1.68$ &  $1.80$  & $-24.6$ & $1.21$ & -- \\ 
 C2 & $0.5$ & $0.5$ & $1.77$ &  $1.86$  & $-7.34$ & $1.26$ & $2.50$\\  
@@
 We plot, in particular, the models of Table~\ref{table:3}, for which the magnetisation is highest ($\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$).
-From left to right the columns of this figure correspond to increasing values of the black hole spin, namely, $a=0.5$, 0.9 and 0.99, while from top to bottom the rows correspond to different combinations of the $\gamma$ and $\beta$ parameters that characterize the ansatz for the angular momentum distribution of~\citet{Qian:2009} (the particular values are indicated in the caption of the figure).
+From left to right the columns of this figure correspond to increasing values of the black hole spin, namely, $a=0.5$, 0.9 and 0.99, while from top to bottom the rows correspond to different combinations of the $\gamma$ and $\beta$ parameters that \sg{characterise} the ansatz for the angular momentum distribution of~\citet{Qian:2009} (the particular values are indicated in the caption of the figure).
 A rapid inspection shows that the structure of the discs noticeable changes when the parameters change.
@@
 $ and the only quantitative differences are found in the location of the centre of the disc (which moves inward with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$) and of the range of variation of the isodensity contours (the maximum being slightly larger with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$).
-This can be more clearly visualized in \sg{Fig.}~\ref{magnetisation-profile} which displays the radial profile at the equatorial plane of the rest-mass density for the same three cases plotted in Fig.~\ref{magnetisation}.
+This can be more clearly \sg{visualised} in \sg{Fig.}~\ref{magnetisation-profile} which displays the radial profile at the equatorial plane of the rest-mass density for the same three cases plotted in Fig.~\ref{magnetisation}.
 

### 2017-11-14 magnetised_polish_doughnuts_revisited/paper_revised_v2/referee_reply.txt
new paper added

Referee Report

The authors have followed carefully all of the suggestions made and I am
pleased to see that they were able to provide more rigorous support to
some of the arguments presented in the paper. The new appendices A and B
present valuable additions to the paper.

In view of these considerations I am glad to recommend the publication of
the manuscript as a regular paper on A&A. At the same time, I'd like the
authors to consider some of the small suggestions listed below and
addressing some of the questions raised.

## A. ...We have included the following comment at the end of the paragraph
## following Eq. (27): "We note that the fluid enthalpy w includes the
## rest-mass density rhos, and can thus be defined as w = rho h where h
## is the specific enthalpy. The relativistic definition of this quantity
## is h = 1+epsilon+p/rho, where epsilon is the specific internal
## energy. From a thermodynamical point of view a non-relativistic fluid
## satisfies h = 1. Therefore, since we use poytropic equations of state
## (relating p with either w or rho in the same functional form) we are
## implictly assuming that h = 1, i.e. the discs we build in our
## procedure are non-relativistic from a thermodynamical point of view."

The authors should note that "w" is the *enthalpy density* and not the
enthalpy. This becomes clear: any "specific" quantity becomes a
"density" when multiplied by a rest-mass density.

## A: The reason we show the middle panel in logarithm scale and the
## right panel in linear scale is because this is the choice in
## Komissarov (2006). We have followed the same choice in order to
## facilitate the qualitative and quantitative comparison for this
## constant angular momentum test. If the referee concurred, we would
## prefer to keep the right panel in linear scale. If not, we would not
## mind changing the right panel to logarithmic scale.

Following too closely the work of Komissarov is not necessary and not
necessarily a good idea. Rather, I think that a plot in logarithmic
scale would be more informative.

## A: We have built models with very small values of beta_mc, such as
## beta_mc = 1e-20 (extremely high magnetisation) without encountering
## numerical difficulties. In practice we have found that there are no
## qualitative differences in the structure of the discs once beta_mc
## becomes smaller than a sufficiently small value...

It is important to incorporate this comment in the revised version.

## R: - Fig. 2: all of the panels would benefit from a legend showing the
## corresponding values of gamma and beta. This would avoid having to read
## the caption repeatedly. The same is true also for Fig. 3.
##
## A: Done.

I think that the legend should also report the value of the
black-hole's spin as this makes the various panels readable also
without having to consult the caption.

## If the referee considered these explanations satisfactory and would
## like to have them included in the manuscript, we would be happy to do
## so.

I find the explanation satisfactory and, as mentioned above, I find
Appendix B a nice addition to the paper.

### 2017-11-14 kbhssh_disks/paper.tex
new paper added

\documentclass{aa}  
\usepackage{graphicx}
\usepackage{txfonts}
\usepackage{hyperref}
\usepackage{color}
\usepackage{float}

\begin{document}

   \title{Magnetized accretion disks around Kerr black holes with scalar hair}

%   \subtitle{}

\author{Sergio Gimeno-Soler\inst{1}, Jos\'e A.~Font\inst{1,2}, Carlos Herdeiro \inst{3}, Eugen Radu\inst{3}}
\institute{Departamento de Astronom\'{\i}a y Astrof\'{\i}sica, Universitat de Val\`encia, Dr. Moliner 50, 46100, Burjassot (Val\`encia), Spain.\\\email{sergio.gimeno@uv.es}
\and
Observatori Astron\`omic, Universitat de Val\`encia, C/ Catedr\'atico Jos\'e Beltr\'an 2, 46980, Paterna (Val\`encia), Spain. \\
\email{j.antonio.font@uv.es}
\and
Departamento de F\'isica da Universidade de Aveiro and Centre for Research and Development in Mathematics and Applications (CIDMA), Campus de Santiago, 3810-183 Aveiro, Portugal
}

% \abstract{}{}{}{}{} 
% 5 {} token are mandatory

  \date{}

  \abstract
  {We present a method to build magnetized constant angular momentum disks around Kerr black holes with scalar hair (KBHsSH).}

   \keywords{black hole physics
               }

   \maketitle
%
%-------------------------------------------------------------------

\section{Introduction}

% Outline:

% Brief description of the work of Herdeiro, recall what we use here and proceed to describe what we have done.
% First, describe framework. Metric, energy-momentum tensor, and equations of motion. Second, angular momentum distribution (including the angular momentum at $r_{\mathrm{mb}}$) and EoS. Third, results: Higher potential well than any possible Kerr-like solution with $r_{\mathrm{in}} = r_{\mathrm{mb}}$. We should graph here the potential well $\Delta W$ vs. the normalized spin parameter $a$ for the KBH case. Maybe get the data for intermediate values of magnetization? I think it is important to have more data of HBH, to test some ideas. Comparison with naked singularities? I would like to obtain the rest-mass and gravitational mass of the total distribution (torus + scalar field).

% Comparison of the structure of the disks obtained for the case of KBHsSH with KBH and Naked Singularities (NS). $\Delta W$, angular velocity, angular momentum, mass of the torus and physical magnitudes (thermodynamical)

% Paint same curves (if possible) as in the case of the previous paper for magnetized toris around KBHs, check differences between the cases. For KBHs with full-relativistic fluid and HBHs.

% Check relations between ergoregions in KBHs and NSs spacetimes and KBHsSH case (morphology?)
% The most important conclusion is we obtain very different disk configurations for HBHs and for KBHs (with the same ADM or Horizon quantities), therefore we can asymptotically distinguish a disk around a KBHsSH from a disk around a KBH. (potential well and so on).

%--------------------------------------------------------------------
\section{Framework}

We use the stationary and axisymmetric metric ansatz provided by\citet{Herdeiro:2014a}

\begin{equation}
\mathrm{d}s^2 = e^{2F_1}\left(\frac{\mathrm{d}r^2}{N} + r^2\mathrm{d}\theta^2\right) + e^{2F_2}r^2\sin^2 \theta(\mathrm{d}\phi-W\mathrm{d}t)^2-e^{2F_0}N\mathrm{d}t^2,
\end{equation}

with $N = 1 - r_H/r$, where $r_H$ is the radius of the event horizon of the BH and $W$, $F_1$, $F_2$, $F_0$ are functions of $r$ and $\theta$.

\begin{figure*}
\centering
\includegraphics[scale=0.14]{figures/fig1_III_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig1_III_0.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig1_III__3.pdf}
\\
\includegraphics[scale=0.14]{figures/fig1_IV_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig1_IV_0.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig1_IV__3.pdf}
\\
\includegraphics[scale=0.14]{figures/fig1_V_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig1_V_0.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig1_V__3.pdf}
\caption{Rest-mass density distribution. From top to bottom the rows correspond to the different models for the KBHsSH (I, II and III). From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$)}
\label{models}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.2]{figures/fig2_III_HBH_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig2_III_ADM_3.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.2]{figures/fig2_III_HBH_0.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig2_III_ADM_0.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.2]{figures/fig2_III_HBH__3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig2_III_ADM__3.pdf}
\hspace{-0.2cm}
\caption{Rest-mass density distribution for the model I. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model and the right column correspond to the corresponding KBH with the same ADM quantities.}
\label{comparison_mag_1}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.2]{figures/fig3_IV_HBH_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig3_IV_ADM_3.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.2]{figures/fig3_IV_HBH_0.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig3_IV_ADM_0.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.2]{figures/fig3_IV_HBH__3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig3_IV_ADM__3.pdf}
\hspace{-0.2cm}
\caption{Rest-mass density distribution for the model II. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model and the right column correspond to the corresponding KBH with the same ADM quantities.}
\label{comparison_mag_2}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.2]{figures/fig4_V_HBH_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig4_V_ADM_3.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.2]{figures/fig4_V_HBH_0.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig4_V_ADM_0.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.2]{figures/fig4_V_HBH__3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig4_V_ADM__3.pdf}
\hspace{-0.2cm}
\caption{Rest-mass density distribution for the model III. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model and the right column correspond to the corresponding KBH with the same ADM quantities.}
\label{comparison_mag_3}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.3]{figures/radial_III_HBH_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_III_ADM_3.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.3]{figures/radial_III_HBH_0.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_III_ADM_0.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.3]{figures/radial_III_HBH__3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_III_ADM__3.pdf}
\hspace{-0.2cm}
\caption{Radial rest-mass density distribution for the model I at the equatorial plane. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model and the right column correspond to the corresponding KBH with the same ADM quantities.}
\label{comparison_radial_1}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.3]{figures/radial_IV_HBH_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_IV_ADM_3.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.3]{figures/radial_IV_HBH_0.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_IV_ADM_0.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.3]{figures/radial_IV_HBH__3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_IV_ADM__3.pdf}
\hspace{-0.2cm}
\caption{Radial rest-mass density distribution for the model II at the equatorial plane. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model and the right column correspond to the corresponding KBH with the same ADM quantities.}
\label{comparison_radial_2}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.3]{figures/radial_V_HBH_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_V_ADM_3.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.3]{figures/radial_V_HBH_0.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_V_ADM_0.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.3]{figures/radial_V_HBH__3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_V_ADM__3.pdf}
\hspace{-0.2cm}
\caption{Radial rest-mass density distribution for the model III at the equatorial plane. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model and the right column correspond to the corresponding KBH with the same ADM quantities.}
\label{comparison_radial_3}
\end{figure*}

\subsection{Distribution of angular momentum and equations of motion}
We consider a constant angular momentum distribution $l(r,\theta) = \mathrm{cte}.$. The specific value of the angular momentum is computed as the minimum of the following equation
\begin{equation}
l^{\pm}_{\mathrm{b}}(r, \theta) = \frac{g_{t\phi}\pm\left(\sqrt{g_{t\phi}^2-g_{tt}g_{t\phi}}\right)\sqrt{1+g_{tt}}}{-g_{tt}}
\end{equation}
where the plus sign is for prograde orbits and the minus is for retrograde orbits.
This expression is given by~\citep{Daigne:2004} for Kerr BHs, but it is valid for any stationary, axisymmetric spacetimes. For prograde motion, the function has a minimum outside the event horizon. The location of said minimum corresponds with the marginally bound orbit $r_{\mathrm{mb}}$, and the angular momentum corresponds to the keplerian angular momentum at that point. This choice of angular momentum distributions is motivated by its simplicity (for a first study of thick tori around KBHsSH) and for allowing the presence of a cusp (this allows matter accretion onto the black hole) and a centre.

\subsection{Magnetized disks}
We use the procedure described by~\citet{Montero:2007}, where we write the equations of ideal general relativistic MHD are the following conservation laws, $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and 
$\nabla_{\mu} (\rho u^{\mu}) = 0$, 
where $\nabla_{\mu}$ is the covariant derivative and
\begin{equation}\label{eq:e-m_tensor}
T^{\mu\nu} = (\rho h + b^2)u^{\mu}u^{\nu} + \left(p + \frac{1}{2}b^2\right)g^{\mu\nu} - b^{\mu}b^{\nu},
\end{equation}
is the energy-momentum tensor of a magnetised perfect fluid, $h$, $\rho$ $p$ being the fluid specific enthalpy, density and fluid pressure, respectively. 
Moreover, $^\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu}$ is the (dual of the) Faraday tensor relative to an observer with 
four-velocity $u^{\mu}$, and $b^{\mu}$ is the magnetic field in that frame, with
$b^2=b^{\mu}b_{\mu}$. Assuming the magnetic field is purely azimuthal, i.e.~$b^r = b^{\theta} = 0$,
and taking into account that the flow is stationary and axisymmetric, the conservation of the current density and of the Faraday tensor follow. Contracting the divergence of Eq.~\eqref{eq:e-m_tensor} with the projection tensor $h^{\alpha}_{\,\,\beta} = \delta^{\alpha}_{\,\,\beta} + u^{\alpha}u_{\beta}$, we arrive at
\begin{equation}
(\rho h + b^2)u_{\nu}\partial_i u^{\nu} + \partial_i\left(p + \frac{b^2}{2}\right) - b_{\nu}\partial_i b^{\nu}=0\,,
\end{equation}
where $i = r, \theta$. Then, we rewrite this equation in terms of the specific angular momentum $l$ and of the angular velocity $\Omega$, to obtain
\begin{equation}\label{eq:diff_ver}
\partial_i(\ln u_t|) - \frac{\Omega \partial_i l}{1-l\Omega} + \frac{\partial_i p}{w} + \frac{\partial_i(\mathcal{L}b^2)}{2\mathcal{L}w} = 0\,,
\end{equation}
where $\mathcal{L} = g_{t\phi}^2 - g_{tt}g_{\phi\phi}$.
To integrate Eq.~\eqref{eq:diff_ver} we first assume a polytropic equation of state of the form
\begin{equation}\label{eq:eos_fluid}
p = K \rho^{\Gamma},
\end{equation}
with $K$ and $\Gamma$ constants.
Then, we define the magnetic pressure as $p_{\mathrm{m}} = b^2/2$, and introduce the definitions $\tilde{p}_{\mathrm{m}} = \mathcal{L} p_{\mathrm{m}}$ and $\tilde{w} = \mathcal{L} w$, in order to write an analogue equation to Eq.~\eqref{eq:eos_fluid} for $\tilde{p}_{\mathrm{m}}$~\citep{Komissarov:2006}
\begin{equation}\label{eq:eos_mag_tilde}
\tilde{p}_{\mathrm{m}} = M \tilde{w}^q,
\end{equation}
or, in terms of the magnetic pressure $p_{\mathrm{m}}$
\begin{equation}\label{eq:eos_mag}
p_{\mathrm{m}} = M \mathcal{L}^{q-1} w^q,
\end{equation}
where $w = \rho h$ is the fluid enthaply density, and $M$ and $q$ are constants.
If we define the potential as $W \equiv \ln u_t|$, then we can integrate the equation~\eqref{eq:diff_ver} as

\begin{equation}\label{eq:final}
W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho^{\gamma -1}\right) + \frac{q}{q-1}M(\mathcal{L}w)^{q-1}=0,
\end{equation}
where $W_{\mathrm{in}}$ is the potential at the inner edfe of the disk.

In this work, we use $q = \Gamma = 4/3$, the density at the disk centre $\rho_{\mathrm{c}} = 1$ and the angular momentum distribution gives us $W_{\mathrm{in}} = 0$. With this information we can compute all the relevant physical quantities.

It is relevant to note that we could have used the framework described by~\citet{Komissarov:2006}. As we will show in appendix~\ref{komissarov_appendix}, we do not take this approach because it is not appropriate for some cases of KBHsSH.

%--------------------------------------------------------------------
\section{Method}

\subsection{Building the disk}

\subsection{Numerical method}

%--------------------------------------------------------------------
\section{Results}

\begin{table}
\caption{List of models of KBHsSH.}             
\label{table:1}      
\centering          
\begin{tabular}{c c c c  c c c c}
\hline\hline       
 & $M_{\mathrm{ADM}}$ & $J_{\mathrm{ADM}}$ & $M_{\mathrm{H}}$ &  $J_{\mathrm{H}}$ & $M_{\mathrm{SF}}$ & $J_{\mathrm{SF}}$ & $r_{\mathrm{H}}$ \\ 
\hline           
I & $0.415$ & $0.172$ & $0.393$ &  $0.15$  & $0.022$ & $0.022$ & $0.2$\\ 
 \hline 
II & $0.933$ & $0.739$ & $0.234$ &  $0.114$  & $0.699$ & $0.625$ & $0.1$ \\
 \hline 
III & $0.975$ & $0.85$ & $0.018$ &  $0.002$  & $0.957$ & $0.848$ & $0.04$ \\ 
\hline      
\end{tabular}
\end{table}

It is easy to note the differences between the cases with scalar hair and their KBH counterparts, specially the disk size, shape and physical magnitudes.

%--------------------------------------------------------------------
\section{Conclusions}
Our results show significant differences between KBHsSH and their counterpart KBH with the same ADM quantities and we think it its worth to expand thses results with more KBHsSH cases.

\begin{acknowledgements}

\end{acknowledgements}

\bibliographystyle{bibtex/aa}
\bibliography{references}

\begin{appendix}
\section{KBHsSH vs $h = 1$ approximation}\label{komissarov_appendix}

In the figures \ref{comparison_alt_mag_1}, \ref{comparison_alt_mag_2}, \ref{comparison_alt_mag_3}, \ref{comparison_alt_radial_1}, \ref{comparison_alt_radial_2}, \ref{comparison_alt_radial_3} we show the comparison between the results for KBHsSH using \citet{Montero:2007} and \citet{Komissarov:2006}. The figures show good agreement for the highly magnetized case ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$) but not quite for the non-magnetized and mildly magnetized cases, especially for the model III. This is due to the $h = 1$ approximation breaking down. In the table~\ref{table:pot} we show the correlation between the value of the potential at the centre and the specific enthalpy at the centre. It is easy to note that for higher absolute values of $W_{\mathrm{c}}$ we get values of $h_{\mathrm{c}}$ further away from the case $h = 1$. This is interesting because these high values of $W_{\mathrm{c}}$ (particularly the one for the model III) is unattaniable for any KBH (as is shown by~\citet{Abramowicz:1978}, the maximum value of $W_{\mathrm{c}}$ for a KBH is $W_{\mathrm{c}} = 0.549$).

\begin{table}
\caption{Potential at the center $W_{\mathrm{c}}$ and specific enthalpy at the center $h_{\mathrm{c}}$ for the non-magnetized case for the three models.}             
\label{table:pot}      
\centering          
\begin{tabular}{c c c c c}
\hline\hline       
 &  & I & II & III\\ 
\hline           
 &$W_{\mathrm{c}}$ & $-0.188$ & $-0.547$ & $-1.236$\\ 
\hline
 &$h_{\mathrm{c}}$ & $1.21$ & $1.73$ & $3.44$\\ 
\hline      
\end{tabular}
\end{table}

\begin{figure*}
\centering
\includegraphics[scale=0.2]{figures/fig2_III_HBH_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig2_III_K_3.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.2]{figures/fig2_III_HBH_0.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig2_III_K_0.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.2]{figures/fig2_III_HBH__3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig2_III_K__3.pdf}
\hspace{-0.2cm}
\caption{Rest-mass density distribution for the model I. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model using~\citet{Montero:2007} and the right column correspond to the~\citet{Komissarov:2006} approximation.}
\label{comparison_alt_mag_1}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.2]{figures/fig3_IV_HBH_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig3_IV_K_3.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.2]{figures/fig3_IV_HBH_0.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig3_IV_K_0.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.2]{figures/fig3_IV_HBH__3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig3_IV_K__3.pdf}
\hspace{-0.2cm}
\caption{Rest-mass density distribution for the model II. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model using~\citet{Montero:2007} and the right column correspond to the~\citet{Komissarov:2006} approximation.}
\label{comparison_alt_mag_2}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.2]{figures/fig4_V_HBH_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig4_V_K_3.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.2]{figures/fig4_V_HBH_0.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig4_V_K_0.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.2]{figures/fig4_V_HBH__3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig4_V_K__3.pdf}
\hspace{-0.2cm}
\caption{Rest-mass density distribution for the model III. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model using~\citet{Montero:2007} and the right column correspond to the~\citet{Komissarov:2006} approximation.}
\label{comparison_alt_mag_3}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.3]{figures/radial_III_HBH_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_III_K_3.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.3]{figures/radial_III_HBH_0.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_III_K_0.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.3]{figures/radial_III_HBH__3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_III_K__3.pdf}
\hspace{-0.2cm}
\caption{Radial rest-mass density distribution for the model I at the equatorial plane. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model using~\citet{Montero:2007} and the right column correspond to the~\citet{Komissarov:2006} approximation.}
\label{comparison_alt_radial_1}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.3]{figures/radial_IV_HBH_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_IV_K_3.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.3]{figures/radial_IV_HBH_0.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_IV_K_0.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.3]{figures/radial_IV_HBH__3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_IV_K__3.pdf}
\hspace{-0.2cm}
\caption{Radial rest-mass density distribution for the model II at the equatorial plane. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model using~\citet{Montero:2007} and the right column correspond to the~\citet{Komissarov:2006} approximation.}
\label{comparison_alt_radial_2}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.3]{figures/radial_V_HBH_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_V_K_3.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.3]{figures/radial_V_HBH_0.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_V_K_0.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.3]{figures/radial_V_HBH__3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_V_K__3.pdf}
\hspace{-0.2cm}
\caption{Radial rest-mass density distribution for the model III at the equatorial plane. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model using~\citet{Montero:2007} and the right column correspond to the~\citet{Komissarov:2006} approximation.}
\label{comparison_alt_radial_3}
\end{figure*}
\end{appendix}

\end{document}

### 2017-11-14 magnetised_polish_doughnuts_revisited/paper_lang_rev/paper_lang_rev.tex
new paper added

--- 2017-07-15 paper_lang_rev/paper_lang_rev.tex
@@
 
-To construct our models of magnetised discs we follow the approach described in \citet{Qian:2009}.
+To construct our models of magnetised discs we \sg{have followed} the approach described in \citet{Qian:2009}.
 First, we find the radial location of the cusp and of the centre of the disc in the equatorial plane, $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$, defined as the solutions to the equation $l(r) - l_{\mathrm{K}} = 0$.
@@
 the specific internal energy. From a thermodynamical point of view a non-relativistic fluid satisfies $h=1$. Therefore,
-since we use poytropic equations of state (relating $p$ with either $w$ or $\rho$ in the same functional form) we are
+since we use \sg{polytropic} equations of state (relating $p$ with either $w$ or $\rho$ in the same functional form) we are
 implicitly assuming that $h=1$, \sg{that is,} the discs we build in our procedure are non-relativistic from a thermodynamical point of view.
 
-For the integration of Eq.~\eqref{eq:equatorial_pot} we use the composite Simpson's rule.
+For the integration of Eq.~\eqref{eq:equatorial_pot} we \sg{have used} the composite Simpson's rule.
 It is important to use a very small integration step because the slope is very steep.
-In this work, we use a step $\Delta r = 10^{-6}$.
+In this work, we \sg{have used} a step $\Delta r = 10^{-6}$.
 Using the analytic, constant angular momentum case for comparison, we tested that
 a larger value of $\Delta r$ gives unacceptable accuracy losses.
-On the other hand, to integrate the ordinary differential equation \eqref{eq:F} we use a fourth-order Runge-Kutta method.
+On the other hand, to integrate the ordinary differential equation \eqref{eq:F} we \sg{have employed} a fourth-order Runge-Kutta method.
 Again, it is also important here to choose a suitable step of integration, especially at the outer end of the disc, because Eq.~\eqref{eq:F} diverges at the equatorial plane (the equipotential surfaces cross the equatorial plane perpendicularly).
@@
 
-To reduce the number of free parameters to build the initial models we do as in~\citet{Komissarov:2006} and fix the values of the equation of state exponents, $\kappa$ and $\lambda$, and of the enthalpy density at the disc centre, $w_{\mathrm{c}}$.
-More precisely, we choose $\kappa = \lambda = 4/3$ and $w_{\mathrm{c}} = 1$.
+To reduce the number of free parameters to build the initial models we \sg{have done} as in~\citet{Komissarov:2006} and \sg{have fixed} the values of the equation of state exponents, $\kappa$ and $\lambda$, and of the enthalpy density at the disc centre, $w_{\mathrm{c}}$.
+More precisely, we \sg{have chosen} $\kappa = \lambda = 4/3$ and $w_{\mathrm{c}} = 1$.
 This still leaves us with five parameters to control the size, shape, thickness, and magnetisation of the disc, namely the magnetisation parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$, the parameters of the angular momentum distribution $\beta$ and $\gamma$, the black hole spin parameter $a$, and the inner radius of the disc $r_{\mathrm{in}}$.
-We build a series of 45 models, whose main features are summarised in Table~\ref{table:1} (for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$, i.e.~models where the effects of the magnetisation are unimportant), Table~\ref{table:2} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$, i.e.~equipartition models), and Table~\ref{table:3} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$, i.e.~highly-magnetised models).
+We \sg{have built} a series of 45 models, whose main features are summarised in Table~\ref{table:1} (for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$, \sg{that is,} models where the effects of the magnetisation are unimportant), Table~\ref{table:2} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$, \sg{that is,} equipartition models), and Table~\ref{table:3} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$, \sg{that is,} highly-magnetised models).
 We note that we can build models with very small values of $\beta_{\mathrm{m}_{\mathrm{c}}}$, such as \sg{for example} $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-20}$ (extremely high magnetisation) without encountering numerical difficulties.
 No qualitative differences in the structure of the discs are found once $\beta_{\mathrm{m}_{\mathrm{c}}}$ becomes smaller than a sufficiently small value, about $\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$.
-This is the reason why we choose that particular value as our lower limit in the figures and tables of the manuscript.
+This is the reason why we \sg{have chosen} that particular value as our lower limit in the figures and tables of the manuscript.
 
@@
 We plot, in particular, the models of Table~\ref{table:3}, for which the magnetisation is highest ($\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$).
-From left to right the columns of this figure correspond to increasing values of the black hole spin, namely, $a=0.5$, 0.9 and 0.99, while from top to bottom the rows correspond to different combinations of the $\gamma$ and $\beta$ parameters that \sg{characterise} the ansatz for the angular momentum distribution of~\citet{Qian:2009} (the particular values are indicated in the caption of the figure).
+From left to right the columns of this figure correspond to increasing values of the black hole spin, namely, $a=0.5$, 0.9 and 0.99, while from top to bottom the rows correspond to different combinations of the $\gamma$ and $\beta$ parameters that \sg{characterise} the ansatz for the angular momentum distribution of~\citet{Qian:2009} (the particular values are indicated in the caption \sg{and legends} of the figure).
 A rapid inspection shows that the structure of the discs noticeable changes when the parameters change.
@@
 
-Figure~\ref{magnetisation} shows the effects of changing the parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$ (the magnetisation) in the structure of the discs.
+\sg{Fig.}~\ref{magnetisation} shows the effects of changing the parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$ (the magnetisation) in the structure of the discs.
 From left to right the values plotted in each panel are $\beta_{\mathrm{m}_{\mathrm{c}}}=10^3$, 1, and $10^{-3}$.
@@
 The line type used indicates the value of the black hole spin $a$, namely, a dotted line is for $a=0.5$, a dashed line for $a=0.9$, and a solid line for $a=0.99$.
-Correspondingly, the colour of the lines indicates the value of $\beta$ and $\gamma$ used, namely, red curves correspond to $\gamma=\beta=0$, the blue ones to $\gamma=\beta=0.5$, and the black ones to $\gamma=\beta=0.9$ \bf{Seg\'un lo que han dicho arriba, todo esto deber\'ia ser borrado.}}.
+Correspondingly, the colour of the lines indicates the value of $\beta$ and $\gamma$ used, namely, red curves correspond to $\gamma=\beta=0$, the blue ones to $\gamma=\beta=0.5$, and the black ones to $\gamma=\beta=0.9$}.
 All curves show the same monotonically decreasing trend with $\beta_{\mathrm{m}_{\mathrm{c}}}$, yet for small enough and large enough values of $\beta_{\mathrm{m}_{\mathrm{c}}} $ the value of the rest-mass density maximum does not change.

### 2017-11-14 magnetised_polish_doughnuts_revisited/paper_lang_rev/to_send.tex
new paper added

--- 2017-07-12 paper_accepted/paper_accepted.tex
@@
 
-The investigation of this type of systems, either by analytical or numerical means, may rely on the ability to construct suitable 
+Investigation of such systems, either by analytical or numerical means, may rely on the ability to construct suitable 
 representations based on physical assumptions.
 The construction of equilibrium models of stationary discs around black holes has indeed a long tradition (see~\cite{Abramowicz:2013} and references therein).
-In particular, the so-called ``Polish doughnuts"~\citep{Abramowicz:1978,Kozlowski:1978} provide a  very general method to build equilibrium configurations of perfect fluid matter orbiting around a Kerr black hole.
+In particular, the `Polish doughnuts'~\citep{Abramowicz:1978,Kozlowski:1978} provide a  very general method to build equilibrium configurations of perfect fluid matter orbiting around a Kerr black hole.
 This fully relativistic model assumes that the disc is non-magnetised and that the matter obeys a  constant specific angular momentum distribution.
 This method was later extended by~\cite{Komissarov:2006}  by adding a purely azimuthal magnetic field to build magnetised tori around rotating black holes.
-Dynamical evolutions of magnetized tori built with the Komissarov solution were first reported by~\cite{Montero:2007}.
+Dynamical evolutions of magnetised tori built with the Komissarov solution were first reported by~\cite{Montero:2007}.
 On the other hand, assuming different distributions of angular momentum in the discs, \citet{Qian:2009} presented a method to build sequences of black hole thick accretion discs in dynamical equilibria, restricted however to the purely hydrodynamical case.
 
- In this paper we combine the two approaches considered in~\cite{Komissarov:2006} and~\citet{Qian:2009} to build new sequences of equilibrium tori around Kerr black holes.
+ In this paper we have combined the two approaches considered in~\cite{Komissarov:2006} and~\citet{Qian:2009} to build new sequences of equilibrium tori around Kerr black holes.
 Building on these works, we present here the extension of the models of~\citet{Qian:2009} to account for discs endowed with a purely toroidal magnetic field.
-In our procedure we hence assume a form of the angular momentum distribution that departs from the constant case considered by~\cite{Komissarov:2006} and from which the location and morphology of the equipotential surfaces can be numerically computed.
+In our procedure we hence assumed a form of the angular momentum distribution that departs from the constant case considered by~\cite{Komissarov:2006} and from which the location and morphology of the equipotential surfaces can be numerically computed.
 As we shall show below, for the particular case of constant angular momentum distributions, our method is in good agreement with the results of~\citet{Komissarov:2006}.
@@
 four-velocity $u^{\mu}$, and $b^{\mu}$ is the magnetic field in that frame, with
-$b^2=b^{\mu}b_{\mu}$. Assuming the magnetic field is purely azimuthal, i.e.~$b^r = b^{\theta} = 0$,
+$b^2=b^{\mu}b_{\mu}$. Assuming the magnetic field is purely azimuthal, that is $b^r = b^{\theta} = 0$,
 and taking into account that the flow is stationary and axisymmetric, the conservation of the current density and of the Faraday tensor follow.
@@
 
-To construct our models of magnetised discs we follow the approach described in \citet{Qian:2009}.
+To construct our models of magnetised discs we have followed the approach described in \citet{Qian:2009}.
 First, we find the radial location of the cusp and of the centre of the disc in the equatorial plane, $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$, defined as the solutions to the equation $l(r) - l_{\mathrm{K}} = 0$.
@@
 \centering
-\includegraphics[scale=0.14]{figures/fig1a.pdf}
+\includegraphics[scale=0.14]{fig1a.pdf}
 \hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig1b.pdf}
+\includegraphics[scale=0.14]{fig1b.pdf}
 \hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig1c.pdf}
+\includegraphics[scale=0.14]{fig1c.pdf}
 \caption{Comparison with Komissarov's solution for a constant angular momentum model.
@@
 the specific internal energy. From a thermodynamical point of view a non-relativistic fluid satisfies $h=1$. Therefore,
-since we use poytropic equations of state (relating $p$ with either $w$ or $\rho$ in the same functional form) we are
-implicitly assuming that $h=1$, i.e.~the discs we build in our procedure are non-relativistic from a thermodynamical point of view.
+since we use polytropic equations of state (relating $p$ with either $w$ or $\rho$ in the same functional form) we are
+implicitly assuming that $h=1$, that is, the discs we build in our procedure are non-relativistic from a thermodynamical point of view.
 
-For the integration of Eq.~\eqref{eq:equatorial_pot} we use the composite Simpson's rule.
+For the integration of Eq.~\eqref{eq:equatorial_pot} we have used the composite Simpson's rule.
 It is important to use a very small integration step because the slope is very steep.
-In this work, we use a step $\Delta r = 10^{-6}$.
+In this work, we have used a step $\Delta r = 10^{-6}$.
 Using the analytic, constant angular momentum case for comparison, we tested that
 a larger value of $\Delta r$ gives unacceptable accuracy losses.
-On the other hand, to integrate the ordinary differential equation \eqref{eq:F} we use a fourth-order Runge-Kutta method.
+On the other hand, to integrate the ordinary differential equation \eqref{eq:F} we have employed a fourth-order Runge-Kutta method.
 Again, it is also important here to choose a suitable step of integration, especially at the outer end of the disc, because Eq.~\eqref{eq:F} diverges at the equatorial plane (the equipotential surfaces cross the equatorial plane perpendicularly).
@@
 
-To reduce the number of free parameters to build the initial models we do as in~\citet{Komissarov:2006} and fix the values of the equation of state exponents, $\kappa$ and $\lambda$, and of the enthalpy density at the disc centre, $w_{\mathrm{c}}$.
-More precisely, we choose $\kappa = \lambda = 4/3$ and $w_{\mathrm{c}} = 1$.
+To reduce the number of free parameters to build the initial models we have done as in~\citet{Komissarov:2006} and have fixed the values of the equation of state exponents, $\kappa$ and $\lambda$, and of the enthalpy density at the disc centre, $w_{\mathrm{c}}$.
+More precisely, we have chosen $\kappa = \lambda = 4/3$ and $w_{\mathrm{c}} = 1$.
 This still leaves us with five parameters to control the size, shape, thickness, and magnetisation of the disc, namely the magnetisation parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$, the parameters of the angular momentum distribution $\beta$ and $\gamma$, the black hole spin parameter $a$, and the inner radius of the disc $r_{\mathrm{in}}$.
-We build a series of 45 models, whose main features are summarised in Table~\ref{table:1} (for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$, i.e.~models where the effects of the magnetisation are unimportant), Table~\ref{table:2} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$, i.e.~equipartition models), and Table~\ref{table:3} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$, i.e.~highly-magnetised models).
-We note that we can build models with very small values of $\beta_{\mathrm{m}_{\mathrm{c}}}$, such as  e.g.~$\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-20}$ (extremely high magnetisation) without encountering numerical difficulties.
+We have built a series of 45 models, whose main features are summarised in Table~\ref{table:1} (for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$, that is, models where the effects of the magnetisation are unimportant), Table~\ref{table:2} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$, that is, equipartition models), and Table~\ref{table:3} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$, that is, highly-magnetised models).
+We note that we can build models with very small values of $\beta_{\mathrm{m}_{\mathrm{c}}}$, such as for example $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-20}$ (extremely high magnetisation) without encountering numerical difficulties.
 No qualitative differences in the structure of the discs are found once $\beta_{\mathrm{m}_{\mathrm{c}}}$ becomes smaller than a sufficiently small value, about $\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$.
-This is the reason why we choose that particular value as our lower limit in the figures and tables of the manuscript.
+This is the reason why we have chosen that particular value as our lower limit in the figures and tables of the manuscript.
 
@@
 \centering
-\includegraphics[scale=0.14]{figures/fig2_1_1.pdf}
+\includegraphics[scale=0.14]{fig2_1_1.pdf}
 \hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig2_1_2.pdf}
+\includegraphics[scale=0.14]{fig2_1_2.pdf}
 \hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig2_1_3.pdf}
+\includegraphics[scale=0.14]{fig2_1_3.pdf}
 \\
-\includegraphics[scale=0.14]{figures/fig2_2_1.pdf}
+\includegraphics[scale=0.14]{fig2_2_1.pdf}
 \hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig2_2_2.pdf}
+\includegraphics[scale=0.14]{fig2_2_2.pdf}
 \hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig2_2_3.pdf}
+\includegraphics[scale=0.14]{fig2_2_3.pdf}
 \\
-\includegraphics[scale=0.14]{figures/fig2_3_1.pdf}
+\includegraphics[scale=0.14]{fig2_3_1.pdf}
 \hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig2_3_2.pdf}
+\includegraphics[scale=0.14]{fig2_3_2.pdf}
 \hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig2_3_3.pdf}
+\includegraphics[scale=0.14]{fig2_3_3.pdf}
 \\
-\includegraphics[scale=0.14]{figures/fig2_4_1.pdf}
+\includegraphics[scale=0.14]{fig2_4_1.pdf}
 \hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig2_4_2.pdf}
+\includegraphics[scale=0.14]{fig2_4_2.pdf}
 \hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig2_4_3.pdf}
+\includegraphics[scale=0.14]{fig2_4_3.pdf}
 \\
-\includegraphics[scale=0.14]{figures/fig2_5_1.pdf}
+\includegraphics[scale=0.14]{fig2_5_1.pdf}
 \hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig2_5_2.pdf}
+\includegraphics[scale=0.14]{fig2_5_2.pdf}
 \hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig2_5_3.pdf}
+\includegraphics[scale=0.14]{fig2_5_3.pdf}
 \caption{Isodensity distributions for all models of Table~\ref{table:3}.
@@
 \centering
-\includegraphics[scale=0.14]{figures/fig3a.pdf}
+\includegraphics[scale=0.14]{fig3a.pdf}
 \hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig3b.pdf}
+\includegraphics[scale=0.14]{fig3b.pdf}
 \hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig3c.pdf}
+\includegraphics[scale=0.14]{fig3c.pdf}
 \caption{Effects of the magnetisation in the structure of the disc. From left to right the values are $\beta_{\mathrm{m}_{\mathrm{c}}}
@@
 
-A representative sample of the isodensity surfaces for some of our models appears in Figure~\ref{models}.
+A representative sample of the isodensity surfaces for some of our models appears in Fig.~\ref{models}.
 We plot, in particular, the models of Table~\ref{table:3}, for which the magnetisation is highest ($\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$).
-From left to right the columns of this figure correspond to increasing values of the black hole spin, namely, $a=0.5$, 0.9 and 0.99, while from top to bottom the rows correspond to different combinations of the $\gamma$ and $\beta$ parameters that characterize the ansatz for the angular momentum distribution of~\citet{Qian:2009} (the particular values are indicated in the caption of the figure).
+From left to right the columns of this figure correspond to increasing values of the black hole spin, namely, $a=0.5$, 0.9 and 0.99, while from top to bottom the rows correspond to different combinations of the $\gamma$ and $\beta$ parameters that characterise the ansatz for the angular momentum distribution of~\citet{Qian:2009} (the particular values are indicated in the caption and legends of the figure).
 A rapid inspection shows that the structure of the discs noticeable changes when the parameters change.
@@
 \centering
-\includegraphics[scale=0.2]{figures/fig4.pdf}
+\includegraphics[scale=0.2]{fig4.pdf}
 \caption{Radial profiles of the rest-mass density in the equatorial plane for {$\beta_{\mathrm{m}_{\mathrm{c}}}=10^3$} (black curve), 1 (blue curve), and $10^{-3}$ (green curve). }
@@
 \centering
-\includegraphics[scale=0.2]{figures/fig5.pdf}
+\includegraphics[scale=0.2]{fig5.pdf}
 \caption{Radial profiles at the equatorial plane for models with $a=0.9$, $\beta_{\mathrm{m}_{\mathrm{c}}}
@@
 \centering
-\includegraphics[scale=0.14]{figures/fig6a.pdf}
+\includegraphics[scale=0.14]{fig6a.pdf}
 \hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig6b.pdf}
+\includegraphics[scale=0.14]{fig6b.pdf}
 \hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig6c.pdf}
+\includegraphics[scale=0.14]{fig6c.pdf}
 \caption{Effects of $\beta_{\mathrm{m}_{\mathrm{c}}}$.
@@
 
-Figure~\ref{magnetisation} shows the effects of changing the parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$ (the magnetisation) in the structure of the discs.
+Fig.~\ref{magnetisation} shows the effects of changing the parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$ (the magnetisation) in the structure of the discs.
 From left to right the values plotted in each panel are $\beta_{\mathrm{m}_{\mathrm{c}}}=10^3$, 1, and $10^{-3}$.
@@
 The larger the value of $\beta_{\mathrm{m}_{\mathrm{c}}}$ the less important the effects of the magnetisation in the disc structure.
-Figure~\ref{magnetisation} shows that, at least for the kind of magnetic field distribution we are considering, the effects of the magnetisation are minor.
+Fig.~\ref{magnetisation} shows that, at least for the kind of magnetic field distribution we are considering, the effects of the magnetisation are minor.
 The disc structure remains fairly similar for all values of $\beta_{\mathrm{m}_{\mathrm{c}}}
 $ and the only quantitative differences are found in the location of the centre of the disc (which moves inward with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$) and of the range of variation of the isodensity contours (the maximum being slightly larger with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$).
-This can be more clearly visualized in Figure~\ref{magnetisation-profile} which displays the radial profile at the equatorial plane of the rest-mass density for the same three cases plotted in Fig.~\ref{magnetisation}.
+This can be more clearly visualised in Fig.~\ref{magnetisation-profile} which displays the radial profile at the equatorial plane of the rest-mass density for the same three cases plotted in Fig.~\ref{magnetisation}.
 
@@
 It is worth noticing that the radial profiles of some of the models overlap below a certain radius.
-More precisely, the black and red curves overlap below $r\sim r_{\mathrm{c}}$ (which corresponds to $\rho \sim 1$) and also the green and orange curves.
+More precisely, the models with equal $\beta$ overlap below $r\sim r_{\mathrm{c}}$ (which corresponds to $\rho \sim 1$).
 In addition, this figure clearly shows that, besides modifying the thickness of the disc, $\beta$ is the parameter which determines the value of the rest-mass density (and pressure) maximum.
@@
 Let us first consider the left panel.
-The line type used indicates the value of the black hole spin $a$, namely, a dotted line is for $a=0.5$, a dashed line for $a=0.9$, and a solid line for $a=0.99$.
-Correspondingly, the colour of the lines indicates the value of $\beta$ and $\gamma$ used, namely, red curves correspond to $\gamma=\beta=0$, the blue ones to $\gamma=\beta=0.5$, and the black ones to $\gamma=\beta=0.9$.
 All curves show the same monotonically decreasing trend with $\beta_{\mathrm{m}_{\mathrm{c}}}$, yet for small enough and large enough values of $\beta_{\mathrm{m}_{\mathrm{c}}} $ the value of the rest-mass density maximum does not change.
@@
 
-\bibliographystyle{bibtex/aa}
+\bibliographystyle{aa}
 \bibliography{references}

### 2017-11-14 magnetised_polish_doughnuts_revisited/paper_revised/beta_gamma_output.tex
new paper added

--- 2017-11-14 magnetised_polish_doughnuts_revisited/paper_lang_rev/to_send.tex
@@
 
-\title{Magnetised Polish doughnuts revisited}
+\title{beta and gamma output}
 
-\author{Sergio Gimeno-Soler\inst{1}   \and Jos\'e A.~Font\inst{1,2} }
+\author{Sergio Gimeno-Soler\inst{1}}
 \institute{Departamento de Astronom\'{\i}a y Astrof\'{\i}sica, Universitat de Val\`encia, Dr. Moliner 50, 46100, Burjassot (Val\`encia), Spain.\\\email{sergio.gimeno@uv.es}
-\and
-Observatori Astron\`omic, Universitat de Val\`encia, C/ Catedr\'atico Jos\'e Beltr\'an 2, 46980, Paterna (Val\`encia), Spain. \\
-\email{j.antonio.font@uv.es}
 }
@@
   \abstract
-{We discuss a procedure to build new sequences of magnetised, equilibrium tori around Kerr black holes which combines two approaches previously considered in the literature.
-For simplicity we have assumed that the test-fluid approximation holds, and hence we neglected the self-gravity of the fluid.
-The models were built assuming a particular form of the angular momentum distribution from which the location and morphology of equipotential surfaces can be computed.
-This ansatz includes, in particular, the  constant angular momentum case originally employed in the construction of thick tori -- or Polish doughnuts -- and it has already been used to build equilibrium sequences of purely hydrodynamical models.
-We discuss the properties of the new models and their dependence on the initial parameters.
-These new sequences can be used as initial data for magnetohydrodynamical evolutions in general relativity.}
+{Document to capture value of $\beta$ and $\gamma$ for the graphs}
 
@@
 \section{Introduction}
-%%%%%%%%%%%
 
-Matter accretion on to black holes is the most efficient form of energy production known in nature. The conversion of the
-gravitational energy of the infalling matter into heat and radiation may reach efficiencies of about 43\% in the case of maximally rotating (Kerr) black holes.
-For this reason, systems formed by a black hole surrounded by an accretion disc are deemed responsible for many of the most energetic astronomical phenomena observed in the cosmos.
-In particular, (geometrically) thick accretion discs (or tori) are believed to be present in quasars and other active galactic nuclei, some X-ray binaries and microquasars, as well as in the central engine of gamma-ray bursts.
-The latter are alluded to in connection with mergers of neutron star binaries and black hole neutron star binaries, as well as with the rotational collapse that ensues at the end of the life of some massive stars.
-As numerical simulations show, such events  often result in a black hole surrounded by a torus (see e.g.~\cite{Rezzolla:2010,Sekiguchi:2011,Faber:2012,Shibata:2011,Baiotti:2017}).
-
-Investigation of such systems, either by analytical or numerical means, may rely on the ability to construct suitable 
-representations based on physical assumptions.
-The construction of equilibrium models of stationary discs around black holes has indeed a long tradition (see~\cite{Abramowicz:2013} and references therein).
-In particular, the `Polish doughnuts'~\citep{Abramowicz:1978,Kozlowski:1978} provide a  very general method to build equilibrium configurations of perfect fluid matter orbiting around a Kerr black hole.
-This fully relativistic model assumes that the disc is non-magnetised and that the matter obeys a  constant specific angular momentum distribution.
-This method was later extended by~\cite{Komissarov:2006}  by adding a purely azimuthal magnetic field to build magnetised tori around rotating black holes.
-Dynamical evolutions of magnetised tori built with the Komissarov solution were first reported by~\cite{Montero:2007}.
-On the other hand, assuming different distributions of angular momentum in the discs, \citet{Qian:2009} presented a method to build sequences of black hole thick accretion discs in dynamical equilibria, restricted however to the purely hydrodynamical case.
-
- In this paper we have combined the two approaches considered in~\cite{Komissarov:2006} and~\citet{Qian:2009} to build new sequences of equilibrium tori around Kerr black holes.
-Building on these works, we present here the extension of the models of~\citet{Qian:2009} to account for discs endowed with a purely toroidal magnetic field.
-In our procedure we hence assumed a form of the angular momentum distribution that departs from the constant case considered by~\cite{Komissarov:2006} and from which the location and morphology of the equipotential surfaces can be numerically computed.
-As we shall show below, for the particular case of constant angular momentum distributions, our method is in good agreement with the results of~\citet{Komissarov:2006}.
-We also note the recent work of~\citet{Wielgus:2015} where Komissarov's solution was extended for the particular case of power-law distributions of angular momentum.
-Moreover, the magnetised tori of~\citet{Wielgus:2015} were used to explore the growth of the magneto-rotational instabilty (MRI) through time-dependent numerical simulations.
-In particular, the long-term evolution of those tori has been recently investigated by~\citet{Fragile:2017}, who paid special attention to the decay of their magnetisation.
-
-The organization of the paper is as follows: Sect.~\ref{framework} presents the analytic framework to build the discs while Sect.~\ref{methodology} explains the corresponding numerical procedure.
-The sequences of models are discussed in Sect.~\ref{results}.
-Finally, the conclusions are summarised in Sect.~\ref{conclusions}, where we also briefly indicate potential extensions of this work we plan to inspect.
-In our work we assume that the test-fluid approximation holds, thus neglecting the self-gravity of the fluid, and further assume that the spacetime is described by the Kerr metric.
-In mathematical expressions below Greek indices are spacetime indices running from 0 to 3 and Latin indices are only spatial.
-We use geometrised units where $G = c = 1$.
-
-%%%%%%%%%%%
-\section{Framework}
-\label{framework}
-%%%%%%%%%%%
-
-Equilibrium tori around Kerr black holes were built assuming that the spacetime gravitational potentials and the fluid fields are stationary and axisymmetric.
-In all the derivations presented below, the Kerr metric is implicitly written using standard Boyer-Lindquist coordinates.
-It is convenient to introduce a number of relevant characteristic radii, such as the radius
-of the marginally stable circular orbit, $r_{\rm ms}$, and the radius of the marginally bound circular orbit, $r_{\rm mb}$, given by
-\begin{eqnarray}
-r_{\rm ms} &=& M\,\left(3+Z_2-\left[(3-Z_1)(3+Z_1+2Z_2)\right]^{1/2})\right)\,,
-\\
-r_{\rm mb} &=& 2M\,\left(  1-\frac{a_*}{2} + \sqrt{1-a_*} \right)\,,
-\end{eqnarray}
-where we have defined the following quantities, $Z_1=1+(1-a_*^2)^{1/3}[(1+a_*)^{1/3}+(1-a_*)^{1/3}]$, $Z_2=(3a_*^2+Z_1^2)^{1/2}$, and $a_*=a/M$, with $a$ and $M$ being the spin Kerr parameter and the black hole mass, respectively.
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Distribution of angular momentum}
-%%%%%%%%%%%%%%%%%%%%%%%%
-
-We introduce the specific angular momentum $l$ and the angular velocity $\Omega$ employing the standard definitions,
 \begin{equation}
-l = - \frac{u_{\phi}}{u_t}, \;\;\; \Omega = \frac{u^{\phi}}{u^t},
+\beta = 0
 \end{equation}
-where $u^{\mu}$ is the fluid four-velocity.
-The relationship between $l$ and $\Omega$ is given by the equations
 \begin{equation}
-l = - \frac{\Omega g_{\phi\phi} + g_{t\phi}}{\Omega g_{t\phi} + g_{tt}}, \;\;\; \Omega = - \frac{l g_{tt} + g_{t\phi}}{l g_{t\phi} + g_{\phi\phi}},
+\gamma = 0
 \end{equation}
-where $g_{\mu\nu}$ is the metric tensor and we are assuming circular motion, that is, the four-velocity can be written as
-\begin{equation}
-u^{\mu} = (u^t, 0, 0, u^{\phi})\,.
-\end{equation}
-We also introduce the Keplerian angular momentum (for prograde motion) in the equatorial plane $l_{\mathrm{K}}$, defined as 
-\begin{equation}\label{eq:kepler}
-l_{\mathrm{K}}(r) = \frac{M^{1/2}(r^{2}-2aM^{1/2}r^{1/2}+a^{2})}{r^{3/2}-2Mr^{1/2}+aM^{1/2}}\,.
-\end{equation}
-
-\cite{Jaroszynski:1980} argued that the slope of the specific angular momentum should range between two limiting cases, namely $l = \mathrm{const.}$ and $\Omega = \mathrm{const}$.
-Following \citet{Qian:2009} we assume an angular momentum distribution ansatz given by
-\begin{equation}
-l (r,\theta) = \left\{ \label{eq:ansatz} 
-  \begin{array}{lr}
-    l_0 \left(\frac{l_{\mathrm{K}}(r)}{l_0}\right)^{\beta}\sin^{2\gamma}{\theta} &  \text{for } r \geq r_{\mathrm{ms}}\\
-    l_{\mathrm{ms}}(r)\sin^{2\gamma}{\theta} & \text{for } r < r_{\mathrm{ms}}
-  \end{array}
-\right.
-\end{equation}
-where constants $l_0$ and $l_{\mathrm{ms}}(r)$ are defined by $l_0 \equiv \eta l_{\mathrm{K}}(r_{\mathrm{ms}})$ and $l_{\mathrm{ms}}(r) \equiv l_0 [l_{\mathrm{K}}(r_{\mathrm{ms}})/l_0]^{\beta}$.
-Therefore, the model for the distribution of angular momentum has three free parameters, $\beta$ , $\gamma$ and $\eta$, whose range of variation is given by~\citep{Qian:2009}
-\begin{equation}
-0 \leq \beta \leq 1, \quad -1 \leq \gamma \leq 1, \quad 1 \leq \eta \leq \eta_{\mathrm{max}},
-\end{equation}
-with $\eta_{\mathrm{max}} = l_{\mathrm{K}}(r_{\mathrm{mb}})/l_{\mathrm{K}}(r_{\mathrm{ms}})$.
-In this paper, and as it is done for hydrodynamical discs in~\citet{Qian:2009}, we choose $\eta = \eta_{\mathrm{max}}$, and then we can write $l_0$ as $l_0 = l_{\mathrm{K}}(r_{\mathrm{mb}})$.
-For this choice of $\eta$, we can find the location of the cusp of the disc  within the range $r_{\mathrm{mb}} \leq r_{\mathrm{cusp}} \leq r_{\mathrm{ms}}$ (for $0 \leq \beta \leq 1$).
-The cusp is defined as the circle in the equatorial plane on which the pressure gradient vanishes and the angular momentum of the disc equals the Keplerian angular momentum.
-Moreover, this value of $\eta$ guarantees that constant angular momentum discs ($\beta = \gamma = 0$) with their inner edge located at the cusp ($r_{\mathrm{in}} = r_{\mathrm{cusp}}$) have no outer boundary, i.e~they are infinite discs (see also~\cite{Font:2002}).
-
-%%%%%%%%%%%%%%%%
-\subsection{Magnetised discs}
-%%%%%%%%%%%%%%%%
-
-The equations of ideal general relativistic MHD are the following conservation laws, $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and 
-$\nabla_{\mu} (\rho u^{\mu}) = 0$, 
-where $\nabla_{\mu}$ is the covariant derivative and
-\begin{equation}\label{eq:e-m_tensor}
-T^{\mu\nu} = (w + b^2)u^{\mu}u^{\nu} + \left(p + \frac{1}{2}b^2\right)g^{\mu\nu} - b^{\mu}b^{\nu},
-\end{equation}
-is the energy-momentum tensor of a magnetised perfect fluid, $w$ and $p$ being the fluid enthalpy density and fluid pressure, respectively. 
-Moreover, $^\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu}$ is the (dual of the) Faraday tensor relative to an observer with 
-four-velocity $u^{\mu}$, and $b^{\mu}$ is the magnetic field in that frame, with
-$b^2=b^{\mu}b_{\mu}$. Assuming the magnetic field is purely azimuthal, that is $b^r = b^{\theta} = 0$,
-and taking into account that the flow is stationary and axisymmetric, the conservation of the current density and of the Faraday tensor follow.
-Contracting Eq.~\eqref{eq:e-m_tensor} with the projection tensor $h^{\alpha}_{\,\,\beta} = \delta^{\alpha}_{\,\,\beta} + u^{\alpha}u_{\beta}$, we arrive at
-\begin{equation}
-(w + b^2)u_{\nu}\partial_i u^{\nu} + \partial_i\left(p + \frac{b^2}{2}\right) - b_{\nu}\partial_i b^{\nu}=0\,,
-\end{equation}
-where $i = r, \theta$. Following~\cite{Komissarov:2006} we rewrite this equation in terms of the specific angular momentum $l$ and of the angular velocity $\Omega$, to obtain
-\begin{equation}\label{eq:diff_ver}
-\partial_i(\ln u_t|) - \frac{\Omega \partial_i l}{1-l\Omega} + \frac{\partial_i p}{w} + \frac{\partial_i(\mathcal{L}b^2)}{2\mathcal{L}w} = 0\,,
-\end{equation}
-where $\mathcal{L} = g_{t\phi}^2 - g_{tt}g_{\phi\phi}$.
-To integrate Eq.~\eqref{eq:diff_ver} we first assume a barotropic equation of state $w = w(p)$ of the form
-\begin{equation}\label{eq:eos_fluid}
-p = K w^{\kappa},
-\end{equation}
-with $K$ and $\kappa$ constants.
-Then, we define the magnetic pressure as $p_{\mathrm{m}} = b^2/2$, and introduce the definitions $\tilde{p}_{\mathrm{m}} = \mathcal{L} p_{\mathrm{m}}$ and $\tilde{w} = \mathcal{L} w$, in order to write an analogue equation to Eq.~\eqref{eq:eos_fluid} for $\tilde{p}_{\mathrm{m}}$~\citep{Komissarov:2006}
-\begin{equation}\label{eq:eos_mag_tilde}
-\tilde{p}_{\mathrm{m}} = K_{\mathrm{m}} \tilde{w}_{\mathrm{m}}^{\lambda
-},
-\end{equation}
-or, in terms of the magnetic pressure $p_{\mathrm{m}}$
-\begin{equation}\label{eq:eos_mag}
-p_{\mathrm{m}} = K_{\mathrm{m}} \mathcal{L}^{\lambda
--1} w^{\lambda
-},
-\end{equation}
-where $K_{\mathrm{m}}$ and $\lambda
-$ are constants.
-This particular choice of barotropic relationships, $w = w(p)$ and $\tilde{w} = \tilde{w}(\tilde{p}_{\mathrm{m}})$, fulfill the general relativistic version of the von Zeipel theorem for a toroidal magnetic field~\citep{vonZeipel:1924, Zanotti:2015}, that is, the surfaces of constant $\Omega$ and constant $l$ coincide.
-
-We can now integrate Eq.~\eqref{eq:diff_ver} to obtain
-\begin{equation}\label{eq:pre_full_int}
-\ln |u_t| - \int^l_0 \frac{\Omega \mathrm{d}l}{1 - \Omega l} + \int^p_0 \frac{\mathrm{d}p}{w} + \int_0^{\tilde{p}_{\mathrm{m}}} \frac{\mathrm{d}\tilde{p}_{\mathrm{m}}}{\tilde{w}} = \mathrm{const}.
-\end{equation}
-On the surface of the disc, and particularly on its inner edge, the conditions
-$p = \tilde{p}_{\mathrm{m}} = 0, \; u_t = u_{t, \mathrm{in}}, \; l = l_{\mathrm{in}}$
-are satisfied and, therefore, the integration constant is simply given by
-\begin{equation}
-\mathrm{const.} = \ln |u_t| - \int^l_{l_\mathrm{in}} \frac{\Omega \mathrm{d}l}{1 - \Omega l}\,.
-\end{equation}
-We can also introduce the total (gravitational plus centrifugal) potential $W$~\citep{Abramowicz:1978} and write the integral form of the equation of motion (the relativistic Euler equation) as
-\begin{equation}\label{eq:potential}
-W - W_{\mathrm{in}} = \ln|u_t| - \ln|u_{t,\mathrm{in}}| - \int^{l}_{l_{\mathrm{in}}} \frac{\Omega \mathrm{d}l}{1 - \Omega l},
-\end{equation}
-where $W_{\mathrm{in}}$ is the potential at the inner edge of the disc (in the equatorial plane). With this definition, we can write Eq.~\eqref{eq:pre_full_int} as
-\begin{equation}\label{eq:full_int}
-W - W_{\mathrm{in}} = \int^p_0 \frac{\mathrm{d}p}{w} + \int_0^{\tilde{p}_{\mathrm{m}}} \frac{\mathrm{d}\tilde{p}_{\mathrm{m}}}{\tilde{w}},
-\end{equation}
-which for a barotropic equation of state can be easily integrated to give
-\begin{equation}\label{eq:pre_enthalpy_eq}
-W - W_{\rm{in}} + \frac{\kappa}{\kappa - 1}\frac{p}{w} + \frac{\lambda
-}{\lambda
- - 1}\frac{p_{\mathrm{m}}}{w} = 0\,.
-\end{equation}
-Replacing $p$ and $p_{\mathrm{m}}$ by equations \eqref{eq:eos_fluid} and \eqref{eq:eos_mag}, the previous equation reduces to
-\begin{equation}\label{eq:enthalpy_eq}
-W - W_{\rm{in}} + \frac{\kappa}{\kappa - 1} K w^{\kappa - 1} + \frac{\lambda
-}{\lambda
- - 1}K_{\mathrm{m}}(\mathcal{L} w)^{\lambda
- - 1} = 0,
-\end{equation}
-which relates the distribution of the potential with the distribution of the enthalpy density.
-
-%%%%%%%%%%%%
-\section{Method}
-\label{methodology}
-%%%%%%%%%%%%
-
-To construct our models of magnetised discs we have followed the approach described in \citet{Qian:2009}.
-First, we find the radial location of the cusp and of the centre of the disc in the equatorial plane, $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$, defined as the solutions to the equation $l(r) - l_{\mathrm{K}} = 0$.
-Next, we compute the partial derivatives of the potential, Eq.~\eqref{eq:potential}
-\begin{equation}\label{eq:radial_der_pot}
-\partial_r W = \partial_r \ln|u_t| - \frac{\Omega \partial_rl}{1 - \Omega l}\,,
-\end{equation}
-and
-\begin{equation}\label{eq:polar_der_pot}
-\partial_{\theta} W = \partial_{\theta} \ln|u_t| - \frac{\Omega \partial_{\theta}l}{1 - \Omega l}\,.
-\end{equation}
-Then, we integrate the radial partial derivative of the potential along the segment $[r_{\mathrm{cusp}}, r_{\mathrm{c}}]$ (assuming $W_{\mathrm{cusp}} = 0$) at the equatorial plane, thus obtaining the equatorial distribution of the potential between $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$
-\begin{equation}\label{eq:equatorial_pot}
-W_{\mathrm{eq}}(r) = \int^{r_{\mathrm{c}}}_{r_{\mathrm{cusp}}}\left(\partial_r \ln|u_t| - \frac{\Omega \partial_rl}{1 - \Omega l}\right).
-\end{equation}
-Following~\citet{Qian:2009} (see also~\citet{Jaroszynski:1980}) we can divide equations \eqref{eq:radial_der_pot} and \eqref{eq:polar_der_pot} to obtain
-\begin{equation}\label{eq:F}
-F(r, \theta) = -\frac{\partial_r W}{\partial_{\theta} W} = \frac{\mathrm{d}\theta}{\mathrm{d}r}\,,
-\end{equation}
-where function $F(r, \theta)$ is known in closed form for the Kerr metric once an assumption for the angular momentum distribution has been made (cf.~Eq.~(\ref{eq:ansatz})).
-For this reason, Eq.~(\ref{eq:F}) also takes the form of an ordinary differential equation for the surfaces of constant potential, $\theta=\theta(r)$, which, upon integration, yields the location of those surfaces.
-We note that in~\citet{Qian:2009} these are surfaces of constant {\it fluid pressure} instead, since their discs are purely hydrodynamical.
-
-\begin{figure*}[t]
-\centering
-\includegraphics[scale=0.14]{fig1a.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{fig1b.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{fig1c.pdf}
-\caption{Comparison with Komissarov's solution for a constant angular momentum model.
-The left panel shows the rest-mass density distribution in logarithm scale for all radii and all angles while the middle and right panels show, respectively, the angular profile of the logarithm of the rest-mass density at the centre of the disc and the radial profile of the logarithm of the rest-mass density at the equatorial plane.}
-\label{komissarov}
-\end{figure*}
-
-Next, we choose all the initial radial values for the integration of Eq.~\eqref{eq:F} to lie between $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$ ($\theta = \pi / 2$).
-Since we are only interested in the equipotential surfaces inside the Roche lobe of the disc, our choice of initial values provides us a mapping of the equipotential surfaces of the torus.
-Given that we have already obtained both the equipotential surfaces $\theta(r)$ which cross the segment $[r_{\mathrm{cusp}}, r_{\mathrm{c}}]$ at the equatorial plane and the values of the potential in that segment, we can obtain the complete potential distribution for the torus (outside of that segment).
-Once we have the potential distribution, we can find the fluid pressure at the centre of the disc from Eq.~\eqref{eq:enthalpy_eq},
-\begin{equation}
-p_{\mathrm{c}} = w_{\mathrm{c}}(W_{\mathrm{in}} - W_{\mathrm{c}})\left(\frac{\kappa}{\kappa - 1} + \frac{\lambda
-}{\lambda
- - 1}\frac{1}{\beta_{\mathrm{m}_{\mathrm{c}}}}\right)^{-1},
-\end{equation}
-where $w_{\mathrm{c}}$ is the enthalpy density at the centre and
-\begin{equation}
-\label{eq:beta_eq}
-\beta_{\mathrm{m}} = p/p_{\mathrm{m}},
-\end{equation}
-is the magnetisation parameter ($\beta_{\mathrm{m}_{\mathrm{c}}}$ being the magnetisation parameter at the centre of the disc). Using this definition, we can find the magnetic pressure at the centre,
-\begin{equation}
-p_{\mathrm{m_{\mathrm{c}}}} = p_{\mathrm{c}}/\beta_{\mathrm{m}_{\mathrm{c}}}\,.
-\end{equation}
-With both pressures known at the centre, fluid and magnetic, we can now find the constants $K$ and $K_{\mathrm{m}}$ using equations \eqref{eq:eos_fluid} and \eqref{eq:eos_mag}.
-Therefore, for a given inner radius of the disc $r_{\mathrm{in}}$ we can obtain the potential $W_{\mathrm{in}}$.
-We now finally have all the ingredients required to find the enthalpy density distribution (Eq.~\eqref{eq:enthalpy_eq}), the fluid pressure and magnetic pressure distributions (Eqs.~\eqref{eq:eos_fluid} and \eqref{eq:eos_mag}), and the rest-mass density distribution, which can be trivially obtained inverting the barotropic relation, $p = K \rho^{\kappa}$.
-We note that the fluid enthalpy density $w$ includes the rest-mass density $\rho$, and can thus be defined as $w=\rho h$ where $h$ is the specific enthalpy.
-The relativistic definition of this quantity is $h=1+\varepsilon+p/\rho$, where $\varepsilon$ is
-the specific internal energy. From a thermodynamical point of view a non-relativistic fluid satisfies $h=1$. Therefore,
-since we use polytropic equations of state (relating $p$ with either $w$ or $\rho$ in the same functional form) we are
-implicitly assuming that $h=1$, that is, the discs we build in our procedure are non-relativistic from a thermodynamical point of view.
-
-For the integration of Eq.~\eqref{eq:equatorial_pot} we have used the composite Simpson's rule.
-It is important to use a very small integration step because the slope is very steep.
-In this work, we have used a step $\Delta r = 10^{-6}$.
-Using the analytic, constant angular momentum case for comparison, we tested that
-a larger value of $\Delta r$ gives unacceptable accuracy losses.
-On the other hand, to integrate the ordinary differential equation \eqref{eq:F} we have employed a fourth-order Runge-Kutta method.
-Again, it is also important here to choose a suitable step of integration, especially at the outer end of the disc, because Eq.~\eqref{eq:F} diverges at the equatorial plane (the equipotential surfaces cross the equatorial plane perpendicularly).
-We show the proof of this statment in Appendix~\ref{div_partial_W}.
-
-\begin{table}
-\caption{Models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$.
-From left to right the columns report: the model name (with A, B and C standing for black hole spin $a = 0.5$, $0.9$ and $0.99$, respectively), the parameters of the angular momentum distribution $\beta$ and $\gamma$, the corresponding radii of the maximum fluid pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential difference between the centre and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the discs, $r_{\mathrm{in}}$ and $r_{\mathrm{out}}$.}
-\label{table:1}      
-\centering          
-\begin{tabular}{c c c c  c c c c}
-\hline\hline       
- & $\beta$ & $\gamma$ & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W$               & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
- &              &                   &                          &                                        & $(\times 10^{-2})$     &                              &  \\
-\hline           
-A1 & $0.0$ & $0.0$ & $7.15$ &  $8.14$  & $-6.35$ & $2.91$ & -- \\ 
-A2 & $0.5$ & $0.5$ & $7.15$ &  $7.65$  & $-2.27$ & $3.20$ & $11.8$\\ 
-A3 & $0.9$ & $0.9$ & $7.15$ &  $7.45$  & $-0.30$ & $3.70$ &  $9.58$\\ 
-A4 & $0.0$ & $0.9$ & $7.15$ &  $8.32$  & $-6.35$ & $2.91$ & $9.68$\\ 
-A5 & $0.9$ & $0.0$ & $7.15$ &  $7.28$  & $-0.30$ & $3.70$ & --\\ 
- \hline 
-B1 & $0.0$ & $0.0$ & $3.59$ &  $3.98$  & $-12.9$ & $1.73$ & -- \\ 
-B2 & $0.5$ & $0.5$ & $3.59$ &  $3.83$  & $-4.32$ & $1.86$ & $5.35$\\ 
-B3 & $0.9$ & $0.9$ & $3.59$ &  $3.73$  & $-0.54$ & $2.08$ & $4.52$\\ 
-B4 & $0.0$ & $0.9$ & $3.59$ &  $3.85$  & $-12.9$ & $1.73$ & $4.54$\\ 
-B5 & $0.9$ & $0.0$ & $3.59$ &  $3.81$  & $-0.54$ & $2.08$ & -- \\  
- \hline 
-C1 & $0.0$ & $0.0$ & $1.98$ &  $2.28$  & $-24.6$ & $1.21$ & -- \\ 
-C2 & $0.5$ & $0.5$ & $1.98$ &  $2.09$  & $-7.34$ & $1.26$ & $2.50$\\ 
-C3 & $0.9$ & $0.9$ & $1.98$ &  $2.04$  & $-0.85$ & $1.35$ & $2.25$\\ 
-C4 & $0.0$ & $0.9$ & $1.98$ &  $2.10$  & $-24.6$ & $1.21$ & $2.26$\\ 
-C5 & $0.9$ & $0.0$ & $1.98$ &  $2.08$  & $-0.85$ & $1.35$ & --\\ 
-\hline      
-\end{tabular}
-\end{table}
-
-\begin{table}
-\caption{Models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 1$. The naming of the models and the parameters reported in the columns are as in Table~\ref{table:1}.}             
-\label{table:2}      
-\centering          
-\begin{tabular}{c c c c  c c c c}
-\hline\hline       
- & $\beta$ & $\gamma$ & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W$               & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
- &              &                   &                          &                                        & $(\times 10^{-2})$     &                              &  \\
-\hline           
-A1 & $0.0$ & $0.0$ & $6.00$ &  $6.49$  & $-6.35$ & $2.91$ & -- \\ 
-A2 & $0.5$ & $0.5$ & $6.25$ &  $6.66$  & $-2.27$ & $3.20$ & $11.8$\\ 
-A3 & $0.9$ & $0.9$ & $6.50$ &  $6.80$  & $-0.30$ & $3.70$ &  $9.58$\\ 
-A4 & $0.0$ & $0.9$ & $6.00$ &  $6.49$  & $-6.35$ & $2.91$ & $9.68$\\ 
-A5 & $0.9$ & $0.0$ & $6.50$ &  $6.80$  & $-0.30$ & $3.70$ & --\\ 
- \hline 
-B1 & $0.0$ & $0.0$ & $3.02$ &  $3.26$  & $-12.9$ & $1.73$ & -- \\ 
-B2 & $0.5$ & $0.5$ & $3.16$ &  $3.35$  & $-4.32$ & $1.86$ & $5.35$\\
-B3 & $0.9$ & $0.9$ & $3.29$ &  $3.43$  & $-0.54$ & $2.08$ & $4.52$\\ 
-B4 & $0.0$ & $0.9$ & $3.02$ &  $3.26$  & $-12.9$ & $1.73$ & $4.54$\\  
-B5 & $0.9$ & $0.0$ & $3.29$ &  $3.43$  & $-0.54$ & $2.08$ & -- \\ 
- \hline 
-C1 & $0.0$ & $0.0$ & $1.68$ &  $1.80$  & $-24.6$ & $1.21$ & -- \\ 
-C2 & $0.5$ & $0.5$ & $1.77$ &  $1.86$  & $-7.34$ & $1.26$ & $2.50$\\  
-C3 & $0.9$ & $0.9$ & $1.84$ &  $1.91$  & $-0.85$ & $1.35$ & $2.25$\\ 
-C4 & $0.0$ & $0.9$ & $1.68$ &  $1.80$  & $-24.6$ & $1.21$ & $2.26$\\ 
-C5 & $0.9$ & $0.0$ & $1.84$ &  $1.91$  & $-0.85$ & $1.35$ & --\\ 
-\hline      
-\end{tabular}
-\end{table}
-
-%%%%%%%%%
-\section{Results}
-\label{results}
-%%%%%%%%%
-
-To reduce the number of free parameters to build the initial models we have done as in~\citet{Komissarov:2006} and have fixed the values of the equation of state exponents, $\kappa$ and $\lambda$, and of the enthalpy density at the disc centre, $w_{\mathrm{c}}$.
-More precisely, we have chosen $\kappa = \lambda = 4/3$ and $w_{\mathrm{c}} = 1$.
-This still leaves us with five parameters to control the size, shape, thickness, and magnetisation of the disc, namely the magnetisation parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$, the parameters of the angular momentum distribution $\beta$ and $\gamma$, the black hole spin parameter $a$, and the inner radius of the disc $r_{\mathrm{in}}$.
-We have built a series of 45 models, whose main features are summarised in Table~\ref{table:1} (for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$, that is, models where the effects of the magnetisation are unimportant), Table~\ref{table:2} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$, that is, equipartition models), and Table~\ref{table:3} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$, that is, highly-magnetised models).
-We note that we can build models with very small values of $\beta_{\mathrm{m}_{\mathrm{c}}}$, such as for example $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-20}$ (extremely high magnetisation) without encountering numerical difficulties.
-No qualitative differences in the structure of the discs are found once $\beta_{\mathrm{m}_{\mathrm{c}}}$ becomes smaller than a sufficiently small value, about $\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$.
-This is the reason why we have chosen that particular value as our lower limit in the figures and tables of the manuscript.
-
-We note in particular that the radii of the maximum fluid pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, respectively, for the same value of $\beta_{\mathrm{m}_{\mathrm{c}}}$, never coincide.
-This also reflects the fact that constant fluid pressure surfaces do not coincide with constant magnetic pressure surfaces.
-
-We start by assessing our procedure by first building an extra disc model that can be directly compared with one of the two models in~\citet{Komissarov:2006}.
-This is shown in Fig.~\ref{komissarov}, which corresponds to the same constant specific angular momentum model A presented by~\citet{Komissarov:2006}.
-The parameters of this model are $a=0.9$, $\beta_{\mathrm{m}_{\mathrm{c}}}=0.1$, and $l=2.8$.
-The visual comparison shows that our approach can reproduce those previous results with good agreement.
-The rest-mass density distribution in the $(r\sin\theta,r\cos\theta)$ plane shown in the left panel of Fig.~\ref{komissarov} is remarkably similar to that shown in the left panel of Fig.~2 in~\citet{Komissarov:2006}.
-Not only the morphology of both models is nearly identical but also the range of variation of the rest-mass density and the location of the disc centre agree well in both cases.
-This can be most clearly seen in the middle and right panels of Fig.~\ref{komissarov} which show, repectively, the angular profile at $r_{\rm c}$ and the radial profile at $\theta=\pi/2$.
-The middle figure can be directly compared with Fig.~3 of~\citet{Komissarov:2006}.
-It is relevant to mention that very small changes in the location of the inner radius $r_{\mathrm{in}}$ have a significant effect on the maximum value of the rest-mass density, which explains the small differences between our figures and the ones presented in~\citet{Komissarov:2006}.
-
-\begin{table}
-\caption{Models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$. The naming of the models and the parameters reported in the columns are as in Table~\ref{table:1}.}             
-\label{table:3}      
-\centering          
-\begin{tabular}{c c c c  c c c c}
-\hline\hline       
- & $\beta$ & $\gamma$ & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W$               & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
- &              &                   &                          &                                        & $(\times 10^{-2})$     &                              &  \\
-\hline           
-A1 & $0.0$ & $0.0$ & $5.11$ &  $5.51$  & $-6.35$ & $2.91$ & -- \\ 
-A2 & $0.5$ & $0.5$ & $5.55$ &  $5.80$  & $-2.27$ & $3.20$ & $11.8$\\ 
-A3 & $0.9$ & $0.9$ & $5.95$ &  $6.15$  & $-0.30$ & $3.70$ &  $9.58$\\ 
-A4 & $0.0$ & $0.9$ & $5.21$ &  $5.51$  & $-6.35$ & $2.91$ & $9.68$\\  
-A5 & $0.9$ & $0.0$ & $5.90$ &  $6.10$  & $-0.30$ & $3.70$ & --\\
- \hline 
-B1 & $0.0$ & $0.0$ & $2.53$ &  $2.73$  & $-12.9$ & $1.73$ & -- \\ 
-B2 & $0.5$ & $0.5$ & $2.81$ &  $2.91$  & $-4.32$ & $1.86$ & $5.35$\\
-B3 & $0.9$ & $0.9$ & $3.03$ &  $3.13$  & $-0.54$ & $2.08$ & $4.52$\\  
-B4 & $0.0$ & $0.9$ & $2.65$ &  $2.80$  & $-12.9$ & $1.73$ & $4.54$\\ 
-B5 & $0.9$ & $0.0$ & $3.03$ &  $3.13$  & $-0.54$ & $2.08$ & -- \\  
- \hline 
-C1 & $0.0$ & $0.0$ & $1.46$ &  $1.51$  & $-24.6$ & $1.21$ & -- \\ 
-C2 & $0.5$ & $0.5$ & $1.56$ &  $1.61$  & $-7.34$ & $1.26$ & $2.50$\\ 
-C3 & $0.9$ & $0.9$ & $1.70$ &  $1.75$  & $-0.85$ & $1.35$ & $2.25$\\ 
-C4 & $0.0$ & $0.9$ & $1.50$ &  $1.57$  & $-24.6$ & $1.21$ & $2.26$\\ 
-C5 & $0.9$ & $0.0$ & $1.72$ &  $1.77$  & $-0.85$ & $1.35$ & --\\ 
-\hline      
-\end{tabular}
-\end{table}
-
-\begin{figure*}
-\centering
-\includegraphics[scale=0.14]{fig2_1_1.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{fig2_1_2.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{fig2_1_3.pdf}
-\\
-\includegraphics[scale=0.14]{fig2_2_1.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{fig2_2_2.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{fig2_2_3.pdf}
-\\
-\includegraphics[scale=0.14]{fig2_3_1.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{fig2_3_2.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{fig2_3_3.pdf}
-\\
-\includegraphics[scale=0.14]{fig2_4_1.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{fig2_4_2.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{fig2_4_3.pdf}
-\\
-\includegraphics[scale=0.14]{fig2_5_1.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{fig2_5_2.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{fig2_5_3.pdf}
-\caption{Isodensity distributions for all models of Table~\ref{table:3}.
-From left to right the columns correspond to increasing values of the black hole spin: $a=0.5$, 0.9 and 0.99.
-From top to bottom the rows correspond to the following parameter combinations: a) $\gamma=\beta=0$; b) $\gamma=\beta=0.5$; c) $\gamma=\beta=0.9$; d) $\gamma=0.9$, $\beta=0$; e) $\gamma=0$, $\beta=0.9$.
-Note that the spatial scale of the plots differs as it has been chosen to facilitate the visualization of the discs.}
-\label{models}
-\end{figure*}
-
-\begin{figure*}[t]
-\centering
-\includegraphics[scale=0.14]{fig3a.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{fig3b.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{fig3c.pdf}
-\caption{Effects of the magnetisation in the structure of the disc. From left to right the values are $\beta_{\mathrm{m}_{\mathrm{c}}}
-=10^3$, 1, and $10^{-3}$.}
-\label{magnetisation}%
-\end{figure*}
-
-A representative sample of the isodensity surfaces for some of our models appears in Fig.~\ref{models}.
-We plot, in particular, the models of Table~\ref{table:3}, for which the magnetisation is highest ($\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$).
-From left to right the columns of this figure correspond to increasing values of the black hole spin, namely, $a=0.5$, 0.9 and 0.99, while from top to bottom the rows correspond to different combinations of the $\gamma$ and $\beta$ parameters that characterise the ansatz for the angular momentum distribution of~\citet{Qian:2009} (the particular values are indicated in the caption and legends of the figure).
-A rapid inspection shows that the structure of the discs noticeable changes when the parameters change.
-Notice that the spatial scale in all of the plots of this figure has been chosen so as to facilitate the visualization of the discs (which can be fairly small in some cases) and, as such, is different in each plot.
-A typical Polish doughnut is represented by the model in the top-left panel.
-As the black hole spin increases, the discs are closer to the black hole and its relative size with respect to the black hole is smaller for all values of $\gamma$ and $\beta$.
-For $\gamma=0$ the discs are infinite, irrespective of the value of $a$ and $\beta$.
-As $\gamma$ and $\beta$ increase from 0 to 0.9 (compare the three top rows) the discs become significantly thinner and radially smaller (see also Fig.~\ref{more-profile} below).
-It is also interesting to note that the maximum value of the rest-mass density is higher (with respect to the value at the disc centre) as the spin increases.
-
-\begin{figure}[t]
-\centering
-\includegraphics[scale=0.2]{fig4.pdf}
-\caption{Radial profiles of the rest-mass density in the equatorial plane for {$\beta_{\mathrm{m}_{\mathrm{c}}}=10^3$} (black curve), 1 (blue curve), and $10^{-3}$ (green curve). }
-\label{magnetisation-profile}
- \end{figure}
-
-\begin{figure}[t]
-\centering
-\includegraphics[scale=0.2]{fig5.pdf}
-\caption{Radial profiles at the equatorial plane for models with $a=0.9$, $\beta_{\mathrm{m}_{\mathrm{c}}}
-=10^{-3}$, and same combination of the $\gamma$ and $\beta$ parameters as in the rows of Fig.~\ref{models} (the specific values are indicated in the legend).}
-\label{more-profile}
-\end{figure}
-
-\begin{figure*}
-\centering
-\includegraphics[scale=0.14]{fig6a.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{fig6b.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{fig6c.pdf}
-\caption{Effects of $\beta_{\mathrm{m}_{\mathrm{c}}}$.
-Left panel: variation of the value of the maximum rest-mass density with respect to the logarithm of the magnetisation parameter.
-The solid, dashed, and dotted lines refer to $a = 0.99$, $0.9$ and $0.5$, respectively, and the colour code refers to the models shown in the legend.
-Middle panel: variation of the location of the rest-mass density maximum (and fluid pressure) with respect to the logarithm of the magnetisation parameter for the three models shown in the legend with $a = 0.99$.
-Right panel: variation (also for $a = 0.99$) of the location of the maximum of the magnetic pressure with respect to the logarithm of $\beta_{\mathrm{m}_{\mathrm{c}}}$.}
-           \label{max-vs-magnetisation}%
- \end{figure*}
-
-Fig.~\ref{magnetisation} shows the effects of changing the parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$ (the magnetisation) in the structure of the discs.
-From left to right the values plotted in each panel are $\beta_{\mathrm{m}_{\mathrm{c}}}=10^3$, 1, and $10^{-3}$.
-The model chosen corresponds to $a=0.9$ and $\gamma=\beta=0.5$.
-The larger the value of $\beta_{\mathrm{m}_{\mathrm{c}}}$ the less important the effects of the magnetisation in the disc structure.
-Fig.~\ref{magnetisation} shows that, at least for the kind of magnetic field distribution we are considering, the effects of the magnetisation are minor.
-The disc structure remains fairly similar for all values of $\beta_{\mathrm{m}_{\mathrm{c}}}
-$ and the only quantitative differences are found in the location of the centre of the disc (which moves inward with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$) and of the range of variation of the isodensity contours (the maximum being slightly larger with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$).
-This can be more clearly visualised in Fig.~\ref{magnetisation-profile} which displays the radial profile at the equatorial plane of the rest-mass density for the same three cases plotted in Fig.~\ref{magnetisation}.
-
-Next, we show in Fig.~\ref{more-profile} the corresponding radial profiles at the equatorial plane for the models with black hole spin $a=0.9$.
-We consider the case $\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$ (highest magnetisation) and the same combination of the $\gamma$ and $\beta$ parameters that we employed in Fig.~\ref{models}.
-Therefore, this plot depicts the radial profiles of the models occupying the central column of Fig.~\ref{models}.
-These profiles allow for a clearer quantification of the radial extent of the discs with $\gamma$ and $\beta$.
-As mentioned in the description of Fig.~\ref{models} as $\gamma$ and $\beta$ increase from 0 to 0.9 (compare black, blue, and green curves) the discs become gradually smaller.
-At the same time, the radial location of the rest-mass density maximum increases and the maximum value of the central rest-mass density (and pressure) decreases.
-It is worth noticing that the radial profiles of some of the models overlap below a certain radius.
-More precisely, the models with equal $\beta$ overlap below $r\sim r_{\mathrm{c}}$ (which corresponds to $\rho \sim 1$).
-In addition, this figure clearly shows that, besides modifying the thickness of the disc, $\beta$ is the parameter which determines the value of the rest-mass density (and pressure) maximum.
-On the other hand, the parameter $\gamma$ is only relevant for controlling the radial size of the discs.
-
-In order to provide a quantitative comparison of the structural differences that appear along the sequence of equilibrium models, we plot in Fig.~\ref{max-vs-magnetisation} the variation of the maximum of the rest-mass density (left panel), the radial location of the maximum of the fluid pressure (middle panel), and the radial location of the maximum of the magnetic pressure (right panel) as a function of the magnetisation parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$.
-All quantities plotted are measured at the equatorial plane.
-Let us first consider the left panel.
-All curves show the same monotonically decreasing trend with $\beta_{\mathrm{m}_{\mathrm{c}}}$, yet for small enough and large enough values of $\beta_{\mathrm{m}_{\mathrm{c}}} $ the value of the rest-mass density maximum does not change.
-However, in the interval $10^{-2}\le \beta_{\mathrm{m}_{\mathrm{c}}} \le 10^{2}$, $\rho_{\rm max}$ changes abruptly.
-The larger the black hole spin the larger the drop in the maximum of the rest-mass density.
-For sufficiently large values of $\beta_{\mathrm{m}_{\mathrm{c}}}$ (small magnetisation) the value of $\rho_{\rm max}$ stays constant to the same value irrespective of the black hole rotation.
-
-In the middle panel of Fig.~\ref{max-vs-magnetisation} we show the radial location of the maximum of the fluid pressure as a function of $\beta_{\mathrm{m}_{\mathrm{c}}}$.
-The black hole spin is $a=0.99$ and the values of $\beta$ and $\gamma$ are indicated in the legend.
-For all values of $\beta$ and $\gamma$, the maximum of the location of the disc fluid pressure decreases with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$.
-Below $\beta_{\mathrm{m}_{\mathrm{c}}}\sim 10^{-3}$ the location of the maximum does no longer change.
-The panel also shows that above $\beta_{\mathrm{m}_{\mathrm{c}}}\sim 10^{3}$ the constant value of $r_{\rm max}$ is the same irrespective of $\beta$ and $\gamma$, as expected, because for purely hydrodynamic discs, $r_{\mathrm{max}} = r_{\mathrm{c}}$.
-
-The dependence of the location of the maximum of the magnetic pressure with $\beta_{\mathrm{m}_{\mathrm{c}}}$ is shown in the right panel of Fig.~\ref{max-vs-magnetisation}.
-While this location also decreases with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$, the constant value achieved for values above $\beta_{\mathrm{m}_{\mathrm{c}}}\sim 10^{3}$ does depend on the specific values of $\beta$ and $\gamma$, contrary to what happens with the fluid pressure.
-It must be noted that the location of the maximum of the magnetic pressure is identical for all models considered when $\beta_{\mathrm{m}_{\mathrm{c}}} \equiv 1/(\lambda - 1) = 3$, as we show in Appendix~\ref{app_magmax}.
-At this value of $\beta_{\mathrm{m}_{\mathrm{c}}}$ all models cross at $r_{\mathrm{m}_{\mathrm{max}}} = r_{\mathrm{c}}$, as it is more clearly shown in the inset of the right panel of Fig.~\ref{max-vs-magnetisation}.
-
-As a final remark we note that in the left and middle panels of Fig.~\ref{max-vs-magnetisation} we do not show the data for models with $\beta \neq \gamma$ as they coincide with the respective models with the same value of $\beta$.
-Moreover, the middle and right panels only show the data for $a=0.99$ because changing the value of the spin parameter of the black hole only yields a change of scale.
-Therefore, if we chose the range of the graph accordingly, the plots would be identical (same relative differences between the curves) irrespective of the value of $a$.
-
-%%%%%%%%%%%
-\section{Conclusions}
-\label{conclusions}
-%%%%%%%%%%%
-
-In this paper we have presented a procedure to build equilibrium sequences of magnetised, non-self-gravitating discs around Kerr black holes which combines the two existing approaches of~\citet{Komissarov:2006} and~\citet{Qian:2009}.
-On the one hand we have followed~\citet{Qian:2009} and have assumed a form of the angular momentum distribution in the disc from which the location and morphology of surfaces of equal potential can be computed.
-As a limiting case, this ansatz includes the constant angular momentum case originally employed in the construction of thick tori -- or Polish doughnuts~\citep{Abramowicz:1978,Kozlowski:1978}  -- and was already used by~\citet{Qian:2009} to build equilibrium sequences of purely hydrodynamical models.
-On the other hand, our discs are endowed with a purely toroidal magnetic field, as in the work of~\citet{Komissarov:2006}, which provides the methodology we have followed to handle the magnetic terms.
-On a similar note, we cite the work of~\citet{Wielgus:2015} who have recently extended the solution of~\citet{Komissarov:2006} to include non-constant specific angular momentum tori.
-These authors limited their consideration to power-law distributions and were particularly focused on the stability of such tori to the MRI.
-The approach discussed in our work differs from that of~\citet{Wielgus:2015} and, moreover, we have explored a much wider parameter space.
-
-We have discussed the properties of the new models and their dependence on the initial parameters, namely the magnetisation parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$, the parameters $\beta$ and $\gamma$ describing the angular momentum distribution, the black hole spin parameter $a$, and the inner radius of the disc $r_{\mathrm{in}}$.
-We have shown the effects of changing $\beta$ and $\gamma$ beyond the purely hydrodynamical case considered in~\citet{Qian:2009}.
-The morphology of the solutions we have built no longer changes for magnetisation values above $\beta_{\mathrm{m}_{\mathrm{c}}} \sim 10^{3}$ and below $\beta_{\mathrm{m}_{\mathrm{c}}} \sim 10^{-3}$.
-These cases can thus be considered as the hydrodynamical and MHD limiting cases, respectively.
-The new sequences of magnetised discs around black holes presented in this work can be used as initial data for magnetohydrodynamical evolutions in general relativity.
-In the near future, we plan to extend this work along two main directions, namely (i) including the self-gravity of the discs, following the approach laid out in~\citet{Stergioulas:2011}, and (ii) constructing accretion discs around hairy black holes, both, with scalar and Proca hair~\citep{Herdeiro:2014,Herdeiro:2016}.
-
-\begin{acknowledgements}
-It is a pleasure to thank P.~C.~Fragile and N.~Stergioulas for useful discussions and comments.
-We thank the referee for his constructive report which improved the manuscript.
-Work supported by the Spanish MINECO (grant AYA2015-66899-C2-1-P) and the Generalitat Valenciana (PROMETEOII-2014-069).
-\end{acknowledgements}
-
-\bibliographystyle{aa}
-\bibliography{references}
-
-\begin{appendix}
-\section{Divergence of equation~\eqref{eq:F} at $\theta = \pi/2$}\label{div_partial_W}
-To prove that Eq.~\eqref{eq:F} diverges at $\theta = \pi/2$ we need to show that
-Eq.~\eqref{eq:polar_der_pot} vanishes at the equator, that is
-\begin{eqnarray}
-\partial_{\theta} W = \partial_{\theta} \ln|u_t| - \frac{\Omega \partial_{\theta}l}{1 - \Omega l}\, = 0.
-\end{eqnarray}
-Then, we have to prove that either the two terms of this equation are equal or they are identically zero at $\theta = \pi/2$. We shall see that the latter is true.
-First, we take the derivative of the angular momentum distribution $\partial_{\theta} l$.
-From Eq.~(7) we can write the angular momentum distribution as $l(r, \theta) = l(r) \sin^{2\gamma} \theta$, so that the derivative reads
-\begin{eqnarray}
-\partial_{\theta} l = 2\gamma l(r) \sin^{2\gamma - 1} \theta \cos \theta \,.
-\end{eqnarray}
-Taking $\theta = \pi/2$ leads to $\partial_{\theta} l = 0$, so the second term equals to zero.
-To show that the first term is also zero, we write it as
-\begin{eqnarray}
-\partial_{\theta} \ln|u_t| = \partial_{\theta} \ln \left(\frac{\mathcal{L}}{\mathcal{A}}\right)^{\frac{1}{2}}\,,
-\end{eqnarray}
-where $\mathcal{L} = g_{t \phi}^2 - g_{tt} g_{\phi\phi}$ and $\mathcal{A} = g_{\phi\phi} + 2 l g_{t\phi} + l^2g_{tt}$, and we have dropped the absolute value, as it is irrelevant to this discussion.
-Then, the derivative is
-\begin{eqnarray}
-\partial_{\theta} \ln|u_t| = \frac{1}{2} \frac{\mathcal{A}}{\mathcal{L}}\frac{\mathcal{A}\partial_{\theta}{\mathcal{L}} - \mathcal{L}\partial_{\theta}\mathcal{A}}{\mathcal{A}^2} = \frac{1}{2} \frac{\mathcal{A}\partial_{\theta}{\mathcal{L}} - \mathcal{L}\partial_{\theta}\mathcal{A}}{\mathcal{A} \mathcal{L}}\,.
-\end{eqnarray}
-We use Boyer-Lindquist coordinates, for which the metric components read
-\begin{eqnarray}
-g_{tt} = - \left(1 - \frac{2Mr}{\rho^2}\right), \ g_{t\phi} = -\frac{2Mar\sin^2\theta}{\rho^2},
-\nonumber \\
-g_{\phi\phi} = \left(r^2 + a^2 + \frac{2Ma^2r\sin^2\theta}{\rho^2}\right) \sin^2 \theta\,,
-\end{eqnarray}
-where $\rho^2 = r^2 + a^2\cos^2 \theta$.
-Therefore, we obtain $\mathcal{L} = \Delta \sin^2 \theta$, where $\Delta = r^2 - 2Mr + a^2$, and its derivative $\partial_{\theta}\mathcal{L} = 2 \Delta \sin \theta \cos \theta$, which is zero for $\theta = \pi/2$.
-Next, we take the derivative of $\mathcal{A}$
-\begin{eqnarray}
-\partial_{\theta} \mathcal{A} = \partial_{\theta} g_{\phi\phi} + 2 (\partial_{\theta} l) g_{t\phi} + 2l\partial_{\theta} g_{t\phi} + 2l(\partial_{\theta} l) g_{tt} + l^2 \partial_{\theta} g_{tt} = 
-\nonumber \\
-= \partial_{\theta} g_{\phi\phi} + 2l\partial_{\theta} g_{t\phi} + l^2 \partial_{\theta} g_{tt}\,,
-\end{eqnarray}
-where we have used the previous result that $\partial_{\theta} l=0$ at $\theta = \pi/2$.
-By inspecting the metric components, it is easy to see that all terms depending on $\theta$ are functions of $\sin^2 \theta$ or $\cos^2 \theta$.
-This means their $\theta$ derivatives will have at least a $\cos \theta$ multiplying.
-Then $\partial_{\theta} \mathcal{A} = 0$ at $\theta = \pi/2$.
-Therefore, $\partial_{\theta} \ln|u_t|$ is also zero at $\theta = \pi/2$.
-
-\section{Value of the magnetisation parameter for $r_{\mathrm{m}_{\mathrm{max}}} = r_{\mathrm{c}}$}\label{app_magmax}
-In this appendix we derive the condition $\beta_{\mathrm{m}_{\mathrm{c}}} = 1/(\lambda - 1)$ for $r_{\mathrm{m}_{\mathrm{max}}} = r_{\mathrm{c}}$.
-First, we can use Eq.~\eqref{eq:eos_mag} to write 
-\begin{eqnarray}\label{eq_max}
-\frac{\partial{p_{\mathrm{m}}(r)}}{\partial r} = \partial_{r} \left(K_{\mathrm{m}} \mathcal{L}^{\lambda -1} w^{\lambda}\right) = 0\,,
-\end{eqnarray}
-which yields
-\begin{eqnarray}
-\partial_{r} p_{\mathrm{m}} = K_{\mathrm{m}} \mathcal{L}^{\lambda - 2}w^{\lambda} [(\lambda - 1)(\partial_r \mathcal{L}) w + \lambda \mathcal{L} (\partial_r w)]=0\,.
-\end{eqnarray}
-Inside the disc $K_{\mathrm{m}} \mathcal{L}^{\lambda - 2}w^{\lambda} \neq 0$. Therefore, to fulfill the extremum condition~\eqref{eq_max} we need 
-\begin{equation}\label{eq:simple_expr}
-(\lambda - 1)(\partial_r \mathcal{L}) w + \lambda \mathcal{L} (\partial_r w) = 0\,.
-\end{equation}
-To evaluate this expression, we need to compute the partial derivatives $\partial_r \mathcal{L}$ and $\partial_r w$.
-The derivative of $\mathcal{L}$ is straightforward, since $\mathcal{L} = \Delta \sin^2 \theta$,
-\begin{equation}
-\partial_r \mathcal{L} = 2(r-M)\sin^2 \theta\,.
-\end{equation}
-Let us now discuss $\partial_r w$. From Eq.~\eqref{eq:enthalpy_eq} we have
-\begin{equation}
-w = \left[-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right]^{\frac{1}{\lambda-1}}\,.
-\end{equation}
-Taking its derivative we obtain
-\begin{eqnarray}
-\partial_r w &=& \frac{w}{\lambda - 1} \left[-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right]^{-1} 
-\nonumber \\
-&\times&
-\left[\left(-\partial_r W \left(\frac{\lambda -1 }{\lambda}\right) \frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right) 
-\right.
-\nonumber \\
-&+& \left.
-\left(-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{-(\lambda - 1) K_{\mathrm{m}} \mathcal{L}^{\lambda - 2} \partial_r \mathcal{L}}{(K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1})^2}\right)\right]\,.
-\end{eqnarray}
-Since at $r = r_{\mathrm{c}}$ the derivative of the potential is zero, $\partial_r W(r, \pi/2)|_{r = r_{\mathrm{c}}} = 0$, we can simplify the above expression to obtain
-\begin{eqnarray}
-\partial_r w &=& \frac{w}{\lambda - 1} \left[-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right]^{-1} 
-\nonumber \\
-&\times&
-\left(-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right)
-\nonumber \\
-&\times&\left[\frac{-(\lambda - 1) K_{\mathrm{m}} \mathcal{L}^{\lambda - 2} \partial_r \mathcal{L}}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right]\,,
-\end{eqnarray}
-which can be further simplified to the following form
-\begin{equation}
-\partial_r w = - w \left[\frac{K_{\mathrm{m}} \mathcal{L}^{\lambda - 2} \partial_r \mathcal{L}}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right]\,.
-\end{equation}
-Next, by inserting this expression in Eq.~\eqref{eq:simple_expr} we obtain
-\begin{equation}
-(\partial_r \mathcal{L}) w [(\lambda -1)(K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}) - \lambda K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}] = 0\,.
-\end{equation}
-Since $(\partial_r \mathcal{L}) w \neq 0$ inside the disc, the above equation leads to 
-\begin{equation}
-K (\lambda - 1) = K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}\,.
-\end{equation}
-Moreover, we can use Eqs.~\eqref{eq:eos_fluid}, \eqref{eq:eos_mag} and \eqref{eq:beta_eq} at the centre (remember that $w_{\mathrm{c}} = 1$) to write $K$ as $K = \beta_{\mathrm{m}_{\mathrm{c}}} K_\mathrm{m}\mathcal{L}^{\lambda -1}$.
-Therefore, this allows us to obtain the following simple expression for the value of the magnetisation parameter at the centre of the disc
-\begin{equation}
-\beta_{\mathrm{m}_{\mathrm{c}}} = \frac{1}{\lambda - 1}\,.
-\end{equation}
-It is relevant to note that the only reference to the explicit form of the metric is done to show that $\mathcal{L} \neq 0$ and $\partial_r \mathcal{L} \neq 0$ inside the disc.
-This means that our result holds for any stationary and axisymmetric metric if the aforementioned inequalities hold.
-Moreover, the result is also true for any angular momentum distribution that allows for the existence of a cusp and a centre (and $r_{\mathrm{c}} \neq r_{\mathrm{cusp}}$).
-
-\end{appendix}
-
 \end{document}

### 2017-11-14 magnetised_polish_doughnuts_revisited/paper_revised/my_changes.tex
new paper added

--- 2017-07-04 paper_revised/paper_revised.tex
@@
-\documentclass[referee]{aa}
+\documentclass[]{aa}
 
@@
 We now finally have all the ingredients required to find the enthalpy distribution (Eq.~\eqref{eq:enthalpy_eq}), the fluid pressure and magnetic pressure distributions (Eqs.~\eqref{eq:eos_fluid} and \eqref{eq:eos_mag}), and the {\bf rest-mass} density distribution, which can be trivially obtained inverting the barotropic relation, $p = K \rho^{\kappa}$.
-{\bf We note that the fluid enthalpy $w$ includes the rest-mass density $\rho$, and can thus be defined as $w=\rho h$ where $h$ is the specific enthalpy.
-The relativistic definition of this quantity is $h=1+\varepsilon+p/\rho$, where $\varepsilon$ is
-the specific internal energy. From a thermodynamical point of view a non-relativistic fluid satisfies $h=1$. Therefore,
-since we use poytropic equations of state (relating $p$ with either $w$ or $\rho$ in the same functional form) we are
-implictly assuming that $h=1$, i.e.~the discs we build in our procedure are non-relativistic from a thermodynamical point of view.}
-%{\bf We note that the specific internal energy $\varepsilon$ is needed to compute the enthalpy. We obtain
-%this quantity by combining the ideal fluid and the barotropic equations of state, which yields 
-%$\varepsilon=\frac{K}{\kappa-1}\rho^{\kappa-1}$.}
 
@@
 It is important to use a very small integration step because the slope is very steep.
-In this work, we use a step $\Delta r = 10^{-6}$.
+In this work, we use a step $h = 10^{-6}$.
 Using the analytic, constant angular momentum case for comparison, we tested that
-a larger value of $\Delta r$ gives unacceptable accuracy losses.
+a larger value of $h$ gives unacceptable accuracy losses.
 On the other hand, to integrate the ordinary differential equation \eqref{eq:F} we use a fourth-order Runge-Kutta method.
 Again, it is also important here to choose a suitable step of integration, especially at the outer end of the disc, because Eq.~\eqref{eq:F} diverges at the equatorial plane (the equipotential surfaces cross the equatorial plane perpendicularly).
-{\bf We show the proof of this statment in Appendix~\ref{div_partial_W}.}
 
@@
 We build a series of 45 models, whose main features are summarised in Table~\ref{table:1} (for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$, i.e.~models where the effects of the magnetisation are unimportant), Table~\ref{table:2} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$, i.e.~equipartition models), and Table~\ref{table:3} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$, i.e.~highly-magnetised models).
-{\bf
-We note in particular that the radii of the maximum fluid pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, respectively, for the same value of $\beta_{\mathrm{m}_{\mathrm{c}}}$, never coincide.
-This also reflects the fact that constant fluid pressure surfaces do not coincide with constant magnetic pressure surfaces.}
 
@@
 The dependence of the location of the maximum of the magnetic pressure with $\beta_{\mathrm{m}_{\mathrm{c}}}$ is shown in the right panel of Fig.~\ref{max-vs-magnetisation}.
-While this location also decreases with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$, the constant value achieved for values above $\beta_{\mathrm{m}_{\mathrm{c}}}\sim 10^{3}$ does depend on the specific values of $\beta$ and $\gamma$, contrary to what happens with the fluid pressure.
-{\bf It must be noted that the location of the maximum of the magnetic pressure is identical for all models considered when $\beta_{\mathrm{m}_{\mathrm{c}}} \equiv 1/(\lambda - 1) = 3$, as we show in Appendix~\ref{app_magmax}.
-At this value of $\beta_{\mathrm{m}_{\mathrm{c}}}$ all models cross at $r_{\mathrm{m}_{\mathrm{max}}} = r_{\mathrm{c}}$, as it is more clearly shown in the inset of the right panel of Fig.~\ref{max-vs-magnetisation}.}
-
+While this location also decreases with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$, the constant value achieved for values above $\beta_{\mathrm{m}_{\mathrm{c}}}\sim 10^{3}$ does depend on the specific values of $\beta$ and $\gamma$, contrary to what happens with the fluid pressure.{\bf It must be noted that the location of the maximum of the magnetic pressure is nearly identical for all models considered when $\beta_{\mathrm{m}_{\mathrm{c}}} = 1/(\lambda - 1) = 3$ (we show the proof for this affirmation at the appendix \ref{app_magmax}).
+At this value of $\beta_{\mathrm{m}_{\mathrm{c}}}$ all models cross at $r_{\mathrm{m}_{\mathrm{max}}} = r_{\mathrm{c}}$, as it is more clearly shown in the inset of the right panel of Fig.~\ref{max-vs-magnetisation}}
  % It must be noted that the location of the maximum of the magnetic pressure is nearly identical for all models considered when $\log_{10}\beta_{\mathrm{m}_{\mathrm{c}}} \sim 0.5$.
@@
 \begin{appendix}
-\section{Divergence of equation~\eqref{eq:F} at $\theta = \pi/2$}\label{div_partial_W}
-To prove that Eq.~\eqref{eq:F} diverges at $\theta = \pi/2$ we need to show that
-Eq.~\eqref{eq:polar_der_pot} vanishes at the equator, i.e.
-\begin{eqnarray}
-\partial_{\theta} W = \partial_{\theta} \ln|u_t| - \frac{\Omega \partial_{\theta}l}{1 - \Omega l}\, = 0.
-\end{eqnarray}
-Then, we have to prove that either the two terms of this equation are equal or they are identically zero at $\theta = \pi/2$. We shall see that the latter is true.
-First, we take the derivative of the angular momentum distribution $\partial_{\theta} l$.
-From Eq.~(7) we can write the angular momentum distribution as $l(r, \theta) = l(r) \sin^{2\gamma} \theta$, so that the derivative reads
-\begin{eqnarray}
-\partial_{\theta} l = 2\gamma l(r) \sin^{2\gamma - 1} \theta \cos \theta \,.
-\end{eqnarray}
-Taking $\theta = \pi/2$ leads to $\partial_{\theta} l = 0$, so the second term equals to zero.
-To show that the first term is also zero, we write it as
-\begin{eqnarray}
-\partial_{\theta} \ln|u_t| = \partial_{\theta} \ln \left(\frac{\mathcal{L}}{\mathcal{A}}\right)^{\frac{1}{2}}\,,
-\end{eqnarray}
-where $\mathcal{L} = g_{t \phi}^2 - g_{tt} g_{\phi\phi}$ and $\mathcal{A} = g_{\phi\phi} + 2 l g_{t\phi} + l^2g_{tt}$, and we have dropped the absolute value, as it is irrelevant to this discussion.
-Then, the derivative is
-\begin{eqnarray}
-\partial_{\theta} \ln|u_t| = \frac{1}{2} \frac{\mathcal{A}}{\mathcal{L}}\frac{\mathcal{A}\partial_{\theta}{\mathcal{L}} - \mathcal{L}\partial_{\theta}\mathcal{A}}{\mathcal{A}^2} = \frac{1}{2} \frac{\mathcal{A}\partial_{\theta}{\mathcal{L}} - \mathcal{L}\partial_{\theta}\mathcal{A}}{\mathcal{A} \mathcal{L}}\,.
-\end{eqnarray}
-We use Boyer-Lindquist coordinates, for which the metric components read
-\begin{eqnarray}
-g_{tt} = - \left(1 - \frac{2Mr}{\rho^2}\right), \ g_{t\phi} = -\frac{2Mar\sin^2\theta}{\rho^2}, \ g_{\phi\phi} = \left(r^2 + a^2 + \frac{2Ma^2r\sin^2\theta}{\rho^2}\right) \sin^2 \theta\,,
-\end{eqnarray}
-where $\rho^2 = r^2 + a^2\cos^2 \theta$.
-Therefore, we obtain $\mathcal{L} = \Delta \sin^2 \theta$, where $\Delta = r^2 - 2Mr + a^2$, and its derivative $\partial_{\theta}\mathcal{L} = 2 \Delta \sin \theta \cos \theta$, which is zero for $\theta = \pi/2$.
-Next, we take the derivative of $\mathcal{A}$
-\begin{eqnarray}
-\partial_{\theta} \mathcal{A} = \partial_{\theta} g_{\phi\phi} + 2 (\partial_{\theta} l) g_{t\phi} + 2l\partial_{\theta} g_{t\phi} + 2l(\partial_{\theta} l) g_{tt} + l^2 \partial_{\theta} g_{tt} = \partial_{\theta} g_{\phi\phi} + 2l\partial_{\theta} g_{t\phi} + l^2 \partial_{\theta} g_{tt}\,,
-\end{eqnarray}
-where we have used the previous result that $\partial_{\theta} l=0$ at $\theta = \pi/2$.
-By inspecting the metric components, it is easy to see that all terms depending on $\theta$ are functions of $\sin^2 \theta$ or $\cos^2 \theta$.
-This means their $\theta$ derivatives will have at least a $\cos \theta$ multiplying.
-Then $\partial_{\theta} \mathcal{A} = 0$ at $\theta = \pi/2$.
-Therefore, $\partial_{\theta} \ln|u_t|$ is also zero at $\theta = \pi/2$.
+\section{Magnetization for $r_{\mathrm{m}_{\mathrm{max}}} = r_{\mathrm{c}}$}\label{app_magmax}
 
-\section{Value of the magnetisation parameter for $r_{\mathrm{m}_{\mathrm{max}}} = r_{\mathrm{c}}$}\label{app_magmax}
-In this appendix we derive the condition $\beta_{\mathrm{m}_{\mathrm{c}}} = 1/(\lambda - 1)$ for $r_{\mathrm{m}_{\mathrm{max}}} = r_{\mathrm{c}}$.
-First, we can use Eq.~\eqref{eq:eos_mag} to write 
-\begin{eqnarray}\label{eq_max}
-\frac{\partial{p_{\mathrm{m}}(r)}}{\partial r} = \partial_{r} \left(K_{\mathrm{m}} \mathcal{L}^{\lambda -1} w^{\lambda}\right) = 0\,,
-\end{eqnarray}
-which yields
-\begin{eqnarray}
-\partial_{r} p_{\mathrm{m}} = K_{\mathrm{m}} \mathcal{L}^{\lambda - 2}w^{\lambda} [(\lambda - 1)(\partial_r \mathcal{L}) w + \lambda \mathcal{L} (\partial_r w)]=0\,.
-\end{eqnarray}
-Inside the disc $K_{\mathrm{m}} \mathcal{L}^{\lambda - 2}w^{\lambda} \neq 0$. Therefore, to fulfill the extremum condition~\eqref{eq_max} we need 
-\begin{equation}\label{eq:simple_expr}
-(\lambda - 1)(\partial_r \mathcal{L}) w + \lambda \mathcal{L} (\partial_r w) = 0\,.
+Here, we derive the condition $\beta_{\mathrm{m}_{\mathrm{c}}} = 1/(\lambda - 1)$ for $r_{\mathrm{m}_{\mathrm{max}}} = r_{\mathrm{c}}$.
+First, we can use equation~\eqref{eq:eos_mag} to write
+
+\begin{equation}\label{eq_max}
+\frac{\partial{p_{\mathrm{m}}(r)}}{\partial r} = \partial_{r} \left(K_{\mathrm{m}} \mathcal{L}^{\lambda -1} w^{\lambda}\right) = 0,
 \end{equation}
+
+Computing, we arrive at
+
+\begin{equation}
+\partial_{r} p_{\mathrm{m}} = K_{\mathrm{m}} \mathcal{L}^{\lambda - 2}w^{\lambda} [(\lambda - 1)(\partial_r \mathcal{L}) w + \lambda \mathcal{L} (\partial_r w)].
+\end{equation}
+
+We can see that, inside the disc $K_{\mathrm{m}} \mathcal{L}^{\lambda - 2}w^{\lambda} \neq 0$, So to fulfill the extremum condition~\eqref{eq_max} we need
+
+\begin{equation}
+(\lambda - 1)(\partial_r \mathcal{L}) w + \lambda \mathcal{L} (\partial_r w) = 0
+\end{equation}
+
 To evaluate this expression, we need to compute the partial derivatives $\partial_r \mathcal{L}$ and $\partial_r w$.
-The derivative of $\mathcal{L}$ is straightforward, since $\mathcal{L} = \Delta \sin^2 \theta$,
-\begin{equation}
-\partial_r \mathcal{L} = 2(r-M)\sin^2 \theta\,.
-\end{equation}
-Let us now discuss $\partial_r w$. From Eq.~\eqref{eq:enthalpy_eq} we have
-\begin{equation}
-w = \left[-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right]^{\frac{1}{\lambda-1}}\,.
-\end{equation}
-Taking its derivative we obtain
-\begin{eqnarray}
-\partial_r w &=& \frac{w}{\lambda - 1} \left[-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right]^{-1} 
-\nonumber \\
-&\times&
-\left[\left(-\partial_r W \left(\frac{\lambda -1 }{\lambda}\right) \frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right) + \left(-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{-(\lambda - 1) K_{\mathrm{m}} \mathcal{L}^{\lambda - 2} \partial_r \mathcal{L}}{(K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1})^2}\right)\right]\,.
-\end{eqnarray}
-Since at $r = r_{\mathrm{c}}$ the derivative of the potential is zero, $\partial_r W(r, \pi/2)|_{r = r_{\mathrm{c}}} = 0$, we can simplify the above expression to obtain
-\begin{eqnarray}
-\partial_r w &=& \frac{w}{\lambda - 1} \left[-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right]^{-1} 
-\nonumber \\
-&\times&
-\left(-\Delta W \left(\frac{\lambda -1}{\lambda}\right)\frac{1}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right)\left[\frac{-(\lambda - 1) K_{\mathrm{m}} \mathcal{L}^{\lambda - 2} \partial_r \mathcal{L}}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right]\,,
-\end{eqnarray}
-which can be further simplified to the following form
-\begin{equation}
-\partial_r w = - w \left[\frac{K_{\mathrm{m}} \mathcal{L}^{\lambda - 2} \partial_r \mathcal{L}}{K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}}\right]\,.
-\end{equation}
-Next, by inserting this expression in Eq.~\eqref{eq:simple_expr} we obtain
-\begin{equation}
-(\partial_r \mathcal{L}) w [(\lambda -1)(K+K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}) - \lambda K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}] = 0\,.
-\end{equation}
-Since $(\partial_r \mathcal{L}) w \neq 0$ inside the disc, the above equation leads to 
-\begin{equation}
-K (\lambda - 1) = K_{\mathrm{m}}\mathcal{L}^{\lambda - 1}\,.
-\end{equation}
-Moreover, we can use Eqs.~\eqref{eq:eos_fluid}, \eqref{eq:eos_mag} and \eqref{eq:beta_eq} at the centre (remember that $w_{\mathrm{c}} = 1$) to write $K$ as $K = \beta_{\mathrm{m}_{\mathrm{c}}} K_\mathrm{m}\mathcal{L}^{\lambda -1}$.
-Therefore, this allows us to obtain the following simple expression for the value of the magnetisation parameter at the centre of the disc
-\begin{equation}
-\beta_{\mathrm{m}_{\mathrm{c}}} = \frac{1}{\lambda - 1}\,.
-\end{equation}
-It is relevant to note that the only reference to the explicit form of the metric is done to show that $\mathcal{L} \neq 0$ and $\partial r \mathcal{L} \neq 0$ inside the disc.
-This means that our result holds for any stationary and axisymmetric metric if the aforementioned inequalities hold.
-Moreover, the result is also true for any angular momentum distribution that allows for the existence of a cusp and a centre (and $r_{\mathrm{c}} \neq r_{\mathrm{cusp}}$).
 

### 2017-11-14 magnetised_polish_doughnuts_revisited/paper_accepted/arXiv_version/compile.py

@@ -1,0 +1,6 @@
+import os
+
+os.system("pdflatex paper_final.tex")
+os.system("bibtex paper_final")
+os.system("pdflatex paper_final.tex")
+os.system("pdflatex paper_final.tex")

### 2017-11-14 magnetised_polish_doughnuts_revisited/paper_accepted/compile.py

@@ -1,0 +1,6 @@
+import os
+
+os.system("pdflatex paper_accepted.tex")
+os.system("bibtex paper_accepted")
+os.system("pdflatex paper_accepted.tex")
+os.system("pdflatex paper_accepted.tex")

### 2017-11-14 magnetised_polish_doughnuts_revisited/paper_lang_rev/compile.py

@@ -1,0 +1,6 @@
+import os
+
+os.system("pdflatex to_send.tex")
+os.system("bibtex to_send")
+os.system("pdflatex to_send.tex")
+os.system("pdflatex to_send.tex")

### 2017-11-14 magnetised_polish_doughnuts_revisited/paper_revised/compile.py

@@ -1,0 +1,6 @@
+import os
+
+os.system("pdflatex paper_revised.tex")
+os.system("bibtex paper_revised")
+os.system("pdflatex paper_revised.tex")
+os.system("pdflatex paper_revised.tex")

### 2017-11-14 magnetised_polish_doughnuts_revisited/paper_revised_v2/compile.py

@@ -1,0 +1,6 @@
+import os
+
+os.system("pdflatex paper_revised_v2.tex")
+os.system("bibtex paper_revised_v2")
+os.system("pdflatex paper_revised_v2.tex")
+os.system("pdflatex paper_revised_v2.tex")

### 2017-11-28 kbhssh_disks/paper_prd.tex
PRD_version

--- 2017-11-14 kbhssh_disks/paper.tex
@@
-\documentclass{aa}  
-\usepackage{graphicx}
-\usepackage{txfonts}
-\usepackage{hyperref}
+%-----------------------------------------------------------------------
+%
+% filename = nube.tex
+%
+% First version: February 2012
+% Last revision: April 2012
+%
+%-----------------------------------------------------------------------
+
+\documentclass[aps, prl, amsmath, floats,floatfix, twocolumn, superscriptaddress, nofootinbib, 
+showpacs]{revtex4}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%   LOAD PACKAGES   %%%
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\usepackage{amssymb}
+\usepackage{amsmath}
+\usepackage{verbatim}
+\usepackage{mathrsfs}
+\usepackage{amsfonts}
+\usepackage{latexsym}
+\usepackage{epsfig}
 \usepackage{color}
-\usepackage{float}
+\usepackage{graphicx,subfigure}
+\usepackage{units}
+\usepackage{slashbox}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%   BEGIN DOCUMENT  %%%
+%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%
+%%%   MACROS   %%%
+%%%%%%%%%%%%%%%%%%
+
+\definecolor{orange}{rgb}{0.9,0.45,0}
+
+\renewcommand{\t}{\times}
+
+\long\def\symbolfootnote[#1]#2{\begingroup%
+\def\thefootnote{\fnsymbol{footnote}}\footnote[#1]{#2}\endgroup}
+
+%%%%%%%%%%%%%%%%%
+%%%   TITLE   %%%
+%%%%%%%%%%%%%%%%%
+
 \title{Magnetized accretion disks around Kerr black holes with scalar hair}
 
-%   \subtitle{}
+\author{Sergio Gimeno-Soler}
+\affiliation{Departamento de
+  Astronom\'{\i}a y Astrof\'{\i}sica, Universitat de Val\`encia,
+  Dr. Moliner 50, 46100, Burjassot (Val\`encia), Spain}
 
-\author{Sergio Gimeno-Soler\inst{1}, Jos\'e A.~Font\inst{1,2}, Carlos Herdeiro \inst{3}, Eugen Radu\inst{3}}
-\institute{Departamento de Astronom\'{\i}a y Astrof\'{\i}sica, Universitat de Val\`encia, Dr. Moliner 50, 46100, Burjassot (Val\`encia), Spain.\\\email{sergio.gimeno@uv.es}
-\and
-Observatori Astron\`omic, Universitat de Val\`encia, C/ Catedr\'atico Jos\'e Beltr\'an 2, 46980, Paterna (Val\`encia), Spain. \\
-\email{j.antonio.font@uv.es}
-\and
-Departamento de F\'isica da Universidade de Aveiro and Centre for Research and Development in Mathematics and Applications (CIDMA), Campus de Santiago, 3810-183 Aveiro, Portugal
+\author{Jos\'e A. Font}
+\affiliation{Departamento de
+  Astronom\'{\i}a y Astrof\'{\i}sica, Universitat de Val\`encia,
+  Dr. Moliner 50, 46100, Burjassot (Val\`encia), Spain}
+\affiliation{Observatori Astron\`omic, Universitat de Val\`encia, C/ Catedr\'atico 
+  Jos\'e Beltr\'an 2, 46980, Paterna (Val\`encia), Spain}
+
+\author{Carlos Herdeiro}
+\affiliation{Departamento de F\'{\i}sica da Universidade de Aveiro and CIDMA, Campus de Santiago, 
+3810-183 Aveiro, Portugal}
+
+\author{Eugen Radu}
+\affiliation{Departamento de F\'{\i}sica da Universidade de Aveiro and CIDMA, Campus de Santiago, 
+3810-183 Aveiro, Portugal}
+
+%%%%%%%%%%%%%%%%
+%%%   DATE   %%%
+%%%%%%%%%%%%%%%%
+
+\date{today}
+
+%%%%%%%%%%%%%%%%%%%%
+%%%   ABSTRACT   %%%
+%%%%%%%%%%%%%%%%%%%%
+
+\begin{abstract} 
+We present a method to build magnetized constant angular momentum disks around Kerr black holes with scalar hair (KBHsSH).
+\end{abstract}
+
+%%%%%%%%%%%%%%%%
+%%%   PACS   %%%
+%%%%%%%%%%%%%%%%
+
+\pacs{
+95.30.Sf, % relativity and gravitation
+04.70.Bw, 
+04.40.Nr, 
+04.25.dg
 }
 
-% \abstract{}{}{}{}{} 
-% 5 {} token are mandatory
-
-  \date{}
-
-  \abstract
-  {We present a method to build magnetized constant angular momentum disks around Kerr black holes with scalar hair (KBHsSH).}
-
-   \keywords{black hole physics
-               }
+%%%%%%%%%%%%%%%%%%%%%%
+%%%   MAKE TITLE   %%%
+%%%%%%%%%%%%%%%%%%%%%%
 
 \maketitle
-%
-%-------------------------------------------------------------------
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+%%%   INTRODUCTION   %%%
+%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-% Outline:
+\section{}
 
-% Brief description of the work of Herdeiro, recall what we use here and proceed to describe what we have done.
-% First, describe framework.
-Metric, energy-momentum tensor, and equations of motion.
-Second, angular momentum distribution (including the angular momentum at $r_{\mathrm{mb}}$) and EoS.
-Third, results: Higher potential well than any possible Kerr-like solution with $r_{\mathrm{in}} = r_{\mathrm{mb}}$.
-We should graph here the potential well $\Delta W$ vs.
-the normalized spin parameter $a$ for the KBH case.
-Maybe get the data for intermediate values of magnetization?
-I think it is important to have more data of HBH, to test some ideas.
-Comparison with naked singularities?
-I would like to obtain the rest-mass and gravitational mass of the total distribution (torus + scalar field).
+\section{Framework}
 
-% Comparison of the structure of the disks obtained for the case of KBHsSH with KBH and Naked Singularities (NS).
-$\Delta W$, angular velocity, angular momentum, mass of the torus and physical magnitudes (thermodynamical)
-
-% Paint same curves (if possible) as in the case of the previous paper for magnetized toris around KBHs, check differences between the cases. For KBHs with full-relativistic fluid and HBHs.
-
-% Check relations between ergoregions in KBHs and NSs spacetimes and KBHsSH case (morphology?)
-% The most important conclusion is we obtain very different disk configurations for HBHs and for KBHs (with the same ADM or Horizon quantities), therefore we can asymptotically distinguish a disk around a KBHsSH from a disk around a KBH.
-(potential well and so on).
-
-%--------------------------------------------------------------------
-\section{Framework}
+%%%%%%%%%%%%%%%%%%%%%
+%%%   RESULTS   %%%
+%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\bibliographystyle{bibtex/aa}
+\bibliographystyle{apsrev}
 \bibliography{references}

### 2017-11-29 kbhssh_disks/paper_prd.tex
bibliography fixed

@@
 
-\documentclass[aps, prl, amsmath, floats,floatfix, twocolumn, superscriptaddress, nofootinbib, 
-showpacs]{revtex4}
+\documentclass[twocolumn,aps,showpacs,showkeys,prd,superscriptaddress,byrevtex, amsmath]{revtex4-1}
 
@@
 \usepackage{slashbox}
+\usepackage{aas_macros}
 
@@
 
-We use the stationary and axisymmetric metric ansatz provided by\citet{Herdeiro:2014a}
+We use the stationary and axisymmetric metric ansatz provided by\cite{Herdeiro:2014a}
 
@@
 \subsection{Magnetized disks}
-We use the procedure described by~\citet{Montero:2007}, where we write the equations of ideal general relativistic MHD are the following conservation laws, $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and
+We use the procedure described by~\cite{Montero:2007}, where we write the equations of ideal general relativistic MHD are the following conservation laws, $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and
 $\nabla_{\mu} (\rho u^{\mu}) = 0$, 
@@
 
-It is relevant to note that we could have used the framework described by~\citet{Komissarov:2006}.
+It is relevant to note that we could have used the framework described by~\cite{Komissarov:2006}.
 As we will show in appendix~\ref{komissarov_appendix}, we do not take this approach because it is not appropriate for some cases of KBHsSH.
@@
 
-\bibliographystyle{apsrev}
-\bibliography{references}
+\bibliography{references.bib}
 
@@
 
-In the figures \ref{comparison_alt_mag_1}, \ref{comparison_alt_mag_2}, \ref{comparison_alt_mag_3}, \ref{comparison_alt_radial_1}, \ref{comparison_alt_radial_2}, \ref{comparison_alt_radial_3} we show the comparison between the results for KBHsSH using \citet{Montero:2007} and \citet{Komissarov:2006}.
+In the figures \ref{comparison_alt_mag_1}, \ref{comparison_alt_mag_2}, \ref{comparison_alt_mag_3}, \ref{comparison_alt_radial_1}, \ref{comparison_alt_radial_2}, \ref{comparison_alt_radial_3} we show the comparison between the results for KBHsSH using \cite{Montero:2007} and \cite{Komissarov:2006}.
 The figures show good agreement for the highly magnetized case ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$) but not quite for the non-magnetized and mildly magnetized cases, especially for the model III.
@@
 It is easy to note that for higher absolute values of $W_{\mathrm{c}}$ we get values of $h_{\mathrm{c}}$ further away from the case $h = 1$.
-This is interesting because these high values of $W_{\mathrm{c}}$ (particularly the one for the model III) is unattaniable for any KBH (as is shown by~\citet{Abramowicz:1978}, the maximum value of $W_{\mathrm{c}}$ for a KBH is $W_{\mathrm{c}} = 0.549$).
+This is interesting because these high values of $W_{\mathrm{c}}$ (particularly the one for the model III) is unattaniable for any KBH (as is shown by~\cite{Abramowicz:1978}, the maximum value of $W_{\mathrm{c}}$ for a KBH is $W_{\mathrm{c}} = 0.549$).
 
@@
 From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$).
-The left column correspond to the KBHsSH model using~\citet{Montero:2007} and the right column correspond to the~\citet{Komissarov:2006} approximation.}
+The left column correspond to the KBHsSH model using~\cite{Montero:2007} and the right column correspond to the~\cite{Komissarov:2006} approximation.}
 \label{comparison_alt_mag_1}
@@
 From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$).
-The left column correspond to the KBHsSH model using~\citet{Montero:2007} and the right column correspond to the~\citet{Komissarov:2006} approximation.}
+The left column correspond to the KBHsSH model using~\cite{Montero:2007} and the right column correspond to the~\cite{Komissarov:2006} approximation.}
 \label{comparison_alt_mag_2}
@@
 From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$).
-The left column correspond to the KBHsSH model using~\citet{Montero:2007} and the right column correspond to the~\citet{Komissarov:2006} approximation.}
+The left column correspond to the KBHsSH model using~\cite{Montero:2007} and the right column correspond to the~\cite{Komissarov:2006} approximation.}
 \label{comparison_alt_mag_3}
@@
 From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$).
-The left column correspond to the KBHsSH model using~\citet{Montero:2007} and the right column correspond to the~\citet{Komissarov:2006} approximation.}
+The left column correspond to the KBHsSH model using~\cite{Montero:2007} and the right column correspond to the~\cite{Komissarov:2006} approximation.}
 \label{comparison_alt_radial_1}
@@
 From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$).
-The left column correspond to the KBHsSH model using~\citet{Montero:2007} and the right column correspond to the~\citet{Komissarov:2006} approximation.}
+The left column correspond to the KBHsSH model using~\cite{Montero:2007} and the right column correspond to the~\cite{Komissarov:2006} approximation.}
 \label{comparison_alt_radial_2}
@@
 From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$).
-The left column correspond to the KBHsSH model using~\citet{Montero:2007} and the right column correspond to the~\citet{Komissarov:2006} approximation.}
+The left column correspond to the KBHsSH model using~\cite{Montero:2007} and the right column correspond to the~\cite{Komissarov:2006} approximation.}
 \label{comparison_alt_radial_3}
